### 2014-11-24 draft3.tex
From this point I am going to use version control on it

\documentclass[useAMS,usenatbib]{mn2e}
%\usepackage{geometry}[left=1.5in, right=1in, bottom=1in, top=1in]
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{natbib}
\bibliographystyle{aas}
\usepackage{amsmath}
\usepackage{times}
\usepackage{float}

\newcommand \kpc	{\,{\rm kpc}}
\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }}$}
\newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }}$}
\newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }}$}
\newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
\newcommand \halpha    {H$\alpha$ \ }
\newcommand \um    {$\mu$m \ }
\newcommand \mice {$\mu$m}
\newcommand \nprime {N$^\prime$}
\newcommand \eqnprime {N^\prime}

\begin{document}
% TITLE
\title[WHICH STAR FORMATION LAW IN M31]{RELATION BETWEEN STAR FORMATION RATE, GAS MASS AND STELLAR MASS IN THE ANDROMEDA GALAXY}
\author[S. Rahmani $\&$ P. Barmby]{S.~Rahmani, P.~Barmby\\
Department of Physics $\&$ Astronomy, University of Western Ontario, London, ON N6A 3K7, Canada}
\maketitle

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\begin{abstract} % it is just my GESF2014 abstract, just for looks I will change it at the end
 We investigate the relation between star formation rate (SFR), gas surface density (\sigmagas) and stellar surface density (\sigmastar) in the Andromeda galaxy (M31) using the Kennicutt-Schmidt (K-S) law and the extended Schmidt law. Shi et al. argued that the surface density of SFR is related not only to gas mass, as in the empirical K-S law,  but also to stellar mass surface density, in the ``extended Schmidt law''. Using all a combination of \halpha and 24 \um emission, a combination of FUV and 24 \um, and the total infrared emission, we estimate the total SFR in M31 to be between 0.35 M$_{\odot}$yr$^{-1}$ - 0.4 M$_{\odot}$yr$^{-1}$. We use maps of $^{12}$CO and 21cm emission to produce the \sigmagas map.% For regions that are not covered in the $^{12}$CO map, we used the dust map (obtained from $SPIRE$ data) as a tracer of total gas. 
 The stellar mass surface density  map is calculated using mid-infrared IRAC imaging. Our preliminary results from testing the K-S law in M31 find a power-law index of  $N = 0.62 \pm 0.01$, at the low end of values compared with previous work. We determine additional K-S law fits using each SFR map independently with molecular hydrogen, atomic hydrogen and total gas maps. We then repeat the analysis considering the stellar mass density in order to test whether the regular or extended Schmidt laws are more appropriate for M31.

\end{abstract}
\begin{keywords}
Galaxies: Andromeda, Star Formation
\end{keywords}
%----------------------------------------------------------------------------------------
%INTRODUCTION
%----------------------------------------------------------------------------------------

\section{Introduction}
\label{sec:intro} %I can add a lot more about calculating star formation and in general why star formation is important but I don't like make my introduction too long. 
%P1: Star formation laws and why they are important (introducing K-S law and E-S law)

Empirical star formation laws, relations, has been investigated for more than 50 years, and results never been precise. Formation of stars is a complicated process. Various phenomena affect the collapse of molecular clouds and star formation which include the environment of the star-forming region, chemical compositions, the initial mass distribution of gas, gas accretion and cooling, H$_2$ formation, etc.

The first idea about scaling the star formation rate on the galaxy scale was proposed as a connection between the total star formation rate and the mass of interstellar gas. \cite{Schmidt59} assumed the constant initial mass function (IMF) of stars, $\Psi (M)$, a stellar lifetime function {$T(M$)}, and a star formation rate {$SFR(T)$} and derived the star formation rate (SFR) over the history of the Milky Way. He scaled SFR with a power {\it n} of the gas mass. $M_{gas}$. %Then $SFR(T)\Sigma_{M}(M) = c[M_{gas}(t)]^n$, for a summation over all stellar type $M$.
A decade later, \cite{Kennicutt98a} examined another group of galaxies. He used \halpha, HI and CO observations of 61 normal spiral galaxies and 36 starburst galaxies and showed that the disk-average SFRs and gas densities for this samples are well represented by the Schmidt law with the power of $1.4 \pm 0.15$. Using this power index, the Schmidt law can be rewritten as:

\begin{equation}
\eqsigmasfr \propto \eqsigmagas^{1.4\pm0.15}
\end{equation}
which is often referred to as the Kennicutt-Schmidt (K-S) law, where \sigmasfr is surface density of star formation, \sigmagas is the surface density of gas in a galaxy and, {\it n} is the power index.

In more recent studies, \cite{Kennicutt08} investigated the local star formation law in M51 with 0.5-2 kpc resolution. For the SFR he used pa${\alpha}$ and $24\mu$m + H${\alpha}$ lines and for gas density he used constant conversion factor for CO to H$_2$. He found a correlation, from the radial variation of both SFR and gas surface density, with an index of $1.56 \pm 0.04$.
%He could not find any correlation between SFR and HI only clouds, but the correlation with the molecular cloud was about the same as the total gas.
It should be noted that the KS law can not be applied for the whole range of gas densities. In parallel studies, the star formation threshold was introduced and it was pointed out that calculated SFR is much lower than the value predicted by the KS law at low gas densities $( < 1-10\sim$ M$_{\odot}$ pc$^{-2})$ e.g. in regions far outside the optical disk \citep[e.g.,][]{Martin01, Bigiel08}.

\cite{Hunter98} have shown that, in low surface brightness galaxies the SFR density is only related to the stellar mass density. Also similar relations between stellar masses and SFR densities are seen within galaxies by \cite{Ryder94}, \cite{Hunter04} and recently by \cite{Leroy08} for specific galaxy types or limited density ranges. \cite{Shi11} found a tight relationship between stellar mass surface density, SFR and gas surface density by studying on a large sample of galaxies. They showed this relation as a power law relation and referred to it as the extended Schmidt law:

\begin{equation}
\eqsigmasfr \propto \eqsigmagas^{\eqnprime} \eqsigmastar^{\beta}
\end{equation}
where \sigmasfr is SFR surface density, \sigmagas and \sigmastar are gas mass and stellar surface density. \nprime and $\beta$ are the power law indexes. Testing new relation on 60 galaxies \nprime and $\beta$ were calculated to be $\sim$ 1.4 and $\sim$ 0.6 respectively. They showed that this relation not only predicts SFR as well as the KS law for galaxies and spatially resolved regions ($\sim$1 kpc sizes) where the KS law works, but also is acceptable for low surface brightness galaxies and regions where the KS law fails.

%P2: SFR, measuring, scaling, ...
For testing any of these star formation laws, first thing one should do is calculating the SFR. Many groups are working to find a translation from the light of star forming regions in galaxies to a rate of the formation of new stars. \cite{Kennicutt98b} calibrated luminosity of galaxies as a way of measuring the SFR in specific wavelengths using relations between the SFR per unit mass or per unit luminosity and the integrated colour of the system provided by synthesis models  \citep[e.g.,][]{Bruzual93}. Afterward many other studies tried to find the similar calibration for measuring the SFR of galaxies in other bands \citep[e.g.,][]{Kennicutt12, Calzetti12, Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}. \cite{Kennicutt09} and \cite{Hao11} introduced new SFR calibration using a combination of \halpha or FUV and far infrared (FIR) emission, respectively. In addition of using suitable calibrations for each region, considering differences between global case and local ($\sim 0.5-1$ kpc) case is important. In section 3, we are talking about the SFR in the Andromeda galaxy and how we did measure it.

%P3: Gas cloud, variety, observing etc
Calculating surface density of gas in galaxies is the other most important ingredients of testing star formation laws. Considering the effect of the interstellar medium (ISM) on studying the star formation law is important due to the fact that stars are born from the gas also release their material into the ISM when they reach the end of their evolution. A map of the total gas in the ISM is produced by direct observations of the gas or using interstellar dust as a tracer. Neutral and molecular hydrogen are the most common elements in the ISM. Therefore, for producing the map of the total gas in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He. Another way to do the mapping is assuming that the ratio of total gas and dust is constant across a galaxy, and convert dust observations to the map of total gas. Section 4 is about the calculation of the gas surface density for the Andromeda galaxy.

%P4: Stellar mass and how to measure it
Additionally, for testing the Extended Schmidt law, measuring the stellar mass density is necessary. Measuring the mass of the stellar population is indirect and subject to significant uncertainties. In principle there are two ways to measure stellar mass in galaxies. First is measuring the dynamical mass of galaxies using kinematics \citep{Cappellari06} or lensing \citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass. This method has been successful to predict and subtract the mass of the dark matter, which is the dominant mass in galaxies \citep{Zaritsky94},  and can easily cause uncertainties as high as the order of the measurement.

The second method is based on stellar population models \citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, like luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations. Having two independent methods to measure stellar mass helps to compare the results and check whether there are any systematic differences. Comparing the results from measuring stellar mass in stellar clusters shows there is no huge difference. Comparing the results from measuring stellar mass within galaxies shows that the deferences are on the order of a few x10 percent, so one should be more careful to model subtleties \citep{McLaughlin05}. Calculating stellar mass in the Andromeda galaxy is described in section 5.

%P5(2*): What we did and why Andromeda and
In this project we test and compare both the K-S law and the extended Schmidt law on the Andromeda galaxy (M31). M31 is the closest spiral galaxy to the Milky Way, therefore, we can have higher resolution images of it than we have of any other spiral galaxy. Having high resolution images provides us data from different regions within
the galaxy with different physical situations (e.g. metallicity, surface brightness and etc.). All these parameters make the Andromeda a suitable test bed for studying the scaling law.
Furthermore, the range of the power index of K-S law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10,Ford13}. Therefore, testing extended Schmidt law on the Andromeda galaxy would help to solve the problem with these controversial results.

%----------------------------------------------------------------------------------------
%DATA
%----------------------------------------------------------------------------------------
\section{Data}
\label{sec:data}
Since the M31 is really close to us, it was aimed by many probes and telescopes, both space based and ground based ones. This advantage, provides us variety of data from X-ray to radio wavelengths. This wide ranges of data gives us the ability to measure all the required parameters to test the star formation laws in M31. Table~\ref{table:data} lists all the data we used in this paper. Each data comes with different Full Width Half Maximum (FWHM), spacial resolution and grids. In order to make sure that all our data contains the same amount of information, we smooth them using Aniano's Kernels' library and convolution code \citep{Aniano12}, to highest resolution available. Also considering Nyquist relation \citep{Nyquist}, we re-sample and re-grid all our maps to have a proper pixel size.

\subsection{Ultra Violet (UV) emission}
\subsection{Visible light}
\subsection{IR Data}
\subsection{Radio Data}

\end{document}

### 2015-01-28 draft3.tex
Update draft3.tex

@@
 \newcommand \kpc        {\,{\rm kpc}}
-\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }}$}
+\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }}$\ }
 \newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
-\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }}$}
+\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }}$\ }
 \newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
-\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }}$}
+\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }}$\ }
 \newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
-\newcommand \halpha    {H$\alpha$ \ }
-\newcommand \um    {$\mu$m \ }
+\newcommand \halpha    {H$\alpha $\ }
+\newcommand \um    {$\mu$m\ }
 \newcommand \mice {$\mu$m}
@@
 \newcommand \eqnprime {N^\prime}
-
+\newcommand \Spitzer {$Spitzer$}
+\newcommand \Galex {$GALEX$}
+\newcommand \Herschel {$Herschel$}
 \begin{document}
@@
 %P1: Star formation laws and why they are important (introducing K-S law and E-S law)
+%PB: agreed with not making it too long, but do start with a sentence about why SF is important.
 
@@
 
+%PB: shorten or leave out dynamical mass, since you don't discuss it further
 %P4: Stellar mass and how to measure it
@@
 the galaxy with different physical situations (e.g. metallicity, surface brightness and etc.). All these parameters make the Andromeda a suitable test bed for studying the scaling law.
+%PB: Give a little more detail in the followin sentence
 Furthermore, the range of the power index of K-S law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10,Ford13}.
@@
 \label{sec:data}
-Since the M31 is really close to us, it was aimed by many probes and telescopes, both space based and ground based ones.
+Since the M31 is the closest spiral galaxy to MW, it was aimed by many probes and telescopes, both space based and ground based ones.
 This advantage, provides us variety of data from X-ray to radio wavelengths.
@@
 
+\begin{table}
+\caption{Data used in this study.}
+\label{table:data}
+\begin{tabular}{@{}lccc}
+\hline\hline
+Wavelength & FWHM & Telescope
+& Ref. \\
+\hline
+%500 \um & 36\arcsec & $Herschel$ & \cite{Fritz12} \\
+%350 \um & 24\arcsec.5 & $Herschel$ & \cite{Fritz12} \\
+%250 \um & 18\arcsec.2 & $Herschel$ & \cite{Fritz12} \\
+2250 \AA & 6\arcsec & $GALEX$ & \cite{Martin05}\\ %:PB: GALEX, KPNO, IRAM should not be in $$
+1550 \AA & 4\arcsec.5 & $GALEX$ & \cite{Martin05}\\ %PB (they are abbreviations)
+6570 \AA  & 1\arcsec & $KPNO$& \cite{Massey07}\\
+3.6 \um & 1\arcsec.7 & $Spitzer$ & \cite{Barmby06} \\ %PB: write {\it Spitzer}, {\it Herschel}
+4.5 \um & 1\arcsec.7 & $Spitzer$ & \cite{Barmby06} \\ %PB because those are both missions and names
+8 \um & 1\arcsec.9 & $Spitzer$ & \cite{Barmby06} \\ % PB: of people - italics means the mission, not
+24 \um & 6\arcsec & $Spitzer$ & \cite{Gordon06} \\ %PB: the person
+70 \um & 18\arcsec & $Spitzer$ & \cite{Gordon06} \\
+160 \um & 12\arcsec & $Herschel$ & \cite{Fritz12} \\
+2.6 mm & 23\arcsec & $IRAM$ 30-m & \cite{Nieten06}\\
+21 cm & 60\arcsec \times \ 90\arcsec & $DRAO$ & \cite{Chemin09}\\
+\hline
+\end{tabular}
+\end{table}
+
+%PB: in general it's good to write number~unit, ie 2750~\AA 
+%PB: this means that number and unit don't end up on separate lines
 \subsection{Ultra Violet (UV) emission}
+
+One of the calibrations we used to calculate SFR uses FUV emission as a tracer of the star forming regions.
+FUV emission of M31 was observed by Galaxy Evolution Explorer ($GALEX$; \citep{Martin05}).
+$GALEX$ telescope data contains information for two bands, FUV:1350-1750 and NUV:1750-2750~\AA, with FWHM of 4\arcsec .5, and 6 \arcsec.
+
 \subsection{Visible light}
-\subsection{IR Data}
-\subsection{Radio Data}
+Our other method to calculate the SFR was using a combination of \halpha emission and 24\um emission.
+\cite{Massey06, Massey07} mapped UBVRI and \halpha emission line of M31 as part of the Nearby Galaxies Survey using KPNO telescope.
+\halpha maps, which were obtained from NOAO science archive are available in 10 overlapping fields.
+Mosaic image of the maps were created using Montage \citep{Montage}.
+Assuming that all stars have the same fraction of \halpha light in their spectra, we subtracted the R band emission from the \halpha using averaged scaling factor between R band images and \halpha provided by \cite{Azimlu11}.
+We also took masked map of stars from \cite{Azimlu11} and masked all point sources (Figure~\ref{fig:halpha}).
+Details of making the making \halpha map can be find in the Appendix ~\ref{appendix: halpha}.
+
+\subsection{IR and sub mm Data}
+In IR and sub mm bands both $Spitzer$ \citep{Wener04} and $Herschel$ \citep{Pilbratt10}  space telescopes observed the M31.
+The Infrared Array Camera (IRAC; \citep{Fazio04}) on the $Spitzer$ is a camera observing at four channels (3.6, 4.5, 5.8, and 8 \um).
+IRAC observation of M31 were obtained by \cite{Barmby06}, which covered $3\degr.7 \times 1\degr.6$.
+IRAC 3.6 and 4.5\um bands  were used to calculate the stellar mass.
+Multiband Imaging Photometer for Spitzer (MIPS) observed the  M31 at 24, 60, and 160\um and covered region $\sim 1\degr \times 3\degr$ \citep{Gordon06}.
+
+Calculation of the SFR using TIR emission needs maps of the m31 in 8, 24, 70, and 160 \um.
+IRAC 8, MIPS 24, MIPS 70 bands were used to calculate TIR emission, but due to better quality and resolution of $Herschel$s$'$data, PACS (Photodetector Array Camera and Spectrometer) \citep{Poglitch10} were used.
+PACS 160\um observation of the Andromeda galaxy alongside of PACS 100 \um band and three (250 \um, 350\um and 500 \um) SPIRE (Spectral and photometric Imaging Receiver) \citep{Griffin10} bands are covered $\sim 5\degr.5 \times 2\degr.5$ regions \citep{Fritz12}.
+
+\subsection{Radio Emission}
+Emission from $^{12}$CO(J:$1\rightarrow0$) line which, was observed on-the-fly with the IRAM 30-m telescope\citep{Nieten06} was used to calculate the H$_2$ column density of interstellar medium.
+This map coveres $2\degr \times 0\degr.5$ that has best resolution available (FWHM = $23\arcsec$) but smallest coverage of halo of the galaxy among our maps.
+In this project we used data of the 21 cm emission from the atomic gas (HI) in the M31 from \cite{chemin9}.
+They used Synthesis telescope and the 26 m antenna at the Dominion Radio Astrophysical Observatory to map HI emission in 21cm band of the M31.
+
+\begin{figure*}
+ {\vfil  \includegraphics[width=164mm]{halpha_copy.eps}
+  \caption{Mosaic created using Montage programme from 6 fields of \halpha emission maps of m31 from \citpe{Massey07}.
+Result from Montage was continuum subtracted and masked out all point sources.
+Centre of galaxy was masked out due to saturation of data in R-band image.\label{fig:halpha}}
+ \vfil}
+\end{figure*}
+
+%----------------------------------------------------------------------------------------
+%STAR FORMATION RATE
+%----------------------------------------------------------------------------------------
+%----------------------------------------------------------------------------------------
+\section{Star Formation Rate}
+\subsection{FUV plus 24\um Star Formation Rate}
+
+In this project first star formation map is produced using a calibration of a combination of the FUV emission and 24\um emission introduced by \cite{Hao11}.
+Since peak of the emission of massive and young stars (O - B and A type) are in the UV, this wavelength is one of the most common used star formation rate indicators \citep[e.g.,][]{Kennicutt89}.
+The UV indicates star forming region with age of $\sim 100$ Myr \citep[e.g.,][]{Kennicutt98, Calzetti05}.
+However, downside of only using the FUV light as a tracer of star forming region is that this emission is really sensitive to dust extinction.
+On the other hand 24\um emission is dominated by emission from dust heated by UV photons from young and hot stars.
+This emission is sensitive to star formation time scale of $\la10$ Myr \citep{Calzetti07}.
+The FUV band of \Galex and the 24\um band of \Spitzer data was used to measure the SFR calibrated by \cite{Hao11} as follow:
+\begin{equation}
+\label{equ: fuvplus24}
+SFR =4.46\times10^{-44}[L(FUV)_{obs}+3.89L(24\mu m)]
+\end{equation}
+where unit of SFR is M$_{\odot}$yr$^{-1}$, and L(24$\mu$m) is in erg/s.
+$L(FUV)_{obs}$ is the luminosity of galaxy in the FUV emission.
+The index of obs is shown to indicate that the FUV emission is not corrected for effect of extinction.
+Nevertheless, this emission is corrected for the foreground stars emission.
+To do so, we followed a method introduced by \cite{Leroy08}.
+We assumed for any pixel, in maps with pixel size the same as the pixel size of NUV map, if I$_{NUV}$/I$_{FUV}$ $>$ 15 that pixel value is dominated by foreground emission and masked them out.
+We also masked the same region in the galaxy for 24\um map.
+
+%----------------------------------------------------------------------------------------
+\subsection{\halpha plus 24\um Star Formation Rate}
+\label{sec:sfr_halpha}
+
+The SFR can be calculated using combination of \halpha and $Spitzer$ 24\um maps.
+\halpha emission of galaxies is dominated by light emitted from young and massive stars.
+Star formation time scaled traced by this emission is $\sim 6-10$ Myr \citep[e.g.,][]{Kennicutt09, Calzetti12}.
+Therefore \halpha alone could be used to calibrate the SFR \citep[e.g.,][]{Osterbrock06, Kennicutt09}.
+However, \halpha emission is very sensitive to dust extinction,too.
+Therefore, combination of the \halpha and 24\um of is considerable choice for calculating the SFR.
+we used calibration introduced by \cite{Kennicutt09} to measure the SFR:
+\begin{equation}
+\label{equ: halphaplus24_g}
+SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.020L(24\mu m)]
+\end{equation}
+where L(H${\alpha}$)$_{obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the unit of erg/s.
+L(24$\mu$ m) is the $24\mu$m IR luminosity in erg/s, and SFR is in M$_{\odot}$yr$^{-1}$.
+It was indicated that the formulation above can only be used at global situation (i.e.
+total SFR).
+
+\cite{Calzetti07} introduced a new calibration using the same bands in case of local regions (figure ~\ref{fig:sfr_halpha}):
+\begin{equation}
+\label{equ: halphaplus24_l}
+SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.033L(24\mu m)]
+\end{equation}
+units here are the same as equation~\ref{equ: halphaplus24_g}.
+Equation~\ref{equ: halphaplus24_l} is useful for regions less than $\sim 1$ kpc.
+According to  \cite{Calzetti07} calibration constant in equations ~\ref{equ: halphaplus24_g} and ~\ref{equ: halphaplus24_l} can be different by changing an IMF.
+Changes in the IMF mostly affect on calibration based on \halpha luminocity, mostly because significant amount of the ionising photons comes from the stars more massive than $\sim 20$M$\sun$.
+Changing the calibration constant would change the total SFR by a factor of 1.5.
+In this paper we used \cite{Kroupa01} IMF with upper mass limit of 100M$\sun$.
+Total SFR calculated from equation~\ref{equ: halphaplus24_g} is 0.35 M$\sun$yr$^{-1}$, which is in good agreement with previous studies.
+%PB: can you put uncertainties on the total SFR numbers?
+
+\subsection{Total Infrared Star Formation Rate}
+\label{sec:sfr_fir}
+Total infrared emission of a system, can also be used as a tracer of the SFR.
+Dust absorbs radiation from hot and young stars and re-emitt it in infrared wavelength, however there is no one-to-one mapping between IR and UV emission \citep{Calzeti12}, therefore, integrating over full wavelength range of the IR part and calculating the TIR luminosity is better tracer of the SFR instead of the IR single-band emission.
+\cite{Calzetti07} assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{star}(bol) = L(TIR)$ and calibrated the TIR luminosity of a system to calculate the SFR for a stellar population undergoing constant star formation over $\tau = 100$ Myr:
+
+\begin{equation}
+\label{equ:sfr_fir}
+SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR)
+\end{equation}
+where SFR(TIR) and L(TIR), star formation rate calculated from TIR emission and TIR luminosity are in M$_{\odot}$yr$^{-1}$ and erg/s respectively.
+
+%PB: I like this figure! Looks nice.
+\begin{figure*}
+        \centering
+        \begin{subfigure}\\(a){}
+                \includegraphics[width=164mm]{sfr_fuv.eps}
+                %\caption{A gull}
+
+               \label{fig:sfr_halpha}
+        \end{subfigure}
+        \begin{subfigure}\\(b){}
+                \includegraphics[width=164mm]{sfr_halpha.eps}
+                %\caption{A gull}
+
+               \label{fig:sfr_halpha}
+        \end{subfigure}
+       % \quad
+        %add desired spacing between images, e. g. ~, \quad, \qquad etc.
+          %(or a blank line to force the subfigure onto a new line)
+        \begin{subfigure}\\(c){}
+                \includegraphics[width=164mm]{sfr_fir.eps}
+                %\caption{A tiger}
+
+                \label{fig:sfr_fir_small}
+        \end{subfigure}
+         \quad
+               \caption{SFR map from a combination of \halpha and 24\um emission (top) and total infrared emission (bottom)}
+\label{ISOnIRS}
+\end{figure*}
+
+IR luminosity can be measured from integration of IR part of a spectral energy distribution (SED) of a galaxy or combining photometry datas in different IR wavelengths.
+For second approach \cite{Draine07} modelled $Spitzer$ data and calibrated IR single-band photometry data to calculate the TIR luminosity.
+\cite{Boquien10} tested and modified this calibration as:
+\begin{equation}
+ \label{equ: TIR}
+L(\rm TIR) = 0.95L(8) + 1.15L(24) + L(70) + L(160)
+\end{equation}
+where L(8 \um),L(24 \um), L(70 \um) and L(160\um) are luminosities of galaxy in 8 \um, 24 \um, 70 \um and 160 \um in unit of erg/s.
+We used equation ~\ref{equ:sfr_fir} to calculate second map of SFR of M31 (figure ~\ref{fig:sfr_fir_small}).
+Using this method we calculated the total SFR 0.40 M$_{\odot}$yr$^{-1}$.
+Table ~\ref{table:sfr} compares total SFR from literature and current work.
+
+\begin{table*}
+\begin{minipage}{100mm}
+\caption{Comparison of Total Star Formation Rate of M31}
+\label{table:sfr}
+\begin{tabular}{@{}lcc}
+\hline\hline
+Ref.&Method&SFR(M$_{\odot}$yr$^{-1}$) \\
+\hline
+Current work&FUV and 24\um&0.31\\
+Current work&\halpha and 24\um&0.35\\
+Current work&TIR luminosity&0.4\\
+\cite{Ford13}&FUV and 24\um&0.25\\
+\cite{Ford13}&TIR luminosity&0.48-0.52\\
+\cite{Azimlu11}& \halpha and 24\um&0.34\\
+\cite{Azimlu11}&Extinction corrected \halpha&0.44\\
+\cite{Tabatabaei10}&Extinction corrected \halpha&0.27-0.38\\
+\cite{Barmby06}&Infrared 8\um luminosity& 0.4\\
+\hline
+\end{tabular}
+\end{minipage}
+\end{table*}
+
+%----------------------------------------------------------------------------------------
+%ISM
+%----------------------------------------------------------------------------------------
+\section{Interstellar Medium}
+%----------------------------------------------------------------------------------------
+%Direct Measurement of the Gas Mass
+%----------------------------------------------------------------------------------------
+%\subsubsection{Direct Measurement of the Gas Mass}
+
+The surface density of gas in the ISM of galaxies can be measured by direct observation of the neutral and molecular hydrogen.
+This method can be promising provided that the spatial resolution of observational data is high enough; nonetheless, due to technical limitations, attaining enough spatial resolutions to resolve clouds is almost impossible.
+This problem shows itself for distant galaxies more than nearby galaxies.
+As a result, using this method is limited and has a lot of uncertainties.
+
+%\subsubsection*{Molecular Clouds}
+%PB: these two paragraphs contain a lot of background information that could either be moved to the
+%PB introduction or be omitted; this info doesn't belong here.
+ The molecular form of hydrogen in the ISM has no permanent electric dipole moment, which makes it really hard to detect.
+H$_2$ molecules are located in cool and dense molecular clouds, but fortunately they are not the only component of the molecular gas.
+The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but the molecular gas also contains heavier elements such as carbon and oxygen which are combined to form CO \citep{Bolato13}.
+
+CO has a weak permanent electric dipole moment and a ground rotational transition with low excitation energy.
+Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
+Hence CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen \citep[see, for example,][] {Sanders84}.
+Higher rotational transition of CO can be used as a tracer as well, but they are not as common as the $J(1\rightarrow 0)$.
+The relation between CO emission and H$_2$ cloud mass is shown as
+
+\begin{equation}
+\label{equ:conversion}
+\rm N_{H_2}/\rm cm^{-2} = X_{CO} \times I_{CO}/\rm K km s^{-1}
+\end{equation}
+where X$_{CO}$ is the conversion factor (also known as the X-factor).
+X-factor could be different in regions within a galaxy due to difference in metallicity.
+Though assuming constant conversion factor for cases such as M82 and M31 can lead to global molecular gas mass estimates that are very accurate,  but in regions with low metallicity there are uncertainties.
+Different groups are working on the various galaxies to measure the X-factor for each \citep{Wilson95, Bosselli02, Bolato13}..
+In case of M31, different values of X-factor ($1-5.6 \times 10^{20}$) were adopted in the previous studies \citep[e.g.][]{Ford13, Bolato13, Leroy11, Bolato08, Nieten06, Sofue94, Strong88}; however, since any constant differences in X-factor leads to horizontal changes in a plot of log(SFR) versus Log($\Sigma_{\rm {gas}}$), and does not affect our K-S law power index for molecular gas,  we chose $X_{\rm {CO}}= 2 \times 10^{20}$  the same as many other works \citep[e.g.][]{Ford13, Smith12}.
+This assumption might have some effect on the total gas mass but considering the fact that HI mass dominates H$_2$ mass in M31 this effect is small.
+The total gas mass was calculated from:
+\begin{equation}
+\label{equ:total_gas}
+\rm M_{\rm \bld {total \, gas}} = 1.36[M_{HI}+M_{H_2}]
+\end{equation}
+where  factor of 1.36 is a constant to consider He and the other heavier elements effect on mass, M$_{HI}$ is mass of neutral hydrogen obtained from 21cm observations and M$_{H_2}$ is from equation ~\ref{equ:conversion} in unit of M$\sun$.
+%----------------------------------------------------------------------------------------
+% Dust Emission as a Tracer of Gas
+%----------------------------------------------------------------------------------------
+
+%\subsubsection{Dust Emission as a Tracer of Gas}
+%A gas map of a galaxy can be produced using the dust mass and assuming the dust mass to gas mass ratio across the galaxy \citep{Hildebran83}.
+This method is the most convenient in order to measure gas mass in distant galaxies, which studying the gas cloud in their ISM by using direct methods is almost impossible and not practical.
+In M31, for regions which are not covered in CO map we used a dust map obtained \cite{Drain14}.
+They also showed that dust/gas mass ratio from radius 0-25Kpc as follow:
+
+%\begin{equation}
+%\label{eq:dust2gas_vs_R}
+%\frac{M_d}{M_H} \approx
+%\left\{ \begin{array}{l l}
+%0.0280 \exp(-R/8.4\kpc)  & R< 8\kpc\\
+%0.0165 \exp(-R/19\kpc)   & 8\kpc < R < 18\kpc\\
+%0.0605 \exp(-R/8\kpc)    & 18\kpc < R \la 25\kpc ~~~,\\
+%\end{array}
+%\right.
+%\end{equation}
+
+%There are many disadvantages regarding the use of the gas to dust ratio in the ISM.
+In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived.
+\cite{Draine03} pointed out that this approach is uncertain because of the uncertainly in the radiative efficiency of dust grains.
+Also methods of measuring the gas to dust ratio in galaxies are not accurate, which means that there are problems in both steps \citep{Hildebran83}.
+ %Certainly the gas to dust ratio as a tracer of the total gas in galaxies has a number of problems.
+Unfortunately, at present, given the available data, we cannot measure the gas mass trough whole galaxy directly.
+Therefore, so far this method is the best available solution for measuring the total gas in regions further out of the disk of galaxy.
+
+%----------------------------------------------------------------------------------------
+%STELLAR MASS
+%----------------------------------------------------------------------------------------
+\section{Stellar Mass}
+\label{starmass}
+Stellar mass can be measured using a suitable calibration between flux/luminosity of stars in specific wavelengths and stellar mass.
+The basic idea behind these kind of calibrations comes from the fact that one can use the star formation histories recovered from synthesizing the stellar optical colour magnitudes in different regions in the galaxies.
+The calculated stellar mass can be used  to calibrate the fluxes from the stars as the easily measurable parameters of stars.
+Using NIR bands, different groups tried to make a map of stellar mass distributions within galaxies \citep[e.g.,][]{Elmgreen84}.
+Using $B-V$ colours \citep{Bell01} and $Spitzer$ 3.6- and 4.5-\um, M/L correction, \cite{Kendall08} produced stellar mass surface densities of M81.
+%PB: do you mean M81 here?
+If so, it's not quite clear why you're mentioning a different galaxy.
+
+We calculated the stellar mass work using calibration of the 3.6\um fluxes by \cite{Eskew12}.
+They used 3.6\um fluxes for calibration of the stellar mass, because this band-pass is almost insensitive to the emission from young stellar population, dust absorption and emission.
+By using data from the large Magellanic cloud, they find an empirical relation between stellar mass and luminosity of stars as following:
+
+\begin{equation}
+\label{equ:eskew}
+M _{\star}= 10^{5.97} F_{3.6}(\frac{D}{0.05})^2
+\end{equation}
+
+where M$_{\star}$ is the stellar mass in mass of The Sun, $F_{3.6}]$ is the 3.6\um flux in $Jy$ , and D in the distance of the galaxy in Mpc.
+Figure ~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6\um.
+\begin{figure*}
+\centering
+\includegraphics[width=164mm]{star.eps}
+\caption{Stellar Mass surface density. This mass is produced using $IRAC$ 3.6 $\mu$ m data and equation ~\ref{equ:eskew}}
+\label{fig:stellarmass}
+\end{figure*}
+
+Using this method we calculated the total stellar mass of galaxy is $6.9 \times 10^{10}$ with 6$\%$ uncertainty. %PB: need to compare with other results, as you did with SFR.
+%----------------------------------------------------------------------------------------
+%SFR LAWS
+%----------------------------------------------------------------------------------------
+\section{Scaling SFR}
+\subsection{Fitting method}
+%For investigating and comparing the SFR laws in M31
+Given available SFR, gas mass and stellar mass map examination and comparison of K-S law and the extended Schmidt law are possible.
+We investigated the K-S law and the extended Schmidt law by using  pixel by pixel method in whole galaxy as well as comparing the laws in three different regions of galaxy based on their distance from the centre of the galaxy.
+Knowing that, we can re-write these two star formation laws in a logarithmic scale we would have two linear equations:
+
+\begin{figure*}
+\centering
+\includegraphics{ks_tot_compt.png}
+\caption{The result from fitting the Kennicutt-Schmidt law on data from whole galaxy using pixel by pixel method.
+Pixel size on each plots are different.
+} %PB: somewhere in this section need to mention the
+%PB: different pixel sizes and the reason for them.
+\label{fig:ks,tot}
+\end{figure*}
+
+\begin{subequations}
+\begin{align}
+\label{eq:sfr_law_log}
+\log_{10} \eqsigmasfr = N~\log_{10} \eqsigmagas + A, \\
+\log_{10} \eqsigmasfr = \eqnprime~\log_{10} \eqsigmagas + \beta~\log_{10}\eqsigmastar  + A,\\
+\end{align}
+\end{subequations}
+units are the same as the units in the K-S law and the extended Schmidt law.
+
+we find the fitting parameters by applying the hierarchical Bayesian linear regression method as described in \cite{Shetty13} paper.
+Shetty and his team used a Bayesian linear regression approached to develop a new method to find the K-S law parameters, considering the measurements uncertainties as well as hierarchical data structure.
+For K-S law fitting parameters, we used a 'R' code provided by Shetty's group.
+Uncertainties on each observable quantity was measured considering the background noise photometry errors and calibration uncertainties.%PB: are the background noise errors and calib uncertainties discussed elsewhere in this paper (in which case reference the section) or do they need to be discussed here.
+
+For the extended Schmidt law, we expended the code from using simple linear regression which is the case of K-S law to use multiple linear regression.
+In this case we could examine the effect of the stellar mass in the SFR as shown in equation ~\ref{eq:sfr_law_log}.
+
+We also test each law on three different regions.
+The regions were chosen the same as regions introduced in \cite{Drain14}.
+This regions are were the dust/H ratio declines monotonically hence metallicitty changes in the same manner.
+%PB: might need a little more explanation here.
+
+\begin{equation}
+\label{eq:dust2gas_vs_R}
+\frac{M_d}{M_H} \approx
+\left\{ \begin{array}{l l}
+0.0280 \exp(-R/8.4\kpc)  & R< 8\kpc\\
+0.0165 \exp(-R/19\kpc)   & 8\kpc < R < 18\kpc\\
+0.0605 \exp(-R/8\kpc)    & 18\kpc < R \la 25\kpc ~~~,\\
+\end{array}
+\right.
+\end{equation}
+
+Testing the SFR in these three regions gives us the tool to test not only effect of the distance from the centre of galaxy on SFR but also effect of the metallicity on that.
+Tables ~\ref{table:sfr_law_all} through ~\ref{table:sfr_law_25} show fitting parameters and their uncertainties for whole galaxy and each different regions.
+all the results from \halpha SFR map will be discuss in appendix ~\ref{app:halpha} %PB: Why?
+
+\subsection{Star formation laws}
+We had three SFR maps, three gas mass density maps.
+We applied both laws on whole galaxy on each two combination of two of them, along with applying the laws on three different regions of them.
+As a result we were be able to test each law 36 times.
+In total we produced 72 different plots which show the either K-S law or the extended Schmidt law, and helps us to compare both laws in whole galaxy and in different regions.
+Additionally, these plots provide us a tool to compare the differences in SFR calibrations, ISM gas tracers, and effect of metallicity on SFR.
+
+Figure ~\ref{fig:ks,tot} shows the pixel by pixel fitting of K-S law from whole galaxy.
+In upper level, SFR is calculated using TIR emission form section ~\ref{sec:sfr_fir} and it is plotted versus gas surface density traced by only molecular gas (H$_2$),  only atomic gas (HI), and total gas.
+The only difference between upper level and lower level is SFR tracer in this case is FUV emission.Figure ~\ref{fig:ks,8}, ~\ref{fig:ks,18} and ~\ref{fig:ks,25} are the same as figure ~\ref{fig:ks,tot}, but in these figures, instead of whole galaxy they are showing the regions with R less than 8$\kpc$, $8\kpc < $R $< 18\kpc$, and $18\kpc <$ R $\la 25\kpc$, respectively.
+
+\begin{figure*}
+\centering
+\includegraphics{ks_8kpc_all.png}
+\caption{same as figure ~\ref{fig:ks,tot}, but for the regions with R less than 8$\kpc$ }
+\label{fig:ks,8}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics{ks_8kpc_18kpc_all.png}
+\caption{same as figure ~\ref{fig:ks,tot}, but for the regions with $8\kpc < $R $< 18\kpc$}
+\label{fig:ks,18}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics{ks_18kpc_25kpc_all.png}
+\caption{same as figure ~\ref{fig:ks,tot}, but for the regions with $18\kpc <$ R $\la 25\kpc$}
+\label{fig:ks,25}
+\end{figure*}
+
+%PB: the instructions for MNRAS say that 3D plots can be included in papers -- can you please
+%PB: look into this and figure out if the format that they want is feasible to generate?
+We took the similar approached for the extended Schmidt law.
+Figures ~\ref{fig:es,tot1} to ~\ref{fig:es,256} shows the result of Bayesian fitting of this law.
+For the extended Schmidt law, we show our results in 3D to illustrate the relation between SFR, gas mass density and stellar mass density more clearly.
+In these series of plots, X-axis is the gas mass  surface density, either H$_2$, HI or total gas, Y-axis is the SFR(TIR) or SFR(FUV + 24 $\mu$m), and Z-axis is the stellar mass surface density.
+Shadow of each surface is also shown.
+For a comparison, one cane asily conclude that shadow on X-Y surface is a reproduction of K-S law.
+Results from fiitings in both K-S law and the Extended Schmidt law are shown in tables ~/ref{table:sf-laws_al} to ~/ref{table:sf-laws_25}.
+
+%We did the same for the extended Schmidt law including stellar mass map to our other maps (fig.
+~\ref{fig:es-law}), results are listed in table ~\ref{table:sf-laws_pix} and table ~\ref{table:sf-laws_cat} .
+
+%\begin{figure}
+%\centering
+%\includegraphics[width=82mm]{es_tot_fuv_vs_h2.png}
+%\caption{Caption}
+%\label{fig:es}
+%\end{figure}
+\begin{figure}
+\begin{subfigure}
+  \centering
+  \includegraphics[width=82mm]{es_tot_fuv_vs_h2.png}
+  \caption{a}
+  \label{fig:sfig1}
+\end{subfigure}%
+\begin{subfigure}
+  \centering
+  \includegraphics[width=82mm]{es_tot_fir_vs_h2.png}
+  \caption{b}
+  \label{fig:sfig2}
+\end{subfigure}
+\begin{subfigure}
+  \centering
+  \includegraphics[width=82mm]{es_tot_fir_vs_hi.png}
+  \caption{c}
+  \label{fig:sfig2}
+\end{subfigure}
+\end{figure}
+\begin{figure}
+ \begin{subfigure}
+  \centering
+  \includegraphics[width=82mm]{es_tot_fuv_vs_hi.png}
+  \caption{d}
+  \label{fig:sfig2}
+\end{subfigure}
+\begin{subfigure}
+  \centering
+  \includegraphics[width=82mm]{es_tot_fir_vs_tot.png}
+  \caption{e}
+  \label{fig:sfig2}
+\end{subfigure}
+\begin{subfigure}
+  \centering
+  \includegraphics[width=82mm]{es_tot_fuv_vs_tot.png}
+  \caption{f}
+  \label{fig:sfig2}
+\end{subfigure}
+\caption{plots of....}
+\label{fig:fig}
+\end{figure*}
+
+%PB: in these tables, having the numbers all in the same format  (eg with or without the 1e-2
+%PB type notation) makes it easier to compare. Negative numbers should be written $-x.xx$.
+%THE REST WOULD BE THE comparison of the results:
+\begin{table*}
+\caption{Fitting parameters of the SF laws from applying the Bayesian fitting on all galaxy regions.}
+\label{table:sf-laws_all}
+\begin{tabular}{@{}lccccccccccc}
+\hline\hline
+SFR Tracer& Gas Tracer & N & \sigma$_N$ & $\log$(const$_{KS}$)& \nprime & $\sigma_{\eqnprime}$ & \beta& \sigma$_\beta$&$\log$(const$_{ES}$)&$\sigma_{scatter}$ \\
+\hline
+FIR&H$_2$only&1.03 &9.47e-3 &-8.92 &0.95 &9.78e-3 &0.34 &4.25 &-9.57 & & &
+FIR&HI only& 1.15&9.13e-3 &-9.87 &0.77 &8.84e-3 &0.74 &4.58e-3 &-10.71 & & &
+FIR&Total gas&0.81 &6.27e-3 &-9.84 &0.30 &8.73e-3 &0.60 & 1.21e-2&-10.40 & & &
+FUV + 24\um&H$_2$only& 1.15&1.16e-2 &-9.28 &1.10 &1.21e-2 &0.25 &4.88e-3 &-9.76 & & &
+FUV + 24\um&HI only& 1.21&9.13e-3 &-9.87 &0.80 &7.33e-3 &0.60 &4.02e-3 &-10.70 & & &
+FUV + 24\um&Total gas&0.78& 4.67e-3&-10.05 &0.80 &7.35e-3 &0.60 &3.98e-3 &-10.70 & & &
+\hline
+\end{tabular}
+\end{table*}
+
+\begin{table*}
+\caption{Fitting parameters of the SF laws from applying the Bayesian fitting on regions with R less than 8$\kpc$ .}
+\label{table:sf-laws_8}
+\begin{tabular}{@{}lccccccccccc}
+\hline\hline
+SFR Tracer& Gas Tracer & N & \sigma$_N$ & $\log$(const$_{KS}$)& \nprime & $\sigma_{\eqnprime}$ & \beta& \sigma$_\beta$&$\log$(const$_{ES}$)&$\sigma_{scatter}$ \\
+\hline
+FIR&H$_2$only&0.96 &1.48e-2 &-8.95 &0.88 &1.48e-2 &0.30 &6.11e-3 &-9.54 & & &
+FIR&HI only&0.79 &0.03 &-9.89 &0.47 &0.30 &1.57 &0.28 &-12.11 & & &
+FIR&Total gas&1.00 &0.03 &-10.12 &0.63 &0.03 &0.53 &0.08 &-10.62 & & &
+FUV + 24\um&H$_2$only&1.04 &1.84e-2 &-9.29 &1.00 &1.85e-2 &0.18 &7.17e-3 &-9.65 & & &
+FUV + 24\um&HI only&0.68 &0.02 &-10.03 &0.92 &0.06 &0.42 &0.04 &-10.50 & & &
+FUV + 24\um&Total gas&0.87 &0.026 &-10.12 &0.75 &0.03 &0.16 &0.04 &-10.28 & & &
+\hline
+\end{tabular}
+\end{table*}
+
+\begin{table*}
+\caption{Fitting parameters of the SF laws from applying the Bayesian fitting on regions with $8\kpc < $R $< 18\kpc$.}
+\label{table:sf-laws_18}
+\begin{tabular}{@{}lccccccccccc}
+\hline\hline
+SFR Tracer& Gas Tracer & N & \sigma$_N$ & $\log$(const$_{KS}$)& \nprime & $\sigma_{\eqnprime}$ & \beta& \sigma$_\beta$&$\log$(const$_{ES}$)&$\sigma_{scatter}$ \\
+\hline
+FIR&H$_2$only&1.08 &1.26e-2 &-8.90 &1.00 &1.29e-2 &0.40 &5.74e-3 &-9.66 & & &
+FIR&HI only&1.09 &2.64e-2 &-8.93 &0.77 &0.025 &0.75 &0.01 &-10.71 & & &
+FIR&Total gas&0.75 &0.02 &-10.02 &0.47 &0.01 &0.55 &0.01 &-10.53 & & &
+FUV + 24\um&H$_2$only&1.21 &1.53e-2 &-9.27 &1.15 &1.58e-2 &0.33 &6.57e-3 &-9.66 & & &
+FUV + 24\um&HI only&1.18 &2.89e-2 &-9.81 &0.81 &2.08e-2 &0.61 &1.12e-2 &-10.73 & & &
+FUV + 24\um&Total gas&0.71 &1.34e-2 &-10.02 &0.44 &0.01 &0.45 &0.01 &-10.58 & & &
+\hline
+\end{tabular}
+\end{table*}
+
+\begin{table*}
+\caption{Fitting parameters of the SF laws from applying the Bayesian fitting on regions with $18\kpc <$ R $\la 25\kpc$.}
+\label{table:sf-laws_25}
+\begin{tabular}{@{}lccccccccccc}
+\hline\hline
+SFR Tracer& Gas Tracer & N & \sigma$_N$ & $\log$(const$_{KS}$)&$\sigma_{scatter,KS}$& \nprime & $\sigma_{\eqnprime}$ & \beta& \sigma$_\beta$&$\log$(const$_{ES}$)&$\sigma_{scatter,ES}$ \\
+\hline
+FIR&H$_2$only&1.57 &0.26 &-8.80 &6.03e+2&0.97 &0.20 &1.19 &0.1 &-10.94 &6.44e+2 & 
+FIR&HI only&1.17 &0.05 &-9.65 &3.60e+2&0.76 &0.03 &0.75 &0.01 &-10.72 &3.96e+2 & 
+FIR&Total gas&0.84 &0.02 &-9.85 &3.13e+2&0.50 &0.01 &0.48 &0.01 &-10.62 & 3.61e+2& 
+FUV + 24\um&H$_2$only&1.87 &0.30 &-9.14 &5.72e+2&1.33 &0.29 &1.38 &0.12 &-11.65 & 5.80e+2& 
+FUV + 24\um&HI only&1.22 &0.03 &-9.22 &2.75e+2&0.79 &0.02 &0.62 &0.01 &-10.73 & 3.82e+2&
+FUV + 24\um&Total gas&0.81 &1.59 &-10.06 &3.80e+2&0.42 &0.01 &0.52 &0.02 &-10.68 &3.53e+2 & 
+\hline
+\end{tabular}
+\end{table*}
+
+%----------------------------------------------------------------------------------------
+%
+%----------------------------------------------------------------------------------------
+\section{Discussion}
+%we should discuss results first
+%----------------------------------------------------------------------------------------
+%SUMMERY
+%----------------------------------------------------------------------------------------
+\section{Summery}
+%----------------------------------------------------------------------------------------
+%BIBLOGRAPHY
+%----------------------------------------------------------------------------------------
+\bibliography{ref.bib}
 

### 2015-02-02 draft3.tex
changing intro's parph5

@@
 \newcommand \eqnprime {N^\prime}
-\newcommand \Spitzer {$Spitzer$}
-\newcommand \Galex {$GALEX$}
-\newcommand \Herschel {$Herschel$}
+\newcommand \Spitzer {\it Spitzer}
+\newcommand \Galex {GALEX}
+\newcommand \Herschel {\it Herschel}
 \begin{document}
@@
 \cite{Kennicutt09} and \cite{Hao11} introduced new SFR calibration using a combination of \halpha or FUV and far infrared (FIR) emission, respectively.
-In addition of using suitable calibrations for each region, considering differences between global case and local ($\sim 0.5-1$ kpc) case is important.
-In section 3, we are talking about the SFR in the Andromeda galaxy and how we did measure it.
+In addition of using suitable calibrations for each region, considering differences between global case and local ($\sim 0.5-1$~\kpc) case is important.
+In $\S3$, we are talking about the SFR in the Andromeda galaxy and how we determined it.
 
@@
 Another way to do the mapping is assuming that the ratio of total gas and dust is constant across a galaxy, and convert dust observations to the map of total gas.
-Section 4 is about the calculation of the gas surface density for the Andromeda galaxy.
+$\S4$ is about the calculation of the gas surface density for the Andromeda galaxy.
 
@@
 Additionally, for testing the Extended Schmidt law, measuring the stellar mass density is necessary.
-Measuring the mass of the stellar population is indirect and subject to significant uncertainties.
-In principle there are two ways to measure stellar mass in galaxies.
+Measuring the mass of the stellar population is indirect and subject to significant uncertainties.% In principle there are two ways to measure stellar mass in galaxies.
 First is measuring the dynamical mass of galaxies using kinematics \citep{Cappellari06} or lensing \citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass.
@@
 
-The second method is based on stellar population models \citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, like luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations.
+One of the methods to calculate stellar mass within a galaxy, is based on stellar population models \citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, like luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations.
 Having two independent methods to measure stellar mass helps to compare the results and check whether there are any systematic differences.
@@
 Comparing the results from measuring stellar mass within galaxies shows that the deferences are on the order of a few x10 percent, so one should be more careful to model subtleties \citep{McLaughlin05}.
-Calculating stellar mass in the Andromeda galaxy is described in section 5.
+Calculating stellar mass in the Andromeda galaxy is described in  $\S5$ .
 
 %P5(2*): What we did and why Andromeda and
-In this project we test and compare both the K-S law and the extended Schmidt law on the Andromeda galaxy (M31).
-M31 is the closest spiral galaxy to the Milky Way, therefore, we can have higher resolution images of it than we have of any other spiral galaxy.
+In this paper we present our results from testing and comparing of both the K-S law and the Extended Schmidt law on the Andromeda galaxy (M31).
+%We used three different gas maps and SFR maps, to identify if any of these laws work better with specific gas mass or SFR tracer.
+Additionally, We applied these laws on three different regions on the M31, to determine whether there is any dependence to a distance from the centre of galaxy or not.
+Since, M31 is the closest spiral galaxy to the Milky Way, therefore, we can have higher resolution images of it than we have of any other spiral galaxy.
 Having high resolution images provides us data from different regions within
@@
 %PB: Give a little more detail in the followin sentence
+
 Furthermore, the range of the power index of K-S law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10,Ford13}.
-Therefore, testing extended Schmidt law on the Andromeda galaxy would help to solve the problem with these controversial results.
+%Different groups, using different SFR or gas mass tracers, applied the K-S law on the M31 and have very different power indexes.
+In the most recent work on the K-S law in M31, \cite{Ford13}, test this law on six regions from centre of the galaxy using three different ISM maps (H2 only, total gas calculated from H2 plus HI maps, and total gas calculated from dust emission).
+The power indexes they measure for each map and each regions vary between 0.6 to 2.03.
+The origin of these contrary results is still ongoing question.
+It is not obvious what makes these difference in the power law indexes calculated by different group.
+Whether it depends to distance from galaxy, metalicity, gas tracers, SFR tracers, fitting methods, or this is because of the K-S law does not work on the M31 at all.
+If we assume the last case is valid, testing extended Schmidt law on the Andromeda galaxy would help to solve the problem with these controversial results.
 
@@
 %250 \um & 18\arcsec.2 & $Herschel$ & \cite{Fritz12} \\
-2250 \AA & 6\arcsec & $GALEX$ & \cite{Martin05}\\ %:PB: GALEX, KPNO, IRAM should not be in $$
-1550 \AA & 4\arcsec.5 & $GALEX$ & \cite{Martin05}\\ %PB (they are abbreviations)
-6570 \AA  & 1\arcsec & $KPNO$& \cite{Massey07}\\
-3.6 \um & 1\arcsec.7 & $Spitzer$ & \cite{Barmby06} \\ %PB: write {\it Spitzer}, {\it Herschel}
-4.5 \um & 1\arcsec.7 & $Spitzer$ & \cite{Barmby06} \\ %PB because those are both missions and names
-8 \um & 1\arcsec.9 & $Spitzer$ & \cite{Barmby06} \\ % PB: of people - italics means the mission, not
-24 \um & 6\arcsec & $Spitzer$ & \cite{Gordon06} \\ %PB: the person
-70 \um & 18\arcsec & $Spitzer$ & \cite{Gordon06} \\
-160 \um & 12\arcsec & $Herschel$ & \cite{Fritz12} \\
-2.6 mm & 23\arcsec & $IRAM$ 30-m & \cite{Nieten06}\\
-21 cm & 60\arcsec \times \ 90\arcsec & $DRAO$ & \cite{Chemin09}\\
+2250~\AA & 6\arcsec & GALEX & \cite{Martin05}\\ %:PB: GALEX, KPNO, IRAM should not be in $$
+1550~\AA & 4\arcsec.5 & GALEX & \cite{Martin05}\\ %PB (they are abbreviations)
+6570~\AA  & 1\arcsec & KPNO& \cite{Massey07}\\
+3.6~\um & 1\arcsec.7 & \Spitzer & \cite{Barmby06} \\ %PB: write {\it Spitzer}, {\it Herschel}
+4.5~\um & 1\arcsec.7 & \Spitzer & \cite{Barmby06} \\ %PB because those are both missions and names
+8~\um & 1\arcsec.9 & \Spitzer & \cite{Barmby06} \\ % PB: of people - italics means the mission, not
+24~\um & 6\arcsec & \Spitzer & \cite{Gordon06} \\ %PB: the person
+70~\um & 18\arcsec & \Spitzer & \cite{Gordon06} \\
+160~\um & 12\arcsec & \Herschel & \cite{Fritz12} \\
+2.6~mm & 23\arcsec & IRAM 30-m & \cite{Nieten06}\\
+21~m & 60\arcsec \times \ 90\arcsec & DRAO & \cite{Chemin09}\\
 \hline
@@
 
-The surface density of gas in the ISM of galaxies can be measured by direct observation of the neutral and molecular hydrogen.
+%The surface density of gas in the ISM of galaxies can be measured by direct observation of the neutral and molecular hydrogen.
 This method can be promising provided that the spatial resolution of observational data is high enough; nonetheless, due to technical limitations, attaining enough spatial resolutions to resolve clouds is almost impossible.
@@
 %PB introduction or be omitted; this info doesn't belong here.
- The molecular form of hydrogen in the ISM has no permanent electric dipole moment, which makes it really hard to detect.
+ %The molecular form of hydrogen in the ISM has no permanent electric dipole moment, which makes it really hard to detect.
 H$_2$ molecules are located in cool and dense molecular clouds, but fortunately they are not the only component of the molecular gas.
@@
 where  factor of 1.36 is a constant to consider He and the other heavier elements effect on mass, M$_{HI}$ is mass of neutral hydrogen obtained from 21cm observations and M$_{H_2}$ is from equation ~\ref{equ:conversion} in unit of M$\sun$.
-%----------------------------------------------------------------------------------------
-% Dust Emission as a Tracer of Gas
-%----------------------------------------------------------------------------------------
-
-%\subsubsection{Dust Emission as a Tracer of Gas}
-%A gas map of a galaxy can be produced using the dust mass and assuming the dust mass to gas mass ratio across the galaxy \citep{Hildebran83}.
-This method is the most convenient in order to measure gas mass in distant galaxies, which studying the gas cloud in their ISM by using direct methods is almost impossible and not practical.
-In M31, for regions which are not covered in CO map we used a dust map obtained \cite{Drain14}.
-They also showed that dust/gas mass ratio from radius 0-25Kpc as follow:
-
-%\begin{equation}
-%\label{eq:dust2gas_vs_R}
-%\frac{M_d}{M_H} \approx
-%\left\{ \begin{array}{l l}
-%0.0280 \exp(-R/8.4\kpc)  & R< 8\kpc\\
-%0.0165 \exp(-R/19\kpc)   & 8\kpc < R < 18\kpc\\
-%0.0605 \exp(-R/8\kpc)    & 18\kpc < R \la 25\kpc ~~~,\\
-%\end{array}
-%\right.
-%\end{equation}
-
-%There are many disadvantages regarding the use of the gas to dust ratio in the ISM.
-In order to use the dust as a tracer of the gas mass, first a relationship between the optical depth and the mass of the dust and then a relationship between the mass of the dust and the mass of the gas must be derived.
-\cite{Draine03} pointed out that this approach is uncertain because of the uncertainly in the radiative efficiency of dust grains.
-Also methods of measuring the gas to dust ratio in galaxies are not accurate, which means that there are problems in both steps \citep{Hildebran83}.
- %Certainly the gas to dust ratio as a tracer of the total gas in galaxies has a number of problems.
-Unfortunately, at present, given the available data, we cannot measure the gas mass trough whole galaxy directly.
-Therefore, so far this method is the best available solution for measuring the total gas in regions further out of the disk of galaxy.
 
@@
 Results from fiitings in both K-S law and the Extended Schmidt law are shown in tables ~/ref{table:sf-laws_al} to ~/ref{table:sf-laws_25}.
+As you can see from tables
 

### 2015-02-02 draft3.tex
every thing before ch 5 is almost edited

@@
 \label{sec:data}
-Since the M31 is the closest spiral galaxy to MW, it was aimed by many probes and telescopes, both space based and ground based ones.
-This advantage, provides us variety of data from X-ray to radio wavelengths.
-This wide ranges of data gives us the ability to measure all the required parameters to test the star formation laws in M31.
+Since the M31 is the closest spiral galaxy to the Milky Way, it was aimed by many probes and telescopes, both space based and ground based ones.
+Therefore, variety of data from X-ray to radio wavelengths are available.
+Wide ranges of data provides us the ability to measure all the required parameters to test the star formation laws in M31.
 Table~\ref{table:data} lists all the data we used in this paper.
 Each data comes with different Full Width Half Maximum (FWHM), spacial resolution and grids.
-In order to make sure that all our data contains the same amount of information, we smooth them using Aniano's Kernels' library and convolution code \citep{Aniano12}, to highest resolution available.
-Also considering Nyquist relation \citep{Nyquist}, we re-sample and re-grid all our maps to have a proper pixel size.
+In order to make sure that all our data contains the same amount of information, we smoothed them using Aniano's Kernels' library and convolution code \citep{Aniano12}, to highest resolution available.
+Moreover, considering Nyquist relation \citep{Nyquist}, we re-sampled and re-gridded all our maps to have a proper pixel size.
 
@@
 & Ref. \\
-\hline
+\hlin
 %500 \um & 36\arcsec & $Herschel$ & \cite{Fritz12} \\
@@
 
-One of the calibrations we used to calculate SFR uses FUV emission as a tracer of the star forming regions.
+One of the calibrations, which was used to calculate SFR, uses FUV emission as a tracer of the star forming regions.
 FUV emission of M31 was observed by Galaxy Evolution Explorer ($GALEX$; \citep{Martin05}).
@@
 \halpha maps, which were obtained from NOAO science archive are available in 10 overlapping fields.
-Mosaic image of the maps were created using Montage \citep{Montage}.
+We created a Mosaic image of the maps using Montage \citep{Montage}.
 Assuming that all stars have the same fraction of \halpha light in their spectra, we subtracted the R band emission from the \halpha using averaged scaling factor between R band images and \halpha provided by \cite{Azimlu11}.
@@
 
-In this project first star formation map is produced using a calibration of a combination of the FUV emission and 24\um emission introduced by \cite{Hao11}.
+In this project first star formation map was produced using a calibration of a combination of the FUV emission and 24\um emission introduced by \cite{Hao11}.
 Since peak of the emission of massive and young stars (O - B and A type) are in the UV, this wavelength is one of the most common used star formation rate indicators \citep[e.g.,][]{Kennicutt89}.
@@
 This emission is sensitive to star formation time scale of $\la10$ Myr \citep{Calzetti07}.
-The FUV band of \Galex and the 24\um band of \Spitzer data was used to measure the SFR calibrated by \cite{Hao11} as follow:
+The FUV band of \Galex and the 24\um band of \Spitzer ~ data was used to measure the SFR calibrated by \cite{Hao11} as follow:
 \begin{equation}
@@
 \end{equation}
-where unit of SFR is M$_{\odot}$yr$^{-1}$, and L(24$\mu$m) is in erg/s.
-$L(FUV)_{obs}$ is the luminosity of galaxy in the FUV emission.
+where unit of SFR is M$_{\odot}$yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{obs}$ are in erg/s.
+L(FUV)$_{obs}$ is the luminosity of galaxy in the FUV emission.
 The index of obs is shown to indicate that the FUV emission is not corrected for effect of extinction.
@@
 To do so, we followed a method introduced by \cite{Leroy08}.
-We assumed for any pixel, in maps with pixel size the same as the pixel size of NUV map, if I$_{NUV}$/I$_{FUV}$ $>$ 15 that pixel value is dominated by foreground emission and masked them out.
+We assumed for any pixel in FUV$_{obs}$ map, %which has a pixel size equals the pixel size of NUV map,
+if I$_{NUV}$/I$_{FUV}$ $>$ 15 that pixel value is dominated by foreground emission and masked them out.
 We also masked the same region in the galaxy for 24\um map.
+Using this method, we calculated the total SFR is 0.31\pm 0.04 M$_{\odot}$yr$^{-1}$.
 
@@
 
-The SFR can be calculated using combination of \halpha and $Spitzer$ 24\um maps.
+The SFR can be calculated using combination of \halpha and \Spitzer 24\um maps.
 \halpha emission of galaxies is dominated by light emitted from young and massive stars.
@@
 where L(H${\alpha}$)$_{obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the unit of erg/s.
-L(24$\mu$ m) is the $24\mu$m IR luminosity in erg/s, and SFR is in M$_{\odot}$yr$^{-1}$.
+L(24$\mu$m) is the $24\mu$m IR luminosity in erg/s, and SFR is in M$_{\odot}$yr$^{-1}$.
 It was indicated that the formulation above can only be used at global situation (i.e.
@@
 According to  \cite{Calzetti07} calibration constant in equations ~\ref{equ: halphaplus24_g} and ~\ref{equ: halphaplus24_l} can be different by changing an IMF.
-Changes in the IMF mostly affect on calibration based on \halpha luminocity, mostly because significant amount of the ionising photons comes from the stars more massive than $\sim 20$M$\sun$.
+Changes in the IMF mostly affect on calibration based on \halpha luminosity, mostly because significant amount of the ionising photons comes from the stars more massive than $\sim 20$M$\sun$.
 Changing the calibration constant would change the total SFR by a factor of 1.5.
 In this paper we used \cite{Kroupa01} IMF with upper mass limit of 100M$\sun$.
-Total SFR calculated from equation~\ref{equ: halphaplus24_g} is 0.35 M$\sun$yr$^{-1}$, which is in good agreement with previous studies.
+Total SFR calculated from equation~\ref{equ: halphaplus24_g} is 0.35 \pm 0.01 M$\sun$yr$^{-1}$, which is in good agreement with previous studies.
 %PB: can you put uncertainties on the total SFR numbers?
@@
 
-%PB: I like this figure! Looks nice.
-\begin{figure*}
-        \centering
-        \begin{subfigure}\\(a){}
-                \includegraphics[width=164mm]{sfr_fuv.eps}
-                %\caption{A gull}
-
-               \label{fig:sfr_halpha}
-        \end{subfigure}
-        \begin{subfigure}\\(b){}
-                \includegraphics[width=164mm]{sfr_halpha.eps}
-                %\caption{A gull}
-
-               \label{fig:sfr_halpha}
-        \end{subfigure}
-       % \quad
-        %add desired spacing between images, e. g. ~, \quad, \qquad etc.
-          %(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}\\(c){}
-                \includegraphics[width=164mm]{sfr_fir.eps}
-                %\caption{A tiger}
-
-                \label{fig:sfr_fir_small}
-        \end{subfigure}
-         \quad
-               \caption{SFR map from a combination of \halpha and 24\um emission (top) and total infrared emission (bottom)}
-\label{ISOnIRS}
-\end{figure*}
-
 IR luminosity can be measured from integration of IR part of a spectral energy distribution (SED) of a galaxy or combining photometry datas in different IR wavelengths.
-For second approach \cite{Draine07} modelled $Spitzer$ data and calibrated IR single-band photometry data to calculate the TIR luminosity.
+For second approach \cite{Draine07} modelled \Spitzer data and calibrated IR single-band photometry data to calculate the TIR luminosity.
 \cite{Boquien10} tested and modified this calibration as:
@@
 We used equation ~\ref{equ:sfr_fir} to calculate second map of SFR of M31 (figure ~\ref{fig:sfr_fir_small}).
-Using this method we calculated the total SFR 0.40 M$_{\odot}$yr$^{-1}$.
+Using this method we calculated the total SFR 0.40 \pm 0.04 M$_{\odot}$yr$^{-1}$.
 Table ~\ref{table:sfr} compares total SFR from literature and current work.
@@
 
+%PB: I like this figure! Looks nice.
+\begin{figure*}
+        \centering
+        \begin{subfigure}\\(a){}
+                \includegraphics[width=164mm]{sfr_fuv.eps}
+                %\caption{A gull}
+
+               \label{fig:sfr_halpha}
+        \end{subfigure}
+        \begin{subfigure}\\(b){}
+                \includegraphics[width=164mm]{sfr_halpha.eps}
+                %\caption{A gull}
+
+               \label{fig:sfr_halpha}
+        \end{subfigure}
+        \begin{subfigure}\\(c){}
+                \includegraphics[width=164mm]{sfr_fir.eps}
+                %\caption{A tiger}
+
+                \label{fig:sfr_fir_small}
+        \end{subfigure}
+         \quad
+               \caption{SFR map from a combination of FUV + 24\um emission (top), \halpha and 24\um emission (middle), and total infrared emission (bottom)}
+\label{fig:sfrs}
+\end{figure*}
 %----------------------------------------------------------------------------------------
@@
 %PB introduction or be omitted; this info doesn't belong here.
- %The molecular form of hydrogen in the ISM has no permanent electric dipole moment, which makes it really hard to detect.
+ The molecular form of hydrogen in the ISM has no permanent electric dipole moment, which makes it really hard to detect.
 H$_2$ molecules are located in cool and dense molecular clouds, but fortunately they are not the only component of the molecular gas.
@@
 The calculated stellar mass can be used  to calibrate the fluxes from the stars as the easily measurable parameters of stars.
-Using NIR bands, different groups tried to make a map of stellar mass distributions within galaxies \citep[e.g.,][]{Elmgreen84}.
-Using $B-V$ colours \citep{Bell01} and $Spitzer$ 3.6- and 4.5-\um, M/L correction, \cite{Kendall08} produced stellar mass surface densities of M81.
+Using NIR bands, different groups tried to make a map of stellar mass distributions within galaxies \citep[e.g.,][]{Elmgreen84}.%  Using $B-V$ colours \citep{Bell01} and $Spitzer$ 3.6- and 4.5-\um, M/L correction, \cite{Kendall08} produced stellar mass surface densities of M81.
 %PB: do you mean M81 here?
@@
 
-We calculated the stellar mass work using calibration of the 3.6\um fluxes by \cite{Eskew12}.
-They used 3.6\um fluxes for calibration of the stellar mass, because this band-pass is almost insensitive to the emission from young stellar population, dust absorption and emission.
+We calculated the stellar mass within the M31 using calibration of the 3.6\um flux by \cite{Eskew12}.
+Since 3.6\um flux is almost insensitive to the emission from young stellar population, dust absorption and emission, this band-pass was used for the calibration of the stellar mass.
 By using data from the large Magellanic cloud, they find an empirical relation between stellar mass and luminosity of stars as following:
@@
 
-where M$_{\star}$ is the stellar mass in mass of The Sun, $F_{3.6}]$ is the 3.6\um flux in $Jy$ , and D in the distance of the galaxy in Mpc.
+where M$_{\star}$ is the stellar mass in mass of The Sun, $F_{3.6}$ is the 3.6\um flux in $Jy$ , and D in the distance of the galaxy in Mpc.
 Figure ~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6\um.
+Using this method we calculated the total stellar mass of galaxy is $6.9 \times 10^{10}$M$_{\odot}$ with 6$\%$ uncertainty.
+This result is consistent with the result from \cite{Tamm2012}.
+They calculated that stellar mass in the M31 is $(10-15) \times 10^{10}$M$_{\odot}$ 56$\%$ which is in the disk and the rest is in the bulge of the galaxy.
+%PB: need to compare with other results, as you did with SFR.
 \begin{figure*}
@@
 \includegraphics[width=164mm]{star.eps}
-\caption{Stellar Mass surface density. This mass is produced using $IRAC$ 3.6 $\mu$ m data and equation ~\ref{equ:eskew}}
+\caption{Stellar Mass surface density. This mass is produced using $IRAC$ 3.6 $\mu$ m data and its calibration presented in equation ~\ref{equ:eskew}}
 \label{fig:stellarmass}
@@
 
-Using this method we calculated the total stellar mass of galaxy is $6.9 \times 10^{10}$ with 6$\%$ uncertainty. %PB: need to compare with other results, as you did with SFR.
 %----------------------------------------------------------------------------------------

### 2015-02-18 draft3.tex
Update draft3.tex

@@
 \newcommand \eqnprime {N^\prime}
-\newcommand \Spitzer {\it Spitzer}
+\newcommand \Spitzer {{\it Spitzer}}
 \newcommand \Galex {GALEX}
-\newcommand \Herschel {\it Herschel}
+\newcommand \Herschel {{\it Herschel}}
 \begin{document}
@@
 
-Empirical star formation laws, relations, has been investigated for more than 50 years, and results never been precise.
+Empirical star formation laws (relations) has been investigated for more than 50 years, and results never been precise.
 Formation of stars is a complicated process.
-Various phenomena affect the collapse of molecular clouds and star formation which include the environment of the star-forming region, chemical compositions, the initial mass distribution of gas, gas accretion and cooling, H$_2$ formation, etc.
+Various phenomena affect the collapse of molecular clouds and star formation which, include the environment of the star-forming region, chemical compositions, the initial mass distribution of gas, gas accretion and cooling, H$_2$ formation, and etc.
 
-The first idea about scaling the star formation rate on the galaxy scale was proposed as a connection between the total star formation rate and the mass of interstellar gas.
-\cite{Schmidt59} assumed the constant initial mass function (IMF) of stars, $\Psi (M)$, a stellar lifetime function {$T(M$)}, and a star formation rate {$SFR(T)$} and derived the star formation rate (SFR) over the history of the Milky Way.
-He scaled SFR with a power {\it n} of the gas mass.
-$M_{gas}$.
+The first idea about scaling the star formation rate (SFR) was proposed as a connection between the total star formation rate and the mass of interstellar gas.
+\cite{Schmidt59} assumed a constant initial mass function (IMF) of stars, $\Psi (M)$, a stellar lifetime function {$T(M$)}, and a  {$SFR(T)$} and derived the star formation rate over the history of the Milky Way.
+He scaled SFR with a power {\it N} of the gas mass, $M_{gas}$.
 %Then $SFR(T)\Sigma_{M}(M) = c[M_{gas}(t)]^n$, for a summation over all stellar type $M$.
 A decade later, \cite{Kennicutt98a} examined another group of galaxies.
-He used \halpha, HI and CO observations of 61 normal spiral galaxies and 36 starburst galaxies and showed that the disk-average SFRs and gas densities for this samples are well represented by the Schmidt law with the power of $1.4 \pm 0.15$.
+By using H$\alpha$, HI, and CO observations of 61 normal spiral galaxies and 36 starburst galaxies, he showed that the disk-average SFRs and gas densities for these samples are well represented by the Schmidt law with the power of $1.4 \pm 0.15$.
 Using this power index, the Schmidt law can be rewritten as:
@@
 \begin{equation}
+\label{equ:ks_org}
 \eqsigmasfr \propto \eqsigmagas^{1.4\pm0.15}
 \end{equation}
-which is often referred to as the Kennicutt-Schmidt (K-S) law, where \sigmasfr is surface density of star formation, \sigmagas is the surface density of gas in a galaxy and, {\it n} is the power index.
+which is often referred to as the Kennicutt-Schmidt (K-S) law, where \sigmasfr is surface density of star formation, and \sigmagas is the surface density of gas in a galaxy.
 
 In more recent studies, \cite{Kennicutt08} investigated the local star formation law in M51 with 0.5-2 kpc resolution.
-For the SFR he used pa${\alpha}$ and $24\mu$m + H${\alpha}$ lines and for gas density he used constant conversion factor for CO to H$_2$.
+For calculation of the SFR he used pa${\alpha}$ and $24\mu$m + H${\alpha}$ lines and for gas density he used constant conversion factor for CO to H$_2$.
 He found a correlation, from the radial variation of both SFR and gas surface density, with an index of $1.56 \pm 0.04$.
@@
 \begin{equation}
+\label{equ:es_org}
 \eqsigmasfr \propto \eqsigmagas^{\eqnprime} \eqsigmastar^{\beta}
 \end{equation}
-where \sigmasfr is SFR surface density, \sigmagas and \sigmastar are gas mass and stellar surface density.
+where \sigmasfr is SFR surface density, \sigmagas and \sigmastar are the gas mass and the stellar mass surface densities.
 \nprime and $\beta$ are the power law indexes.
@@
 Therefore, for producing the map of the total gas in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He.
-Another way to do the mapping is assuming that the ratio of total gas and dust is constant across a galaxy, and convert dust observations to the map of total gas.
+Another way to do the mapping of total gas mass of the galaxy is to assum that the ratio of total gas mass and dust mass is the same across a galaxy, and convert dust observations to the map of total gas.
 $\S4$ is about the calculation of the gas surface density for the Andromeda galaxy.
@@
 Comparing the results from measuring stellar mass in stellar clusters shows there is no huge difference.
-Comparing the results from measuring stellar mass within galaxies shows that the deferences are on the order of a few x10 percent, so one should be more careful to model subtleties \citep{McLaughlin05}.
+Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few x10 percent, so one should be more careful to model subtleties \citep{McLaughlin05}.
 Calculating stellar mass in the Andromeda galaxy is described in  $\S5$ .
@@
 Using this method we calculated the total stellar mass of galaxy is $6.9 \times 10^{10}$M$_{\odot}$ with 6$\%$ uncertainty.
-This result is consistent with the result from \cite{Tamm2012}.
-They calculated that stellar mass in the M31 is $(10-15) \times 10^{10}$M$_{\odot}$ 56$\%$ which is in the disk and the rest is in the bulge of the galaxy.
+This result is in fair agreement with the result from \cite{Tamm2012}.
+They calculated that stellar mass in the M31 is $(10-15) \times 10^{10}$M$_{\odot}$, 56$\%$ which is in the disk and the rest is in the bulge of the galaxy.
 %PB: need to compare with other results, as you did with SFR.
@@
 \subsection{Fitting method}
+\label{sec:fittinhg}
 %For investigating and comparing the SFR laws in M31
-Given available SFR, gas mass and stellar mass map examination and comparison of K-S law and the extended Schmidt law are possible.
-We investigated the K-S law and the extended Schmidt law by using  pixel by pixel method in whole galaxy as well as comparing the laws in three different regions of galaxy based on their distance from the centre of the galaxy.
-Knowing that, we can re-write these two star formation laws in a logarithmic scale we would have two linear equations:
+%Given available
+Producing the SFR, gas mass and stellar mass maps, provides of with enough data to examine and compare the K-S law and the extended Schmidt law.% are possible. 
+We investigated the K-S law and the extended Schmidt law by using  pixel by pixel method.
+Our final results are divided by two sets of different pixel sizes.
+That's because the H2 gass mass map has better resolution and lower pixel size of the  HI gas mass map.
+Consequently, any plots with surface density of H2 as a tracer of the gas mass, have more data points.%in whole galaxy as well as comparing the laws in three different regions of galaxy based on their distance from the centre of the galaxy.
+We can re-write equations ~\ref{equ:ks_org} and ~\ref{equ:es_org} in a logarithmic scale. Hence, we would have two linear equations, as following:
 
@@
 \caption{The result from fitting the Kennicutt-Schmidt law on data from whole galaxy using pixel by pixel method.
-Pixel size on each plots are different.
-} %PB: somewhere in this section need to mention the
-%PB: different pixel sizes and the reason for them.
-\label{fig:ks,tot}
+Plots have a different pixel size.
+Each point in the plots with the surface density of H2 as a tracer of gas mass represents regions $~$ Kpc and points in plots with surface density of HI or total gas mass, represeents region in $~$Kpc.}
+\label{fig:ks,all}
 \end{figure*}
@@
 \begin{align}
+\left%\{ \begin{array}{l l}
 \label{eq:sfr_law_log}
 \log_{10} \eqsigmasfr = N~\log_{10} \eqsigmagas + A, \\
-\log_{10} \eqsigmasfr = \eqnprime~\log_{10} \eqsigmagas + \beta~\log_{10}\eqsigmastar  + A,\\
+\log_{10} \eqsigmasfr = \eqnprime~\log_{10} \eqsigmagas + \beta~\log_{10}\eqsigmastar  + A^\prime ~~~,
 \end{align}
 \end{subequations}
-units are the same as the units in the K-S law and the extended Schmidt law.
+where, N, $\eqnprime$, $\beta$, A, and A$^\prime$ are free parameters of fittings. Units in equation above, are the same as the units in the equations ~\ref{equ:ks_org} and ~\ref{equ:es_org}.
 
-we find the fitting parameters by applying the hierarchical Bayesian linear regression method as described in \cite{Shetty13} paper.
-Shetty and his team used a Bayesian linear regression approached to develop a new method to find the K-S law parameters, considering the measurements uncertainties as well as hierarchical data structure.
-For K-S law fitting parameters, we used a 'R' code provided by Shetty's group.
+We found the free parameters by applying the hierarchical Bayesian linear regression method as described in \cite{Shetty13}.
+Shetty and his colleagues used a Bayesian linear regression approached to develop a new method to find the K-S law parameters, considering the measurements uncertainties as well as hierarchical data structure.
+For the K-S law's fitting parameters, we used a 'R' code provided by Shetty's group.
 Uncertainties on each observable quantity was measured considering the background noise photometry errors and calibration uncertainties.%PB: are the background noise errors and calib uncertainties discussed elsewhere in this paper (in which case reference the section) or do they need to be discussed here.
+%SR no they didn't, should I discusse more?
+%SR usually nobody write about them.
+%PB I think you should discuss the uncertainties somewhere -- presumably they affect your fitting results, so the reader needs to know where the uncertainties come from and their approximate size.
 
-For the extended Schmidt law, we expended the code from using simple linear regression which is the case of K-S law to use multiple linear regression.
-In this case we could examine the effect of the stellar mass in the SFR as shown in equation ~\ref{eq:sfr_law_log}.
+For the extended Schmidt law, we expended the code in the way that instead of using simple linear regression, which is the case of the K-S law, it uses multiple linear regression.
+In this case, we were able to examine the effect of the stellar mass in the SFR as shown in equation ~\ref{eq:sfr_law_log}.
 
-We also test each law on three different regions.
+We also test each laws on three different regions.
 The regions were chosen the same as regions introduced in \cite{Drain14}.
-This regions are were the dust/H ratio declines monotonically hence metallicitty changes in the same manner.
-%PB: might need a little more explanation here.
+They found that across the galaxy, with increasing distance from the centre of galaxy dust/H ratio declines monotonically.
+Considering that dust/H ratio has a direct relation to metallicity, they showed that the metallicity of the M31 changes in the same manner.
+%PB: need to expand this a bit: it's well-known that dust-to-gas and metallicity both go down as distance to galaxy centre increase, but how would you expect this to affect  the SFR/gas/stellar mass relation?
 
@@
 
-Testing the SFR in these three regions gives us the tool to test not only effect of the distance from the centre of galaxy on SFR but also effect of the metallicity on that.
+Applying the SFR laws in these regions, provides a tool to consider the effect of the distance from the centre of galaxy on SFR laws as well as the effect of the metallicity on those.
 Tables ~\ref{table:sfr_law_all} through ~\ref{table:sfr_law_25} show fitting parameters and their uncertainties for whole galaxy and each different regions.
-all the results from \halpha SFR map will be discuss in appendix ~\ref{app:halpha} %PB: Why?
+\halpha data dose not have a smooth background.
+Also centre of galaxy in this dta is diffused, so we do not have any data from centre of the M31.
+Since it was the only available \halpha data from the M31, We used this data anyway.
+However, results from the \halpha SFR map are not shown here and will be discuss in appendix ~\ref{app:halpha}.
+%can I make it foot note?
 
 \subsection{Star formation laws}
-We had three SFR maps, three gas mass density maps.
+In total, we produced 72 different plots which, show either the K-S law or the extended Schmidt law, both in whole galaxy and in different distances from the centre of the M31.
+Additionally we can use these results to see if there is any correlation  between the SFR laws and the metallicity, as it was decribed in ~\ref{sec:fittinng}.
+
+%We had three SFR maps, three gas mass density maps.
 We applied both laws on whole galaxy on each two combination of two of them, along with applying the laws on three different regions of them.
@@
 Additionally, these plots provide us a tool to compare the differences in SFR calibrations, ISM gas tracers, and effect of metallicity on SFR.
+% PB: I think you should keep some of the text commented-out above, so that you can show where the number 72 comes from.
 
-Figure ~\ref{fig:ks,tot} shows the pixel by pixel fitting of K-S law from whole galaxy.
-In upper level, SFR is calculated using TIR emission form section ~\ref{sec:sfr_fir} and it is plotted versus gas surface density traced by only molecular gas (H$_2$),  only atomic gas (HI), and total gas.
-The only difference between upper level and lower level is SFR tracer in this case is FUV emission.Figure ~\ref{fig:ks,8}, ~\ref{fig:ks,18} and ~\ref{fig:ks,25} are the same as figure ~\ref{fig:ks,tot}, but in these figures, instead of whole galaxy they are showing the regions with R less than 8$\kpc$, $8\kpc < $R $< 18\kpc$, and $18\kpc <$ R $\la 25\kpc$, respectively.
+Figure ~\ref{fig:ks,tot} shows the pixel by pixel fitting of the K-S law on the whole galaxy.
+First row plots are the surface density of the SFR(TIR), which is calculated using  the TIR emission form section ~\ref{sec:sfr_fir}, versus the gas surface density traced by only the molecular gas (H$_2$),  only atomic gas (HI), and total gas from right to left, respectivly.
+The only difference between the upper and lower plots is that in lower row the SFR indicators is the FUV plus 24\um emission.
+Figure ~\ref{fig:ks,regs} is the same as figure ~\ref{fig:ks,all}.
+However, in this figure we separated pixels from different regions in galaxy by their colours.
+The regions with R less than 8$\kpc$, $8\kpc < $R $< 18\kpc$, and $18\kpc <$ R $\la 25\kpc$ are shown in red, green and blue, respectively.
+
+% \begin{figure*}
+% %\centering
+% \includegraphics{ks_8kpc_all.png}
+% \caption{same as figure ~\ref{fig:ks,tot}, but for the regions with R less than 8$\kpc$ }
+% \label{fig:ks,8}
+% \end{figure*}
+
+% \begin{figure*}
+% %\centering
+% \includegraphics{ks_8kpc_18kpc_all.png}
+% \caption{same as figure ~\ref{fig:ks,tot}, but for the regions with $8\kpc < $R $< 18\kpc$}
+% \label{fig:ks,18}
+% \end{figure*}
+
+% \begin{figure*}
+% %\centering
+% \includegraphics{ks_18kpc_25kpc_all.png}
+% \caption{same as figure ~\ref{fig:ks,tot}, but for the regions with $18\kpc <$ R $\la 25\kpc$}
+% \label{fig:ks,25}
+% \end{figure*}
+
+\begin{figure*}
+\includegraphics[width=164mm]{c3d_all_ks_regs.png}
+\caption{same as figure ~\ref{fig:ks,tot}, but in this figure we separated pixels from different regions in galaxy by their colours.
+The regions with R less than 8$\kpc$, $8\kpc < $R $< 18\kpc$, and $18\kpc <$ R $\la 25\kpc$ are shown in red, green and blue, respectively.}
+\label{fig:ks,regs}
+\end{figure*}
+
+We took the similar approach for the extended Schmidt law.
+Figures ~\ref{fig:es,all} to ~\ref{fig:es,regs,fuv,tot} show the results of the pixel by pixel fitting of this law.
+For the extended Schmidt law fittings, we plotted our results in 3D to illustrate the relationship between the surface density of the SFR, the gas mass surface density, and stellar mass density more clearly.
+In these series of plots, X-axis is the gas mass  surface density, either molecular gas (H$_2$), the atomic gas (HI) or the total gas, Y-axis is the SFR(TIR) or SFR(FUV + 24 $\mu$m), and Z-axis is the stellar mass surface density.
+Shadows of our data on each surface are also plotted, to have a more clear picture of correlations between components .
+For a comparison, one cane asily conclude that shadows on a X-Y surface is a reproduction of K-S law.
+Colours used in plots ~\ref{fig:es,regs,fir,h2} to ~\ref{fig:es,regs,fuv,tot} are the same as colours in  ~\ref{fig:ks,regs}.
+
+%We did the same for the extended Schmidt law including stellar mass map to our other maps (fig.
+~\ref{fig:es-law}), results are listed in table ~\ref{table:sf-laws_pix} and table ~\ref{table:sf-laws_cat} .
+
+\begin{figure}
+	\begin{subfigure}\\(a){}
+  	\left
+	\includegraphics[width=80mm]{es_tot_fuv_vs_h2.png}
+ 	\end{subfigure}%
+
+	 \begin{subfigure}\\(b){}
+	\right
+	\includegraphics[width=80mm]{es_tot_fir_vs_h2.png}
+ 	\end{subfigure}
+
+	 \begin{subfigure}\\(c){}
+ 	\left
+	\includegraphics[width=80mm]{es_tot_fir_vs_hi.png}
+ 	\end{subfigure}
+
+ 	\begin{subfigure}\\(d){}
+   	\right
+	\includegraphics[width=80mm]{es_tot_fuv_vs_hi.png}
+ 	\end{subfigure}
+
+ 	\begin{subfigure}\\(e){}
+   	\left
+	\includegraphics[width=80mm]{es_tot_fir_vs_tot.png}
+ 	\end{subfigure}
+
+ 	\begin{subfigure}\\(f){}
+   	\right
+	\includegraphics[width=80mm]{es_tot_fuv_vs_tot.png}
+	 \end{subfigure}
+
+\caption{The result from fitting the extended Schmidt law on data from whole galaxy using pixel by pixel method.
+Plots have a different pixel size.
+Each point in the plots with the surface density of H2 as a tracer of gas mass represents regions $~$ Kpc and points in plots with surface density of HI or total gas mass, represeents region in $~$Kpc.}
+%PB: explain a little more here what you mean by "plots have different pixel size", or refer to the relevant text section.
+   \label{fig:es,all}
+ \end{figure}
 
@@
 \centering
-\includegraphics{ks_8kpc_all.png}
-\caption{same as figure ~\ref{fig:ks,tot}, but for the regions with R less than 8$\kpc$ }
-\label{fig:ks,8}
+\includegraphics[width=162mm]{c3d_fuv_tot.png}
+\caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs total gas.}
+\label{fig:es,regs,fuv,tot}
 \end{figure*}
@@
 \centering
-\includegraphics{ks_8kpc_18kpc_all.png}
-\caption{same as figure ~\ref{fig:ks,tot}, but for the regions with $8\kpc < $R $< 18\kpc$}
-\label{fig:ks,18}
+\includegraphics[width=162mm]{c3d_fir_tot.png}
+\caption{Fitting result from the SFR(TIR) vs total gas.}
+\label{fig:es,regs,fir,tot}
 \end{figure*}
@@
 \centering
-\includegraphics{ks_18kpc_25kpc_all.png}
-\caption{same as figure ~\ref{fig:ks,tot}, but for the regions with $18\kpc <$ R $\la 25\kpc$}
-\label{fig:ks,25}
+\includegraphics[width=162mm]{c3d_fir_hi.png}
+\caption{Fitting result from the SFR(TIR) vs HI.}
+\label{fig:es,regs,fir,hi}
 \end{figure*}
 
-%PB: the instructions for MNRAS say that 3D plots can be included in papers -- can you please
-%PB: look into this and figure out if the format that they want is feasible to generate?
-We took the similar approached for the extended Schmidt law.
-Figures ~\ref{fig:es,tot1} to ~\ref{fig:es,256} shows the result of Bayesian fitting of this law.
-For the extended Schmidt law, we show our results in 3D to illustrate the relation between SFR, gas mass density and stellar mass density more clearly.
-In these series of plots, X-axis is the gas mass  surface density, either H$_2$, HI or total gas, Y-axis is the SFR(TIR) or SFR(FUV + 24 $\mu$m), and Z-axis is the stellar mass surface density.
-Shadow of each surface is also shown.
-For a comparison, one cane asily conclude that shadow on X-Y surface is a reproduction of K-S law.
-Results from fiitings in both K-S law and the Extended Schmidt law are shown in tables ~/ref{table:sf-laws_al} to ~/ref{table:sf-laws_25}.
-As you can see from tables
+\begin{figure*}
+\centering
+\includegraphics[width=162mm]{c3d_fir_h2.png}
+\caption{Fitting result from the SFR(TIR) vs H$_{2}$.}
+\label{fig:es,regs,fir,h2}
+\end{figure*}
 
-%We did the same for the extended Schmidt law including stellar mass map to our other maps (fig.
-~\ref{fig:es-law}), results are listed in table ~\ref{table:sf-laws_pix} and table ~\ref{table:sf-laws_cat} .
+\begin{figure*}
+\centering
+\includegraphics[width=162mm]{c3d_fuv_hi.png}
+\caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs HI.}
+\label{fig:es,regs,fuv,hi}
+\end{figure*}
 
-%\begin{figure}
-%\centering
-%\includegraphics[width=82mm]{es_tot_fuv_vs_h2.png}
-%\caption{Caption}
-%\label{fig:es}
-%\end{figure}
-\begin{figure}
-\begin{subfigure}
+\begin{figure*}
 \centering
-  \includegraphics[width=82mm]{es_tot_fuv_vs_h2.png}
-  \caption{a}
-  \label{fig:sfig1}
-\end{subfigure}%
-\begin{subfigure}
-  \centering
-  \includegraphics[width=82mm]{es_tot_fir_vs_h2.png}
-  \caption{b}
-  \label{fig:sfig2}
-\end{subfigure}
-\begin{subfigure}
-  \centering
-  \includegraphics[width=82mm]{es_tot_fir_vs_hi.png}
-  \caption{c}
-  \label{fig:sfig2}
-\end{subfigure}
-\end{figure}
-\begin{figure}
- \begin{subfigure}
-  \centering
-  \includegraphics[width=82mm]{es_tot_fuv_vs_hi.png}
-  \caption{d}
-  \label{fig:sfig2}
-\end{subfigure}
-\begin{subfigure}
-  \centering
-  \includegraphics[width=82mm]{es_tot_fir_vs_tot.png}
-  \caption{e}
-  \label{fig:sfig2}
-\end{subfigure}
-\begin{subfigure}
-  \centering
-  \includegraphics[width=82mm]{es_tot_fuv_vs_tot.png}
-  \caption{f}
-  \label{fig:sfig2}
-\end{subfigure}
-\caption{plots of....}
-\label{fig:fig}
+\includegraphics[width=162mm]{c3d_fuv_h2.png}
+\caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs H$_{2}$.}
+\label{fig:es,regs,fuv,h2}
 \end{figure*}
@@
 \begin{table*}
-\caption{Fitting parameters of the SF laws from applying the Bayesian fitting on all galaxy regions.}
+\caption{global fitting parameters of the SF laws from applying the Bayesian fitting.}
 \label{table:sf-laws_all}
@@
 FIR&Total gas&0.81 &6.27e-3 &-9.84 &0.30 &8.73e-3 &0.60 & 1.21e-2&-10.40 & & &
-FUV + 24\um&H$_2$only& 1.15&1.16e-2 &-9.28 &1.10 &1.21e-2 &0.25 &4.88e-3 &-9.76 & & &
-FUV + 24\um&HI only& 1.21&9.13e-3 &-9.87 &0.80 &7.33e-3 &0.60 &4.02e-3 &-10.70 & & &
-FUV + 24\um&Total gas&0.78& 4.67e-3&-10.05 &0.80 &7.35e-3 &0.60 &3.98e-3 &-10.70 & & &
+FUV + 24\um &H$_2$only& 1.15&1.16e-2 &-9.28 &1.10 &1.21e-2 &0.25 &4.88e-3 &-9.76 & & &
+FUV + 24\um &HI only& 1.21&9.13e-3 &-9.87 &0.80 &7.33e-3 &0.60 &4.02e-3 &-10.70 & & &
+FUV + 24\um &Total gas&0.78& 4.67e-3&-10.05 &0.80 &7.35e-3 &0.60 &3.98e-3 &-10.70 & & &
 \hline
@@
 FIR&Total gas&1.00 &0.03 &-10.12 &0.63 &0.03 &0.53 &0.08 &-10.62 & & &
-FUV + 24\um&H$_2$only&1.04 &1.84e-2 &-9.29 &1.00 &1.85e-2 &0.18 &7.17e-3 &-9.65 & & &
-FUV + 24\um&HI only&0.68 &0.02 &-10.03 &0.92 &0.06 &0.42 &0.04 &-10.50 & & &
-FUV + 24\um&Total gas&0.87 &0.026 &-10.12 &0.75 &0.03 &0.16 &0.04 &-10.28 & & &
+FUV + 24\um &H$_2$only&1.04 &1.84e-2 &-9.29 &1.00 &1.85e-2 &0.18 &7.17e-3 &-9.65 & & &
+FUV + 24\um &HI only&0.68 &0.02 &-10.03 &0.92 &0.06 &0.42 &0.04 &-10.50 & & &
+FUV + 24\um &Total gas&0.87 &0.026 &-10.12 &0.75 &0.03 &0.16 &0.04 &-10.28 & & &
 \hline
@@
 FIR&Total gas&0.75 &0.02 &-10.02 &0.47 &0.01 &0.55 &0.01 &-10.53 & & &
-FUV + 24\um&H$_2$only&1.21 &1.53e-2 &-9.27 &1.15 &1.58e-2 &0.33 &6.57e-3 &-9.66 & & &
-FUV + 24\um&HI only&1.18 &2.89e-2 &-9.81 &0.81 &2.08e-2 &0.61 &1.12e-2 &-10.73 & & &
-FUV + 24\um&Total gas&0.71 &1.34e-2 &-10.02 &0.44 &0.01 &0.45 &0.01 &-10.58 & & &
+FUV + 24\um &H$_2$only&1.21 &1.53e-2 &-9.27 &1.15 &1.58e-2 &0.33 &6.57e-3 &-9.66 & & &
+FUV + 24\um &HI only&1.18 &2.89e-2 &-9.81 &0.81 &2.08e-2 &0.61 &1.12e-2 &-10.73 & & &
+FUV + 24\um &Total gas&0.71 &1.34e-2 &-10.02 &0.44 &0.01 &0.45 &0.01 &-10.58 & & &
 \hline
@@
 FIR&Total gas&0.84 &0.02 &-9.85 &3.13e+2&0.50 &0.01 &0.48 &0.01 &-10.62 & 3.61e+2& 
-FUV + 24\um&H$_2$only&1.87 &0.30 &-9.14 &5.72e+2&1.33 &0.29 &1.38 &0.12 &-11.65 & 5.80e+2& 
-FUV + 24\um&HI only&1.22 &0.03 &-9.22 &2.75e+2&0.79 &0.02 &0.62 &0.01 &-10.73 & 3.82e+2&
-FUV + 24\um&Total gas&0.81 &1.59 &-10.06 &3.80e+2&0.42 &0.01 &0.52 &0.02 &-10.68 &3.53e+2 & 
+FUV + 24\um &H$_2$only&1.87 &0.30 &-9.14 &5.72e+2&1.33 &0.29 &1.38 &0.12 &-11.65 & 5.80e+2& 
+FUV + 24\um &HI only&1.22 &0.03 &-9.22 &2.75e+2&0.79 &0.02 &0.62 &0.01 &-10.73 & 3.82e+2&
+FUV + 24\um &Total gas&0.81 &1.59 &-10.06 &3.80e+2&0.42 &0.01 &0.52 &0.02 &-10.68 &3.53e+2 & 
 \hline
@@
 \section{Discussion}
-%we should discuss results first
+% PB: Here's an idea for how to organize this in paragraphs:
+% 1. Global KS law: linear or sublinear?
+% 2. KS laws with gas components separated: same or different?
+% 3. KS law variation with distance
+% 4. EKS law: agrees with Shi? Better or worse than KS?
+% 5. EKS with gas components separated: same or different?, compare to KS
+% 6. EKS law variation with distance, compare to KS
+% 7. Answer the question in the title: which SF law best captures what's going on?
+
+% Not sure where to put this but you also want to answer the question "does it matter which SFR tracer you use" somewhere.
+All of the factors that go into the "72 plots" should be discussed at some point.
+
+%PB: By the way: better not to start paragraphs with "However" and "On the other hand" as it makes for an awkward transition between topics.
+
+Figures ~\ref{fig:fit,params,fir} and ~\ref{fig:fit,params,fuv} show results of the fitting parameters for SFR(TIR) and SFR(FUV+24\um) in three different regions.
+In case of Total gas for the K-S law, there is a sublinear retaliation between SFR and gas mass, in global case and all regions.This result is significatly lower than results from \cite{Ford13}.
+But it is similar to prediction of the \cite{Shetty13}, which argued that using the hierarchical Bayesian fit leads to power index N lower than other works.
+%PB: more detailed comparison to Ford here: what values did he find, are these significantly different from yours?
+%PB: Also compare to Shetty's results: what did he find for other galaxies and are your results compatible with those?
+
+However, if we look at the H$_{2}$ gas or HI gas, we could see power indexes are more similar to the initial sugeestion of the K-S law power index, N$ ~ 1.4\pm 0.15 $.
+Moreover, these results are in a good agreement with results from \cite{tabatabyi10}.
+For regions with R less than 8 \kpc, we could see some sublinear values, but it is mostly because H$_2$ is dominant gas in the ISM, and lack of HI gas makes our results very uncertain.
+Moreover, the K-S law power index increases by the distance from the centre of the galaxy.
+This could be an affect of metallicity on the SFR or the consequence of lack of H$_2$ gas on outher regions of the galaxy.
+% PB: I would start this paragraph off with a sentence that says what you find by comparing total gas with H_2 only or HI only: different or not? 
+% PB: when comparing with Tabatabyi, give values from that paper
+% PB: by "lack of HI gas makes our results very uncertain" you mean that the total gas and Hi-only fits are not reliable?
+% PB: not sure I see where the last sentence comes from; may need more detail.
+
+\begin{figure*}
+\centering
+\includegraphics[width=162mm]{fir_res2.png}
+\caption{Fitting parameters for SFR(TIR) }
+\label{fig:fir,params,fir}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\includegraphics[width=162mm]{fuv_res.png}
+\caption{Fitting parameters for SFR(FUV + 24\um ) }
+\label{fig:fir,params,fuv}
+\end{figure*}
+
+On the other hand, from fitting the the extended Schmidt law, we have sublinear relation between SFR and gas surface density in global case and all the regions, execpt for gas surface density traced by H$_2$.
+Besides, for all cases we can see $\beta ~ 0.6$, which is the same as prediction of the \cite{Shi11}.
+For gas traced by H$_2$ in regions with $18\kpc <$ R $\la 25\kpc$, $\beta$ is way higher than this value.
+This is could be a result of the lack of H$_2$ gas in these regions.
+\cite{Kim13} using 3D numirical hydrodynamic simulations showed that in outer disk regions of the galaxy $\eqsigmasfr \propto \eqsigmagas \pho_{sd}^0.5$ where \pho$_{sd}$ is the midplane density of the stellar disk.
+our results for total gas in regions with $18\kpc <$ R $\la 25\kpc$ shows $\log_{10}(\eqsigmasfr) \propto 0.5 \times \log_{10}(\eqsigmastar)$, which is the same as simulations.
+However, in this case we found a sublinear relation between \sigmasfr and \sigmagas while \cite{Kim13} found a linear relation.
 %----------------------------------------------------------------------------------------

### 2015-02-25 draft3.tex
with final tables

@@
 \usepackage{float}
+\usepackage{caption}
+%\usepackage[caption=false]{subfig}
+\usepackage{subcaption}
+\usepackage{multirow}
 
@@
 & Ref. \\
-\hlin
+\hline
 %500 \um & 36\arcsec & $Herschel$ & \cite{Fritz12} \\
@@
 %PB: I like this figure! Looks nice.
+
 \begin{figure*}
     \centering
-        \begin{subfigure}\\(a){}
+    \begin{subfigure}[b]{1\textwidth}
+        \centering
         \includegraphics[width=164mm]{sfr_fuv.eps}
-                %\caption{A gull}
-
+        \caption{SFR,FUV+24\um}
+        \label{fig:sfr,fuv}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{1\textwidth}
+        \centering
+        \includegraphics[width=164mm]{sfr_halpha.eps}
+        \caption{SFR,H$_{\alpha}$}
         \label{fig:sfr_halpha}
     \end{subfigure}
-        \begin{subfigure}\\(b){}
-                \includegraphics[width=164mm]{sfr_halpha.eps}
-                %\caption{A gull}
-
-               \label{fig:sfr_halpha}
+    \hfill
+    \begin{subfigure}[b]{1\textwidth}
+        \centering
+        \includegraphics[width=164mm]{sfr_fir.eps}
+        \caption{SFR,TIR}
+        \label{fig:sfr,fir}
     \end{subfigure}
-        \begin{subfigure}\\(c){}
-                \includegraphics[width=164mm]{sfr_fir.eps}
-                %\caption{A tiger}
-
-                \label{fig:sfr_fir_small}
-        \end{subfigure}
-         \quad
     \caption{SFR map from a combination of FUV + 24\um emission (top), \halpha and 24\um emission (middle), and total infrared emission (bottom)}
@@
 \centering
-\includegraphics{ks_tot_compt.png}
+\includegraphics[width=164mm]{ks_all_1.png}
 \caption{The result from fitting the Kennicutt-Schmidt law on data from whole galaxy using pixel by pixel method.
@@
 
-% \begin{figure*}
-% %\centering
-% \includegraphics{ks_8kpc_all.png}
-% \caption{same as figure ~\ref{fig:ks,tot}, but for the regions with R less than 8$\kpc$ }
-% \label{fig:ks,8}
-% \end{figure*}
-
-% \begin{figure*}
-% %\centering
-% \includegraphics{ks_8kpc_18kpc_all.png}
-% \caption{same as figure ~\ref{fig:ks,tot}, but for the regions with $8\kpc < $R $< 18\kpc$}
-% \label{fig:ks,18}
-% \end{figure*}
-
-% \begin{figure*}
-% %\centering
-% \includegraphics{ks_18kpc_25kpc_all.png}
-% \caption{same as figure ~\ref{fig:ks,tot}, but for the regions with $18\kpc <$ R $\la 25\kpc$}
-% \label{fig:ks,25}
-% \end{figure*}
-
 \begin{figure*}
-\includegraphics[width=164mm]{c3d_all_ks_regs.png}
-\caption{same as figure ~\ref{fig:ks,tot}, but in this figure we separated pixels from different regions in galaxy by their colours.
+\includegraphics[width=164mm]{c3d_all_ks_regs_1.png}
+\caption{same as figure ~\ref{fig:ks,all}, but in this figure we separated pixels from different regions in galaxy by their colours.
 The regions with R less than 8$\kpc$, $8\kpc < $R $< 18\kpc$, and $18\kpc <$ R $\la 25\kpc$ are shown in red, green and blue, respectively.}
@@
 
-\begin{figure}
-	\begin{subfigure}\\(a){}
-  	\left
-	\includegraphics[width=80mm]{es_tot_fuv_vs_h2.png}
- 	\end{subfigure}%
-
-	 \begin{subfigure}\\(b){}
-	\right
-	\includegraphics[width=80mm]{es_tot_fir_vs_h2.png}
- 	\end{subfigure}
-
-	 \begin{subfigure}\\(c){}
- 	\left
-	\includegraphics[width=80mm]{es_tot_fir_vs_hi.png}
- 	\end{subfigure}
-
- 	\begin{subfigure}\\(d){}
-   	\right
-	\includegraphics[width=80mm]{es_tot_fuv_vs_hi.png}
- 	\end{subfigure}
-
- 	\begin{subfigure}\\(e){}
-   	\left
-	\includegraphics[width=80mm]{es_tot_fir_vs_tot.png}
- 	\end{subfigure}
-
- 	\begin{subfigure}\\(f){}
-   	\right
-	\includegraphics[width=80mm]{es_tot_fuv_vs_tot.png}
-	 \end{subfigure}
-
-\caption{The result from fitting the extended Schmidt law on data from whole galaxy using pixel by pixel method.
-Plots have a different pixel size.
-Each point in the plots with the surface density of H2 as a tracer of gas mass represents regions $~$ Kpc and points in plots with surface density of HI or total gas mass, represeents region in $~$Kpc.}
-%PB: explain a little more here what you mean by "plots have different pixel size", or refer to the relevant text section.
-   \label{fig:es,all}
- \end{figure}
-
 \begin{figure*}
     \centering
-\includegraphics[width=162mm]{c3d_fuv_tot.png}
-\caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs total gas.}
-\label{fig:es,regs,fuv,tot}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{es_tot_fir_vs_h2.png}
+        \caption{SFR,TIR vs surface density of H$_2$}
+        \label{fig:es,all,fir,h2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{es_tot_fuv_vs_h2.png}
+        \caption{SFR,FUV+24\um vs surface density of H$_2$}
+        \label{fig:es,all,fuv,h2}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \includegraphics[width=\textwidth]{es_tot_fir_vs_hi.png}
+        \caption{SFR,TIR vs surface density of HI}
+        \label{fig:es,all,fir,hi}
+    \end{subfigure}
+     \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{es_tot_fuv_vs_hi.png}
+        \caption{SFR,FUV+24\um vs surface density of HI}
+        \label{fig:es,all,fuv,hi}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{es_tot_fir_vs_tot.png}
+        \caption{SFR,TIR vs surface density of total gas}
+        \label{fig:es,all,fir,tot}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{es_tot_fuv_vs_tot.png}
+        \caption{SFR,FUV+24\um vs surface density of total gas}
+        \label{fig:es,all,fuv,tot}
+    \end{subfigure}
+    \caption{The result from fitting the extended Schmidt law on data from whole galaxy using pixel by pixel method.
+Plots show SFR vs surface density of gas, and z-axis is surface density of the stellar mass.
+Each figure shows different combination of the SFR tracer and gas mass tracer results.
+Plots have a different pixel size.
+Each point in the plots with the surface density of H2 as a tracer of gas mass represents regions $\sim$30~Kpc and points in plots with surface density of HI or total gas mass, represents region in $\sim$155~Kpc.}
+    \label{fig:es,all}
 \end{figure*}
+
+% \begin{figure*}
+% \centering
+% \includegraphics[width=162mm]{c3d_fir_h2.png}
+% \caption{Fitting result from the SFR(TIR) vs H$_{2}$.}
+% \label{fig:es,regs,fir,h2}
+% \end{figure*}
+
+% \begin{figure*}
+% \centering
+% \includegraphics[width=162mm]{c3d_fuv_h2.png}
+% \caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs H$_{2}$.}
+% \label{fig:es,regs,fuv,h2}
+% \end{figure*}
+
+% \begin{figure*}
+% \centering
+% \includegraphics[width=162mm]{c3d_fir_hi.png}
+% \caption{Fitting result from the SFR(TIR) vs HI.}
+% \label{fig:es,regs,fir,hi}
+% \end{figure*}
+
+% \begin{figure*}
+% \centering
+% \includegraphics[width=162mm]{c3d_fuv_hi.png}
+% \caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs HI.}
+% \label{fig:es,regs,fuv,hi}
+% \end{figure*}
 
@@
 \centering
-\includegraphics[width=162mm]{c3d_fir_hi.png}
-\caption{Fitting result from the SFR(TIR) vs HI.}
-\label{fig:es,regs,fir,hi}
+\includegraphics[width=162mm]{c3d_fuv_tot.png}
+\caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs total gas.}
+\label{fig:es,regs,fuv,tot}
 \end{figure*}
 
-\begin{figure*}
-\centering
-\includegraphics[width=162mm]{c3d_fir_h2.png}
-\caption{Fitting result from the SFR(TIR) vs H$_{2}$.}
-\label{fig:es,regs,fir,h2}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=162mm]{c3d_fuv_hi.png}
-\caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs HI.}
-\label{fig:es,regs,fuv,hi}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[width=162mm]{c3d_fuv_h2.png}
-\caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs H$_{2}$.}
-\label{fig:es,regs,fuv,h2}
-\end{figure*}
-
-%PB: in these tables, having the numbers all in the same format  (eg with or without the 1e-2
-%PB type notation) makes it easier to compare. Negative numbers should be written $-x.xx$.
-%THE REST WOULD BE THE comparison of the results:
 \begin{table*}
-\caption{global fitting parameters of the SF laws from applying the Bayesian fitting.}
-\label{table:sf-laws_all}
-\begin{tabular}{@{}lccccccccccc}
+\caption{Fitting parameters of the SF laws from applying the Bayesian.}
+\label{table:res}
+\begin{tabular}{||cc||cccrcccccr}
 \hline\hline
-SFR Tracer& Gas Tracer & N & \sigma$_N$ & $\log$(const$_{KS}$)& \nprime & $\sigma_{\eqnprime}$ & \beta& \sigma$_\beta$&$\log$(const$_{ES}$)&$\sigma_{scatter}$ \\
+\multicolumn{1}{||c||}{\multirow{1}{*}{Region}} & SFR Tracer& Gas Tracer & N & $\sigma_N$ & A & \nprime & $\sigma_{\eqnprime}$ & $\beta$ & $\sigma_\beta$ & A$^\prime$& \\
 \hline
-FIR&H$_2$only&1.03 &9.47e-3 &-8.92 &0.95 &9.78e-3 &0.34 &4.25 &-9.57 & & &
-FIR&HI only& 1.15&9.13e-3 &-9.87 &0.77 &8.84e-3 &0.74 &4.58e-3 &-10.71 & & &
-FIR&Total gas&0.81 &6.27e-3 &-9.84 &0.30 &8.73e-3 &0.60 & 1.21e-2&-10.40 & & &
-FUV + 24\um &H$_2$only& 1.15&1.16e-2 &-9.28 &1.10 &1.21e-2 &0.25 &4.88e-3 &-9.76 & & &
-FUV + 24\um &HI only& 1.21&9.13e-3 &-9.87 &0.80 &7.33e-3 &0.60 &4.02e-3 &-10.70 & & &
-FUV + 24\um &Total gas&0.78& 4.67e-3&-10.05 &0.80 &7.35e-3 &0.60 &3.98e-3 &-10.70 & & &
+\multicolumn{1}{||c||}{\multirow{6}{*}{Global case}} & TIR & H$_2$ only & 1.03 & 9.47e-3  & -8.92  & 0.95 & 9.77e-3 & 0.34 & 4.25e-3 & -9.57  \\
+ & TIR         & HI only    & 1.15 & 1.47e-2 & $-9.63$  & 0.77 & 8.84e-3 & 0.75 & 4.58e-3 & $-10.71$ \\
+ & TIR         & Total gas  & 0.81 & 6.27e-3 & $-9.84$  & 0.50 & 4.49e-3 & 0.55 & 4.57e-3 & $-10.53$\\
+ & FUV + 24\um & H$_2$ only & 1.15 & 1.16e-2 & $-9.28$  & 1.09 & 1.21e-2 & 0.25 & 4.88e-3 & $-9.76$  \\
+ & FUV + 24\um & HI only    & 1.21 & 9.13e-3 & $-9.87$  & 0.81 & 7.34e-3 & 0.60 & 4.10e-3 & $-10.70$ \\
+ & FUV + 24\um & Total gas  & 0.78 & 4.67e-3 & $-10.06$ & 0.48 & 4.61e-3 & 0.45 & 4.69e-3 & $-10.57$ \\
 \hline
-\end{tabular}
-\end{table*}
-
-\begin{table*}
-\caption{Fitting parameters of the SF laws from applying the Bayesian fitting on regions with R less than 8$\kpc$ .}
-\label{table:sf-laws_8}
-\begin{tabular}{@{}lccccccccccc}
-\hline\hline
-SFR Tracer& Gas Tracer & N & \sigma$_N$ & $\log$(const$_{KS}$)& \nprime & $\sigma_{\eqnprime}$ & \beta& \sigma$_\beta$&$\log$(const$_{ES}$)&$\sigma_{scatter}$ \\
+\multicolumn{1}{||c||}{\multirow{6}{*}{R$< 8\kpc$}}& TIR & H$_2$ only & 0.96 & 1.48e-2 & -8.95  & 0.88 & 1.49e-2 & 0.30 & 6.11e-3 & -9.54  \\
+ & TIR         & HI only    & 1.52 & 7.73e-2  & -9.91  & 1.00 & 7.27e-2  & 0.60 & 4.22e-2  & -10.60 \\
+ & TIR         & Total gas  & 1.00 & 3.51e-2  & -10.04 & 0.63 & 3.47e-2  & 0.53 & 7.57e-2  & -10.63 \\
+ & FUV + 24\um & H$_2$ only & 1.04 & 1.84e-2 & -9.29  & 1.00 & 1.85e-2 & 0.18 & 7.17e-3 & -9.64  \\
+ & FUV + 24\um & HI only    & 1.28 & 4.73e-2  & -10.00 & 0.93 & 5.68e-2  & 0.42 & 3.81e-2  & -10.50 \\
+ & FUV + 24\um & Total gas  & 0.88 & 2.59e-2  & -10.12 & 0.75 & 3.53e-2  & 0.16 & 3.93e-2  & -10.28 \\
 \hline
-FIR&H$_2$only&0.96 &1.48e-2 &-8.95 &0.88 &1.48e-2 &0.30 &6.11e-3 &-9.54 & & &
-FIR&HI only&0.79 &0.03 &-9.89 &0.47 &0.30 &1.57 &0.28 &-12.11 & & &
-FIR&Total gas&1.00 &0.03 &-10.12 &0.63 &0.03 &0.53 &0.08 &-10.62 & & &
-FUV + 24\um &H$_2$only&1.04 &1.84e-2 &-9.29 &1.00 &1.85e-2 &0.18 &7.17e-3 &-9.65 & & &
-FUV + 24\um &HI only&0.68 &0.02 &-10.03 &0.92 &0.06 &0.42 &0.04 &-10.50 & & &
-FUV + 24\um &Total gas&0.87 &0.026 &-10.12 &0.75 &0.03 &0.16 &0.04 &-10.28 & & &
+\multicolumn{1}{||c||}{\multirow{6}{*}{$8\kpc < $R $< 18\kpc$}} & TIR & H$_2$ only & 1.08 & 1.26e-2 & -8.90  & 1.00 & 1.29e-2 & 0.40 & 5.74e-3 & -9.66  \\
+ & TIR         & HI only    & 1.09 & 4.50e-2 & -9.54  & 0.77 & 2.52e-2  & 0.75 & 1.26e-2  & -10.71 \\
+ & TIR         & Total gas  & 0.75 & 1.76e-2  & -9.81  & 0.47 & 1.18e-2  & 0.55 & 1.24e-2  & -10.53 \\
+ & FUV + 24\um & H$_2$ only & 1.21 & 1.53e-2 & -9.27  & 1.15 & 1.57e-2 & 0.33 & 6.57e-3 & -9.89  \\
+ & FUV + 24\um & HI only    & 1.18 & 2.89e-2 & -9.81  & 0.81 & 2.08e-2 & 0.61 & 1.12e-2 & -10.73 \\
+ & FUV + 24\um & Total gas  & 0.71 & 1.34e-2 & -9.81  & 0.44 & 1.18e-2  & 0.45 & 1.28e-2  & -10.58 \\
 \hline
-\end{tabular}
-\end{table*}
-
-\begin{table*}
-\caption{Fitting parameters of the SF laws from applying the Bayesian fitting on regions with $8\kpc < $R $< 18\kpc$.}
-\label{table:sf-laws_18}
-\begin{tabular}{@{}lccccccccccc}
-\hline\hline
-SFR Tracer& Gas Tracer & N & \sigma$_N$ & $\log$(const$_{KS}$)& \nprime & $\sigma_{\eqnprime}$ & \beta& \sigma$_\beta$&$\log$(const$_{ES}$)&$\sigma_{scatter}$ \\
-\hline
-FIR&H$_2$only&1.08 &1.26e-2 &-8.90 &1.00 &1.29e-2 &0.40 &5.74e-3 &-9.66 & & &
-FIR&HI only&1.09 &2.64e-2 &-8.93 &0.77 &0.025 &0.75 &0.01 &-10.71 & & &
-FIR&Total gas&0.75 &0.02 &-10.02 &0.47 &0.01 &0.55 &0.01 &-10.53 & & &
-FUV + 24\um &H$_2$only&1.21 &1.53e-2 &-9.27 &1.15 &1.58e-2 &0.33 &6.57e-3 &-9.66 & & &
-FUV + 24\um &HI only&1.18 &2.89e-2 &-9.81 &0.81 &2.08e-2 &0.61 &1.12e-2 &-10.73 & & &
-FUV + 24\um &Total gas&0.71 &1.34e-2 &-10.02 &0.44 &0.01 &0.45 &0.01 &-10.58 & & &
-\hline
-\end{tabular}
-\end{table*}
-
-\begin{table*}
-\caption{Fitting parameters of the SF laws from applying the Bayesian fitting on regions with $18\kpc <$ R $\la 25\kpc$.}
-\label{table:sf-laws_25}
-\begin{tabular}{@{}lccccccccccc}
-\hline\hline
-SFR Tracer& Gas Tracer & N & \sigma$_N$ & $\log$(const$_{KS}$)&$\sigma_{scatter,KS}$& \nprime & $\sigma_{\eqnprime}$ & \beta& \sigma$_\beta$&$\log$(const$_{ES}$)&$\sigma_{scatter,ES}$ \\
-\hline
-FIR&H$_2$only&1.57 &0.26 &-8.80 &6.03e+2&0.97 &0.20 &1.19 &0.1 &-10.94 &6.44e+2 & 
-FIR&HI only&1.17 &0.05 &-9.65 &3.60e+2&0.76 &0.03 &0.75 &0.01 &-10.72 &3.96e+2 & 
-FIR&Total gas&0.84 &0.02 &-9.85 &3.13e+2&0.50 &0.01 &0.48 &0.01 &-10.62 & 3.61e+2& 
-FUV + 24\um &H$_2$only&1.87 &0.30 &-9.14 &5.72e+2&1.33 &0.29 &1.38 &0.12 &-11.65 & 5.80e+2& 
-FUV + 24\um &HI only&1.22 &0.03 &-9.22 &2.75e+2&0.79 &0.02 &0.62 &0.01 &-10.73 & 3.82e+2&
-FUV + 24\um &Total gas&0.81 &1.59 &-10.06 &3.80e+2&0.42 &0.01 &0.52 &0.02 &-10.68 &3.53e+2 & 
+\multicolumn{1}{||c||}{\multirow{6}{*}{$18\kpc <$ R $\la 25\kpc$}}  & TIR & H$_2$ only & 1.57 & 2.63e-1  & -8.80  & 0.97 & 2.00e-1  & 1.19 & 1.01e-1  & -10.94 \\
+ & TIR         & HI only    & 1.17 & 4.67e-2 & -9.65  & 0.76 & 2.82e-2 & 0.75 & 1.48e-2 & -10.72 \\
+ & TIR         & Total gas  & 0.84 & 2.06e-2  & -9.85  & 0.52 & 1.45e-2  & 0.56 & 1.42e-2  & -10.56 \\
+ & FUV + 24\um & H$_2$ only & 1.87 & 3.03e-1  & -9.15  & 1.33 & 2.95e-1  & 1.38 & 1.12e-1  & -11.65 \\
+ & FUV + 24\um & HI only    & 1.22 & 2.96e-2 & -9.88  & 0.79 & 2.31e-2 & 0.62 & 1.28e-2 & -10.73 \\
+ & FUV + 24\um & Total gas  & 0.81 & 1.59e-2 & -10.06 & 0.42 & 1.14e-2  & 0.52 & 2.06e-1  & -10.69 \\
  \hline
@@
 
-Figures ~\ref{fig:fit,params,fir} and ~\ref{fig:fit,params,fuv} show results of the fitting parameters for SFR(TIR) and SFR(FUV+24\um) in three different regions.
+Table ~\ref{table:res} shows results of the fitting parameters for SFR(TIR) and SFR(FUV+24\um) in three different regions.
 In case of Total gas for the K-S law, there is a sublinear retaliation between SFR and gas mass, in global case and all regions.This result is significatly lower than results from \cite{Ford13}.
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=162mm]{fir_res2.png}
-\caption{Fitting parameters for SFR(TIR) }
-\label{fig:fir,params,fir}
-\end{figure*}
+% \begin{figure*}
+% \centering
+% \includegraphics[width=162mm]{fir_res2.png}
+% \caption{Fitting parameters for SFR(TIR) }
+% \label{fig:fit,params,fir}
+% \end{figure*}
 
-\begin{figure*}
-\centering
-\includegraphics[width=162mm]{fuv_res.png}
-\caption{Fitting parameters for SFR(FUV + 24\um ) }
-\label{fig:fir,params,fuv}
-\end{figure*}
+% \begin{figure*}
+% \centering
+% \includegraphics[width=162mm]{fuv_res.png}
+% \caption{Fitting parameters for SFR(FUV + 24\um ) }
+% \label{fig:fit,params,fuv}
+% \end{figure*}
 

### 2015-03-04 draft3.tex
changing in discussion and correct for refs.

@@
 \documentclass[useAMS,usenatbib]{mn2e}
-%\usepackage{geometry}[left=1.5in, right=1in, bottom=1in, top=1in]
 \usepackage{hyperref}
@@
 \usepackage{natbib}
-\bibliographystyle{aas}
+\bibliographystyle{mn2e}
 \usepackage{amsmath}
@@
 \usepackage{caption}
-%\usepackage[caption=false]{subfig}
 \usepackage{subcaption}
@@
 \newcommand \eqnprime {N^\prime}
-\newcommand \Spitzer {{\it Spitzer}}
+\newcommand \Spitzer {{\it Spitzer }}
 \newcommand \Galex {GALEX}
 \newcommand \Herschel {{\it Herschel}}
+\newcommand \aaj {A\&A}
+\newcommand \aarv {A\&ARv}%: Astronomy and Astrophysics Review (the)
+\newcommand \aas{A\&AS}%: Astronomy and Astrophysics Supplement Series
+\newcommand \afz {Afz}%: Astrofizika
+\newcommand \aj {AJ}%: Astronomical Journal (the)
+\newcommand \apss {Ap\&SS}%: Astrophysics and Space Science
+\newcommand \apj {ApJ}
+\newcommand \apjs {ApJS}%: Astrophysical Journal Supplement Series (the)
+\newcommand \araa {ARA\&A} %: Annual Review of Astronomy and Astrophysics
+\newcommand \asp {ASP Conf. Ser.}%: Astronomy Society of the Pacific Conference Series
+\newcommand \azh {Azh}%: Astronomicheskij Zhurnal
+\newcommand \baas {BAAS}%: Bulletin of the American Astronomical Society
+\newcommand \mem {Mem. RAS}%: Memoirs of the Royal Astronomical Society
+\newcommand \mnassa {MNASSA}%: Monthly Notes of the Astronomical Society of Southern Africa
+\newcommand \mnras {MNRAS} %: Monthly Notices of the Royal Astronomical Society
+%\newcommand {Nature}%(do not abbreviate)
+\newcommand \pasj {PASJ}%: Publications of the Astronomical Society of Japan
+\newcommand \pasp {PASP}%: Publications of the Astronomical Society of the Pacific
+\newcommand \qjras {QJRAS}%: Quarterly Journal of the Royal Astronomical Society
+\newcommand \mex {Rev. Mex. Astron. Astrofis.}%: Revista Mexicana de Astronomia y Astrofisica
+%\newcommand {Science }%}%(do not abbreviate)
+\newcommand \sva {SvA}%: Soviet Astronomy
+\newcommand \aap {APP} %:American Academy of Pediatrics
+\newcommand \apjl {ApJL} %:The Astrophysical Journal Letters
 \begin{document}
@@
 \begin{abstract} % it is just my GESF2014 abstract, just for looks I will change it at the end
- We investigate the relation between star formation rate (SFR), gas surface density (\sigmagas) and stellar surface density (\sigmastar) in the Andromeda galaxy (M31) using the Kennicutt-Schmidt (K-S) law and the extended Schmidt law.
-Shi et al.
-argued that the surface density of SFR is related not only to gas mass, as in the empirical K-S law,  but also to stellar mass surface density, in the ``extended Schmidt law''.
+ We investigate the relation between star formation rate (SFR), gas surface density (\sigmagas) and stellar surface density (\sigmastar) in the Andromeda galaxy (M31) using the Kennicutt-Schmidt (K-S) law and the extended Schmidt law \cite{Shi11} argued that the surface density of SFR is related not only to gas mass, as in the empirical K-S law,  but also to stellar mass surface density, in the ``extended Schmidt law''.
 Using all a combination of \halpha and 24 \um emission, a combination of FUV and 24 \um, and the total infrared emission, we estimate the total SFR in M31 to be between 0.35 M$_{\odot}$yr$^{-1}$ - 0.4 M$_{\odot}$yr$^{-1}$.
@@
 \nprime and $\beta$ are the power law indexes.
-Testing new relation on 60 galaxies \nprime and $\beta$ were calculated to be $\sim$ 1.4 and $\sim$ 0.6 respectively.
-They showed that this relation not only predicts SFR as well as the KS law for galaxies and spatially resolved regions ($\sim$1 kpc sizes) where the KS law works, but also is acceptable for low surface brightness galaxies and regions where the KS law fails.
+\cite{Shi11} calculated power indexes are $\eqnprime = 1.13 \pm 0.05$ and $\beta = 0.36\pm0.04$ in a global case.
+By testing this relation on sub-kiloparces resolution regions on 12 spiral galaxies, they showed that the extended Schmidt law predicts SFR as well as the K-S law for spatially resolved regions ($\sim$1 kpc sizes).
+They demonstrated the power indexes for the local regions are $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$.
+They concluded that this law is acceptable for low surface brightness galaxies and regions where the KS law fails.
 
@@
 \cite{Kennicutt98b} calibrated luminosity of galaxies as a way of measuring the SFR in specific wavelengths using relations between the SFR per unit mass or per unit luminosity and the integrated colour of the system provided by synthesis models  \citep[e.g.,][]{Bruzual93}.
-Afterward many other studies tried to find the similar calibration for measuring the SFR of galaxies in other bands \citep[e.g.,][]{Kennicutt12, Calzetti12, Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
+Afterward many other studies tried to find the similar calibration for measuring the SFR of galaxies in other bands \citep[e.g.,][]{Kennicutt12, Calzetti13, Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
 \cite{Kennicutt09} and \cite{Hao11} introduced new SFR calibration using a combination of \halpha or FUV and far infrared (FIR) emission, respectively.
@@
 Therefore, for producing the map of the total gas in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He.
-Another way to do the mapping of total gas mass of the galaxy is to assum that the ratio of total gas mass and dust mass is the same across a galaxy, and convert dust observations to the map of total gas.
+Another way to do the mapping of total gas mass of the galaxy is to assume that the ratio of total gas mass and dust mass is the same across a galaxy, and convert dust observations to the map of total gas.
 $\S4$ is about the calculation of the gas surface density for the Andromeda galaxy.
@@
 the galaxy with different physical situations (e.g. metallicity, surface brightness and etc.). All these parameters make the Andromeda a suitable test bed for studying the scaling law.
-%PB: Give a little more detail in the followin sentence
+%PB: Give a little more detail in the following sentence
 
@@
 %Different groups, using different SFR or gas mass tracers, applied the K-S law on the M31 and have very different power indexes.
-In the most recent work on the K-S law in M31, \cite{Ford13}, test this law on six regions from centre of the galaxy using three different ISM maps (H2 only, total gas calculated from H2 plus HI maps, and total gas calculated from dust emission).
+In the most recent work on the K-S law in M31, \cite{Ford13}, test this law on six regions from centre of the galaxy using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus HI maps, and total gas calculated from dust emission).
 The power indexes they measure for each map and each regions vary between 0.6 to 2.03.
@@
 It is not obvious what makes these difference in the power law indexes calculated by different group.
-Whether it depends to distance from galaxy, metalicity, gas tracers, SFR tracers, fitting methods, or this is because of the K-S law does not work on the M31 at all.
+Whether it depends to distance from galaxy, metallicity, gas tracers, SFR tracers, fitting methods, or this is because of the K-S law does not work on the M31 at all.
 If we assume the last case is valid, testing extended Schmidt law on the Andromeda galaxy would help to solve the problem with these controversial results.
@@
 2.6~mm & 23\arcsec & IRAM 30-m & \cite{Nieten06}\\
-21~m & 60\arcsec \times \ 90\arcsec & DRAO & \cite{Chemin09}\\
+21~m & 60\arcsec $\times$ \ 90\arcsec & DRAO & \cite{Chemin09}\\
 \hline
@@
 \halpha maps, which were obtained from NOAO science archive are available in 10 overlapping fields.
-We created a Mosaic image of the maps using Montage \citep{Montage}.
+We created a Mosaic image of the maps using Montage.
 Assuming that all stars have the same fraction of \halpha light in their spectra, we subtracted the R band emission from the \halpha using averaged scaling factor between R band images and \halpha provided by \cite{Azimlu11}.
 We also took masked map of stars from \cite{Azimlu11} and masked all point sources (Figure~\ref{fig:halpha}).
-Details of making the making \halpha map can be find in the Appendix ~\ref{appendix: halpha}.
+Details of making the making \halpha map can be find in the Appendix ~\ref{app:halpha}.
 
@@
 Calculation of the SFR using TIR emission needs maps of the m31 in 8, 24, 70, and 160 \um.
-IRAC 8, MIPS 24, MIPS 70 bands were used to calculate TIR emission, but due to better quality and resolution of $Herschel$s$'$data, PACS (Photodetector Array Camera and Spectrometer) \citep{Poglitch10} were used.
+IRAC 8, MIPS 24, MIPS 70 bands were used to calculate TIR emission, but due to better quality and resolution of $Herschel$s$'$data, PACS (Photodetector Array Camera and Spectrometer) \citep{Poglitsch10} were used.
 PACS 160\um observation of the Andromeda galaxy alongside of PACS 100 \um band and three (250 \um, 350\um and 500 \um) SPIRE (Spectral and photometric Imaging Receiver) \citep{Griffin10} bands are covered $\sim 5\degr.5 \times 2\degr.5$ regions \citep{Fritz12}.
@@
 Emission from $^{12}$CO(J:$1\rightarrow0$) line which, was observed on-the-fly with the IRAM 30-m telescope\citep{Nieten06} was used to calculate the H$_2$ column density of interstellar medium.
-This map coveres $2\degr \times 0\degr.5$ that has best resolution available (FWHM = $23\arcsec$) but smallest coverage of halo of the galaxy among our maps.
-In this project we used data of the 21 cm emission from the atomic gas (HI) in the M31 from \cite{chemin9}.
+This map covers $2\degr \times 0\degr.5$ that has best resolution available (FWHM = $23\arcsec$) but smallest coverage of halo of the galaxy among our maps.
+In this project we used data of the 21 cm emission from the atomic gas (HI) in the M31 from \cite{Chemin09}.
 They used Synthesis telescope and the 26 m antenna at the Dominion Radio Astrophysical Observatory to map HI emission in 21cm band of the M31.
-
-\begin{figure*}
- {\vfil  \includegraphics[width=164mm]{halpha_copy.eps}
-  \caption{Mosaic created using Montage programme from 6 fields of \halpha emission maps of m31 from \citpe{Massey07}.
-Result from Montage was continuum subtracted and masked out all point sources.
-Centre of galaxy was masked out due to saturation of data in R-band image.\label{fig:halpha}}
- \vfil}
-\end{figure*}
 
@@
 Since peak of the emission of massive and young stars (O - B and A type) are in the UV, this wavelength is one of the most common used star formation rate indicators \citep[e.g.,][]{Kennicutt89}.
-The UV indicates star forming region with age of $\sim 100$ Myr \citep[e.g.,][]{Kennicutt98, Calzetti05}.
+The UV indicates star forming region with age of $\sim 100$ Myr \citep[e.g.,][]{Kennicutt98a, Calzetti05}.
 However, downside of only using the FUV light as a tracer of star forming region is that this emission is really sensitive to dust extinction.
@@
 We also masked the same region in the galaxy for 24\um map.
-Using this method, we calculated the total SFR is 0.31\pm 0.04 M$_{\odot}$yr$^{-1}$.
-
-%----------------------------------------------------------------------------------------
-\subsection{\halpha plus 24\um Star Formation Rate}
-\label{sec:sfr_halpha}
-
-The SFR can be calculated using combination of \halpha and \Spitzer  24\um maps.
-\halpha emission of galaxies is dominated by light emitted from young and massive stars.
-Star formation time scaled traced by this emission is $\sim 6-10$ Myr \citep[e.g.,][]{Kennicutt09, Calzetti12}.
-Therefore \halpha alone could be used to calibrate the SFR \citep[e.g.,][]{Osterbrock06, Kennicutt09}.
-However, \halpha emission is very sensitive to dust extinction,too.
-Therefore, combination of the \halpha and 24\um of is considerable choice for calculating the SFR.
-we used calibration introduced by \cite{Kennicutt09} to measure the SFR:
-\begin{equation}
-\label{equ: halphaplus24_g}
-SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.020L(24\mu m)]
-\end{equation}
-where L(H${\alpha}$)$_{obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the unit of erg/s.
-L(24$\mu$m) is the $24\mu$m IR luminosity in erg/s, and SFR is in M$_{\odot}$yr$^{-1}$.
-It was indicated that the formulation above can only be used at global situation (i.e.
-total SFR).
-
-\cite{Calzetti07} introduced a new calibration using the same bands in case of local regions (figure ~\ref{fig:sfr_halpha}):
-\begin{equation}
-\label{equ: halphaplus24_l}
-SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.033L(24\mu m)]
-\end{equation}
-units here are the same as equation~\ref{equ: halphaplus24_g}.
-Equation~\ref{equ: halphaplus24_l} is useful for regions less than $\sim 1$ kpc.
-According to  \cite{Calzetti07} calibration constant in equations ~\ref{equ: halphaplus24_g} and ~\ref{equ: halphaplus24_l} can be different by changing an IMF.
-Changes in the IMF mostly affect on calibration based on \halpha luminosity, mostly because significant amount of the ionising photons comes from the stars more massive than $\sim 20$M$\sun$.
-Changing the calibration constant would change the total SFR by a factor of 1.5.
-In this paper we used \cite{Kroupa01} IMF with upper mass limit of 100M$\sun$.
-Total SFR calculated from equation~\ref{equ: halphaplus24_g} is 0.35 \pm 0.01 M$\sun$yr$^{-1}$, which is in good agreement with previous studies.
-%PB: can you put uncertainties on the total SFR numbers?
-
-\subsection{Total Infrared Star Formation Rate}
-\label{sec:sfr_fir}
-Total infrared emission of a system, can also be used as a tracer of the SFR.
-Dust absorbs radiation from hot and young stars and re-emitt it in infrared wavelength, however there is no one-to-one mapping between IR and UV emission \citep{Calzeti12}, therefore, integrating over full wavelength range of the IR part and calculating the TIR luminosity is better tracer of the SFR instead of the IR single-band emission.
-\cite{Calzetti07} assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{star}(bol) = L(TIR)$ and calibrated the TIR luminosity of a system to calculate the SFR for a stellar population undergoing constant star formation over $\tau = 100$ Myr:
-
-\begin{equation}
-\label{equ:sfr_fir}
-SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR)
-\end{equation}
-where SFR(TIR) and L(TIR), star formation rate calculated from TIR emission and TIR luminosity are in M$_{\odot}$yr$^{-1}$ and erg/s respectively.
-
-IR luminosity can be measured from integration of IR part of a spectral energy distribution (SED) of a galaxy or combining photometry datas in different IR wavelengths.
-For second approach \cite{Draine07} modelled \Spitzer data and calibrated IR single-band photometry data to calculate the TIR luminosity.
-\cite{Boquien10} tested and modified this calibration as:
-\begin{equation}
- \label{equ: TIR}
-L(\rm TIR) = 0.95L(8) + 1.15L(24) + L(70) + L(160)
-\end{equation}
-where L(8 \um),L(24 \um), L(70 \um) and L(160\um) are luminosities of galaxy in 8 \um, 24 \um, 70 \um and 160 \um in unit of erg/s.
-We used equation ~\ref{equ:sfr_fir} to calculate second map of SFR of M31 (figure ~\ref{fig:sfr_fir_small}).
-Using this method we calculated the total SFR 0.40 \pm 0.04 M$_{\odot}$yr$^{-1}$.
-Table ~\ref{table:sfr} compares total SFR from literature and current work.
-
-\begin{table*}
-\begin{minipage}{100mm}
-\caption{Comparison of Total Star Formation Rate of M31}
-\label{table:sfr}
-\begin{tabular}{@{}lcc}
-\hline\hline
-Ref.&Method&SFR(M$_{\odot}$yr$^{-1}$) \\
-\hline
-Current work&FUV and 24\um&0.31\\
-Current work&\halpha and 24\um&0.35\\
-Current work&TIR luminosity&0.4\\
-\cite{Ford13}&FUV and 24\um&0.25\\
-\cite{Ford13}&TIR luminosity&0.48-0.52\\
-\cite{Azimlu11}& \halpha and 24\um&0.34\\
-\cite{Azimlu11}&Extinction corrected \halpha&0.44\\
-\cite{Tabatabaei10}&Extinction corrected \halpha&0.27-0.38\\
-\cite{Barmby06}&Infrared 8\um luminosity& 0.4\\
-\hline
-\end{tabular}
-\end{minipage}
-\end{table*}
+Using this method, we calculated the total SFR is 0.31$\pm$ 0.04 M$_{\odot}$yr$^{-1}$.
 
@@
 \end{figure*}
+
+%----------------------------------------------------------------------------------------
+\subsection{\halpha plus 24\um Star Formation Rate}
+\label{sec:sfr_halpha}
+
+The SFR can be calculated using combination of \halpha and \Spitzer  24\um maps.
+\halpha emission of galaxies is dominated by light emitted from young and massive stars.
+Star formation time scaled traced by this emission is $\sim 6-10$ Myr \citep[e.g.,][]{Kennicutt09, Calzetti13}.
+Therefore \halpha alone could be used to calibrate the SFR \citep[e.g.,][]{Osterbrock06, Kennicutt09}.
+However, \halpha emission is very sensitive to dust extinction, too.
+Therefore, combination of the \halpha and 24\um of is considerable choice for calculating the SFR.
+we used calibration introduced by \cite{Kennicutt09} to measure the SFR:
+\begin{equation}
+\label{equ: halphaplus24_g}
+SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.020L(24\mu m)]
+\end{equation}
+where L(H${\alpha}$)$_{obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the unit of erg/s.
+L(24$\mu$m) is the $24\mu$m IR luminosity in erg/s, and SFR is in M$_{\odot}$yr$^{-1}$.
+It was indicated that the formulation above can only be used at global situation (i.e.
+total SFR).
+
+\cite{Calzetti07} introduced a new calibration using the same bands in case of local regions (figure ~\ref{fig:sfr_halpha}):
+\begin{equation}
+\label{equ: halphaplus24_l}
+SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.033L(24\mu m)]
+\end{equation}
+units here are the same as equation~\ref{equ: halphaplus24_g}.
+Equation~\ref{equ: halphaplus24_l} is useful for regions less than $\sim 1$ kpc.
+According to  \cite{Calzetti07} calibration constant in equations ~\ref{equ: halphaplus24_g} and ~\ref{equ: halphaplus24_l} can be different by changing an IMF.
+Changes in the IMF mostly affect on calibration based on \halpha luminosity, mostly because significant amount of the ionizing photons comes from the stars more massive than $\sim 20$M$\sun$.
+Changing the calibration constant would change the total SFR by a factor of 1.5.
+In this paper we used \cite{Kroupa01} IMF with upper mass limit of 100M$\sun$.
+Total SFR calculated from equation~\ref{equ: halphaplus24_g} is 0.35 $\pm$ 0.01 M$\sun$yr$^{-1}$, which is in good agreement with previous studies.
+%PB: can you put uncertainties on the total SFR numbers?
+
+\subsection{Total Infrared Star Formation Rate}
+\label{sec:sfr_fir}
+Total infrared emission of a system, can also be used as a tracer of the SFR.
+Dust absorbs radiation from hot and young stars and re-emit it in infrared wavelength, however there is no one-to-one mapping between IR and UV emission \citep{Calzetti13}, therefore, integrating over full wavelength range of the IR part and calculating the TIR luminosity is better tracer of the SFR instead of the IR single-band emission.
+\cite{Calzetti07} assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{star}(bol) = L(TIR)$ and calibrated the TIR luminosity of a system to calculate the SFR for a stellar population undergoing constant star formation over $\tau = 100$ Myr:
+
+\begin{equation}
+\label{equ:sfr_fir}
+SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR)
+\end{equation}
+where SFR(TIR) and L(TIR), star formation rate calculated from TIR emission and TIR luminosity are in M$_{\odot}$yr$^{-1}$ and erg/s respectively.
+
+IR luminosity can be measured from integration of IR part of a spectral energy distribution (SED) of a galaxy or combining photometry data in different IR wavelengths.
+For second approach \cite{Draine07} modeled \Spitzer data and calibrated IR single-band photometry data to calculate the TIR luminosity.
+\cite{Boquien10} tested and modified this calibration as:
+\begin{equation}
+ \label{equ: TIR}
+L(\rm TIR) = 0.95L(8) + 1.15L(24) + L(70) + L(160)
+\end{equation}
+where L(8 \um),L(24 \um), L(70 \um) and L(160\um) are luminosities of galaxy in 8 \um, 24 \um, 70 \um and 160 \um in unit of erg/s.
+We used equation ~\ref{equ:sfr_fir} to calculate second map of SFR of M31 (figure ~\ref{fig:sfr,fir}).
+Using this method we calculated the total SFR 0.40 $\pm$ 0.04 M$_{\odot}$yr$^{-1}$.
+Table ~\ref{table:sfr} compares total SFR from literature and current work.
+
+\begin{table*}
+\begin{minipage}{100mm}
+\caption{Comparison of Total Star Formation Rate of M31}
+\label{table:sfr}
+\begin{tabular}{@{}lcc}
+\hline\hline
+Ref.&Method&SFR(M$_{\odot}$yr$^{-1}$) \\
+\hline
+Current work&FUV and 24\um&0.31\\
+Current work&\halpha and 24\um&0.35\\
+Current work&TIR luminosity&0.4\\
+\cite{Ford13}&FUV and 24\um&0.25\\
+\cite{Ford13}&TIR luminosity&0.48-0.52\\
+\cite{Azimlu11}& \halpha and 24\um&0.34\\
+\cite{Azimlu11}&Extinction corrected \halpha&0.44\\
+\cite{Tabatabaei10}&Extinction corrected \halpha&0.27-0.38\\
+\cite{Barmby06}&Infrared 8\um luminosity& 0.4\\
+\hline
+\end{tabular}
+\end{minipage}
+\end{table*}
+
 %----------------------------------------------------------------------------------------
@@
 Different groups are working on the various galaxies to measure the X-factor for each \citep{Wilson95, Bosselli02, Bolato13}..
-In case of M31, different values of X-factor ($1-5.6 \times 10^{20}$) were adopted in the previous studies \citep[e.g.][]{Ford13, Bolato13, Leroy11, Bolato08, Nieten06, Sofue94, Strong88}; however, since any constant differences in X-factor leads to horizontal changes in a plot of log(SFR) versus Log($\Sigma_{\rm {gas}}$), and does not affect our K-S law power index for molecular gas,  we chose $X_{\rm {CO}}= 2 \times 10^{20}$  the same as many other works \citep[e.g.][]{Ford13, Smith12}.
+In case of M31, different values of X-factor ($1-5.6 \times 10^{20}$) were adopted in the previous studies \citep[e.g.][]{Ford13, Bolato13, Leroy11, Bolato08, Nieten06}; however, since any constant differences in X-factor leads to horizontal changes in a plot of log(SFR) versus Log($\Sigma_{\rm {gas}}$), and does not affect our K-S law power index for molecular gas,  we chose $X_{\rm {CO}}= 2 \times 10^{20}$  the same as many other works \citep[e.g.][]{Ford13, Smith12}.
 This assumption might have some effect on the total gas mass but considering the fact that HI mass dominates H$_2$ mass in M31 this effect is small.
@@
 \section{Stellar Mass}
-\label{starmass}
+\label{sec:starmass}
+\begin{figure*}
+\centering
+\includegraphics[width=164mm]{star.eps}
+\caption{Stellar Mass surface density. This mass is produced using $IRAC$ 3.6 $\mu$ m data and its calibration presented in equation ~\ref{equ:eskew}}
+\label{fig:stellarmass}
+\end{figure*}
+
 Stellar mass can be measured using a suitable calibration between flux/luminosity of stars in specific wavelengths and stellar mass.
@@
 Using this method we calculated the total stellar mass of galaxy is $6.9 \times 10^{10}$M$_{\odot}$ with 6$\%$ uncertainty.
-This result is in fair agreement with the result from \cite{Tamm2012}.
+This result is in fair agreement with the result from \cite{Tamm12}.
 They calculated that stellar mass in the M31 is $(10-15) \times 10^{10}$M$_{\odot}$, 56$\%$ which is in the disk and the rest is in the bulge of the galaxy.
 %PB: need to compare with other results, as you did with SFR.
-\begin{figure*}
-\centering
-\includegraphics[width=164mm]{star.eps}
-\caption{Stellar Mass surface density. This mass is produced using $IRAC$ 3.6 $\mu$ m data and its calibration presented in equation ~\ref{equ:eskew}}
-\label{fig:stellarmass}
-\end{figure*}
 
@@
 \subsection{Fitting method}
-\label{sec:fittinhg}
+\label{sec:fitting}
 %For investigating and comparing the SFR laws in M31
 %Given available
+\begin{figure*}
+\centering
+\includegraphics[width=164mm]{ks_all_f.png}
+\caption{The result from fitting the Kennicutt-Schmidt law on data from whole galaxy using pixel by pixel method.
+Plots have a different pixel size.
+Each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents regions $~$ Kpc and points in plots with surface density of HI or total gas mass, represents region in $~$Kpc.}
+\label{fig:ks,all}
+\end{figure*}
+
 Producing the SFR, gas mass and stellar mass maps, provides of with enough data to examine and compare the K-S law and the extended Schmidt law.% are possible. 
@@
 Our final results are divided by two sets of different pixel sizes.
-That's because the H2 gass mass map has better resolution and lower pixel size of the  HI gas mass map.
-Consequently, any plots with surface density of H2 as a tracer of the gas mass, have more data points.%in whole galaxy as well as comparing the laws in three different regions of galaxy based on their distance from the centre of the galaxy.
+That's because the H$_2$ gas mass map has better resolution and lower pixel size of the  HI gas mass map.
+Consequently, any plots with surface density of H$_2$ as a tracer of the gas mass, have more data points.%in whole galaxy as well as comparing the laws in three different regions of galaxy based on their distance from the centre of the galaxy.
 We can re-write equations ~\ref{equ:ks_org} and ~\ref{equ:es_org} in a logarithmic scale. Hence, we would have two linear equations, as following:
 
-\begin{figure*}
-\centering
-\includegraphics[width=164mm]{ks_all_1.png}
-\caption{The result from fitting the Kennicutt-Schmidt law on data from whole galaxy using pixel by pixel method.
-Plots have a different pixel size.
-Each point in the plots with the surface density of H2 as a tracer of gas mass represents regions $~$ Kpc and points in plots with surface density of HI or total gas mass, represeents region in $~$Kpc.}
-\label{fig:ks,all}
-\end{figure*}
-
 \begin{subequations}
-\begin{align}
-\left%\{ \begin{array}{l l}
-\label{eq:sfr_law_log}
-\log_{10} \eqsigmasfr = N~\log_{10} \eqsigmagas + A, \\
-\log_{10} \eqsigmasfr = \eqnprime~\log_{10} \eqsigmagas + \beta~\log_{10}\eqsigmastar  + A^\prime ~~~,
-\end{align}
+\begin{equation}
+\label{eq:sfr_law_ks_log}
+\log_{10} \eqsigmasfr = N~\log_{10} \eqsigmagas + A
+\end{equation}
+\begin{equation}
+\label{eq:sfr_law_es_log}
+\log_{10} \eqsigmasfr = \eqnprime~\log_{10} \eqsigmagas + \beta~\log_{10}\eqsigmastar  + A^\prime
+\end{equation}
 \end{subequations}
@@
 For the extended Schmidt law, we expended the code in the way that instead of using simple linear regression, which is the case of the K-S law, it uses multiple linear regression.
-In this case, we were able to examine the effect of the stellar mass in the SFR as shown in equation ~\ref{eq:sfr_law_log}.
+In this case, we were able to examine the effect of the stellar mass in the SFR as shown in equation ~\ref{eq:sfr_law_es_log}.
 
 We also test each laws on three different regions.
-The regions were chosen the same as regions introduced in \cite{Drain14}.
+The regions were chosen the same as regions introduced in \cite{Draine14}.
 They found that across the galaxy, with increasing distance from the centre of galaxy dust/H ratio declines monotonically.
@@
 Applying the SFR laws in these regions, provides a tool to consider the effect of the distance from the centre of galaxy on SFR laws as well as the effect of the metallicity on those.
-Tables ~\ref{table:sfr_law_all} through ~\ref{table:sfr_law_25} show fitting parameters and their uncertainties for whole galaxy and each different regions.
+Table ~\ref{table:res} shows fitting parameters and their uncertainties for whole galaxy and each different regions.
 \halpha data dose not have a smooth background.
@@
 In total, we produced 72 different plots which, show either the K-S law or the extended Schmidt law, both in whole galaxy and in different distances from the centre of the M31.
-Additionally we can use these results to see if there is any correlation  between the SFR laws and the metallicity, as it was decribed in ~\ref{sec:fittinng}.
+Additionally we can use these results to see if there is any correlation  between the SFR laws and the metallicity, as it was described in ~\ref{sec:fitting}.
 
@@
 
-Figure ~\ref{fig:ks,tot} shows the pixel by pixel fitting of the K-S law on the whole galaxy.
-First row plots are the surface density of the SFR(TIR), which is calculated using  the TIR emission form section ~\ref{sec:sfr_fir}, versus the gas surface density traced by only the molecular gas (H$_2$),  only atomic gas (HI), and total gas from right to left, respectivly.
+\begin{figure*}
+\includegraphics[width=164mm]{c3d_all_ks_regs_f.png}
+\caption{same as figure ~\ref{fig:ks,all}, but in this figure we separated pixels from different regions in galaxy by their colours.
+The regions with R less than 8$\kpc$, $8\kpc < $R $< 18\kpc$, and $18\kpc <$ R $\la 25\kpc$ are shown in red, green and blue, respectively.}
+\label{fig:ks,regs}
+\end{figure*}
+
+Figure ~\ref{fig:ks,all} shows the pixel by pixel fitting of the K-S law on the whole galaxy.
+First row plots are the surface density of the SFR(TIR), which is calculated using  the TIR emission form section ~\ref{sec:sfr_fir}, versus the gas surface density traced by only the molecular gas (H$_2$),  only atomic gas (HI), and total gas from right to left, respectively.
 The only difference between the upper and lower plots is that in lower row the SFR indicators is the FUV plus 24\um emission.
@@
 The regions with R less than 8$\kpc$, $8\kpc < $R $< 18\kpc$, and $18\kpc <$ R $\la 25\kpc$ are shown in red, green and blue, respectively.
-
-\begin{figure*}
-\includegraphics[width=164mm]{c3d_all_ks_regs_1.png}
-\caption{same as figure ~\ref{fig:ks,all}, but in this figure we separated pixels from different regions in galaxy by their colours.
-The regions with R less than 8$\kpc$, $8\kpc < $R $< 18\kpc$, and $18\kpc <$ R $\la 25\kpc$ are shown in red, green and blue, respectively.}
-\label{fig:ks,regs}
-\end{figure*}
 
@@
 Shadows of our data on each surface are also plotted, to have a more clear picture of correlations between components .
-For a comparison, one cane asily conclude that shadows on a X-Y surface is a reproduction of K-S law.
-Colours used in plots ~\ref{fig:es,regs,fir,h2} to ~\ref{fig:es,regs,fuv,tot} are the same as colours in  ~\ref{fig:ks,regs}.
+For a comparison, one can easily conclude that shadows on a X-Y surface is a reproduction of K-S law.
+Colours used in plots ~\ref{fig:es,regs,fir,tot} to ~\ref{fig:es,regs,fuv,tot} are the same as colours in  ~\ref{fig:ks,regs}.
 
@@
 Plots have a different pixel size.
-Each point in the plots with the surface density of H2 as a tracer of gas mass represents regions $\sim$30~Kpc and points in plots with surface density of HI or total gas mass, represents region in $\sim$155~Kpc.}
+Each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents regions $\sim$30~Kpc and points in plots with surface density of HI or total gas mass, represents region in $\sim$155~Kpc.}
     \label{fig:es,all}
 \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \includegraphics[width=162mm]{c3d_fir_h2.png}
-% \caption{Fitting result from the SFR(TIR) vs H$_{2}$.}
-% \label{fig:es,regs,fir,h2}
-% \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \includegraphics[width=162mm]{c3d_fuv_h2.png}
-% \caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs H$_{2}$.}
-% \label{fig:es,regs,fuv,h2}
-% \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \includegraphics[width=162mm]{c3d_fir_hi.png}
-% \caption{Fitting result from the SFR(TIR) vs HI.}
-% \label{fig:es,regs,fir,hi}
-% \end{figure*}
-
-% \begin{figure*}
-% \centering
-% \includegraphics[width=162mm]{c3d_fuv_hi.png}
-% \caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs HI.}
-% \label{fig:es,regs,fuv,hi}
-% \end{figure*}
 
@@
 \label{table:res}
-\begin{tabular}{||cc||cccrcccccr}
+\begin{tabular}{cccccrccccrr}
 \hline\hline
-\multicolumn{1}{||c||}{\multirow{1}{*}{Region}} & SFR Tracer& Gas Tracer & N & $\sigma_N$ & A & \nprime & $\sigma_{\eqnprime}$ & $\beta$ & $\sigma_\beta$ & A$^\prime$& \\
+\multicolumn{1}{c}{\multirow{1}{*}{Region}} & SFR Tracer& Gas Tracer & N & $\sigma_N$ & A & \nprime & $\sigma_{\eqnprime}$ & $\beta$ & $\sigma_\beta$ & A$^\prime$& \\
 \hline
-\multicolumn{1}{||c||}{\multirow{6}{*}{Global case}} & TIR & H$_2$ only & 1.03 & 9.47e-3  & -8.92  & 0.95 & 9.77e-3 & 0.34 & 4.25e-3 & -9.57  \\
+\multicolumn{1}{c}{\multirow{6}{*}{Global case}} & TIR & H$_2$ only & 1.03 & 9.47e-3  & $-8.92$  & 0.95 & 9.77e-3 & 0.34 & 4.25e-3 & $-9.57$  \\
  & TIR         & HI only    & 1.15 & 1.47e-2 & $-9.63$  & 0.77 & 8.84e-3 & 0.75 & 4.58e-3 & $-10.71$ \\
@@
 \hline
-\multicolumn{1}{||c||}{\multirow{6}{*}{R$< 8\kpc$}}& TIR & H$_2$ only & 0.96 & 1.48e-2 & -8.95  & 0.88 & 1.49e-2 & 0.30 & 6.11e-3 & -9.54  \\
- & TIR         & HI only    & 1.52 & 7.73e-2  & -9.91  & 1.00 & 7.27e-2  & 0.60 & 4.22e-2  & -10.60 \\
- & TIR         & Total gas  & 1.00 & 3.51e-2  & -10.04 & 0.63 & 3.47e-2  & 0.53 & 7.57e-2  & -10.63 \\
- & FUV + 24\um & H$_2$ only & 1.04 & 1.84e-2 & -9.29  & 1.00 & 1.85e-2 & 0.18 & 7.17e-3 & -9.64  \\
- & FUV + 24\um & HI only    & 1.28 & 4.73e-2  & -10.00 & 0.93 & 5.68e-2  & 0.42 & 3.81e-2  & -10.50 \\
- & FUV + 24\um & Total gas  & 0.88 & 2.59e-2  & -10.12 & 0.75 & 3.53e-2  & 0.16 & 3.93e-2  & -10.28 \\
+\multicolumn{1}{c}{\multirow{6}{*}{R$< 8\kpc$}}& TIR & H$_2$ only & 0.96 & 1.48e-2 & $-8.95$  & 0.88 & 1.49e-2 & 0.30 & 6.11e-3 & $-9.54$  \\
+ & TIR         & HI only    & 1.52 & 7.73e-2  & $-9.91$ & 1.00 & 7.27e-2  & 0.60 & 4.22e-2  & $-10.60$ \\
+ & TIR         & Total gas  & 1.00 & 3.51e-2  & $-10.04$ & 0.63 & 3.47e-2  & 0.53 & 7.57e-2  & $-10.63$ \\
+ & FUV + 24\um & H$_2$ only & 1.04 & 1.84e-2 & $-9.29$  & 1.00 & 1.85e-2 & 0.18 & 7.17e-3 & $-9.64$  \\
+ & FUV + 24\um & HI only    & 1.28 & 4.73e-2  & $-10.00$ & 0.93 & 5.68e-2  & 0.42 & 3.81e-2  & $-10.50$ \\
+ & FUV + 24\um & Total gas  & 0.88 & 2.59e-2  & $-10.12$ & 0.75 & 3.53e-2  & 0.16 & 3.93e-2  & $-10.28$ \\
 \hline
-\multicolumn{1}{||c||}{\multirow{6}{*}{$8\kpc < $R $< 18\kpc$}} & TIR & H$_2$ only & 1.08 & 1.26e-2 & -8.90  & 1.00 & 1.29e-2 & 0.40 & 5.74e-3 & -9.66  \\
- & TIR         & HI only    & 1.09 & 4.50e-2 & -9.54  & 0.77 & 2.52e-2  & 0.75 & 1.26e-2  & -10.71 \\
- & TIR         & Total gas  & 0.75 & 1.76e-2  & -9.81  & 0.47 & 1.18e-2  & 0.55 & 1.24e-2  & -10.53 \\
- & FUV + 24\um & H$_2$ only & 1.21 & 1.53e-2 & -9.27  & 1.15 & 1.57e-2 & 0.33 & 6.57e-3 & -9.89  \\
- & FUV + 24\um & HI only    & 1.18 & 2.89e-2 & -9.81  & 0.81 & 2.08e-2 & 0.61 & 1.12e-2 & -10.73 \\
- & FUV + 24\um & Total gas  & 0.71 & 1.34e-2 & -9.81  & 0.44 & 1.18e-2  & 0.45 & 1.28e-2  & -10.58 \\
+\multicolumn{1}{c}{\multirow{6}{*}{$8\kpc < $R $< 18\kpc$}} & TIR & H$_2$ only & 1.08 & 1.26e-2 & $-8.90$  & 1.00 & 1.29e-2 & 0.40 & 5.74e-3 & $-9.66$  \\
+ & TIR         & HI only    & 1.09 & 4.50e-2 & $-9.54$  & 0.77 & 2.52e-2  & 0.75 & 1.26e-2  & $-10.71$ \\
+ & TIR         & Total gas  & 0.75 & 1.76e-2  & $-9.81$  & 0.47 & 1.18e-2  & 0.55 & 1.24e-2  & $-10.53$ \\
+ & FUV + 24\um & H$_2$ only & 1.21 & 1.53e-2 & $-9.27$  & 1.15 & 1.57e-2 & 0.33 & 6.57e-3 & $-9.89$  \\
+ & FUV + 24\um & HI only    & 1.18 & 2.89e-2 & $-9.81$  & 0.81 & 2.08e-2 & 0.61 & 1.12e-2 & $-10.73$ \\
+ & FUV + 24\um & Total gas  & 0.71 & 1.34e-2 & $-9.81$  & 0.44 & 1.18e-2  & 0.45 & 1.28e-2  & $-10.58$ \\
 \hline
-\multicolumn{1}{||c||}{\multirow{6}{*}{$18\kpc <$ R $\la 25\kpc$}}  & TIR & H$_2$ only & 1.57 & 2.63e-1  & -8.80  & 0.97 & 2.00e-1  & 1.19 & 1.01e-1  & -10.94 \\
- & TIR         & HI only    & 1.17 & 4.67e-2 & -9.65  & 0.76 & 2.82e-2 & 0.75 & 1.48e-2 & -10.72 \\
- & TIR         & Total gas  & 0.84 & 2.06e-2  & -9.85  & 0.52 & 1.45e-2  & 0.56 & 1.42e-2  & -10.56 \\
- & FUV + 24\um & H$_2$ only & 1.87 & 3.03e-1  & -9.15  & 1.33 & 2.95e-1  & 1.38 & 1.12e-1  & -11.65 \\
- & FUV + 24\um & HI only    & 1.22 & 2.96e-2 & -9.88  & 0.79 & 2.31e-2 & 0.62 & 1.28e-2 & -10.73 \\
- & FUV + 24\um & Total gas  & 0.81 & 1.59e-2 & -10.06 & 0.42 & 1.14e-2  & 0.52 & 2.06e-1  & -10.69 \\
+\multicolumn{1}{c}{\multirow{6}{*}{$18\kpc <$ R $\la 25\kpc$}}  & TIR & H$_2$ only & 1.57 & 2.63e-1  & $-8.80$  & 0.97 & 2.00e-1  & 1.19 & 1.01e-1  & $-10.94$ \\
+ & TIR         & HI only    & 1.17 & 4.67e-2 & $-9.65$  & 0.76 & 2.82e-2 & 0.75 & 1.48e-2 & $-10.72$ \\
+ & TIR         & Total gas  & 0.84 & 2.06e-2  & $-9.85$  & 0.52 & 1.45e-2  & 0.56 & 1.42e-2  & $-10.56$ \\
+ & FUV + 24\um & H$_2$ only & 1.87 & 3.03e-1  & $-9.15$  & 1.33 & 2.95e-1  & 1.38 & 1.12e-1  & $-11.65$ \\
+ & FUV + 24\um & HI only    & 1.22 & 2.96e-2 & $-9.88$  & 0.79 & 2.31e-2 & 0.62 & 1.28e-2 & $-10.73$ \\
+ & FUV + 24\um & Total gas  & 0.81 & 1.59e-2 & $-10.06$ & 0.42 & 1.14e-2  & 0.52 & 2.06e-1  & $-10.69$\\
  \hline
@@
 \end{table*}
-
 %----------------------------------------------------------------------------------------
@@
 
-Table ~\ref{table:res} shows results of the fitting parameters for SFR(TIR) and SFR(FUV+24\um) in three different regions.
-In case of Total gas for the K-S law, there is a sublinear retaliation between SFR and gas mass, in global case and all regions.This result is significatly lower than results from \cite{Ford13}.
-But it is similar to prediction of the \cite{Shetty13}, which argued that using the hierarchical Bayesian fit leads to power index N lower than other works.
-%PB: more detailed comparison to Ford here: what values did he find, are these significantly different from yours?
-%PB: Also compare to Shetty's results: what did he find for other galaxies and are your results compatible with those?
+Table ~\ref{table:res} shows the results from the hierarchical Bayesian fit.
+Due to the similarity of our results for both SFR(TIR) and SFR(FUV+24$\mu$m) and the fact that they are in close agreement with each other, We only interpret the results from the SFR(FUV+24$\mu$m).
+Results from the SFR(\halpha) fitting are going to discussed in the Appendix ~\ref{app:halpha}.
+%In this section we are going to talk about result from fitting the K-S Law, results from fitting the extended Schmidt law and the comparison between these two star formation laws and which one works better in the M31.
+%SR: Should I keep that or not
 
-However, if we look at the H$_{2}$ gas or HI gas, we could see power indexes are more similar to the initial sugeestion of the K-S law power index, N$ ~ 1.4\pm 0.15 $.
-Moreover, these results are in a good agreement with results from \cite{tabatabyi10}.
-For regions with R less than 8 \kpc, we could see some sublinear values, but it is mostly because H$_2$ is dominant gas in the ISM, and lack of HI gas makes our results very uncertain.
-Moreover, the K-S law power index increases by the distance from the centre of the galaxy.
-This could be an affect of metallicity on the SFR or the consequence of lack of H$_2$ gas on outher regions of the galaxy.
-% PB: I would start this paragraph off with a sentence that says what you find by comparing total gas with H_2 only or HI only: different or not? 
-% PB: when comparing with Tabatabyi, give values from that paper
-% PB: by "lack of HI gas makes our results very uncertain" you mean that the total gas and Hi-only fits are not reliable?
-% PB: not sure I see where the last sentence comes from; may need more detail.
+\subsection{The K-S law in M31}
 
-% \begin{figure*}
-% \centering
-% \includegraphics[width=162mm]{fir_res2.png}
-% \caption{Fitting parameters for SFR(TIR) }
-% \label{fig:fit,params,fir}
-% \end{figure*}
+As mentioned before, the K-S law in the M31 was tested by many groups.
+In the most recent work on M31, \cite{Ford13} investigated the K-S law in six radial annuli and the global case using ordinary least square (OLS)fitting method.
+To make comparisons between our results easier, we averaged the power indexes of annuli which, overlap with out three different regions.
+\cite{Tabatabaei10} also applied the K-S law on the M31 using the OLS fitting method, and have a different result from the \cite{Ford13}.
 
-% \begin{figure*}
-% \centering
-% \includegraphics[width=162mm]{fuv_res.png}
-% \caption{Fitting parameters for SFR(FUV + 24\um ) }
-% \label{fig:fit,params,fuv}
-% \end{figure*}
+Our results for the global case of the K-S law show that using total gas gives a sub-linear relation between the surface density of the SFR and the total gas surface density.
+While, for using the H$_{2}$ only gas or HI only gas we find the super-linear relation.
+These results are different from power indexes estimated by \cite{Ford13}, $N=2.03\pm0.04$ in case of total gas and $N=0.6\pm0.01$ in case of H$_{2}$ only gas.
+\cite{Tabatabaei10} estimated the K-S law $N=1.30\pm0.05$ using the total gas and $N=0.96\pm0.03$ using the H$_{2}$ only gas.
+The reason behind these differences is mostly because of the statical method we chose.The OLS fitting on the H$_{2}$ only gas gives us the power index of $N=0.54\pm0.003$ which is in good agreement with previous results.
 
-On the other hand, from fitting the the extended Schmidt law, we have sublinear relation between SFR and gas surface density in global case and all the regions, execpt for gas surface density traced by H$_2$.
-Besides, for all cases we can see $\beta ~ 0.6$, which is the same as prediction of the \cite{Shi11}.
-For gas traced by H$_2$ in regions with $18\kpc <$ R $\la 25\kpc$, $\beta$ is way higher than this value.
-This is could be a result of the lack of H$_2$ gas in these regions.
-\cite{Kim13} using 3D numirical hydrodynamic simulations showed that in outer disk regions of the galaxy $\eqsigmasfr \propto \eqsigmagas \pho_{sd}^0.5$ where \pho$_{sd}$ is the midplane density of the stellar disk.
-our results for total gas in regions with $18\kpc <$ R $\la 25\kpc$ shows $\log_{10}(\eqsigmasfr) \propto 0.5 \times \log_{10}(\eqsigmastar)$, which is the same as simulations.
-However, in this case we found a sublinear relation between \sigmasfr and \sigmagas while \cite{Kim13} found a linear relation.
+ \cite{Bigiel08} argued that there is no universal relation ship between surface density of the total gas and the SFR.
+They also showed that the SFR and the molecular hydrogen have a linear relationship.
+Furthermore, \cite{Shetty13} used the same data as \cite{Bigiel08} and argued that using the hierarchical Bayesian fit leads to significant galaxy-by-galaxy variation between power indexes and all of them are lower than \cite{Bigiel08}.
+
+The sub-linear power index in the case of the total gas surface density suggests that the star formation efficiency (surface density of SFR per surface density of gas, SFE) is decreasing by increasing the total gas.
+Consequently, the depletion time increases by increasing the total gas.
+On the contrary, the super-linear relation suggests that the depletion time is decreasing by increasing the amount of the CO or/ and HI gas.
+The further conclusion is more similar to the initial the initial suggestion of the K-S law.
+However, the question stills unanswered that, why for both H$_2$ gas and HI gas we have a super-linear relation while, for the total gas surface density we have sub linear relation?
+%what dose suppress the SFR?
+I could not find any reason.
+Do you have any idea about these questions?
+
+The results from the hierarchical Bayesian fitting on the regions with different distances from the centre of the galaxy give us similar values to the global case.
+For all three regions, the K-S law using the total gas leads to sub-linear relation between the SFR and the surface density of the total gas.
+Likewise, for using the H$_{2}$ only gas or HI only gas, this relationship is either linear or super-linear.
+The K-S law power index is vary by the distance of the galaxy.
+Considering molecular gas, the power law index is increasing by going to further distances of the centre of galaxy.
+This trend also can be seen in the \cite{Ford13}.
+For the atomic gas only or the total gas this trend cannot be seen.
+This could be the result of the fact that, the atomic gas in the centre of the galaxy is less than the other regions in galaxy.
+The increasing of power index in this case may be an effect of the decreasing metallicity across the galaxy, or another physical properties of the galaxy such as stellar mass (see section ~\ref{sec:es_res})
+
+\subsection{The extended Schmidt law in M31}
+\label{sec:es_res}
+The extended Schmidt law is a recently proposed law \citep{Shi11}, which shows a tight correlation between the SFR and the total gas surface density and the surface density of the stellar mass.
+Results of the fitting the extended Schmidt law in a global case gives us a sub-linear relation between the SFR and the density of stars.
+Results from the fitting the extended Schmidt law using the molecular gas only are $\eqnprime = 1.09$ and $\beta = 0.25$ which is the close to the original suggestion of the extended Schmidt law in the global case, $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$.
+Although, the original results were from using the total gas surface density instead of the molecular gas only.
+Our results from the fitting the total gas surface density gives us a lower power index of the gas mass and a higher power index of the stellar mass.This relation suggests that, although increasing the total gas cause to decrease the SFE but the existing stars will increase the SFE.
+
+ The fitting results on the regions with different distances from the centre of galaxy are more similar to result from \cite{Shi11}.
+Taking average of our three regions leads us to the conclusion that using molecular gas only or atomic gas only $\beta$ is 0.60 and 0.55 which is very close to prediction of \cite{Shi11}.
+In the local case, the same as global case power indexes calculated using total gas surface density, are much smaller than the original suggestion of \cite{Shi11}.
+
+ \cite{Kim13} using 3D numerical hydrodynamic simulations showed that in outer disk regions of the galaxy $\eqsigmasfr \propto \eqsigmagas \pho_{sd}^{0.5}$ where \pho$_{sd}$ is the mid-plane density of the stellar disk.
+Our results for total gas in regions with 18kpc$<$ R $\la 25$ kpc shows $log_{10}(\eqsigmasfr) \propto 0.5 \times log_{10}(\eqsigmastar)$, which is the same as simulations.
+However, in this case we found a sub-linear relation between \sigmasfr and \sigmagas while \cite{Kim13} found a linear relation.
+
 %----------------------------------------------------------------------------------------
@@
 \section{Summery}
+
+%----------------------------------------------------------------------------------------
+%Acknowledgment 
+%----------------------------------------------------------------------------------------
+\section*{Acknowledgment}
+This research made use of Montage, funded by the National Aeronautics and Space Administration's Earth Science Technology Office, Computation Technologies Project, under Cooperative Agreement Number NCC5-626 between NASA and the California Institute of Technology.
+Montage is maintained by the NASA/IPAC Infrared Science Archive.
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
+\newpage
 \bibliography{ref.bib}
 
+%----------------------------------------------------------------------------------------
+%Appendix
+%----------------------------------------------------------------------------------------
+
+\appendix
+\section{SFR from H$\alpha$ plus 24 $\mu$m produces and result}
+\label{app:halpha}
+\begin{figure*}
+\includegraphics[width=164mm]{halpha_copy.eps}
+\caption{Mosaic created using Montage programme from 6 fields of \halpha emission maps of m31 from \citpe{Massey07}.
+Result from Montage was continuum subtracted and masked out all point sources.
+Centre of galaxy was masked out due to saturation of data in R-band image.}
+\label{fig:halpha}
+\end{figure*}
+
 \end{document}

### 2015-03-06 draft3.tex
With pbarmby's comments on discussion section.

@@
 \documentclass[useAMS,usenatbib]{mn2e}
+%\usepackage{geometry}[left=1.5in, right=1in, bottom=1in, top=1in]
 \usepackage{hyperref}
@@
 %PB: agreed with not making it too long, but do start with a sentence about why SF is important.
+Understanding the processes that go into the formation and evolution of stars and stellar systems is crucial in the study of the chemical composition and structure formation of the universe.
+Stars are also central to the formation of planetary systems and are where the ingredients for life were formed.
+The energy provided by stars is necessary to maintain the life on planets.
+The study of the formation and evolution of the Sun, and more generally that of stars, would help us understand more about our origin and the future of our Solar System.
+This is one of the main reasons that the study of stellar structure and evolution has been a central topic in astronomy and astrophysics for decades.
 
-Empirical star formation laws (relations) has been investigated for more than 50 years, and results never been precise.
+In order to completely understand the formation and evolution of galaxies from the early universe to the current epoch, the knowledge of the formation of stars is necessary.
+Star formation determines the structure and evolution of galaxies, by transforming the gas into stars.
+Moreover, the knowledge of star formation is essential to understanding the origin of planetary systems.
+The physical process of star formation is naturally complex.
+Therefore, the basis for a theory of star formation requires a strong foundation of empirical data or observations.
+
+Empirical star formation laws (relations) has been investigated for more than 50 years, and the results never been precise.
 Formation of stars is a complicated process.
@@
 \end{equation}
-which is often referred to as the Kennicutt-Schmidt (K-S) law, where \sigmasfr is surface density of star formation, and \sigmagas is the surface density of gas in a galaxy.
+which is often referred to as the Kennicutt-Schmidt (K-S) law, where \sigmasfr is the surface density of star formation, and \sigmagas is the surface density of gas in a galaxy.
 
@@
 %He could not find any correlation between SFR and HI only clouds, but the correlation with the molecular cloud was about the same as the total gas.
-It should be noted that the KS law can not be applied for the whole range of gas densities.
+It should be noted that the KS law cannot be applied to the whole range of gas densities.
 In parallel studies, the star formation threshold was introduced and it was pointed out that calculated SFR is much lower than the value predicted by the KS law at low gas densities $( < 1-10\sim$ M$_{\odot}$ pc$^{-2})$ e.g.
@@
 %P2: SFR, measuring, scaling, ...
-For testing any of these star formation laws, first thing one should do is calculating the SFR.
+For testing any of these star formation laws, the first thing one should do is calcule the SFR.
 Many groups are working to find a translation from the light of star forming regions in galaxies to a rate of the formation of new stars.
 \cite{Kennicutt98b} calibrated luminosity of galaxies as a way of measuring the SFR in specific wavelengths using relations between the SFR per unit mass or per unit luminosity and the integrated colour of the system provided by synthesis models  \citep[e.g.,][]{Bruzual93}.
-Afterward many other studies tried to find the similar calibration for measuring the SFR of galaxies in other bands \citep[e.g.,][]{Kennicutt12, Calzetti13, Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
+Afterward, many other studies tried to find the similar calibration for measuring the SFR of galaxies in other bands \citep[e.g.,][]{Kennicutt12, Calzetti13, Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
 \cite{Kennicutt09} and \cite{Hao11} introduced new SFR calibration using a combination of \halpha or FUV and far infrared (FIR) emission, respectively.
@@
 
-One of the methods to calculate stellar mass within a galaxy, is based on stellar population models \citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, like luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations.
+One of the methods to calculate the stellar mass within a galaxy, is based on stellar population models \citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, like luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations.
 Having two independent methods to measure stellar mass helps to compare the results and check whether there are any systematic differences.
-Comparing the results from measuring stellar mass in stellar clusters shows there is no huge difference.
+Comparing the results from measuring the stellar mass in stellar clusters shows there is no huge difference.
 Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few x10 percent, so one should be more careful to model subtleties \citep{McLaughlin05}.
-Calculating stellar mass in the Andromeda galaxy is described in  $\S5$ .
+Calculating stellar mass in the Andromeda galaxy is described in $\S5$.
 
 %P5(2*): What we did and why Andromeda and
-In this paper we present our results from testing and comparing of both the K-S law and the Extended Schmidt law on the Andromeda galaxy (M31).
+In this paper, we present our results from testing and comparing both the K-S law and the Extended Schmidt law on the Andromeda galaxy (M31).
 %We used three different gas maps and SFR maps, to identify if any of these laws work better with specific gas mass or SFR tracer.
-Additionally, We applied these laws on three different regions on the M31, to determine whether there is any dependence to a distance from the centre of galaxy or not.
+Additionally, We applied these laws on three different regions on the M31, to determine whether there is any dependence to a distance from the centre of the galaxy or not.
 Since, M31 is the closest spiral galaxy to the Milky Way, therefore, we can have higher resolution images of it than we have of any other spiral galaxy.
-Having high resolution images provides us data from different regions within
-the galaxy with different physical situations (e.g. metallicity, surface brightness and etc.). All these parameters make the Andromeda a suitable test bed for studying the scaling law.
+Having high resolution images provides us data from different regions within the galaxy with different physical situations (e.g.
+metallicity, surface brightness and etc.).
+All these parameters make the Andromeda a suitable test bed for studying the scaling law.
 %PB: Give a little more detail in the following sentence
@@
 %Different groups, using different SFR or gas mass tracers, applied the K-S law on the M31 and have very different power indexes.
-In the most recent work on the K-S law in M31, \cite{Ford13}, test this law on six regions from centre of the galaxy using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus HI maps, and total gas calculated from dust emission).
-The power indexes they measure for each map and each regions vary between 0.6 to 2.03.
+In the most recent work of the K-S law in M31, \cite{Ford13}, test this law on six regions from the centre of the galaxy using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus HI maps, and total gas calculated from dust emission).
+The power indexes they measure for each map and each region vary between 0.6 to 2.03.
 The origin of these contrary results is still ongoing question.
-It is not obvious what makes these difference in the power law indexes calculated by different group.
+It is not obvious what makes these differences in the power law indexes calculated by different groups.
 Whether it depends to distance from galaxy, metallicity, gas tracers, SFR tracers, fitting methods, or this is because of the K-S law does not work on the M31 at all.
@@
 Since the M31 is the closest spiral galaxy to the Milky Way, it was aimed by many probes and telescopes, both space based and ground based ones.
-Therefore, variety of data from X-ray to radio wavelengths are available.
-Wide ranges of data provides us the ability to measure all the required parameters to test the star formation laws in M31.
+Therefore, a variety of data from X-ray to radio wavelengths are available.
+Wide ranges of data provide us the ability to measure all the required parameters to test the star formation laws in M31.
 Table~\ref{table:data} lists all the data we used in this paper.
 Each data comes with different Full Width Half Maximum (FWHM), spacial resolution and grids.
-In order to make sure that all our data contains the same amount of information, we smoothed them using Aniano's Kernels' library and convolution code \citep{Aniano12}, to highest resolution available.
+In order to make sure that all our data contains the same amount of information, we smoothed them using Aniano's Kernels' library and convolution code \citep{Aniano12}, to the highest resolution available.
 Moreover, considering Nyquist relation \citep{Nyquist}, we re-sampled and re-gridded all our maps to have a proper pixel size.
 
-\begin{table}
+\begin{table*}
+\centering
 \caption{Data used in this study.}
@@
 \end{tabular}
-\end{table}
+\end{table*}
 
@@
 One of the calibrations, which was used to calculate SFR, uses FUV emission as a tracer of the star forming regions.
-FUV emission of M31 was observed by Galaxy Evolution Explorer ($GALEX$; \citep{Martin05}).
+FUV emission of M31 was observed by the Galaxy Evolution Explorer ($GALEX$; \citep{Martin05}).
 $GALEX$ telescope data contains information for two bands, FUV:1350-1750 and NUV:1750-2750~\AA, with FWHM of 4\arcsec .5, and 6 \arcsec.
@@
 Our other method to calculate the SFR was using a combination of \halpha emission and 24\um emission.
-\cite{Massey06, Massey07} mapped UBVRI and \halpha emission line of M31 as part of the Nearby Galaxies Survey using KPNO telescope.
-\halpha maps, which were obtained from NOAO science archive are available in 10 overlapping fields.
+\cite{Massey06, Massey07} mapped UBVRI and \halpha emission line of M31 as part of the Nearby Galaxies Survey using the KPNO telescope.
+\halpha maps, which were obtained from the NOAO science archive are available in 10 overlapping fields.
 We created a Mosaic image of the maps using Montage.
 Assuming that all stars have the same fraction of \halpha light in their spectra, we subtracted the R band emission from the \halpha using averaged scaling factor between R band images and \halpha provided by \cite{Azimlu11}.
-We also took masked map of stars from \cite{Azimlu11} and masked all point sources (Figure~\ref{fig:halpha}).
-Details of making the making \halpha map can be find in the Appendix ~\ref{app:halpha}.
+We also took masked map of stars from \cite{Azimlu11} and masked all point sources (Figure ~\ref{fig:halpha}).
+Details about making the making \halpha map can be found in the Appendix ~\ref{app:halpha}.
 
 \subsection{IR and sub mm Data}
-In IR and sub mm bands both $Spitzer$ \citep{Wener04} and $Herschel$ \citep{Pilbratt10}  space telescopes observed the M31.
+In IR and sub mm bands, both $Spitzer$ \citep{Wener04} and $Herschel$ \citep{Pilbratt10}  space telescopes observed the M31.
 The Infrared Array Camera (IRAC; \citep{Fazio04}) on the $Spitzer$ is a camera observing at four channels (3.6, 4.5, 5.8, and 8 \um).
-IRAC observation of M31 were obtained by \cite{Barmby06}, which covered $3\degr.7 \times 1\degr.6$.
+IRAC observations of the M31 were obtained by \cite{Barmby06}, which covered $3\degr.7 \times 1\degr.6$.
 IRAC 3.6 and 4.5\um bands  were used to calculate the stellar mass.
@@
 \subsection{Radio Emission}
-Emission from $^{12}$CO(J:$1\rightarrow0$) line which, was observed on-the-fly with the IRAM 30-m telescope\citep{Nieten06} was used to calculate the H$_2$ column density of interstellar medium.
-This map covers $2\degr \times 0\degr.5$ that has best resolution available (FWHM = $23\arcsec$) but smallest coverage of halo of the galaxy among our maps.
+Emission from $^{12}$CO(J:$1\rightarrow0$) line which, was observed on-the-fly with the IRAM 30-m telescope\citep{Nieten06} was used to calculate the H$_2$ column density of the interstellar medium.
+This map covers $2\degr \times 0\degr.5$ that has the best resolution available (FWHM = $23\arcsec$) but smallest coverage of the halo of the galaxy among our maps.
 In this project we used data of the 21 cm emission from the atomic gas (HI) in the M31 from \cite{Chemin09}.
@@
 This emission is sensitive to star formation time scale of $\la10$ Myr \citep{Calzetti07}.
-The FUV band of \Galex and the 24\um band of \Spitzer ~ data was used to measure the SFR calibrated by \cite{Hao11} as follow:
+The FUV band of \Galex and the 24\um band of \Spitzer ~ data was used to measure the SFR calibrated by \cite{Hao11} as:
 \begin{equation}
@@
 \end{equation}
-where unit of SFR is M$_{\odot}$yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{obs}$ are in erg/s.
+where a unit of SFR is M$_{\odot}$yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{obs}$ are in erg/s.
 L(FUV)$_{obs}$ is the luminosity of galaxy in the FUV emission.
 The index of obs is shown to indicate that the FUV emission is not corrected for effect of extinction.
-Nevertheless, this emission is corrected for the foreground stars emission.
+Nevertheless, this emission is corrected for the foreground stars' emission.
 To do so, we followed a method introduced by \cite{Leroy08}.
@@
 However, \halpha emission is very sensitive to dust extinction, too.
-Therefore, combination of the \halpha and 24\um of is considerable choice for calculating the SFR.
-we used calibration introduced by \cite{Kennicutt09} to measure the SFR:
+Therefore, the combination of the \halpha and 24\um of is considerable choice for calculating the SFR.
+we used a calibration introduced by \cite{Kennicutt09} to measure the SFR:
 \begin{equation}
@@
 L(24$\mu$m) is the $24\mu$m IR luminosity in erg/s, and SFR is in M$_{\odot}$yr$^{-1}$.
-It was indicated that the formulation above can only be used at global situation (i.e.
+It was indicated that the formulation above can only be used at the global situation (i.e.
 total SFR).
@@
 \end{equation}
-units here are the same as equation~\ref{equ: halphaplus24_g}.
+the units here are the same as equation~\ref{equ: halphaplus24_g}.
 Equation~\ref{equ: halphaplus24_l} is useful for regions less than $\sim 1$ kpc.
 According to  \cite{Calzetti07} calibration constant in equations ~\ref{equ: halphaplus24_g} and ~\ref{equ: halphaplus24_l} can be different by changing an IMF.
-Changes in the IMF mostly affect on calibration based on \halpha luminosity, mostly because significant amount of the ionizing photons comes from the stars more massive than $\sim 20$M$\sun$.
+Changes in the IMF mostly affect on calibration based on \halpha luminosity, mostly because a significant amount of the ionizing photons comes from the stars more massive than $\sim 20$M$\sun$.
 Changing the calibration constant would change the total SFR by a factor of 1.5.
-In this paper we used \cite{Kroupa01} IMF with upper mass limit of 100M$\sun$.
+In this paper, we used \cite{Kroupa01} IMF with an upper mass limit of 100M$\sun$.
 Total SFR calculated from equation~\ref{equ: halphaplus24_g} is 0.35 $\pm$ 0.01 M$\sun$yr$^{-1}$, which is in good agreement with previous studies.
@@
 \label{sec:sfr_fir}
-Total infrared emission of a system, can also be used as a tracer of the SFR.
-Dust absorbs radiation from hot and young stars and re-emit it in infrared wavelength, however there is no one-to-one mapping between IR and UV emission \citep{Calzetti13}, therefore, integrating over full wavelength range of the IR part and calculating the TIR luminosity is better tracer of the SFR instead of the IR single-band emission.
+The total infrared emission of a system, can also be used as a tracer of the SFR.
+Dust absorbs radiation from hot and young stars and re-emit it in infrared wavelengths, however, there is no one-to-one mapping between IR and UV emission \citep{Calzetti13}, therefore, integrating over full wavelength range of the IR part and calculating the TIR luminosity is a better tracer of the SFR instead of the IR single-band emission.
 \cite{Calzetti07} assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{star}(bol) = L(TIR)$ and calibrated the TIR luminosity of a system to calculate the SFR for a stellar population undergoing constant star formation over $\tau = 100$ Myr:
@@
 
-IR luminosity can be measured from integration of IR part of a spectral energy distribution (SED) of a galaxy or combining photometry data in different IR wavelengths.
+IR luminosity can be measured from the integration of the IR part of a spectral energy distribution (SED) of a galaxy or combining photometry data in different IR wavelengths.
 For second approach \cite{Draine07} modeled \Spitzer data and calibrated IR single-band photometry data to calculate the TIR luminosity.
@@
 \end{equation}
-where L(8 \um),L(24 \um), L(70 \um) and L(160\um) are luminosities of galaxy in 8 \um, 24 \um, 70 \um and 160 \um in unit of erg/s.
-We used equation ~\ref{equ:sfr_fir} to calculate second map of SFR of M31 (figure ~\ref{fig:sfr,fir}).
+where L(8 \um),L(24 \um), L(70 \um) and L(160\um) are luminosities of the galaxy in 8 \um, 24 \um, 70 \um and 160 \um in unit of erg/s.
+We used equation ~\ref{equ:sfr_fir} to calculate second map of the SFR of M31 (figure ~\ref{fig:sfr,fir}).
 Using this method we calculated the total SFR 0.40 $\pm$ 0.04 M$_{\odot}$yr$^{-1}$.
-Table ~\ref{table:sfr} compares total SFR from literature and current work.
+Table ~\ref{table:sfr} compares the total SFR from literature and current work.
 
@@
 Higher rotational transition of CO can be used as a tracer as well, but they are not as common as the $J(1\rightarrow 0)$.
-The relation between CO emission and H$_2$ cloud mass is shown as
+The relation between CO emission and H$_2$ cloud mass is shown as:
 
@@
 where X$_{CO}$ is the conversion factor (also known as the X-factor).
-X-factor could be different in regions within a galaxy due to difference in metallicity.
-Though assuming constant conversion factor for cases such as M82 and M31 can lead to global molecular gas mass estimates that are very accurate,  but in regions with low metallicity there are uncertainties.
-Different groups are working on the various galaxies to measure the X-factor for each \citep{Wilson95, Bosselli02, Bolato13}..
+The X-factor could be different in regions within a galaxy due to difference in metallicity.
+Though assuming a constant conversion factor in cases such as M82 and M31 can lead to global molecular gas mass estimates that are very accurate,  but in regions with a low metallicity, there are uncertainties.
+Different groups are working on the various galaxies to measure the X-factor for each \citep{Wilson95, Bosselli02, Bolato13}.
 In case of M31, different values of X-factor ($1-5.6 \times 10^{20}$) were adopted in the previous studies \citep[e.g.][]{Ford13, Bolato13, Leroy11, Bolato08, Nieten06}; however, since any constant differences in X-factor leads to horizontal changes in a plot of log(SFR) versus Log($\Sigma_{\rm {gas}}$), and does not affect our K-S law power index for molecular gas,  we chose $X_{\rm {CO}}= 2 \times 10^{20}$  the same as many other works \citep[e.g.][]{Ford13, Smith12}.
-This assumption might have some effect on the total gas mass but considering the fact that HI mass dominates H$_2$ mass in M31 this effect is small.
+This assumption might have some effect on the total gas mass, but considering the fact that HI mass dominates H$_2$ mass in M31 this effect is small.
 The total gas mass was calculated from:
@@
 \end{equation}
-where  factor of 1.36 is a constant to consider He and the other heavier elements effect on mass, M$_{HI}$ is mass of neutral hydrogen obtained from 21cm observations and M$_{H_2}$ is from equation ~\ref{equ:conversion} in unit of M$\sun$.
+where  factor of 1.36 is a constant to consider He and the other heavier elements effect on mass, M$_{HI}$ is a mass of neutral hydrogen obtained from 21cm observations and M$_{H_2}$ is from equation ~\ref{equ:conversion} in unit of M$\sun$.
 
@@
 We calculated the stellar mass within the M31 using calibration of the 3.6\um flux by \cite{Eskew12}.
-Since 3.6\um flux is almost insensitive to the emission from young stellar population, dust absorption and emission, this band-pass was used for the calibration of the stellar mass.
-By using data from the large Magellanic cloud, they find an empirical relation between stellar mass and luminosity of stars as following:
+Since 3.6\um flux is almost insensitive to the emission from the young stellar population, dust absorption and emission, this band-pass was used for the calibration of the stellar mass.
+By using data from the large Magellanic cloud, they find an empirical relation between stellar mass and luminosity of stars as:
 
@@
 \end{equation}
-
 where M$_{\star}$ is the stellar mass in mass of The Sun, $F_{3.6}$ is the 3.6\um flux in $Jy$ , and D in the distance of the galaxy in Mpc.
 Figure ~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6\um.
-Using this method we calculated the total stellar mass of galaxy is $6.9 \times 10^{10}$M$_{\odot}$ with 6$\%$ uncertainty.
+Using this method we calculated the total stellar mass of the galaxy is $6.9 \times 10^{10}$M$_{\odot}$ with 6$\%$ uncertainty.
 This result is in fair agreement with the result from \cite{Tamm12}.
@@
 
-Producing the SFR, gas mass and stellar mass maps, provides of with enough data to examine and compare the K-S law and the extended Schmidt law.% are possible. 
+Producing the SFR, gas mass and stellar mass maps, provides of with enough data to examine and compare the K-S law and the extended Schmidt law. % are possible. 
 We investigated the K-S law and the extended Schmidt law by using  pixel by pixel method.
@@
 Consequently, any plots with surface density of H$_2$ as a tracer of the gas mass, have more data points.%in whole galaxy as well as comparing the laws in three different regions of galaxy based on their distance from the centre of the galaxy.
-We can re-write equations ~\ref{equ:ks_org} and ~\ref{equ:es_org} in a logarithmic scale. Hence, we would have two linear equations, as following:
+We can re-write equations ~\ref{equ:ks_org} and ~\ref{equ:es_org} in a logarithmic scale. Hence, we would have two linear equations, as:
 
@@
 \end{subequations}
-where, N, $\eqnprime$, $\beta$, A, and A$^\prime$ are free parameters of fittings. Units in equation above, are the same as the units in the equations ~\ref{equ:ks_org} and ~\ref{equ:es_org}.
+where, N, $\eqnprime$, $\beta$, A, and A$^\prime$ are free parameters of fittings. Units in the equation above, are the same as the units in the equations ~\ref{equ:ks_org} and ~\ref{equ:es_org}.
 
 We found the free parameters by applying the hierarchical Bayesian linear regression method as described in \cite{Shetty13}.
-Shetty and his colleagues used a Bayesian linear regression approached to develop a new method to find the K-S law parameters, considering the measurements uncertainties as well as hierarchical data structure.
+Shetty and his colleagues used a Bayesian linear regression approached to develop a new method to find the K-S law parameters, considering the measurement uncertainties as well as hierarchical data structure.
 For the K-S law's fitting parameters, we used a 'R' code provided by Shetty's group.
@@
 
-Applying the SFR laws in these regions, provides a tool to consider the effect of the distance from the centre of galaxy on SFR laws as well as the effect of the metallicity on those.
-Table ~\ref{table:res} shows fitting parameters and their uncertainties for whole galaxy and each different regions.
-\halpha data dose not have a smooth background.
-Also centre of galaxy in this dta is diffused, so we do not have any data from centre of the M31.
+Applying the SFR laws in these regions, provides a tool to consider the effect of the distance from the centre of the galaxy on SFR laws as well as the effect of the metallicity on those.
+Table ~\ref{table:res} shows fitting parameters and their uncertainties for the whole galaxy and each different regions.
+\halpha data does not have a smooth background.
+Also the centre of galaxy in this data is diffused, so we do not have any data from the centre of the M31.
 Since it was the only available \halpha data from the M31, We used this data anyway.
-However, results from the \halpha SFR map are not shown here and will be discuss in appendix ~\ref{app:halpha}.
+However, results from the \halpha SFR map are not shown here and will be discussed in appendix ~\ref{app:halpha}.
 %can I make it foot note?
@@
 \subsection{Star formation laws}
-In total, we produced 72 different plots which, show either the K-S law or the extended Schmidt law, both in whole galaxy and in different distances from the centre of the M31.
-Additionally we can use these results to see if there is any correlation  between the SFR laws and the metallicity, as it was described in ~\ref{sec:fitting}.
+In total, we produced 72 different plots, which show either the K-S law or the extended Schmidt law, both in whole galaxy and in different distances from the centre of the M31.
+Additionally, we can use these results to see if there is any correlation  between the SFR laws and the metallicity, as it was described in ~\ref{sec:fitting}.
 
@@
 \includegraphics[width=164mm]{c3d_all_ks_regs_f.png}
-\caption{same as figure ~\ref{fig:ks,all}, but in this figure we separated pixels from different regions in galaxy by their colours.
+\caption{Same as figure ~\ref{fig:ks,all}, but in this figure we separated pixels from different regions in the galaxy by their colours.
 The regions with R less than 8$\kpc$, $8\kpc < $R $< 18\kpc$, and $18\kpc <$ R $\la 25\kpc$ are shown in red, green and blue, respectively.}
@@
 
+%SR: Should I talk SFR(TIR) or SFR (TIR)?!!!
+%PB: no space, so SFR(TIR)
+
 Figure ~\ref{fig:ks,all} shows the pixel by pixel fitting of the K-S law on the whole galaxy.
 First row plots are the surface density of the SFR(TIR), which is calculated using  the TIR emission form section ~\ref{sec:sfr_fir}, versus the gas surface density traced by only the molecular gas (H$_2$),  only atomic gas (HI), and total gas from right to left, respectively.
-The only difference between the upper and lower plots is that in lower row the SFR indicators is the FUV plus 24\um emission.
+The only difference between the upper and lower plots is that in the lower row the SFR indicator is the FUV plus 24\um emission.
 Figure ~\ref{fig:ks,regs} is the same as figure ~\ref{fig:ks,all}.
-However, in this figure we separated pixels from different regions in galaxy by their colours.
+However, in this figure we separated pixels from different regions in the galaxy by their colours.
 The regions with R less than 8$\kpc$, $8\kpc < $R $< 18\kpc$, and $18\kpc <$ R $\la 25\kpc$ are shown in red, green and blue, respectively.
@@
 In these series of plots, X-axis is the gas mass  surface density, either molecular gas (H$_2$), the atomic gas (HI) or the total gas, Y-axis is the SFR(TIR) or SFR(FUV + 24 $\mu$m), and Z-axis is the stellar mass surface density.
-Shadows of our data on each surface are also plotted, to have a more clear picture of correlations between components .
-For a comparison, one can easily conclude that shadows on a X-Y surface is a reproduction of K-S law.
+Shadows of our data on each surface are also plotted, to have a more clear picture of correlations between components.
+For a comparison, one can easily conclude that shadows on the X-Y surface is a reproduction of the K-S law.
 Colours used in plots ~\ref{fig:es,regs,fir,tot} to ~\ref{fig:es,regs,fuv,tot} are the same as colours in  ~\ref{fig:ks,regs}.
-
-%We did the same for the extended Schmidt law including stellar mass map to our other maps (fig.
-~\ref{fig:es-law}), results are listed in table ~\ref{table:sf-laws_pix} and table ~\ref{table:sf-laws_cat} .
 
@@
         \centering
-        \includegraphics[width=\textwidth]{es_tot_fuv_vs_h2.png}
-        \caption{SFR,FUV+24\um vs surface density of H$_2$}
-        \label{fig:es,all,fuv,h2}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.3\textwidth}
         \includegraphics[width=\textwidth]{es_tot_fir_vs_hi.png}
@@
         \label{fig:es,all,fir,hi}
-    \end{subfigure}
-     \centering
-    \begin{subfigure}[b]{0.3\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{es_tot_fuv_vs_hi.png}
-        \caption{SFR,FUV+24\um vs surface density of HI}
-        \label{fig:es,all,fuv,hi}
     \end{subfigure}
@@
         \centering
+        \includegraphics[width=\textwidth]{es_tot_fuv_vs_h2.png}
+        \caption{SFR,FUV+24\um vs surface density of H$_2$}
+        \label{fig:es,all,fuv,h2}
+    \end{subfigure}
+     \hfill
+   \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{es_tot_fuv_vs_hi.png}
+        \caption{SFR,FUV+24\um vs surface density of HI}
+        \label{fig:es,all,fuv,hi}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
         \includegraphics[width=\textwidth]{es_tot_fuv_vs_tot.png}
@@
     \caption{The result from fitting the extended Schmidt law on data from whole galaxy using pixel by pixel method.
-Plots show SFR vs surface density of gas, and z-axis is surface density of the stellar mass.
-Each figure shows different combination of the SFR tracer and gas mass tracer results.
+The plots show the SFR vs surface density of gas, and z-axis is the surface density of the stellar mass.
+Each figure shows different combinations of the SFR tracer and gas mass tracer results.
 Plots have a different pixel size.
@@
 \centering
-\includegraphics[width=162mm]{c3d_fir_tot.png}
+\includegraphics[width=162mm]{c3d_fir_tot_f.png}
 \caption{Fitting result from the SFR(TIR) vs total gas.}
@@
 \centering
-\includegraphics[width=162mm]{c3d_fuv_tot.png}
+\includegraphics[width=162mm]{c3d_fuv_tot_f.png}
 \caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs total gas.}
@@
 
-Table ~\ref{table:res} shows the results from the hierarchical Bayesian fit.
-Due to the similarity of our results for both SFR(TIR) and SFR(FUV+24$\mu$m) and the fact that they are in close agreement with each other, We only interpret the results from the SFR(FUV+24$\mu$m).
-Results from the SFR(\halpha) fitting are going to discussed in the Appendix ~\ref{app:halpha}.
+Table ~\ref{table:res} shows the results of the hierarchical Bayesian fit.
+Due to the similarity of our results for both SFR(TIR) and SFR(FUV+24$\mu$m) and the fact that they are in close agreement with each other,
+%PB: the two parts of the sentence above ("similarity of results" and "in close agreement") seem to say the same thing -- or am I not understanding what you mean here?
+We only interpret the results from the SFR(FUV+24$\mu$m).
+Results from the SFR(H$\alpha$) fitting are going to be discussed in the Appendix ~\ref{app:halpha}.
 %In this section we are going to talk about result from fitting the K-S Law, results from fitting the extended Schmidt law and the comparison between these two star formation laws and which one works better in the M31.
 %SR: Should I keep that or not
+%PB: I don't think you need the "In this section" sentence; the content is clear from the subsection headings.
 
@@
 
-As mentioned before, the K-S law in the M31 was tested by many groups.
-In the most recent work on M31, \cite{Ford13} investigated the K-S law in six radial annuli and the global case using ordinary least square (OLS)fitting method.
-To make comparisons between our results easier, we averaged the power indexes of annuli which, overlap with out three different regions.
-\cite{Tabatabaei10} also applied the K-S law on the M31 using the OLS fitting method, and have a different result from the \cite{Ford13}.
+As mentioned before, the K-S law in the M31 was tested by many groups. %PB: edits made to next sentences. Note that plural of "index" is "indices".
+In the most recent work on M31, \cite{Ford13} investigated the K-S law in six annuli and the global case using the ordinary least squares (OLS) fitting method.
+To make comparisons between our results easier, we averaged the power indices of their annuli which overlap with our three different regions.
+\cite{Tabatabaei10} also applied the K-S law to M31 using the OLS fitting method, and have different results from \cite{Ford13}.
 
@@
 These results are different from power indexes estimated by \cite{Ford13}, $N=2.03\pm0.04$ in case of total gas and $N=0.6\pm0.01$ in case of H$_{2}$ only gas.
-\cite{Tabatabaei10} estimated the K-S law $N=1.30\pm0.05$ using the total gas and $N=0.96\pm0.03$ using the H$_{2}$ only gas.
+\cite{Tabatabaei10} estimated the K-S law power index $N=1.30\pm0.05$ using the total gas and $N=0.96\pm0.03$ using the H$_{2}$ only gas.
 The reason behind these differences is mostly because of the statical method we chose.The OLS fitting on the H$_{2}$ only gas gives us the power index of $N=0.54\pm0.003$ which is in good agreement with previous results.
+%PB: well, 0.54 agrees with 0.6, but it doesn't agree with 0.96. If your
+%uncertainties and theirs are right, 0.54 pm 0.003  is actually in poor agreement 
+% with 0.06 pm 0.01- it's at least 6 standard deviations away.
+% so need to clarify your argument here.
 
- \cite{Bigiel08} argued that there is no universal relation ship between surface density of the total gas and the SFR.
+ \cite{Bigiel08} argued that there is no universal relationship between the surface density of the total gas and the SFR.
 They also showed that the SFR and the molecular hydrogen have a linear relationship.
@@
 Consequently, the depletion time increases by increasing the total gas.
-On the contrary, the super-linear relation suggests that the depletion time is decreasing by increasing the amount of the CO or/ and HI gas.
+On the contrary, the super-linear relation suggests that the depletion time is decreasing with increasing the amount of the CO or/ and HI gas.
 The further conclusion is more similar to the initial the initial suggestion of the K-S law.
-However, the question stills unanswered that, why for both H$_2$ gas and HI gas we have a super-linear relation while, for the total gas surface density we have sub linear relation?
-%what dose suppress the SFR?
-I could not find any reason.
-Do you have any idea about these questions?
+% PB: extra "to the initial" here?
+If we assume that stars form in the molecular clouds, the decreasing of the SFE with increasing the total gas is justifiable.
 
-The results from the hierarchical Bayesian fitting on the regions with different distances from the centre of the galaxy give us similar values to the global case.
+The results of the hierarchical Bayesian fitting on the regions with different distances from the centre of the galaxy give us similar values in the global case.
 For all three regions, the K-S law using the total gas leads to sub-linear relation between the SFR and the surface density of the total gas.
 Likewise, for using the H$_{2}$ only gas or HI only gas, this relationship is either linear or super-linear.
-The K-S law power index is vary by the distance of the galaxy.
-Considering molecular gas, the power law index is increasing by going to further distances of the centre of galaxy.
+The K-S law power index varies with the distance of the galaxy.
+Considering molecular gas, the power law index is increasing by going to further distances from the center of the galaxy.
 This trend also can be seen in the \cite{Ford13}.
 For the atomic gas only or the total gas this trend cannot be seen.
-This could be the result of the fact that, the atomic gas in the centre of the galaxy is less than the other regions in galaxy.
-The increasing of power index in this case may be an effect of the decreasing metallicity across the galaxy, or another physical properties of the galaxy such as stellar mass (see section ~\ref{sec:es_res})
+This could be the result of the fact that, the atomic gas in the center of the galaxy is less than the other regions in the galaxy.
+% PB: I don't quite understand your argument in the previous sentence.
+The increasing of the power index in this case may be an effect of the decreasing metallicity across the galaxy, or other physical properties of the galaxy such as stellar mass (see section ~\ref{sec:es_res}).
 
@@
 \label{sec:es_res}
-The extended Schmidt law is a recently proposed law \citep{Shi11}, which shows a tight correlation between the SFR and the total gas surface density and the surface density of the stellar mass.
-Results of the fitting the extended Schmidt law in a global case gives us a sub-linear relation between the SFR and the density of stars.
-Results from the fitting the extended Schmidt law using the molecular gas only are $\eqnprime = 1.09$ and $\beta = 0.25$ which is the close to the original suggestion of the extended Schmidt law in the global case, $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$.
+The extended Schmidt law has been a recently proposed law \citep{Shi11}, which shows a tight correlation between the SFR and the total gas surface density and the surface density of the stellar mass.
+The results of the fitting the extended Schmidt law in a global case give us a sub-linear relation between the SFR and the density of stars.
+Results from the fitting the extended Schmidt law using the molecular gas only are $\eqnprime = 1.09$ and $\beta = 0.25$ which is close to the original suggestion of the extended Schmidt law in the global case, $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$.
 Although, the original results were from using the total gas surface density instead of the molecular gas only.
 Our results from the fitting the total gas surface density gives us a lower power index of the gas mass and a higher power index of the stellar mass.This relation suggests that, although increasing the total gas cause to decrease the SFE but the existing stars will increase the SFE.
+% PB: as above, not convinced that 1.09 is "close" to 0.8 pm 0.01.
+% and 0.25 is close to 0.6
 
- The fitting results on the regions with different distances from the centre of galaxy are more similar to result from \cite{Shi11}.
-Taking average of our three regions leads us to the conclusion that using molecular gas only or atomic gas only $\beta$ is 0.60 and 0.55 which is very close to prediction of \cite{Shi11}.
+ The fitting results on the regions with different distances from the centre of the galaxy are more similar to the results from \cite{Shi11}.
+Taking the average of our three regions leads us to the conclusion that using molecular gas only or atomic gas only $\beta$ is 0.60 and 0.55 which is very close to prediction of \cite{Shi11}.
 In the local case, the same as global case power indexes calculated using total gas surface density, are much smaller than the original suggestion of \cite{Shi11}.
+% PB: can you explain why this might be?
 
- \cite{Kim13} using 3D numerical hydrodynamic simulations showed that in outer disk regions of the galaxy $\eqsigmasfr \propto \eqsigmagas \pho_{sd}^{0.5}$ where \pho$_{sd}$ is the mid-plane density of the stellar disk.
+ \cite{Kim13} using 3D numerical hydrodynamic simulations showed that in outer disk regions of the galaxy $\eqsigmasfr \propto \eqsigmagas \rho_{sd}^{0.5}$ where $\rho_{sd}$ is the mid-plane density of the stellar disk.
 Our results for total gas in regions with 18kpc$<$ R $\la 25$ kpc shows $log_{10}(\eqsigmasfr) \propto 0.5 \times log_{10}(\eqsigmastar)$, which is the same as simulations.
 However, in this case we found a sub-linear relation between \sigmasfr and \sigmagas while \cite{Kim13} found a linear relation.
+% PB: So what does this difference mean?
 
@@
 \section{Summery}
+In order to test the effect of stars on the SFR in both global and local scales in the M31, we have determined surface density of star formation rate, gas mass and the stellar mass of this galaxy.
+We produced three SFR maps in M31.
+The first uses a combination of the FUV and 24 \um emission.
+For the second SFR map, we used a combination of the H$\alpha$ and 24 \um emission, and the third one was produced using total-infrared luminosity.
+We noticed that H$_\alpha$ data available for M31 have a non-smooth background and the SFR map using this data would lead us to not accurately answer ~\ref{app:halpha}.
+We calculated the total SFR from FUV and 24 \um emission is 0.31$\pm$ 0.04 M$_{\odot}$yr$^{-1}$.
+
+We also produced the ISM map, using molecular gas only, atomic gas only and the total gas.
+For the molecular gas map, we assumed the CO-H$_2$ conversion factor is $2 \times 10^{20}$ (K km s$^{-1}$)$^{-1}$cm$^{-2}$.
+In order to calculate the total gas, we combined the molecular gas and atomic gas and multiplied this combination by a factor of 1.36 for effect of the heavier elements.
+We have determined the stellar mass using 3.6 \um emission to create the stellar mass surface density.
+Then, we used the hierarchical Bayesian fitting to apply both the K-S law and the extended Schmidt law on M31.
 
@@
 \appendix
-\section{SFR from H$\alpha$ plus 24 $\mu$m produces and result}
+\section{SFR from H$\alpha$ plus 24 \um produces and result}
 \label{app:halpha}
+
 \begin{figure*}
-\includegraphics[width=164mm]{halpha_copy.eps}
-\caption{Mosaic created using Montage programme from 6 fields of \halpha emission maps of m31 from \citpe{Massey07}.
-Result from Montage was continuum subtracted and masked out all point sources.
-Centre of galaxy was masked out due to saturation of data in R-band image.}
+\centering
+\includegraphics[width=164mm]{halpha.eps}
+\caption{Mosaic created using the Montage programme from six fields of H$\alpha$ emission maps of the M31 from \cite{Massey07}.
+The result image from Montage was continuum subtracted and masked out for all point sources.
+Centre of the galaxy was masked out due to saturation of data in an R-band image.}
 \label{fig:halpha}

### 2015-03-24 draft3.tex
from untitled

@@
 where \sigmasfr is SFR surface density, \sigmagas and \sigmastar are the gas mass and the stellar mass surface densities.
-\nprime and $\beta$ are the power law indexes.
-\cite{Shi11} calculated power indexes are $\eqnprime = 1.13 \pm 0.05$ and $\beta = 0.36\pm0.04$ in a global case.
+\nprime and $\beta$ are the power law indices.
+\cite{Shi11} calculated power indices are $\eqnprime = 1.13 \pm 0.05$ and $\beta = 0.36\pm0.04$ in a global case.
 By testing this relation on sub-kiloparces resolution regions on 12 spiral galaxies, they showed that the extended Schmidt law predicts SFR as well as the K-S law for spatially resolved regions ($\sim$1 kpc sizes).
-They demonstrated the power indexes for the local regions are $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$.
+They demonstrated the power indices for the local regions are $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$.
 They concluded that this law is acceptable for low surface brightness galaxies and regions where the KS law fails.
@@
 Furthermore, the range of the power index of K-S law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10,Ford13}.
-%Different groups, using different SFR or gas mass tracers, applied the K-S law on the M31 and have very different power indexes.
+%Different groups, using different SFR or gas mass tracers, applied the K-S law on the M31 and have very different power indices.
 In the most recent work of the K-S law in M31, \cite{Ford13}, test this law on six regions from the centre of the galaxy using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus HI maps, and total gas calculated from dust emission).
-The power indexes they measure for each map and each region vary between 0.6 to 2.03.
+The power indices they measure for each map and each region vary between 0.6 to 2.03.
 The origin of these contrary results is still ongoing question.
-It is not obvious what makes these differences in the power law indexes calculated by different groups.
+It is not obvious what makes these differences in the power law indices calculated by different groups.
 Whether it depends to distance from galaxy, metallicity, gas tracers, SFR tracers, fitting methods, or this is because of the K-S law does not work on the M31 at all.
@@
         \centering
-        \includegraphics[width=\textwidth]{es_tot_fir_vs_h2.png}
+        \includegraphics[width=\textwidth]{es_tot_fir_h2_f.png}
         \caption{SFR,TIR vs surface density of H$_2$}
@@
         \centering
-        \includegraphics[width=\textwidth]{es_tot_fir_vs_hi.png}
+        \includegraphics[width=\textwidth]{es_tot_fir_hi_f.png}
         \caption{SFR,TIR vs surface density of HI}
@@
         \centering
-        \includegraphics[width=\textwidth]{es_tot_fir_vs_tot.png}
+        \includegraphics[width=\textwidth]{es_tot_fir_tot_gas_f.png}
         \caption{SFR,TIR vs surface density of total gas}
@@
         \centering
-        \includegraphics[width=\textwidth]{es_tot_fuv_vs_h2.png}
+        \includegraphics[width=\textwidth]{es_tot_fuv_h2_f.png}
         \caption{SFR,FUV+24\um vs surface density of H$_2$}
@@
         \centering
-        \includegraphics[width=\textwidth]{es_tot_fuv_vs_hi.png}
+        \includegraphics[width=\textwidth]{es_tot_fuv_hi_f.png}
         \caption{SFR,FUV+24\um vs surface density of HI}
@@
         \centering
-        \includegraphics[width=\textwidth]{es_tot_fuv_vs_tot.png}
+        \includegraphics[width=\textwidth]{es_tot_fuv_tot_gas_f.png}
         \caption{SFR,FUV+24\um vs surface density of total gas}
@@
 While, for using the H$_{2}$ only gas or HI only gas we find the super-linear relation.
-These results are different from power indexes estimated by \cite{Ford13}, $N=2.03\pm0.04$ in case of total gas and $N=0.6\pm0.01$ in case of H$_{2}$ only gas.
+These results are different from power indices estimated by \cite{Ford13}, $N=2.03\pm0.04$ in case of total gas and $N=0.6\pm0.01$ in case of H$_{2}$ only gas.
 \cite{Tabatabaei10} estimated the K-S law power index $N=1.30\pm0.05$ using the total gas and $N=0.96\pm0.03$ using the H$_{2}$ only gas.
@@
 They also showed that the SFR and the molecular hydrogen have a linear relationship.
-Furthermore, \cite{Shetty13} used the same data as \cite{Bigiel08} and argued that using the hierarchical Bayesian fit leads to significant galaxy-by-galaxy variation between power indexes and all of them are lower than \cite{Bigiel08}.
+Furthermore, \cite{Shetty13} used the same data as \cite{Bigiel08} and argued that using the hierarchical Bayesian fit leads to significant galaxy-by-galaxy variation between power indices and all of them are lower than \cite{Bigiel08}.
 
@@
 Taking the average of our three regions leads us to the conclusion that using molecular gas only or atomic gas only $\beta$ is 0.60 and 0.55 which is very close to prediction of \cite{Shi11}.
-In the local case, the same as global case power indexes calculated using total gas surface density, are much smaller than the original suggestion of \cite{Shi11}.
+In the local case, the same as global case power indices calculated using total gas surface density, are much smaller than the original suggestion of \cite{Shi11}.
 % PB: can you explain why this might be?

### 2015-03-24 draft3.tex
This is the final one so far

--- 2015-03-06 draft3.tex
@@
 Additionally, We applied these laws on three different regions on the M31, to determine whether there is any dependence to a distance from the centre of the galaxy or not.
-Since, M31 is the closest spiral galaxy to the Milky Way, therefore, we can have higher resolution images of it than we have of any other spiral galaxy.
+The M31 is the nearest spiral galaxy to the Milky Way.
+Therefore, we can have higher resolution images of it than we have of any other spiral galaxy.
 Having high resolution images provides us data from different regions within the galaxy with different physical situations (e.g.
@@
 \halpha maps, which were obtained from the NOAO science archive are available in 10 overlapping fields.
-We created a Mosaic image of the maps using Montage.
+We created a Mosaic image of the maps using Montage \citep{Berriman08}.
 Assuming that all stars have the same fraction of \halpha light in their spectra, we subtracted the R band emission from the \halpha using averaged scaling factor between R band images and \halpha provided by \cite{Azimlu11}.
@@
 %PB: the two parts of the sentence above ("similarity of results" and "in close agreement") seem to say the same thing -- or am I not understanding what you mean here?
-We only interpret the results from the SFR(FUV+24$\mu$m).
-Results from the SFR(H$\alpha$) fitting are going to be discussed in the Appendix ~\ref{app:halpha}.
-%In this section we are going to talk about result from fitting the K-S Law, results from fitting the extended Schmidt law and the comparison between these two star formation laws and which one works better in the M31.
-%SR: Should I keep that or not
-%PB: I don't think you need the "In this section" sentence; the content is clear from the subsection headings.
-
+We only interpret the results from the SFR(FUV+24$\mu$m). Results from the SFR(H$\alpha$) fitting are going to be discussed in the Appendix ~\ref{app:halpha}.
 \subsection{The K-S law in M31}

### 2015-03-24 draft3.tex
Update draft3.tex

@@
 
-Stellar mass can be measured using a suitable calibration between flux/luminosity of stars in specific wavelengths and stellar mass.
+Stellar mass can be measured using a suitable calibration between flux$/$luminosity of stars in specific wavelengths and stellar mass.
 The basic idea behind these kind of calibrations comes from the fact that one can use the star formation histories recovered from synthesizing the stellar optical colour magnitudes in different regions in the galaxies.
@@
         \includegraphics[width=\textwidth]{es_tot_fuv_tot_gas_f.png}
-        \caption{SFR,FUV+24\um vs surface density of total gas}
+        \caption{SFR,FUV+24\um vs. surface density of total gas}
         \label{fig:es,all,fuv,tot}
@@
     \caption{The result from fitting the extended Schmidt law on data from whole galaxy using pixel by pixel method.
-The plots show the SFR vs surface density of gas, and z-axis is the surface density of the stellar mass.
+The plots show the SFR vs.
+surface density of gas, and z-axis is the surface density of the stellar mass.
 Each figure shows different combinations of the SFR tracer and gas mass tracer results.
@@
 The K-S law power index varies with the distance of the galaxy.
-Considering molecular gas, the power law index is increasing by going to further distances from the center of the galaxy.
+Considering molecular gas, the power law index is increasing by going to further distances from the centre of the galaxy.
 This trend also can be seen in the \cite{Ford13}.
 For the atomic gas only or the total gas this trend cannot be seen.
-This could be the result of the fact that, the atomic gas in the center of the galaxy is less than the other regions in the galaxy.
+This could be the result of the fact that, the atomic gas in the centre of the galaxy is less than the other regions in the galaxy.
 % PB: I don't quite understand your argument in the previous sentence.
@@
 %----------------------------------------------------------------------------------------
-%Acknowledgment 
+%Acknowledgement 
 %----------------------------------------------------------------------------------------
-\section*{Acknowledgment}
+\section*{Acknowledgement}
+Authors would thanks S. Lianou for very useful conversations with her specially at early stage of project, and from D. Kruijssen for his idea about 3D plots.
 This research made use of Montage, funded by the National Aeronautics and Space Administration's Earth Science Technology Office, Computation Technologies Project, under Cooperative Agreement Number NCC5-626 between NASA and the California Institute of Technology.
-Montage is maintained by the NASA/IPAC Infrared Science Archive.
+Montage is maintained by the NASA/IPAC Infra-red Science Archive.
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
+\newpage
 \newpage

### 2015-06-02 draft3.tex
I applied part of Maryam's corrections

--- 2015-03-24 draft3.tex
@@
 \newcommand \kpc        {\,{\rm kpc}}
-\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }}$\ }
+\newcommand \sigmagas    {$\Sigma_{\rm \bld {gas }} $\ }
+\newcommand \sigmatotalgas {$\Sigma_{\rm \bld {total gas }} $\ }
 \newcommand \eqsigmagas    {\Sigma_{\rm \bld {gas }}}
-\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }}$\ }
+\newcommand \sigmasfr     {$\Sigma_{\rm \bld {SFR }} $\ }
 \newcommand \eqsigmasfr     {\Sigma_{\rm \bld {SFR }}}
-\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }}$\ }
+\newcommand \sigmastar    {$\Sigma_{\rm \bld {star }} $\ }
 \newcommand \eqsigmastar    {\Sigma_{\rm \bld {star }}}
@@
 \newcommand \Spitzer {{\it Spitzer }}
-\newcommand \Galex {GALEX}
+\newcommand \Galex {GALEX }
 \newcommand \Herschel {{\it Herschel}}
@@
 % TITLE
-\title[WHICH STAR FORMATION LAW IN M31]{RELATION BETWEEN STAR FORMATION RATE, GAS MASS AND STELLAR MASS IN THE ANDROMEDA GALAXY}
-\author[S. Rahmani $\&$ P. Barmby]{S.~Rahmani, P.~Barmby\\
-Department of Physics $\&$ Astronomy, University of Western Ontario, London, ON N6A 3K7, Canada}
+\title[STAR FORMATION LAW IN M31]{Star formation law in the Andromeda galaxy: effect of the gas mass, stellar mass, and metallicity }
+\author[S. Rahmani, et. al.]{S.~Rahmani, S.~Lianou, P.~Barmby\\
+Department of Physics $\&$ Astronomy, Western University, London, ON N6A 3K7, Canada}
 \maketitle
@@
 %----------------------------------------------------------------------------------------
-\begin{abstract} % it is just my GESF2014 abstract, just for looks I will change it at the end
- We investigate the relation between star formation rate (SFR), gas surface density (\sigmagas) and stellar surface density (\sigmastar) in the Andromeda galaxy (M31) using the Kennicutt-Schmidt (K-S) law and the extended Schmidt law \cite{Shi11} argued that the surface density of SFR is related not only to gas mass, as in the empirical K-S law,  but also to stellar mass surface density, in the ``extended Schmidt law''.
+\begin{abstract} % it is just my GESF2014 abstract, just for looks I will change it at the end. %PBNew: OK, no comments on this yet.
+ We investigate the relation between star formation rate (SFR), gas surface density (\sigmagas) and stellar surface density (\sigmastar) in the Andromeda galaxy (M31) using the Kennicutt-Schmidt (K-S) law and the extended Schmidt law.
+\cite{Shi11} argued that the surface density of SFR is related not only to gas mass, as in the empirical K-S law,  but also to stellar mass surface density, in the ``extended Schmidt law''.
 Using all a combination of \halpha and 24 \um emission, a combination of FUV and 24 \um, and the total infrared emission, we estimate the total SFR in M31 to be between 0.35 M$_{\odot}$yr$^{-1}$ - 0.4 M$_{\odot}$yr$^{-1}$.
@@
 \end{abstract}
+
 \begin{keywords} 
-Galaxies: Andromeda, Star Formation
+galaxies: individual: M31, galaxies: spiral, galaxies: star formation, galaxies: stellar content, galaxies: ISM, stars: formation, ISM: clouds, methods: observational, methods: statistical, techniques: image processing
 \end{keywords}
@@
 \section{Introduction}
-\label{sec:intro} %I can add a lot more about calculating star formation and in general why star formation is important but I don't like make my introduction too long.
+\label{sec:intro}
 %P1: Star formation laws and why they are important (introducing K-S law and E-S law)
-%PB: agreed with not making it too long, but do start with a sentence about why SF is important.
-Understanding the processes that go into the formation and evolution of stars and stellar systems is crucial in the study of the chemical composition and structure formation of the universe.
-Stars are also central to the formation of planetary systems and are where the ingredients for life were formed.
-The energy provided by stars is necessary to maintain the life on planets.
-The study of the formation and evolution of the Sun, and more generally that of stars, would help us understand more about our origin and the future of our Solar System.
-This is one of the main reasons that the study of stellar structure and evolution has been a central topic in astronomy and astrophysics for decades.
 
-In order to completely understand the formation and evolution of galaxies from the early universe to the current epoch, the knowledge of the formation of stars is necessary.
-Star formation determines the structure and evolution of galaxies, by transforming the gas into stars.
-Moreover, the knowledge of star formation is essential to understanding the origin of planetary systems.
-The physical process of star formation is naturally complex.
-Therefore, the basis for a theory of star formation requires a strong foundation of empirical data or observations.
+Understanding the undergoing processes of formation of stars is a necessary step for explaining the formation and evolution of galaxies from the early universe to current epoch, as well as the origin of planetary systems.
+Stars form by converting the gas inside galaxies; However, no complete answer on how this transformation happens and what physical properties affect it, is available.
+Various phenomena trigger the collapse of molecular clouds and star formation including the environment of the star-forming region, gas accretion and cooling, H$_2$ formation, the initial mass distribution of gas, chemical compositions of the gas,  dust existence, and other quantities in a galaxy.
+The physical processes leading to star formation are naturally complex.
+Therefore, the basis for a theory of star formation requires a strong foundation of empirical data and/or observations.
+%me
 
-Empirical star formation laws (relations) has been investigated for more than 50 years, and the results never been precise.
-Formation of stars is a complicated process.
-Various phenomena affect the collapse of molecular clouds and star formation which, include the environment of the star-forming region, chemical compositions, the initial mass distribution of gas, gas accretion and cooling, H$_2$ formation, and etc.
-
-The first idea about scaling the star formation rate (SFR) was proposed as a connection between the total star formation rate and the mass of interstellar gas.
-\cite{Schmidt59} assumed a constant initial mass function (IMF) of stars, $\Psi (M)$, a stellar lifetime function {$T(M$)}, and a  {$SFR(T)$} and derived the star formation rate over the history of the Milky Way.
-He scaled SFR with a power {\it N} of the gas mass, $M_{gas}$.
-%Then $SFR(T)\Sigma_{M}(M) = c[M_{gas}(t)]^n$, for a summation over all stellar type $M$.
-A decade later, \cite{Kennicutt98a} examined another group of galaxies.
-By using H$\alpha$, HI, and CO observations of 61 normal spiral galaxies and 36 starburst galaxies, he showed that the disk-average SFRs and gas densities for these samples are well represented by the Schmidt law with the power of $1.4 \pm 0.15$.
-Using this power index, the Schmidt law can be rewritten as:
+Finding a relation between the total star formation rate (SFR) and the mass of interstellar gas was proposed as the first attempt at scaling the star formation rate.
+\cite{Schmidt59} scaled SFR with a power {\it N} of the gas mass, $M_{\rm gas}$.
+Since then, for more than 50 years empirical star formation laws (relations) have been investigated using both observational data and numerical simulations.
+Later, \cite{Kennicutt98a} examined H$\alpha$, HI, and CO observations of 61 normal spiral galaxies and 36 starburst galaxies.
+He showed that the disk-average SFRs and gas densities for these samples are well represented by the Schmidt law with the power-low exponent of $1.4 \pm 0.15$.
+Using this power index, the Schmidt law can be rewritten as: %me, Schmidt, Kennicutt and every papers on K-S law
 
@@
 which is often referred to as the Kennicutt-Schmidt (K-S) law, where \sigmasfr is the surface density of star formation, and \sigmagas is the surface density of gas in a galaxy.
+Moreover, \cite{Kennicutt07} investigated the K-S law in spatially resolved regions (0.5 - 2 kpc) in the spiral galaxy M51.
+To calculate the SFR they used $24 \mu$m plus H${\alpha}$ emission, and for the gas surface density, a constant conversion factor for CO to H$_2$ was applied.
+They found a correlation, from the radial variation of both the SFR and the gas surface density, with an index of $1.56 \pm 0.04$.
+%kennicutt07
 
-In more recent studies, \cite{Kennicutt08} investigated the local star formation law in M51 with 0.5-2 kpc resolution.
-For calculation of the SFR he used pa${\alpha}$ and $24\mu$m + H${\alpha}$ lines and for gas density he used constant conversion factor for CO to H$_2$.
-He found a correlation, from the radial variation of both SFR and gas surface density, with an index of $1.56 \pm 0.04$.
-%He could not find any correlation between SFR and HI only clouds, but the correlation with the molecular cloud was about the same as the total gas.
-It should be noted that the KS law cannot be applied to the whole range of gas densities.
-In parallel studies, the star formation threshold was introduced and it was pointed out that calculated SFR is much lower than the value predicted by the KS law at low gas densities $( < 1-10\sim$ M$_{\odot}$ pc$^{-2})$ e.g.
-in regions far outside the optical disk \citep[e.g.,][]{Martin01, Bigiel08}.
-
-\cite{Hunter98} have shown that, in low surface brightness galaxies the SFR density is only related to the stellar mass density.
-Also similar relations between stellar masses and SFR densities are seen within galaxies by \cite{Ryder94}, \cite{Hunter04} and recently by \cite{Leroy08} for specific galaxy types or limited density ranges.
-\cite{Shi11} found a tight relationship between stellar mass surface density, SFR and gas surface density by studying on a large sample of galaxies.
-They showed this relation as a power law relation and referred to it as the extended Schmidt law:
+The K-S law was applied to different types of both local and high redshift galaxies \citep[e.g.,][]{Boissier07,Kennicutt07, Bigiel08, Freundlich13}, but the results were never precise.
+Low gas density regions, $( < 1-10\sim$ M$_{\odot}$ pc$^{-2})$, such as regions outside the disk of the galaxy, are one of the regions, for which the K-S law fails.
+The calculated SFR for these regions is much lower than the value predicted by the K-S law \citep[e.g.,][]{Martin01, Bigiel08}.
+Using different instability models, \cite{Hunter98} showed that in low surface brightness galaxies, the current star formation activity correlates with stellar mass density.
+Furthermore, a correlation between the star formation rate and the stellar mass density was measured in many studies using both observational data and numerical simulations \citep[e.g.][]{Hunter04,Leroy08,Krumholz09,Shi11,Kim11,Kim13}.
+\cite{Shi11} found a tight relationship between stellar mass surface density, SFR and gas surface density by studying a large sample of galaxies.
+They showed this relation as a power law relation and referred to it as the extended Schmidt law: %me + all the ppl I cite
 
@@
 \end{equation}
-where \sigmasfr is SFR surface density, \sigmagas and \sigmastar are the gas mass and the stellar mass surface densities.
-\nprime and $\beta$ are the power law indices.
-\cite{Shi11} calculated power indices are $\eqnprime = 1.13 \pm 0.05$ and $\beta = 0.36\pm0.04$ in a global case.
-By testing this relation on sub-kiloparces resolution regions on 12 spiral galaxies, they showed that the extended Schmidt law predicts SFR as well as the K-S law for spatially resolved regions ($\sim$1 kpc sizes).
-They demonstrated the power indices for the local regions are $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$.
-They concluded that this law is acceptable for low surface brightness galaxies and regions where the KS law fails.
+where \sigmasfr is the SFR surface density while \sigmagas and \sigmastar are the gas mass and stellar mass surface densities, \nprime and $\beta$ are the indices found by \cite{Shi11} to be $1.13 \pm 0.05$ and $0.36\pm0.04$ respectibely in a global case.
+By testing this relation on sub-kiloparsec resolution regions in 12 spiral galaxies, they showed that the extended Schmidt law predicts SFR as well as the K-S law for spatially resolved regions ($\sim$1 kpc).
+They demonstrated that the power indices for the local regions are $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$, and concluded that this law is acceptable for low surface brightness galaxies and regions where the K-S law fails.%me
 
 %P2: SFR, measuring, scaling, ...
-For testing any of these star formation laws, the first thing one should do is calcule the SFR.
-Many groups are working to find a translation from the light of star forming regions in galaxies to a rate of the formation of new stars.
+In order to investigate star formation laws, the first step is to calculate the SFR.
+Many studies are devoted to determining how flux measurments of the star forming regions can accuratelly be traslated to the rate of the formation of new stars \citep[e.g.,][]{Kennicutt12, Calzetti13, Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
 \cite{Kennicutt98b} calibrated luminosity of galaxies as a way of measuring the SFR in specific wavelengths using relations between the SFR per unit mass or per unit luminosity and the integrated colour of the system provided by synthesis models \citep[e.g.,][]{Bruzual93}.
-Afterward, many other studies tried to find the similar calibration for measuring the SFR of galaxies in other bands \citep[e.g.,][]{Kennicutt12, Calzetti13, Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
-\cite{Kennicutt09} and \cite{Hao11} introduced new SFR calibration using a combination of \halpha or FUV and far infrared (FIR) emission, respectively.
-In addition of using suitable calibrations for each region, considering differences between global case and local ($\sim 0.5-1$~\kpc) case is important.
-In $\S3$, we are talking about the SFR in the Andromeda galaxy and how we determined it.
+Subsequent studies tried to find a similar calibration for measuring the SFR of galaxies in other bands.
+\cite{Kennicutt09} and \cite{Hao11} introduced new SFR calibrations using a combination of \halpha or FUV and far-infrared (FIR) emission, respectively.
+In addition to using suitable calibrations for each region, considering the differences between the global case and local ($\sim 0.5-1$~\kpc) case is important.
+In $\S$\ref{sec:sfr}, we will discuss the SFR in the Andromeda galaxy and how it was determined.
+%me and Keniccutt98b and then me again, with Maryam's corrections
 
 %P3: Gas cloud, variety, observing etc
-Calculating surface density of gas in galaxies is the other most important ingredients of testing star formation laws.
-Considering the effect of the interstellar medium (ISM) on studying the star formation law is important due to the fact that stars are born from the gas also release their material into the ISM when they reach the end of their evolution.
-A map of the total gas in the ISM is produced by direct observations of the gas or using interstellar dust as a tracer.
+Calculating the surface density of gas in galaxies is the other most important ingredient of testing star formation laws.
+Considering the effect of the interstellar medium (ISM) on studying the star formation law is important due to the fact that stars are born from the gas and also release their material into the ISM when they reach the end of their evolution.
+A map of the total gas in the ISM is produced by direct observations of the gas or by using interstellar dust as a tracer.
 Neutral and molecular hydrogen are the most common elements in the ISM.
 Therefore, for producing the map of the total gas in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He.
-Another way to do the mapping of total gas mass of the galaxy is to assume that the ratio of total gas mass and dust mass is the same across a galaxy, and convert dust observations to the map of total gas.
-$\S4$ is about the calculation of the gas surface density for the Andromeda galaxy.
+Calculations of the gas surface density for the Andromeda galaxy are shown in $\S$\ref{sec:ISM}.
+%me
 
-%PB: shorten or leave out dynamical mass, since you don't discuss it further
 %P4: Stellar mass and how to measure it
 Additionally, for testing the Extended Schmidt law, measuring the stellar mass density is necessary.
-Measuring the mass of the stellar population is indirect and subject to significant uncertainties.% In principle there are two ways to measure stellar mass in galaxies.
-First is measuring the dynamical mass of galaxies using kinematics \citep{Cappellari06} or lensing \citep{Auger09}, and then modelling the mass of the dark matter and subtracting it from the measured mass.
-This method has been successful to predict and subtract the mass of the dark matter, which is the dominant mass in galaxies \citep{Zaritsky94},  and can easily cause uncertainties as high as the order of the measurement.
-
-One of the methods to calculate the stellar mass within a galaxy, is based on stellar population models \citep[e.g.][]{ Bruzual93, Kotulla09} and using them to connect stellar mass to an observable, like luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations.
-Having two independent methods to measure stellar mass helps to compare the results and check whether there are any systematic differences.
-Comparing the results from measuring the stellar mass in stellar clusters shows there is no huge difference.
-Comparing the results from measuring stellar mass within galaxies shows that the differences are on the order of a few x10 percent, so one should be more careful to model subtleties \citep{McLaughlin05}.
-Calculating stellar mass in the Andromeda galaxy is described in $\S5$.
+Measuring the mass of the stellar population is indirect and subject to significant uncertainties.
+One method to calculate the stellar mass within a galaxy is based on stellar population models \citep[e.g.][]{ Bruzual93, Kotulla09}.
+These models are used to connect stellar mass to an observable quantity such as, luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations.
+Having different methods to measure stellar mass helps to compare the results and determine whether there are any systematic differences.
+Comparing the results from measuring the stellar mass via different methods in stellar clusters shows there is no significant difference \citep{Tamm12}.
+In fact, the differences are found to be on the order of a few x10 percent; so one should be more careful to model subtleties \citep{McLaughlin05}.
+Calculating stellar mass in the Andromeda galaxy is described in $\S$\ref{sec:starmass}.
+%me and Tamm and the rest I cited
 
@@
 In this paper, we present our results from testing and comparing both the K-S law and the Extended Schmidt law on the Andromeda galaxy (M31).
-%We used three different gas maps and SFR maps, to identify if any of these laws work better with specific gas mass or SFR tracer.
-Additionally, We applied these laws on three different regions on the M31, to determine whether there is any dependence to a distance from the centre of the galaxy or not.
-Since, M31 is the closest spiral galaxy to the Milky Way, therefore, we can have higher resolution images of it than we have of any other spiral galaxy.
-Having high resolution images provides us data from different regions within the galaxy with different physical situations (e.g.
-metallicity, surface brightness and etc.).
-All these parameters make the Andromeda a suitable test bed for studying the scaling law.
-%PB: Give a little more detail in the following sentence
+Additionally, We applied these two laws on three different regions in M31 to determine if there is any dependence on distance from the centre of the galaxy.
+Since M31 is the nearest spiral galaxy to the Milky Way, we can have higher resolution images of this spiral galaxy.
+High resolution images provide data from various regions within the galaxy with different physical situations (e.g.
+metallicity, surface brightness, gas density).
+This inside look helps us to test star formation laws in diverse physical conditions.
+Thus, M31 is a suitable test bed for studying scaling laws.
+%me
 
-Furthermore, the range of the power index of K-S law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10,Ford13}.
-%Different groups, using different SFR or gas mass tracers, applied the K-S law on the M31 and have very different power indices.
-In the most recent work of the K-S law in M31, \cite{Ford13}, test this law on six regions from the centre of the galaxy using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus HI maps, and total gas calculated from dust emission).
-The power indices they measure for each map and each region vary between 0.6 to 2.03.
-The origin of these contrary results is still ongoing question.
+Furthermore, the range of the power index of the K-S law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10,Ford13}.
+Various groups used different methods and data, and have different value for the power index.
+In the most recent study of the K-S law in M31, \cite{Ford13} tested this law on six regions from the centre of the galaxy using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus HI maps, and total gas calculated from dust emission).
+The measured power indices for each map and each region vary between 0.6 to 2.03.
+The origin of these variation in results is still ongoing
+question.
 It is not obvious what makes these differences in the power law indices calculated by different groups.
-Whether it depends to distance from galaxy, metallicity, gas tracers, SFR tracers, fitting methods, or this is because of the K-S law does not work on the M31 at all.
-If we assume the last case is valid, testing extended Schmidt law on the Andromeda galaxy would help to solve the problem with these controversial results.
+It is unclear whether it depends on distance from the centre of the galaxy, metallicity, gas tracers, SFR tracers, fitting methods, or because of the K-S law does not work on M31 at all.
+We also applied a new statistical method instead of the ordinary least square fitting (OLS), which is the most common fitting method for testing K-S law, to test the importance of the fitting method in results.
+%me
 
@@
 \label{sec:data}
-Since the M31 is the closest spiral galaxy to the Milky Way, it was aimed by many probes and telescopes, both space based and ground based ones.
-Therefore, a variety of data from X-ray to radio wavelengths are available.
+Since M31 is the closest spiral galaxy to the Milky Way, it was aimed by many probes and telescopes, both space based and ground based ones.
+Therefore, a variety of data from gamma-ray to radio wavelengths are available.
 Wide ranges of data provide us the ability to measure all the required parameters to test the star formation laws in M31.
@@
 Each data comes with different Full Width Half Maximum (FWHM), spacial resolution and grids.
-In order to make sure that all our data contains the same amount of information, we smoothed them using Aniano's Kernels' library and convolution code \citep{Aniano12}, to the highest resolution available.
-Moreover, considering Nyquist relation \citep{Nyquist}, we re-sampled and re-gridded all our maps to have a proper pixel size.
+In order to make sure that all our data contains the same amount of information, we smoothed maps with smaller FWHM using Aniano's Kernels' library and convolution code \citep{Aniano12}, to have the same resolution as either the $^{12}$CO(J:$1\rightarrow0$) data or atomic gas data.
+Moreover, considering the Nyquist relation \citep{Nyquist}, we re-sampled and re-gridded all our maps to have a pixel size which match with their new resolution.
+%I do not like this centence but I am not sure how to fixt it.
+%PBnew: what exactly does 'highest resolution available' mean? Same for 'proper pixel size' ? /done!
 
@@
 \label{table:data}
-\begin{tabular}{@{}lccc}
+\begin{tabular}{@{}lcccc}
 \hline\hline
-Wavelength & FWHM & Telescope
+Wavelength & FWHM & Coverage area &Telescope
 & Ref. \\
@@
 %500 \um & 36\arcsec & $Herschel$ & \cite{Fritz12} \\
-%350 \um & 24\arcsec.5 & $Herschel$ & \cite{Fritz12} \\
 %250 \um & 18\arcsec.2 & $Herschel$ & \cite{Fritz12} \\
-2250~\AA & 6\arcsec & GALEX & \cite{Martin05}\\ %:PB: GALEX, KPNO, IRAM should not be in $$
-1550~\AA & 4\arcsec.5 & GALEX & \cite{Martin05}\\ %PB (they are abbreviations)
-6570~\AA  & 1\arcsec & KPNO& \cite{Massey07}\\
-3.6~\um & 1\arcsec.7 & \Spitzer & \cite{Barmby06} \\ %PB: write {\it Spitzer}, {\it Herschel}
-4.5~\um & 1\arcsec.7 & \Spitzer & \cite{Barmby06} \\ %PB because those are both missions and names
-8~\um & 1\arcsec.9 & \Spitzer & \cite{Barmby06} \\ % PB: of people - italics means the mission, not
-24~\um & 6\arcsec & \Spitzer & \cite{Gordon06} \\ %PB: the person
-70~\um & 18\arcsec & \Spitzer & \cite{Gordon06} \\
-160~\um & 12\arcsec & \Herschel & \cite{Fritz12} \\
-2.6~mm & 23\arcsec & IRAM 30-m & \cite{Nieten06}\\
-21~m & 60\arcsec $\times$ \ 90\arcsec & DRAO & \cite{Chemin09}\\
+1550~\AA & 4\arcsec.5 & 5\degr $\times$ 5\degr &GALEX & \cite{Martin05}\\  %:PB: GALEX, KPNO, IRAM should not be in $$
+2250~\AA & 6\arcsec & 5\degr $\times$ 5\degr &GALEX & \cite{Martin05}\\%PB (they are abbreviations)
+6570~\AA  & 1\arcsec & 2\arcmin.2 $\times$ 0\degr.6 &KPNO& \cite{Massey07}\\
+3.6~\um & 1\arcsec.7 & 3\degr.7 $\times$ 1\degr.6 &\Spitzer & \cite{Barmby06} \\ %PB: write {\it Spitzer}, {\it Herschel}
+4.5~\um & 1\arcsec.7 & 3\degr.7 $\times$ 1\degr.6 &\Spitzer & \cite{Barmby06} \\ %PB because those are both missions and names
+8~\um & 1\arcsec.9 & 1\degr $\times$ 3\degr &\Spitzer & \cite{Barmby06} \\ % PB: of people - italics means the mission, not
+24~\um & 6\arcsec & 1\degr $\times$ 3\degr &\Spitzer & \cite{Gordon06} \\ %PB: the person
+70~\um & 18\arcsec & 1\degr $\times$ 3\degr &\Spitzer & \cite{Gordon06} \\
+160~\um & 12\arcsec & 5\degr.5 $\times$ 2\degr.5 &\Herschel & \cite{Fritz12} \\
+350~\um & 24\arcsec.5 & 5\degr.5 $\times$ 2\degr.5 &\Herschel & \cite{Fritz12} \\
+2.6~mm & 23\arcsec & 2\degr $\times$ 0\degr.5 &IRAM 30-m & \cite{Nieten06}\\
+21~cm & 60\arcsec $\times$ 90\arcsec & 5\degr.2 $\times$ 1\degr.5 &DRAO & \cite{Chemin09}\\
 \hline
@@
 \end{table*}
-
-%PB: in general it's good to write number~unit, ie 2750~\AA 
+%PB: in general it's good to write number~unit, ie 2750~\AA /Done
 %PB: this means that number and unit don't end up on separate lines
-\subsection{Ultra Violet (UV) emission}
 
 One of the calibrations, which was used to calculate SFR, uses FUV emission as a tracer of the star forming regions.
-FUV emission of M31 was observed by the Galaxy Evolution Explorer ($GALEX$; \citep{Martin05}).
-$GALEX$ telescope data contains information for two bands, FUV:1350-1750 and NUV:1750-2750~\AA, with FWHM of 4\arcsec .5, and 6 \arcsec.
+FUV emission of M31 was observed by the Galaxy Evolution Explorer (GALEX; \citep{Martin05}).
+GALEX telescope data contains information for two bands, FUV:1350--1750 and NUV:1750--2750~\AA, with FWHM of 4~\farcs5, and 6~\arcsec.
 
-\subsection{Visible light}
+%\subsection{Visible light}
+\label{sec:vislight}
 Our other method to calculate the SFR was using a combination of \halpha emission and 24\um emission.
 \cite{Massey06, Massey07} mapped UBVRI and \halpha emission line of M31 as part of the Nearby Galaxies Survey using the KPNO telescope.
-\halpha maps, which were obtained from the NOAO science archive are available in 10 overlapping fields.
-We created a Mosaic image of the maps using Montage.
-Assuming that all stars have the same fraction of \halpha light in their spectra, we subtracted the R band emission from the \halpha using averaged scaling factor between R band images and \halpha provided by \cite{Azimlu11}.
-We also took masked map of stars from \cite{Azimlu11} and masked all point sources (Figure ~\ref{fig:halpha}).
+\halpha maps, which were obtained from the NOAO science archive, are available in 10 overlapping fields and were observed between 2000 August and 2002 September.
+We created a Mosaic image of the maps using the Montage \citep{Berriman08}.
+Assuming that all stars have the same fraction of \halpha light in their spectra, we subtracted the R band emission from the \halpha image using the averaged scaling factor between R band images and \halpha provided by \cite{Azimlu11}.
+We also took a masked map from \cite{Azimlu11} and masked all foreground star or partially saturated stars(Figure~\ref{fig:halpha}).
 Details about making the making \halpha map can be found in the Appendix ~\ref{app:halpha}.
 
-\subsection{IR and sub mm Data}
-In IR and sub mm bands, both $Spitzer$ \citep{Wener04} and $Herschel$ \citep{Pilbratt10}  space telescopes observed the M31.
-The Infrared Array Camera (IRAC; \citep{Fazio04}) on the $Spitzer$ is a camera observing at four channels (3.6, 4.5, 5.8, and 8 \um).
+%\subsection{IR and sub mm Data}
+In IR and sub mm bands, both {\em Spitzer} \citep{Wener04} and {\em Herschel} \citep{Pilbratt10}  space telescopes observed the M31.
+The Infrared Array Camera (IRAC; \citep{Fazio04}) on {\em Spitzer} is a camera observing at four channels (3.6, 4.5, 5.8, and 8 \um).
 IRAC observations of the M31 were obtained by \cite{Barmby06}, which covered $3\degr.7 \times 1\degr.6$.
 IRAC 3.6 and 4.5\um bands  were used to calculate the stellar mass.
-Multiband Imaging Photometer for Spitzer (MIPS) observed the  M31 at 24, 60, and 160\um and covered region $\sim 1\degr \times 3\degr$ \citep{Gordon06}.
+%PBnew: did you use 4.5um?
+Multiband Imaging Photometer for \Spitzer (MIPS) observed the  M31 at 24, 60, and 160\um and covered region $\sim 1\degr \times 3\degr$ \citep{Gordon06}.
 
 Calculation of the SFR using TIR emission needs maps of the m31 in 8, 24, 70, and 160 \um.
-IRAC 8, MIPS 24, MIPS 70 bands were used to calculate TIR emission, but due to better quality and resolution of $Herschel$s$'$data, PACS (Photodetector Array Camera and Spectrometer) \citep{Poglitsch10} were used.
-PACS 160\um observation of the Andromeda galaxy alongside of PACS 100 \um band and three (250 \um, 350\um and 500 \um) SPIRE (Spectral and photometric Imaging Receiver) \citep{Griffin10} bands are covered $\sim 5\degr.5 \times 2\degr.5$ regions \citep{Fritz12}.
+IRAC 8, MIPS 24, MIPS 70 bands were used to calculate TIR emission, but due to better quality and resolution of $Herschel$s$'$data, PACS \citep[Photodetector Array Camera and Spectrometer;][]{Poglitsch10} were used.
+PACS 160\um observation of the Andromeda galaxy alongside of PACS 100 \um band and three (250 \um, 350\um and 500 \um) SPIRE \citep[Spectral and Photometric Imaging Receiver;][]{Griffin10} bands are covered $\sim 5\degr.5 \times 2\degr.5$ regions \citep{Fritz12}.
 
-\subsection{Radio Emission}
+%\subsection{Radio Emission}
 Emission from $^{12}$CO(J:$1\rightarrow0$) line which, was observed on-the-fly with the IRAM 30-m telescope\citep{Nieten06} was used to calculate the H$_2$ column density of the interstellar medium.
-This map covers $2\degr \times 0\degr.5$ that has the best resolution available (FWHM = $23\arcsec$) but smallest coverage of the halo of the galaxy among our maps.
-In this project we used data of the 21 cm emission from the atomic gas (HI) in the M31 from \cite{Chemin09}.
-They used Synthesis telescope and the 26 m antenna at the Dominion Radio Astrophysical Observatory to map HI emission in 21cm band of the M31.
+This map covers $2\degr \times 0\degr.5$ that has the best resolution CO image of M31 (FWHM = $23\arcsec$), but the smallest coverage of the halo of the galaxy among the maps we used in this paper.
+In this project we also used 21cm emission map from the atomic gas (HI) in M31 from \cite{Chemin09}.
+They used Synthesis telescope and the 26m antenna at the Dominion Radio Astrophysical Observatory to map HI emission in the 21cm band of the M31.
+
+\section{Measuring Star Formation Laws Components}
 
@@
 %----------------------------------------------------------------------------------------
-\section{Star Formation Rate}
-\subsection{FUV plus 24\um Star Formation Rate}
+\subsection{Star Formation Rate}
+\label{sec:sfr}
+\subsubsection{FUV plus 24\um Star Formation Rate}
 
-In this project first star formation map was produced using a calibration of a combination of the FUV emission and 24\um emission introduced by \cite{Hao11}.
-Since peak of the emission of massive and young stars (O - B and A type) are in the UV, this wavelength is one of the most common used star formation rate indicators \citep[e.g.,][]{Kennicutt89}.
-The UV indicates star forming region with age of $\sim 100$ Myr \citep[e.g.,][]{Kennicutt98a, Calzetti05}.
-However, downside of only using the FUV light as a tracer of star forming region is that this emission is really sensitive to dust extinction.
+In this project the first star formation map was produced using a calibration of a combination of FUV emission and 24\um emission introduced by \cite{Hao11}.
+Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.,][]{Kennicutt89}.
+The UV emission traces recently formed stars with age of $\sim 100$ Myr \citep[e.g.,][]{Kennicutt98a, Calzetti05}.
+However, the downside of only using the FUV light as a tracer of the star forming region is that this emission is really sensitive to dust extinction.
 On the other hand 24\um emission is dominated by emission from dust heated by UV photons from young and hot stars.
-This emission is sensitive to star formation time scale of $\la10$ Myr \citep{Calzetti07}.
-The FUV band of \Galex and the 24\um band of \Spitzer ~ data was used to measure the SFR calibrated by \cite{Hao11} as:
+This emission is sensitive to the star formation time scale of $\la10$ Myr \citep{Calzetti07}.
+The FUV band of \Galex and the 24\um band of \Spitzer data were used to measure the SFR calibrated by \cite{Hao11} as:
 \begin{equation}
@@
 \end{equation}
-where a unit of SFR is M$_{\odot}$yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{obs}$ are in erg/s.
-L(FUV)$_{obs}$ is the luminosity of galaxy in the FUV emission.
-The index of obs is shown to indicate that the FUV emission is not corrected for effect of extinction.
-Nevertheless, this emission is corrected for the foreground stars' emission.
-To do so, we followed a method introduced by \cite{Leroy08}.
-We assumed for any pixel in FUV$_{obs}$ map, %which has a pixel size equals the pixel size of NUV map,
-if I$_{NUV}$/I$_{FUV}$ $>$ 15 that pixel value is dominated by foreground emission and masked them out.
+where a unit of SFR is M$_{\odot}$yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{obs}$ are in erg~s$^{-1}$.
+L(FUV)$_{obs}$ is the luminosity of the galaxy in the FUV emission.
+The index of "obs" is shown to indicate that the FUV emission is not corrected for the effect of extinction.
+Nevertheless, this emission was corrected for the foreground stars' emission using a method introduced by \cite{Leroy08}.
+We assumed for any pixel in FUV$_{obs}$ map, if I$_{NUV}$/I$_{FUV}$ $>$ 15 that pixel value is dominated by foreground emission and masked them out.
 We also masked the same region in the galaxy for 24\um map.
-Using this method, we calculated the total SFR is 0.31$\pm$ 0.04 M$_{\odot}$yr$^{-1}$.
+Using this method, we calculated the total SFR is $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$.
 
@@
 
-%----------------------------------------------------------------------------------------
-\subsection{\halpha plus 24\um Star Formation Rate}
-\label{sec:sfr_halpha}
-
-The SFR can be calculated using combination of \halpha and \Spitzer  24\um maps.
-\halpha emission of galaxies is dominated by light emitted from young and massive stars.
-Star formation time scaled traced by this emission is $\sim 6-10$ Myr \citep[e.g.,][]{Kennicutt09, Calzetti13}.
-Therefore \halpha alone could be used to calibrate the SFR \citep[e.g.,][]{Osterbrock06, Kennicutt09}.
-However, \halpha emission is very sensitive to dust extinction, too.
-Therefore, the combination of the \halpha and 24\um of is considerable choice for calculating the SFR.
-we used a calibration introduced by \cite{Kennicutt09} to measure the SFR:
-\begin{equation}
-\label{equ: halphaplus24_g}
-SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.020L(24\mu m)]
-\end{equation}
-where L(H${\alpha}$)$_{obs}$ is the observed H${\alpha}$ luminosity without correction for internal dust attenuation, given in the unit of erg/s.
-L(24$\mu$m) is the $24\mu$m IR luminosity in erg/s, and SFR is in M$_{\odot}$yr$^{-1}$.
-It was indicated that the formulation above can only be used at the global situation (i.e.
-total SFR).
-
-\cite{Calzetti07} introduced a new calibration using the same bands in case of local regions (figure ~\ref{fig:sfr_halpha}):
-\begin{equation}
-\label{equ: halphaplus24_l}
-SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.033L(24\mu m)]
-\end{equation}
-the units here are the same as equation~\ref{equ: halphaplus24_g}.
-Equation~\ref{equ: halphaplus24_l} is useful for regions less than $\sim 1$ kpc.
-According to  \cite{Calzetti07} calibration constant in equations ~\ref{equ: halphaplus24_g} and ~\ref{equ: halphaplus24_l} can be different by changing an IMF.
-Changes in the IMF mostly affect on calibration based on \halpha luminosity, mostly because a significant amount of the ionizing photons comes from the stars more massive than $\sim 20$M$\sun$.
-Changing the calibration constant would change the total SFR by a factor of 1.5.
-In this paper, we used \cite{Kroupa01} IMF with an upper mass limit of 100M$\sun$.
-Total SFR calculated from equation~\ref{equ: halphaplus24_g} is 0.35 $\pm$ 0.01 M$\sun$yr$^{-1}$, which is in good agreement with previous studies.
-%PB: can you put uncertainties on the total SFR numbers?
-
-\subsection{Total Infrared Star Formation Rate}
+\subsubsection{Total Infrared Star Formation Rate}
 \label{sec:sfr_fir}
 The total infrared emission of a system, can also be used as a tracer of the SFR.
-Dust absorbs radiation from hot and young stars and re-emit it in infrared wavelengths, however, there is no one-to-one mapping between IR and UV emission \citep{Calzetti13}, therefore, integrating over full wavelength range of the IR part and calculating the TIR luminosity is a better tracer of the SFR instead of the IR single-band emission.
-\cite{Calzetti07} assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{star}(bol) = L(TIR)$ and calibrated the TIR luminosity of a system to calculate the SFR for a stellar population undergoing constant star formation over $\tau = 100$ Myr:
+Dust absorbs radiation from hot and young stars and re-emit it in infrared wavelengths, however, there is no one-to-one mapping between IR and UV emission.
+Therefore, integrating over the full wavelength range of the IR part and calculating the TIR luminosity is a better tracer of the SFR instead of IR single-band emission \citep{Calzetti13}.
+\cite{Calzetti13} assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{star}(bol) = L(TIR)$ and calibrated the TIR luminosity of a system to calculate the SFR for a stellar population undergoing constant star formation over 100 Myr:
 
@@
 \end{equation}
-where SFR(TIR) and L(TIR), star formation rate calculated from TIR emission and TIR luminosity are in M$_{\odot}$yr$^{-1}$ and erg/s respectively.
+where SFR(TIR) and L(TIR), the star formation rate calculated from TIR emission and TIR luminosity, are in M$_{\odot}$~yr$^{-1}$ and erg~s$^{-1}$ respectively.
+Part of the dust emission in galaxies (specially in M31) comes from the dust heated by the cosmic background radiation \citep[e.g.][]{Dole06, Calzetti13, Mattsson14}, hence, using the equation ~\ref{equ:sfr_fir} overestimates the SFR in M31.
 
-IR luminosity can be measured from the integration of the IR part of a spectral energy distribution (SED) of a galaxy or combining photometry data in different IR wavelengths.
-For second approach \cite{Draine07} modeled \Spitzer data and calibrated IR single-band photometry data to calculate the TIR luminosity.
+TIR luminosity can be measured from the integration of the IR part of a spectral energy distribution (SED) of a galaxy or combining photometry data in different IR wavelengths.
+For the second approach \cite{Draine07} modelled \Spitzer data and calibrated IR single-band photometry data to calculate the TIR luminosity.
 \cite{Boquien10} tested and modified this calibration as:
@@
 \end{equation}
-where L(8 \um),L(24 \um), L(70 \um) and L(160\um) are luminosities of the galaxy in 8 \um, 24 \um, 70 \um and 160 \um in unit of erg/s.
-We used equation ~\ref{equ:sfr_fir} to calculate second map of the SFR of M31 (figure ~\ref{fig:sfr,fir}).
-Using this method we calculated the total SFR 0.40 $\pm$ 0.04 M$_{\odot}$yr$^{-1}$.
-Table ~\ref{table:sfr} compares the total SFR from literature and current work.
+where L(8), L(24), L(70), and L(160) are luminosities of the galaxy in 8 \um, 24 \um, 70 \um and 160 \um in units of erg~s$^{-1}$.
+We used equation~\ref{equ:sfr_fir} to calculate the second map of the SFR of M31 (Figure~\ref{fig:sfr,fir}).
+Using this method we calculated the total SFR as $0.40 \pm 0.04$~M$_{\odot}$~yr$^{-1}$.
+Table~\ref{table:sfr} compares the total SFR from literature and current work.
 
@@
 \begin{minipage}{100mm}
-\caption{Comparison of Total Star Formation Rate of M31}
+\caption{Comparison of the total star formation rate of M31}
 \label{table:sfr}
@@
 \hline
-Current work&FUV and 24\um&0.31\\
-Current work&\halpha and 24\um&0.35\\
-Current work&TIR luminosity&0.4\\
+Current work&FUV and 24\um&0.31 $\pm$ 0.04\\
+Current work&\halpha and 24\um&0.35 \\
+Current work&TIR luminosity&0.4 $\pm$ 0.04\\
 \cite{Ford13}&FUV and 24\um&0.25\\
@@
 \cite{Azimlu11}&Extinction corrected \halpha&0.44\\
-\cite{Tabatabaei10}&Extinction corrected \halpha&0.27-0.38\\
+\cite{Tabatabaei10}&Extinction corrected \halpha&0.27--0.38\\
 \cite{Barmby06}&Infrared 8\um luminosity& 0.4\\
@@
 %----------------------------------------------------------------------------------------
-\section{Interstellar Medium}
-%----------------------------------------------------------------------------------------
-%Direct Measurement of the Gas Mass
-%----------------------------------------------------------------------------------------
-%\subsubsection{Direct Measurement of the Gas Mass}
+\subsection{Gas Surface Density}
+\label{sec:ISM}
 
-%The surface density of gas in the ISM of galaxies can be measured by direct observation of the neutral and molecular hydrogen.
-This method can be promising provided that the spatial resolution of observational data is high enough; nonetheless, due to technical limitations, attaining enough spatial resolutions to resolve clouds is almost impossible.
-This problem shows itself for distant galaxies more than nearby galaxies.
-As a result, using this method is limited and has a lot of uncertainties.
-
-%\subsubsection*{Molecular Clouds}
-%PB: these two paragraphs contain a lot of background information that could either be moved to the
-%PB introduction or be omitted; this info doesn't belong here.
- The molecular form of hydrogen in the ISM has no permanent electric dipole moment, which makes it really hard to detect.
+ The molecular form of hydrogen is really hard to detect.
 H$_2$ molecules are located in cool and dense molecular clouds, but fortunately they are not the only component of the molecular gas.
-The second dominant component, helium, is a mono-atomic gas and has the same problem as hydrogen, but the molecular gas also contains heavier elements such as carbon and oxygen which are combined to form CO \citep{Bolato13}.
-
-CO has a weak permanent electric dipole moment and a ground rotational transition with low excitation energy.
-Given its low energy and critical density, CO can easily be excited even in cold molecular clouds.
-Hence CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen \citep[see, for example,][] {Sanders84}.
-Higher rotational transition of CO can be used as a tracer as well, but they are not as common as the $J(1\rightarrow 0)$.
+CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen \citep[see, for example,][] {Sanders84}.
+Higher rotational transition of CO can be used as a tracer as well, but they are not as common as $J(1\rightarrow 0)$.
 The relation between CO emission and H$_2$ cloud mass is shown as:
@@
 where X$_{CO}$ is the conversion factor (also known as the X-factor).
-The X-factor could be different in regions within a galaxy due to difference in metallicity.
-Though assuming a constant conversion factor in cases such as M82 and M31 can lead to global molecular gas mass estimates that are very accurate,  but in regions with a low metallicity, there are uncertainties.
-Different groups are working on the various galaxies to measure the X-factor for each \citep{Wilson95, Bosselli02, Bolato13}.
+The X-factor could be different in regions within a galaxy due to the difference in metallicity \citep{Wilson95, Bosselli02, Bolato13}.
 In case of M31, different values of X-factor ($1-5.6 \times 10^{20}$) were adopted in the previous studies \citep[e.g.][]{Ford13, Bolato13, Leroy11, Bolato08, Nieten06}; however, since any constant differences in X-factor leads to horizontal changes in a plot of log(SFR) versus Log($\Sigma_{\rm {gas}}$), and does not affect our K-S law power index for molecular gas,  we chose $X_{\rm {CO}}= 2 \times 10^{20}$  the same as many other works \citep[e.g.][]{Ford13, Smith12}.
-This assumption might have some effect on the total gas mass, but considering the fact that HI mass dominates H$_2$ mass in M31 this effect is small.
+Since HI mass dominates H$_2$ mass in M31, the constant X-factor has negligible affect on the total gas mass.
 The total gas mass was calculated from:
@@
 \end{equation}
-where  factor of 1.36 is a constant to consider He and the other heavier elements effect on mass, M$_{HI}$ is a mass of neutral hydrogen obtained from 21cm observations and M$_{H_2}$ is from equation ~\ref{equ:conversion} in unit of M$\sun$.
+where  factor of 1.36 is a constant to consider He and the other heavier elements affect on the total gas mass, M$_{HI}$ is mass of neutral hydrogen that were obtained from 21cm observations, and M$_{H_2}$ calculated from equation~\ref{equ:conversion} in units of M$_{\sun}$.
 
@@
 %----------------------------------------------------------------------------------------
-\section{Stellar Mass}
+\subsection{Stellar Mass}
 \label{sec:starmass}
@@
 \includegraphics[width=164mm]{star.eps}
-\caption{Stellar Mass surface density. This mass is produced using $IRAC$ 3.6 $\mu$ m data and its calibration presented in equation ~\ref{equ:eskew}}
+\caption{Stellar Mass surface density with pixel size of 4.3\arcsec and FWHM of 1\arcsec.7.
+The stellar surface density map is produced using IRAC 3.6~$\mu$m data and its calibration presented in equation~\ref{equ:eskew}.}
 \label{fig:stellarmass}
@@
 
-Stellar mass can be measured using a suitable calibration between flux/luminosity of stars in specific wavelengths and stellar mass.
-The basic idea behind these kind of calibrations comes from the fact that one can use the star formation histories recovered from synthesizing the stellar optical colour magnitudes in different regions in the galaxies.
-The calculated stellar mass can be used  to calibrate the fluxes from the stars as the easily measurable parameters of stars.
-Using NIR bands, different groups tried to make a map of stellar mass distributions within galaxies \citep[e.g.,][]{Elmgreen84}.%  Using $B-V$ colours \citep{Bell01} and $Spitzer$ 3.6- and 4.5-\um, M/L correction, \cite{Kendall08} produced stellar mass surface densities of M81.
-%PB: do you mean M81 here?
-If so, it's not quite clear why you're mentioning a different galaxy.
-
-We calculated the stellar mass within the M31 using calibration of the 3.6\um flux by \cite{Eskew12}.
-Since 3.6\um flux is almost insensitive to the emission from the young stellar population, dust absorption and emission, this band-pass was used for the calibration of the stellar mass.
-By using data from the large Magellanic cloud, they find an empirical relation between stellar mass and luminosity of stars as:
+Near IR band such as: 3.6\um, 4.5\um and K band emission, are almost insensitive to the emission from the young stellar population, dust absorption and emission, which make them a good tracer of the mass of the older stellar populations\citep[e.g.,][]{Elmgreen84, Eskew12, Zhu10}.
+We calculated the stellar mass within M31 using calibration of the 3.6\um flux by \cite{Eskew12}.
+They used data from the Large Magellanic Cloud, and introduced an empirical relation between stellar mass and flux of stars:
 
@@
 \label{equ:eskew}
-M _{\star}= 10^{5.97} F_{3.6}(\frac{D}{0.05})^2
+M _{\star}= 10^{5.97} F_{3.6}\left(\frac{D}{0.05}\right)^2
 \end{equation}
-where M$_{\star}$ is the stellar mass in mass of The Sun, $F_{3.6}$ is the 3.6\um flux in $Jy$ , and D in the distance of the galaxy in Mpc.
-Figure ~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6\um.
-Using this method we calculated the total stellar mass of the galaxy is $6.9 \times 10^{10}$M$_{\odot}$ with 6$\%$ uncertainty.
+where M$_{\star}$ is the stellar mass in solar masses, $F_{3.6}$ is 3.6\um flux in Jy, and $D$ is the distance of the galaxy in Mpc.
+Figure~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6\um.
+In this figure pixels with dark blue colour show zero M$_{\odot}$, while dark red ones show pixels with mass of more than 6.4e3 M$_{\odot}$.
+Using this method we calculated the total stellar mass of the galaxy to be $6.9 \times 10^{10}$M$_{\odot}$ with 6$\%$ uncertainty.
 This result is in fair agreement with the result from \cite{Tamm12}.
-They calculated that stellar mass in the M31 is $(10-15) \times 10^{10}$M$_{\odot}$, 56$\%$ which is in the disk and the rest is in the bulge of the galaxy.
-%PB: need to compare with other results, as you did with SFR.
+They calculated that stellar mass in M31 is $(10-15) \times 10^{10}$M$_{\odot}$, 56$\%$ of which is in the disk with the rest in the bulge of the galaxy.
 
@@
 \section{Scaling SFR}
-\subsection{Fitting method}
-\label{sec:fitting}
-%For investigating and comparing the SFR laws in M31
-%Given available
-\begin{figure*}
-\centering
-\includegraphics[width=164mm]{ks_all_f.png}
-\caption{The result from fitting the Kennicutt-Schmidt law on data from whole galaxy using pixel by pixel method.
-Plots have a different pixel size.
-Each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents regions $~$ Kpc and points in plots with surface density of HI or total gas mass, represents region in $~$Kpc.}
-\label{fig:ks,all}
-\end{figure*}
+\subsection{Star formation laws}
 
-Producing the SFR, gas mass and stellar mass maps, provides of with enough data to examine and compare the K-S law and the extended Schmidt law. % are possible. 
-We investigated the K-S law and the extended Schmidt law by using  pixel by pixel method.
-Our final results are divided by two sets of different pixel sizes.
-That's because the H$_2$ gas mass map has better resolution and lower pixel size of the  HI gas mass map.
-Consequently, any plots with surface density of H$_2$ as a tracer of the gas mass, have more data points.%in whole galaxy as well as comparing the laws in three different regions of galaxy based on their distance from the centre of the galaxy.
-We can re-write equations ~\ref{equ:ks_org} and ~\ref{equ:es_org} in a logarithmic scale. Hence, we would have two linear equations, as:
-
-\begin{subequations}
-\begin{equation}
-\label{eq:sfr_law_ks_log}
-\log_{10} \eqsigmasfr = N~\log_{10} \eqsigmagas + A
-\end{equation}
-\begin{equation}
-\label{eq:sfr_law_es_log}
-\log_{10} \eqsigmasfr = \eqnprime~\log_{10} \eqsigmagas + \beta~\log_{10}\eqsigmastar  + A^\prime
-\end{equation}
-\end{subequations}
-where, N, $\eqnprime$, $\beta$, A, and A$^\prime$ are free parameters of fittings. Units in the equation above, are the same as the units in the equations ~\ref{equ:ks_org} and ~\ref{equ:es_org}.
-
-We found the free parameters by applying the hierarchical Bayesian linear regression method as described in \cite{Shetty13}.
-Shetty and his colleagues used a Bayesian linear regression approached to develop a new method to find the K-S law parameters, considering the measurement uncertainties as well as hierarchical data structure.
-For the K-S law's fitting parameters, we used a 'R' code provided by Shetty's group.
-Uncertainties on each observable quantity was measured considering the background noise photometry errors and calibration uncertainties.%PB: are the background noise errors and calib uncertainties discussed elsewhere in this paper (in which case reference the section) or do they need to be discussed here.
-%SR no they didn't, should I discusse more?
-%SR usually nobody write about them.
-%PB I think you should discuss the uncertainties somewhere -- presumably they affect your fitting results, so the reader needs to know where the uncertainties come from and their approximate size.
-
-For the extended Schmidt law, we expended the code in the way that instead of using simple linear regression, which is the case of the K-S law, it uses multiple linear regression.
-In this case, we were able to examine the effect of the stellar mass in the SFR as shown in equation ~\ref{eq:sfr_law_es_log}.
-
-We also test each laws on three different regions.
-The regions were chosen the same as regions introduced in \cite{Draine14}.
-They found that across the galaxy, with increasing distance from the centre of galaxy dust/H ratio declines monotonically.
-Considering that dust/H ratio has a direct relation to metallicity, they showed that the metallicity of the M31 changes in the same manner.
-%PB: need to expand this a bit: it's well-known that dust-to-gas and metallicity both go down as distance to galaxy centre increase, but how would you expect this to affect  the SFR/gas/stellar mass relation?
-
-\begin{equation}
-\label{eq:dust2gas_vs_R}
-\frac{M_d}{M_H} \approx
-\left\{ \begin{array}{l l}
-0.0280 \exp(-R/8.4\kpc)  & R< 8\kpc\\
-0.0165 \exp(-R/19\kpc)   & 8\kpc < R < 18\kpc\\
-0.0605 \exp(-R/8\kpc)    & 18\kpc < R \la 25\kpc ~~~,\\
-\end{array}
-\right.
-\end{equation}
-
-Applying the SFR laws in these regions, provides a tool to consider the effect of the distance from the centre of the galaxy on SFR laws as well as the effect of the metallicity on those.
-Table ~\ref{table:res} shows fitting parameters and their uncertainties for the whole galaxy and each different regions.
-\halpha data does not have a smooth background.
-Also the centre of galaxy in this data is diffused, so we do not have any data from the centre of the M31.
-Since it was the only available \halpha data from the M31, We used this data anyway.
-However, results from the \halpha SFR map are not shown here and will be discussed in appendix ~\ref{app:halpha}.
-%can I make it foot note?
-
-\subsection{Star formation laws}
+We made three SFR maps, three gas mass density maps and a stellar mass density map of whole galaxy.
+We applied both laws on whole galaxy on each two combination of SFR and gas mass density maps, along with applying the laws on three different regions.
+As a result we were be able to test each law 36 times.
 In total, we produced 72 different plots, which show either the K-S law or the extended Schmidt law, both in whole galaxy and in different distances from the centre of the M31.
-Additionally, we can use these results to see if there is any correlation  between the SFR laws and the metallicity, as it was described in ~\ref{sec:fitting}.
-
-%We had three SFR maps, three gas mass density maps.
-We applied both laws on whole galaxy on each two combination of two of them, along with applying the laws on three different regions of them.
-As a result we were be able to test each law 36 times.
-In total we produced 72 different plots which show the either K-S law or the extended Schmidt law, and helps us to compare both laws in whole galaxy and in different regions.
-Additionally, these plots provide us a tool to compare the differences in SFR calibrations, ISM gas tracers, and effect of metallicity on SFR.
-% PB: I think you should keep some of the text commented-out above, so that you can show where the number 72 comes from.
+Additionally, we can use these results to see if there is any correlation between the SFR laws and the metallicity, as it is going to be described in ~\ref{sec:fitting}.
 
@@
 \includegraphics[width=164mm]{c3d_all_ks_regs_f.png}
-\caption{Same as figure ~\ref{fig:ks,all}, but in this figure we separated pixels from different regions in the galaxy by their colours.
-The regions with R less than 8$\kpc$, $8\kpc < $R $< 18\kpc$, and $18\kpc <$ R $\la 25\kpc$ are shown in red, green and blue, respectively.}
+\caption{Same as Figure~\ref{fig:ks,all}, but in this figure we separated pixels from different regions in the galaxy by their colours.
+The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$ are shown in red, green and blue, respectively.}
 \label{fig:ks,regs}
@@
 
-%SR: Should I talk SFR(TIR) or SFR (TIR)?!!!
 %PB: no space, so SFR(TIR)
-
-Figure ~\ref{fig:ks,all} shows the pixel by pixel fitting of the K-S law on the whole galaxy.
+Figure~\ref{fig:ks,all} shows the pixel by pixel fitting of the K-S law on the whole galaxy.
 First row plots are the surface density of the SFR(TIR), which is calculated using  the TIR emission form section ~\ref{sec:sfr_fir}, versus the gas surface density traced by only the molecular gas (H$_2$),  only atomic gas (HI), and total gas from right to left, respectively.
 The only difference between the upper and lower plots is that in the lower row the SFR indicator is the FUV plus 24\um emission.
-Figure ~\ref{fig:ks,regs} is the same as figure ~\ref{fig:ks,all}.
+Figure~\ref{fig:ks,regs} shows the same data as Figure~\ref{fig:ks,all}.
 However, in this figure we separated pixels from different regions in the galaxy by their colours.
@@
 We took the similar approach for the extended Schmidt law.
-Figures ~\ref{fig:es,all} to ~\ref{fig:es,regs,fuv,tot} show the results of the pixel by pixel fitting of this law.
-For the extended Schmidt law fittings, we plotted our results in 3D to illustrate the relationship between the surface density of the SFR, the gas mass surface density, and stellar mass density more clearly.
+Figures~\ref{fig:es,all}--\ref{fig:es,regs,fuv,tot} show the results of the pixel by pixel fitting of this law.
+For the extended Schmidt law fitting, we plotted our results in 3D to illustrate the relationship between the surface density of the SFR, the gas mass surface density, and stellar mass density more clearly.
 In these series of plots, X-axis is the gas mass  surface density, either molecular gas (H$_2$), the atomic gas (HI) or the total gas, Y-axis is the SFR(TIR) or SFR(FUV + 24 $\mu$m), and Z-axis is the stellar mass surface density.
@@
 For a comparison, one can easily conclude that shadows on the X-Y surface is a reproduction of the K-S law.
-Colours used in plots ~\ref{fig:es,regs,fir,tot} to ~\ref{fig:es,regs,fuv,tot} are the same as colours in  ~\ref{fig:ks,regs}.
 
@@
         \includegraphics[width=\textwidth]{es_tot_fuv_tot_gas_f.png}
-        \caption{SFR,FUV+24\um vs surface density of total gas}
+        \caption{SFR,FUV+24\um vs. surface density of total gas}
         \label{fig:es,all,fuv,tot}
     \end{subfigure}
-    \caption{The result from fitting the extended Schmidt law on data from whole galaxy using pixel by pixel method.
-The plots show the SFR vs surface density of gas, and z-axis is the surface density of the stellar mass.
+    \caption{The results from fitting the extended Schmidt law on data from whole galaxy using pixel by pixel method.
+The plots show the SFR vs.
+the surface density of gas, and z-axis is the surface density of the stellar mass.
 Each figure shows different combinations of the SFR tracer and gas mass tracer results.
-Plots have a different pixel size.
-Each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents regions $\sim$30~Kpc and points in plots with surface density of HI or total gas mass, represents region in $\sim$155~Kpc.}
+As in Figure~\ref{fig:ks,all}, the analyses use different pixel sizes.
+Each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents a region of size $\sim$30~pc and each point in plots with surface density of HI or total gas mass represent a region of size $\sim$155~pc.}
     \label{fig:es,all}
@@
 \includegraphics[width=162mm]{c3d_fir_tot_f.png}
-\caption{Fitting result from the SFR(TIR) vs total gas.}
+\caption{Fitting result from the SFR(TIR) vs total gas.
+Same as Figure~\ref{fig:es,all,fir,tot}, but in this figure we denote pixels from different regions in the galaxy by their colours.
+The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$ are shown in red, green and blue, respectively.}
 \label{fig:es,regs,fir,tot}
@@
 \includegraphics[width=162mm]{c3d_fuv_tot_f.png}
-\caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs total gas.}
+\caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs total gas.
+Same as Figure~\ref{fig:es,all,fuv,tot}, but in this figure we denote pixels from different regions in the galaxy by their colours.
+The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$ are shown in red, green and blue, respectively.}
 \label{fig:es,regs,fuv,tot}
@@
 \begin{table*}
-\caption{Fitting parameters of the SF laws from applying the Bayesian.}
+\caption{Fitting parameters of the SF laws from applying the Bayesian method}
 \label{table:res}
@@
 \hline\hline
-\multicolumn{1}{c}{\multirow{1}{*}{Region}} & SFR Tracer& Gas Tracer & N & $\sigma_N$ & A & \nprime & $\sigma_{\eqnprime}$ & $\beta$ & $\sigma_\beta$ & A$^\prime$& \\
+\multicolumn{1}{c}{\multirow{1}{*}{Region}} & SFR Tracer& Gas Tracer & $N$ & $\sigma_N$ & $A$ & \nprime & $\sigma_{\eqnprime}$ & $\beta$ & $\sigma_\beta$ & A$^\prime$& \\
 \hline
@@
 \end{table*}
+
+\subsection{Fitting method}
+\label{sec:fitting}
+
+\begin{figure*}
+\centering
+\includegraphics[width=164mm]{ks_all_f.png}
+\caption{The result from fitting the Kennicutt-Schmidt law on data from whole galaxy using the pixel by pixel method. The points in the plots represent 
+different pixel sizes due to differences in the resolution of the H$_2$ and HI maps.
+Each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents a region of size $\sim$30~pc and each point in the plots with surface density of HI or total gas mass represents a region of size $\sim$155~pc.
+} 
+\label{fig:ks,all}
+\end{figure*}
+
+Producing the SFR, gas mass and stellar mass maps, provides enough data to examine and compare the K-S law and the extended Schmidt law.
+We investigated the K-S law and the extended Schmidt law by using pixel by pixel method in whole galaxy as well as comparing the laws in three different regions of galaxy based on their distance from the centre of the galaxy.
+Our final results have two sets of different pixel sizes.
+That is because the H$_2$ gas mass map has better resolution and smaller pixel size of the HI gas mass map.
+Consequently, any plots with surface density of H$_2$ as a tracer of the gas mass will have more data points.
+
+We can re-write equations~\ref{equ:ks_org}~and~\ref{equ:es_org} in a logarithmic scale. Hence, we would have two linear equations, as:
+
+\begin{subequations}
+\begin{equation}
+\label{eq:sfr_law_ks_log}
+\log_{10} \eqsigmasfr = N~\log_{10} \eqsigmagas + A
+\end{equation}
+\begin{equation}
+\label{eq:sfr_law_es_log}
+\log_{10} \eqsigmasfr = \eqnprime~\log_{10} \eqsigmagas + \beta~\log_{10}\eqsigmastar  + A^\prime
+\end{equation}
+\end{subequations}
+where, N, $\eqnprime$, $\beta$, A, and A$^\prime$ are free parameters of fittings. Units in the equation above, are the same as the units in the equations ~\ref{equ:ks_org} and ~\ref{equ:es_org}.
+
+We found the free parameters by applying the hierarchical Bayesian linear regression method as described in \cite{Shetty13}.
+Shetty and his colleagues used a Bayesian linear regression approached to develop a new method to find the K-S law parameters, considering the measurement uncertainties as well as hierarchical data structure.
+For the K-S law's fitting parameters, we used a 'R' code provided by Shetty's group.
+For the extended Schmidt law, we expended the code in the way that instead of using simple linear regression, which is the case of the K-S law, it uses multiple linear regression.
+In this case, we were able to examine the effect of the stellar mass in the SFR as shown in equation ~\ref{eq:sfr_law_es_log}.
+
+Uncertainties on each observable quantities were measured by following the method described in \cite{Kennicutt07}.
+We used quadratic sum of variance of the local background of each luminosity map, from the original pixel size images, Poisson noise of images, and calibration uncertainties.
+Since we used pixel by pixel fitting, we do not consider the photometric uncertainties in our methods.
+%PBnew: not sure I see how pixel by pixel fitting means that you don't have to
+% worry about photometric uncertainty; maybe I am just not understanding this sentence
+%meeting: background uncertainties
+
+%PB20150428: I just realized that you first  discuss the 3 different regions a couple of paragraphs above this. Think this means that this paragraph should go after the first paragraph of section 4.1.
+We also test each laws on three different regions.
+The regions were chosen the same as regions introduced in \cite{Draine14}.
+They found that across the galaxy, with increasing distance from the centre of galaxy dust/H ratio declines monotonically.
+Considering that dust/H ratio has a direct relation to metallicity, they conclude that the metallicity of the M31 changes in the same manner.
+As a result they introduced these three different regions as $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$.
+%PB20150428: not really clear from the text above why the 3 different regions are defined where they are.
+Need more detail about what Draine et al did.
+that made them think that 8 and 18 kpc were important, although I still think that (as in my comments below) the precise Md/Mh values are not what's important.
+Also, from the Draine paper I see that they are using elliptical annuli and not circular ones (which Ford et al did as well).
+You are doing the same, right?
+Need to describe this.
+%PBnew: don't think you really need the Md/MH values here, just giving the
+% region locations is enough. But this makes me think: what are the effects of
+% a changing Md/Mh on the derived SFR? Could they be driving (or hiding) differences in SFR laws between regions?
+
+% \begin{equation}
+% \label{eq:dust2gas_vs_R}
+% \frac{M_d}{M_H} \approx
+% \left\{ \begin{array}{l l}
+% 0.0280 \exp(-R/8.4\kpc)  & R< 8\kpc\\
+% 0.0165 \exp(-R/19\kpc)   & 8\kpc < R < 18\kpc\\
+% 0.0605 \exp(-R/8\kpc)    & 18\kpc < R \la 25\kpc ~~~,\\
+% \end{array}
+% \right.
+% \end{equation}
+
+%new metal materials
+%PB20150428: this is a good start but needs more detail and grammar work.
+(Some of this material might go better in the introduction.) List the other things besides metallicity that change with distance from the centre of the galaxy.
+Explain in more detail how the metallicity affects the components of the SFR law.
+If there is a correlation between metallicity and SFR (last sentence), what is the sense of the correlation, how big is it?
+Applying the SFR laws in these regions, provides a tool to consider the effect of the distance from the centre of the galaxy on SFR laws as well as the effect of the metallicity on them.
+
+The effect of the metallicity on the star formation laws are very complicated.
+Metallicity affect on each component of the star formation laws in different way.
+There are many studies on correlation of the metallicity with stellar mass, SFR, and the effect of the metallicity on the ISM \citep[e.g.,][]{Boissier03, Leroy08, Krumholz09, Mannucci10, Dib11, Lilly13}.
+The scope of these studies is that metallicity has a critical role on the formation of the H$_2$ gas.
+Thus, there should be a correlation between metallicity and the SFR.
+
 %----------------------------------------------------------------------------------------
@@
 \section{Discussion}
-% PB: Here's an idea for how to organize this in paragraphs:
-% 1. Global KS law: linear or sublinear?
-% 2. KS laws with gas components separated: same or different?
-% 3. KS law variation with distance
-% 4. EKS law: agrees with Shi? Better or worse than KS?
-% 5. EKS with gas components separated: same or different?, compare to KS
-% 6. EKS law variation with distance, compare to KS
-% 7. Answer the question in the title: which SF law best captures what's going on?
 
-% Not sure where to put this but you also want to answer the question "does it matter which SFR tracer you use" somewhere.
-All of the factors that go into the "72 plots" should be discussed at some point.
-
-%PB: By the way: better not to start paragraphs with "However" and "On the other hand" as it makes for an awkward transition between topics.
-
-Table ~\ref{table:res} shows the results of the hierarchical Bayesian fit.
-Due to the similarity of our results for both SFR(TIR) and SFR(FUV+24$\mu$m) and the fact that they are in close agreement with each other,
-%PB: the two parts of the sentence above ("similarity of results" and "in close agreement") seem to say the same thing -- or am I not understanding what you mean here?
-We only interpret the results from the SFR(FUV+24$\mu$m).
+Table ~\ref{table:res} shows the results of the hierarchical Bayesian fit and their uncertainties for the whole galaxy and each different regions..
+Due to the similarity of our results for both SFR(TIR) and SFR(FUV+24$\mu$m), we only interpret the results from the SFR(FUV+24$\mu$m).
 Results from the SFR(H$\alpha$) fitting are going to be discussed in the Appendix ~\ref{app:halpha}.
-%In this section we are going to talk about result from fitting the K-S Law, results from fitting the extended Schmidt law and the comparison between these two star formation laws and which one works better in the M31.
-%SR: Should I keep that or not
-%PB: I don't think you need the "In this section" sentence; the content is clear from the subsection headings.
+%PBnew: Use a few sentences to discuss similarity between SFR(TIR) and SFR(FUV+24$\mu$m), then go on to say you're only going to discuss one. /done
 
@@
 
-As mentioned before, the K-S law in the M31 was tested by many groups. %PB: edits made to next sentences. Note that plural of "index" is "indices".
-In the most recent work on M31, \cite{Ford13} investigated the K-S law in six annuli and the global case using the ordinary least squares (OLS) fitting method.
-To make comparisons between our results easier, we averaged the power indices of their annuli which overlap with our three different regions.
+As mentioned before, the K-S law in the M31 was tested by many groups.
+In one of the most recent works on M31, \cite{Ford13} investigated the K-S law in six annuli and the global case using the ordinary least squares (OLS) fitting method.
+To make comparisons between our results easier, we averaged the power indices for their annuli which overlap with our three different regions so we could compare results in the same regions.
 \cite{Tabatabaei10} also applied the K-S law to M31 using the OLS fitting method, and have different results from \cite{Ford13}.
 
-Our results for the global case of the K-S law show that using total gas gives a sub-linear relation between the surface density of the SFR and the total gas surface density.
-While, for using the H$_{2}$ only gas or HI only gas we find the super-linear relation.
+Our results for the global case of the K-S law show that using total gas gives a sub-linear relation between the \sigmasfr and \sigmatotalgas.
+While, for using the H$_{2}$ only gas or HI only gas we find the nearly super-linear relation.
 These results are different from power indices estimated by \cite{Ford13}, $N=2.03\pm0.04$ in case of total gas and $N=0.6\pm0.01$ in case of H$_{2}$ only gas.
 \cite{Tabatabaei10} estimated the K-S law power index $N=1.30\pm0.05$ using the total gas and $N=0.96\pm0.03$ using the H$_{2}$ only gas.
-The reason behind these differences is mostly because of the statical method we chose.The OLS fitting on the H$_{2}$ only gas gives us the power index of $N=0.54\pm0.003$ which is in good agreement with previous results.
-%PB: well, 0.54 agrees with 0.6, but it doesn't agree with 0.96. If your
-%uncertainties and theirs are right, 0.54 pm 0.003  is actually in poor agreement 
-% with 0.06 pm 0.01- it's at least 6 standard deviations away.
-% so need to clarify your argument here.
+The reason behind these differences is mostly because of the statical method we chose.
+The OLS fitting using \sigmatotalgas gives us the power index of $N=1.20\pm0.10$ which is in good agreement with \cite{Tabatabaei10} results.
 
@@
 Furthermore, \cite{Shetty13} used the same data as \cite{Bigiel08} and argued that using the hierarchical Bayesian fit leads to significant galaxy-by-galaxy variation between power indices and all of them are lower than \cite{Bigiel08}.
+%PBnew: Need to link material in this paragraph to our results.
 
@@
 Consequently, the depletion time increases by increasing the total gas.
-On the contrary, the super-linear relation suggests that the depletion time is decreasing with increasing the amount of the CO or/ and HI gas.
-The further conclusion is more similar to the initial the initial suggestion of the K-S law.
-% PB: extra "to the initial" here?
+On the contrary, the super-linear relation suggests that the depletion time is decreasing with increasing the amount of the CO or/and HI gas.
+The further conclusion is more similar to the initial suggestion of the K-S law.
 If we assume that stars form in the molecular clouds, the decreasing of the SFE with increasing the total gas is justifiable.
 
-The results of the hierarchical Bayesian fitting on the regions with different distances from the centre of the galaxy give us similar values in the global case.
+% PBnew: in following paragraph, switch the order so that you compare with Ford
+% (observational) first, then Krumholz (theory). Is there theoretical work that 
+% predicts different dependencies? It's important to note the work that disagrees
+% with you as well as agrees.
+The results of the hierarchical Bayesian fitting on the regions with different distances from the centre of the galaxy give us similar values as the global case.
 For all three regions, the K-S law using the total gas leads to sub-linear relation between the SFR and the surface density of the total gas.
-Likewise, for using the H$_{2}$ only gas or HI only gas, this relationship is either linear or super-linear.
+Likewise, for using the H$_{2}$ only gas or HI only gas, this relationship is either linear or nearly super-linear.
+These results agree with results from \cite{Krumholz09}.
+They showed that for the regions with \sigmagas $\leq 100$ M$_{\odot}$pc$^{-2}$, \sigmasfr and $\Sigma_{H_2}$ have a nearly linear correlation.
+They also conclude that, at the intermediate total gas column density, (\sigmagas $\leq 100$ M$_{\odot}$pc$^{-2}$), \sigmasfr and \sigmagas have a linear or slightly sub-linear correlation which is similar to our results.
 The K-S law power index varies with the distance of the galaxy.
-Considering molecular gas, the power law index is increasing by going to further distances from the center of the galaxy.
-This trend also can be seen in the \cite{Ford13}.
-For the atomic gas only or the total gas this trend cannot be seen.
-This could be the result of the fact that, the atomic gas in the center of the galaxy is less than the other regions in the galaxy.
-% PB: I don't quite understand your argument in the previous sentence.
-The increasing of the power index in this case may be an effect of the decreasing metallicity across the galaxy, or other physical properties of the galaxy such as stellar mass (see section ~\ref{sec:es_res}).
+Considering molecular gas, the power law index is increasing by going to further distances from the centre of the galaxy, which can be seen in the results from \cite{Ford13}, too.
+However, this growth does not happen for total gas or atomic gas cases.
+The increasing of the power index in this case may be an effect of the decreasing metallicity across the galaxy, which leads to have less SFE, or other physical properties of the galaxy such as stellar mass (see section ~\ref{sec:es_res}).
 
@@
 The results of the fitting the extended Schmidt law in a global case give us a sub-linear relation between the SFR and the density of stars.
-Results from the fitting the extended Schmidt law using the molecular gas only are $\eqnprime = 1.09$ and $\beta = 0.25$ which is close to the original suggestion of the extended Schmidt law in the global case, $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$.
-Although, the original results were from using the total gas surface density instead of the molecular gas only.
-Our results from the fitting the total gas surface density gives us a lower power index of the gas mass and a higher power index of the stellar mass.This relation suggests that, although increasing the total gas cause to decrease the SFE but the existing stars will increase the SFE.
-% PB: as above, not convinced that 1.09 is "close" to 0.8 pm 0.01.
-% and 0.25 is close to 0.6
+Results from the fitting the extended Schmidt law using the molecular gas only are %$\eqnprime = 1.09 \pm 0.01$ and $\beta = 0.25 \pm 0.004$ which
+follows the same trend of the extended Schmidt law in the global case,% $\eqnprime = 1.38 \pm 0.05$ and $\beta = 0.36\pm0.02$, 
+,which is the nearly super-linear correlation with \sigmagas and sub-linear correlation with \sigmastar.
+Although, the original results were average results of many type galaxies using the total gas surface density.
+Our results from the fitting the total gas surface density gives us a lower power index of the gas mass and a higher power index of the stellar mass.This relation suggests that, although increasing the total gas causes a decrease to the SFE but the existing stars will increase the SFE.
 
- The fitting results on the regions with different distances from the centre of the galaxy are more similar to the results from \cite{Shi11}.
-Taking the average of our three regions leads us to the conclusion that using molecular gas only or atomic gas only $\beta$ is 0.60 and 0.55 which is very close to prediction of \cite{Shi11}.
+ The fitting results on the regions with different distances from the centre of the galaxy are more similar to the results from \cite{Shi11}, $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$.
+Taking the average $\beta$  from results of using molecular gas only gives us $\beta = 0.63$ which is in good agreement with \cite{Shi11} but, $\eqnprime$ is more than the original suggestion.
 In the local case, the same as global case power indices calculated using total gas surface density, are much smaller than the original suggestion of \cite{Shi11}.
-% PB: can you explain why this might be?
+However, the final indices reported in the extended Schmidt law are an average over 12 different spiral galaxies, and our result is a lower limit for this law.
+%PBnew: why is our result a lower limit? 
+ Another reason of differences between indices could be because of fitting method.
+Using the OLS fitting, one only will consider the SFR errors, nevertheless, the hierarchical Bayesian regression fitting considers uncertainties on all the parameters.
+Different treating with uncertainties would give us the different result.
 
- \cite{Kim13} using 3D numerical hydrodynamic simulations showed that in outer disk regions of the galaxy $\eqsigmasfr \propto \eqsigmagas \rho_{sd}^{0.5}$ where $\rho_{sd}$ is the mid-plane density of the stellar disk.
-Our results for total gas in regions with 18kpc$<$ R $\la 25$ kpc shows $log_{10}(\eqsigmasfr) \propto 0.5 \times log_{10}(\eqsigmastar)$, which is the same as simulations.
-However, in this case we found a sub-linear relation between \sigmasfr and \sigmagas while \cite{Kim13} found a linear relation.
-% PB: So what does this difference mean?
+ Thus, we can conclude that the stars affect on the SFR specially on the regions with lower amount of the gas.
+\cite{Kim13} using 3D numerical hydrodynamic simulations showed that in outer disk regions of the galaxy  where the total gas is dominated by HI gas,, the SFR have correlation with $\rho_{sd}^{0.5}$ where $\rho_{sd}$ is the mid-plane density of the stellar disk plus dark matter.
+This is because of the fact that in outer regions of the disk the gravity from stars dominates.
+This results are in agree with our finding regarding that in outer regions of M31 the stellar surfaces density has more effect on the SFR.
+
+%PBnew: need to discuss metallicity here as well.
+%new metal material
+%%PB20150428: this paragraph neeeds a topic sentence
+\cite{Leroy08} showed that the SFR(FUV+24$\mu$m) does not change with changing metallicity.
+However, \cite{Boissier03} showed that the metallicity has inverse correlation with CO-H$_2$ conversion factor, which means that, using a constant conversion factor at high metallicity regions causes the overestimation of the molecular gas, and in low metallicity it leads to the underestimation of the H$_2$.
+Since \cite{Draine14} showed that metallicity in the centre of M31 is more than the outer disk regions, power index from the fitting the K-S law in the case of the molecular gas only or total gas should be steeper than what we measured.
+%PB20150428: rather than saying "the true PL index should be steeper" I think it's better to say "our estimate is an underestimate" or "our estimate is a lower limit".
+What does it mean for the PL index in the centre to be an underestimate?
+(ie if we corrected for this would it agree better with other regions/other studies, or worse, or what?)
+
+%%PB20150428: this paragraph neeeds a topic sentence
+\cite{Mannucci10} and \cite{Lilly13} using both observations and simulation results showed that metallicity depends on both the stellar mass and the SFR.
+They found that at any fixed stellar mass, metallicity and the SFR have an inverse correlation.
+Afterward, assuming the K-S law holds for their sample they found the correlation between, metallicity and the stellar mass, the gas mass and the SFR.
+They found that increasing both the SFR and the stellar mass increases metallicity, but increasing the gas mass decreases metallicity (equation 9 in \citep{Mannucci10}).
+ %%PB20150428: what does this mean for our work? Does it agree or disagree?
 
@@
 %----------------------------------------------------------------------------------------
-\section{Summery}
+\section{Summary}
+
 In order to test the effect of stars on the SFR in both global and local scales in the M31, we have determined surface density of star formation rate, gas mass and the stellar mass of this galaxy.
@@
 For the second SFR map, we used a combination of the H$\alpha$ and 24 \um emission, and the third one was produced using total-infrared luminosity.
-We noticed that H$_\alpha$ data available for M31 have a non-smooth background and the SFR map using this data would lead us to not accurately answer ~\ref{app:halpha}.
+We noticed that H$_\alpha$ data available for M31 is not suitable for SFR study ~\ref{app:halpha}.
 We calculated the total SFR from FUV and 24 \um emission is 0.31$\pm$ 0.04 M$_{\odot}$yr$^{-1}$.
 
-We also produced the ISM map, using molecular gas only, atomic gas only and the total gas.
+We also produced the ISM map, using molecular gas only, atomic gas only and the total gas. %PBnew: following 2 sentences are too much detail for a summary. 
 For the molecular gas map, we assumed the CO-H$_2$ conversion factor is $2 \times 10^{20}$ (K km s$^{-1}$)$^{-1}$cm$^{-2}$. 
@@
 
+We confirmed \cite{Shi11} suggestions that the surface density of stars has impact on the SFR, and in regions with law gas surface brightness this impact is even more important.
+We also showed that, one of the reasons of adversity of results of power index of K-S law in M31 comes from differences in fitting method and error analysis.
+%PBnew: do you mean 'diversity' instead of 'adversity' ?
+%PBnew: description of your results should be more extensive: 2 sentences is not enough.
+
 %----------------------------------------------------------------------------------------
-%Acknowledgment 
+%Acknowledgement 
 %----------------------------------------------------------------------------------------
-\section*{Acknowledgment}
+%\section*{Acknowledgement}
+The authors thank Dr. R. Shetty for giving us his hierarchical Bayesian fitting code, and Dr. D. Kruijssen for his idea about 3D plots.
+The authors acknowledge research support from the Natural Sciences and Engineering Research Council of Canada and from the Academic Development Fund of the University of Western Ontario. 
 This research made use of Montage, funded by the National Aeronautics and Space Administration's Earth Science Technology Office, Computation Technologies Project, under Cooperative Agreement Number NCC5-626 between NASA and the California Institute of Technology.
-Montage is maintained by the NASA/IPAC Infrared Science Archive.
+Montage is maintained by the NASA/IPAC Infra-red Science Archive.
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
-\newpage
+%PBnew: something is wrong with the references here: should have 'et al.' instead of 'e.a.'
 \bibliography{ref.bib}
@@
 
+As mentioned in Section~\ref{sec:vislight}, we used the H$\alpha$ data from the Nearby Galaxies Survey \citep{Massey07} to create the SFR map.
+These data are publicly available in H$\alpha$ and R band in 10 overlapping fields across the disk of M31.
+Making a spatially resolved SFR map of M31 using H$\alpha$ emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of H$\alpha$ continuum-subtracted map, and finally correcting for the flux contribution to the \halpha filter from the [N II] 6583~\AA line.
+
+ R-band images were used to remove the stellar emission from H$\alpha$ using scaling factor between fluxes in these two band passes determined by \cite{Azimlu11}.
+They estimated continuum emission in each H$\alpha$ image, using photometry results in both \halpha and R-band images, and determined the scaling factor.
+These images were observed from a ground base telescope over two years time.
+Consequently, there is a non-negligible sky contribution in the background which should be estimated and removed from each image in both bands.
+On the other hand, there is no image of the further area in the sky to measure the sky contribution from there, which makes the removal of background emission even harder.
+The only choice were left here is to subtract the local background for each region% which gave us an image with non-smooth background.
+. However, subtracting a local background of images will result in a non-smooth background in final mosaic image.
+
+To create the final mosaic, first we removed the background from each region in both \halpha and R-band.
+Our second step was to subtract the continuum from the \halpha images.
+Since both \halpha and R-band images were aligned on the same coordinate grid, for each field, \halpha image was subtracted by R-band image multiplied by the scaling factor.
+At the end, we masked out all the foreground and saturated regions which include a $10\arcmin \times 10\arcmin$ region in the centre of the galaxy.
+In total, nearly 50$\%$ of the pixels in the \halpha map were masked out.
+To account for the flux contribution of the [N II] emission we used the flux ratio of the [NII]$/$\halpha $= 0.54$ from \cite{Kennicutt08}.
+
+\subsubsection{\halpha plus 24\um Star Formation Rate}
+\label{sec:sfr_halpha}
+
+The SFR can be calculated using combination of \halpha and \Spitzer  24\um maps.
+\halpha emission of galaxies is dominated by light emitted from young and massive stars.
+Star formation time scaled traced by this emission is $\sim 6-10$ Myr \citep[e.g.,][]{Kennicutt09, Calzetti13}.
+Therefore, \halpha alone could be used to calibrate the SFR \citep[e.g.,][]{Osterbrock06, Kennicutt09}.
+However, \halpha emission is very sensitive to dust extinction, too.
+Therefore, the combination of the \halpha and 24\um of is considerable choice for calculating the SFR.
+wW used a calibration introduced by \cite{Kennicutt09} to measure the SFR:
+\begin{equation}
+\label{equ: halphaplus24_g}
+SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.020L(24\mu m)]
+\end{equation}
+where L(H${\alpha}$)$_{obs}$ is the observed \halpha luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$.
+L(24$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}$yr$^{-1}$.
+It was indicated that the formulation above can only be used at the global situation i.e., the total SFR.
+
+\cite{Calzetti07} introduced a new calibration using the same band passes in a case of local regions (Figure~\ref{fig:sfr_halpha}):
+\begin{equation}
+\label{equ: halphaplus24_l}
+SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.033L(24\mu m)]
+\end{equation}
+the units here are the same as equation~\ref{equ: halphaplus24_g}.
+Equation~\ref{equ: halphaplus24_l} is useful for regions less than $\sim 1$ kpc.
+According to  \cite{Calzetti07} calibration constant in equations ~\ref{equ: halphaplus24_g} and ~\ref{equ: halphaplus24_l} can be different by changing an IMF.
+Changes in the IMF mostly affect on calibration based on \halpha luminosity, mostly because a significant amount of the ionizing photons comes from the stars more massive than $\sim 20$M$\sun$.
+Changing the calibration constant would change the total SFR by a factor of 1.5.
+In this paper, we used \cite{Kroupa01} IMF with an upper mass limit of 100M$\sun$.
+Total SFR calculated from equation~\ref{equ: halphaplus24_g} is $0.35 \pm 0.01$~M$\sun$~yr$^{-1}$, which is in good agreement with previous studies.
+
+Creating the SFR map using \halpha plus 24 \um was described in Section~\ref{sec:sfr_halpha}.
+In order to investigate the SFR laws, we used the same method of the fitting as Section~\ref{sec:fitting}.
+The fitting results using SFR(\halpha $+$ 24 \um ) are totally different from the other two SFR tracers.
+The main reason for this difference could is mainly because of the extreme amount of the nan values in the map especially lost of the data in the centre of the galaxy.\halpha data does not have a smooth background.
+Also the centre of galaxy in this data is diffused, so we do not have any data from the centre of the M31.
+Since it was the only available \halpha data from the M31, We used this data anyway.
+
 \end{document}

### 2015-06-24 draft3.tex
maryam's comment

@@
 \newcommand \apjl {ApJL} %:The Astrophysical Journal Letters
+
 \begin{document}
 % TITLE
-\title[STAR FORMATION LAW IN M31]{Star formation law in the Andromeda galaxy: effect of the gas mass, stellar mass, and metallicity }
+\title[STAR FORMATION LAWs IN M31]{Star formation laws in the Andromeda galaxy: effect of the gas mass, stellar mass, and metallicity }
 \author[S. Rahmani, et. al.]{S.~Rahmani, S.~Lianou, P.~Barmby\\
@@
 \cite{Shi11} argued that the surface density of SFR is related not only to gas mass, as in the empirical K-S law,  but also to stellar mass surface density, in the ``extended Schmidt law''.
-Using all a combination of \halpha and 24 \um emission, a combination of FUV and 24 \um, and the total infrared emission, we estimate the total SFR in M31 to be between 0.35 M$_{\odot}$yr$^{-1}$ - 0.4 M$_{\odot}$yr$^{-1}$.
+Using all a combination of \halpha and 24 \um emission, a combination of FUV and 24 $\mu$m, and the total infrared emission, we estimate the total SFR in M31 to be between 0.35 M$_{\odot}$yr$^{-1}$ - 0.4 M$_{\odot}$yr$^{-1}$.
 We use maps of $^{12}$CO and 21cm emission to produce the \sigmagas map.% For regions that are not covered in the $^{12}$CO map, we used the dust map (obtained from $SPIRE$ data) as a tracer of total gas.
@@
 \label{equ:ks_org}
-\eqsigmasfr \propto \eqsigmagas^{1.4\pm0.15}
+\eqsigmasfr \propto \eqsigmagas^{1.4\pm0.15},
 \end{equation}
@@
 Since M31 is the nearest spiral galaxy to the Milky Way, we can have higher resolution images of this spiral galaxy.
-High resolution images provide data from various regions within the galaxy with different physical situations (e.g.
+High resolution images of this spiral galaxy are avaiable that provide data from various regions within the galaxy with different physical properties (e.g.
 metallicity, surface brightness, gas density).
@@
 Furthermore, the range of the power index of the K-S law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10,Ford13}.
-Various groups used different methods and data, and have different value for the power index.
+Various groups used different methods and data, and measured different values for the power index.
 In the most recent study of the K-S law in M31, \cite{Ford13} tested this law on six regions from the centre of the galaxy using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus HI maps, and total gas calculated from dust emission).
 The measured power indices for each map and each region vary between 0.6 to 2.03.
-The origin of these variation in results is still ongoing
+The origin of these variations in the results is still an open
 question.
-It is not obvious what makes these differences in the power law indices calculated by different groups.
-It is unclear whether it depends on distance from the centre of the galaxy, metallicity, gas tracers, SFR tracers, fitting methods, or because of the K-S law does not work on M31 at all.
-We also applied a new statistical method instead of the ordinary least square fitting (OLS), which is the most common fitting method for testing K-S law, to test the importance of the fitting method in results.
+It is unclear whether it depends on distance from the centre of the galaxy, metallicity, gas tracers, SFR tracers, fitting methods, or because of the K-S law not working on M31.
+We also applied a new statistical method instead of the ordinary least square fitting (OLS), which is the most common fitting method for testing K-S law, to test the importance of the fitting method on the results.
 %me
@@
 \label{sec:data}
-Since M31 is the closest spiral galaxy to the Milky Way, it was aimed by many probes and telescopes, both space based and ground based ones.
-Therefore, a variety of data from gamma-ray to radio wavelengths are available.
-Wide ranges of data provide us the ability to measure all the required parameters to test the star formation laws in M31.
-Table~\ref{table:data} lists all the data we used in this paper.
-Each data comes with different Full Width Half Maximum (FWHM), spacial resolution and grids.
-In order to make sure that all our data contains the same amount of information, we smoothed maps with smaller FWHM using Aniano's Kernels' library and convolution code \citep{Aniano12}, to have the same resolution as either the $^{12}$CO(J:$1\rightarrow0$) data or atomic gas data.
-Moreover, considering the Nyquist relation \citep{Nyquist}, we re-sampled and re-gridded all our maps to have a pixel size which match with their new resolution.
+Being the closest neighbouring galaxy to our own Milky Way, M31 has extensively been studied using both ground- and space- based telescopes.
+%Since M31 is the closest spiral galaxy to the Milky Way, it was aimed by many probes and telescopes, both space based and ground based ones. 
+Therefore, large data sets exist on M31 spanning from gamma-ray to radio wavelengths, allowing us to %a variety of data from gamma-ray to radio wavelengths are available.
+Wide ranges of data provide us the ability to
+measure all the required parameters to test the star formation laws in this galaxy.
+Table~\ref{table:data} lists the data we used in this paper.
+Each data comes with a different Full Width Half Maximum (FWHM), spacial resolution and grids.
+In order to make sure that all our data contains the same amount of information, we smoothed maps with smaller FWHM using Aniano's Kernels' library and convolution code \citep{Aniano12} to have the same resolution as either the $^{12}$CO(J:$1\rightarrow0$) data or atomic gas data.
+Moreover, considering the Nyquist relation \citep{Nyquist}, we re-sampled and re-gridded all our maps to have a pixel size matching with their new resolution.
 %I do not like this centence but I am not sure how to fixt it.
@@
 
-One of the calibrations, which was used to calculate SFR, uses FUV emission as a tracer of the star forming regions.
-FUV emission of M31 was observed by the Galaxy Evolution Explorer (GALEX; \citep{Martin05}).
+One of the calibrations used to calculate SFR uses FUV emission as a tracer of the star forming regions.
+FUV emission of M31 was observed by the Galaxy Evolution Explorer (GALEX; \cite{Martin05}).
 GALEX telescope data contains information for two bands, FUV:1350--1750 and NUV:1750--2750~\AA, with FWHM of 4~\farcs5, and 6~\arcsec.
@@
 \label{sec:vislight}
-Our other method to calculate the SFR was using a combination of \halpha emission and 24\um emission.
+Our other method to calculate the SFR involved using a combination of \halpha and 24 M emission.
 \cite{Massey06, Massey07} mapped UBVRI and \halpha emission line of M31 as part of the Nearby Galaxies Survey using the KPNO telescope.
-\halpha maps, which were obtained from the NOAO science archive, are available in 10 overlapping fields and were observed between 2000 August and 2002 September.
+\halpha maps, which were obtained from the NOAO science archive, are available in 10 overlapping fields and were observed between August 2000 and September 2002.
 We created a Mosaic image of the maps using the Montage \citep{Berriman08}.
 Assuming that all stars have the same fraction of \halpha light in their spectra, we subtracted the R band emission from the \halpha image using the averaged scaling factor between R band images and \halpha provided by \cite{Azimlu11}.
-We also took a masked map from \cite{Azimlu11} and masked all foreground star or partially saturated stars(Figure~\ref{fig:halpha}).
-Details about making the making \halpha map can be found in the Appendix ~\ref{app:halpha}.
+We also took a masked map from \cite{Azimlu11} and masked all foreground or partially saturated stars (Figure~\ref{fig:halpha}).
+Details about making the \halpha map can be found in Appendix ~\ref{app:halpha}.
 
 %\subsection{IR and sub mm Data}
-In IR and sub mm bands, both {\em Spitzer} \citep{Wener04} and {\em Herschel} \citep{Pilbratt10}  space telescopes observed the M31.
-The Infrared Array Camera (IRAC; \citep{Fazio04}) on {\em Spitzer} is a camera observing at four channels (3.6, 4.5, 5.8, and 8 \um).
-IRAC observations of the M31 were obtained by \cite{Barmby06}, which covered $3\degr.7 \times 1\degr.6$.
-IRAC 3.6 and 4.5\um bands  were used to calculate the stellar mass.
-%PBnew: did you use 4.5um?
-Multiband Imaging Photometer for \Spitzer (MIPS) observed the  M31 at 24, 60, and 160\um and covered region $\sim 1\degr \times 3\degr$ \citep{Gordon06}.
+Both {\em Spitzer} \citep{Werner04} and {\em Herschel} \citep{Pilbratt10}  space telescopes observed M31 at IR and sub mm bands.
+Observations with Infrared Array Camera (IRAC; \citep{Fazio04}) are made in four channels (3.6, 4.5, 5.8, and 8 \um).
+IRAC observations of M31 were obtained by \cite{Barmby06}, covering a region $3\degr.7 \times 1\degr.6$.
+IRAC 3.6 \um bands were used to calculate the stellar mass.
+Multiband Imaging Photometer for \Spitzer (MIPS) observed M31 at 24, 60, and 160 \um and covered region $\sim 1\degr \times 3\degr$ \citep{Gordon06}.
 
-Calculation of the SFR using TIR emission needs maps of the m31 in 8, 24, 70, and 160 \um.
-IRAC 8, MIPS 24, MIPS 70 bands were used to calculate TIR emission, but due to better quality and resolution of $Herschel$s$'$data, PACS \citep[Photodetector Array Camera and Spectrometer;][]{Poglitsch10} were used.
-PACS 160\um observation of the Andromeda galaxy alongside of PACS 100 \um band and three (250 \um, 350\um and 500 \um) SPIRE \citep[Spectral and Photometric Imaging Receiver;][]{Griffin10} bands are covered $\sim 5\degr.5 \times 2\degr.5$ regions \citep{Fritz12}.
+Calculation of the SFR using TIR emission requires maps of M31 in 8, 24, 70, and 160 \um.
+IRAC 8, MIPS 24, MIPS 70 bands were used to calculate TIR emission; however due to better quality and resolution of $Herschel$s$'$data, PACS \citep[Photodetector Array Camera and Spectrometer;][]{Poglitsch10} were used.
+PACS 160 \um observation of the Andromeda galaxy alongside of PACS 100 \um band and three (250 $\mu$m, 350 $\mu$m, and 500 \um) SPIRE \citep[Spectral and Photometric Imaging Receiver;][]{Griffin10} bands coveres $\sim 5\degr.5 \times 2\degr.5$ regions in M31 \citep{Fritz12}.
 
 %\subsection{Radio Emission}
-Emission from $^{12}$CO(J:$1\rightarrow0$) line which, was observed on-the-fly with the IRAM 30-m telescope\citep{Nieten06} was used to calculate the H$_2$ column density of the interstellar medium.
-This map covers $2\degr \times 0\degr.5$ that has the best resolution CO image of M31 (FWHM = $23\arcsec$), but the smallest coverage of the halo of the galaxy among the maps we used in this paper.
-In this project we also used 21cm emission map from the atomic gas (HI) in M31 from \cite{Chemin09}.
-They used Synthesis telescope and the 26m antenna at the Dominion Radio Astrophysical Observatory to map HI emission in the 21cm band of the M31.
+Emission from $^{12}$CO (J:$1\rightarrow0$) line that, was observed on-the-fly with the IRAM 30-m telescope \citep{Nieten06} was used to calculate the H$_2$ column density of the interstellar medium.
+This mapa a region $2\degr \times 0\degr.5$ that has the best resolution CO image of M31 (FWHM = $23\arcsec$), but the smallest coverage of the halo of the galaxy among the maps we used in this paper.
+In this study we also used 21 cm emission map from the atomic gas (HI) in M31 from \cite{Chemin09}.
+They used Synthesis telescope and the 26 m antenna at the Dominion Radio Astrophysical Observatory to map HI emission in the 21 cm band of M31.
 
-\section{Measuring Star Formation Laws Components}
+\section{Measuring the component of Star Formation Laws}
 
@@
 \label{sec:sfr}
-\subsubsection{FUV plus 24\um Star Formation Rate}
+\subsubsection{FUV plus 24 M Star Formation Rate}
 
-In this project the first star formation map was produced using a calibration of a combination of FUV emission and 24\um emission introduced by \cite{Hao11}.
+In this project the first star formation map was produced using a calibration of a combination of FUV emission and 24 \um emission introduced by \cite{Hao11}.
 Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.,][]{Kennicutt89}.
-The UV emission traces recently formed stars with age of $\sim 100$ Myr \citep[e.g.,][]{Kennicutt98a, Calzetti05}.
-However, the downside of only using the FUV light as a tracer of the star forming region is that this emission is really sensitive to dust extinction.
-On the other hand 24\um emission is dominated by emission from dust heated by UV photons from young and hot stars.
-This emission is sensitive to the star formation time scale of $\la10$ Myr \citep{Calzetti07}.
-The FUV band of \Galex and the 24\um band of \Spitzer data were used to measure the SFR calibrated by \cite{Hao11} as:
+The UV emission traces recently formed stars with the age of $\sim 100$ Myr \citep[e.g.,][]{Kennicutt98a, Calzetti05}.
+However, the downside of only using the FUV light as a tracer of the star forming region is that this emission is very sensitive to dust extinction.
+On the other hand, 24 \um emission is dominated by emission from dust heated by UV photons from young and hot stars.
+This emission is sensitive to the star formation timescale of $\la10$ Myr \citep{Calzetti07}.
+The FUV band of \Galex and the 24 \um band of \Spitzer data were used to measure the SFR calibrated by \cite{Hao11} as:
 \begin{equation}
 \label{equ: fuvplus24}
-SFR =4.46\times10^{-44}[L(FUV)_{obs}+3.89L(24\mu m)]
+SFR =4.46\times10^{-44}[L(FUV)_{obs}+3.89L(24\mu m)],
 \end{equation}
-where a unit of SFR is M$_{\odot}$yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{obs}$ are in erg~s$^{-1}$.
+where SFR is in M$_{\odot}$yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{obs}$ are in erg~s$^{-1}$.
 L(FUV)$_{obs}$ is the luminosity of the galaxy in the FUV emission.
-The index of "obs" is shown to indicate that the FUV emission is not corrected for the effect of extinction.
-Nevertheless, this emission was corrected for the foreground stars' emission using a method introduced by \cite{Leroy08}.
+The subscript "obs" is shown to indicate that the FUV emission is not corrected for the effect of extinction.
+Nevertheless, this emission was corrected for the foreground star's emission using a method introduced by \cite{Leroy08}.
 We assumed for any pixel in FUV$_{obs}$ map, if I$_{NUV}$/I$_{FUV}$ $>$ 15 that pixel value is dominated by foreground emission and masked them out.
-We also masked the same region in the galaxy for 24\um map.
-Using this method, we calculated the total SFR is $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$.
+We also masked the same region in the galaxy for the 24 \um map.
+Using this method, we calculated the total SFR to be $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$.
 
@@
         \includegraphics[width=164mm]{sfr_fuv.eps}
-        \caption{SFR,FUV+24\um}
+        \caption{SFR,FUV+24 M}
         \label{fig:sfr,fuv}
@@
     \end{subfigure}
-    \caption{SFR map from a combination of FUV + 24\um emission (top), \halpha and 24\um emission (middle), and total infrared emission (bottom)}
+    \caption{SFR map from a combination of FUV + 24 M emission (top), \halpha and 24 M emission (middle), and total infrared emission (bottom)}
     \label{fig:sfrs}
@@
 
+\subsubsection{\halpha plus 24 \um Star Formation Rate}
+\label{sec:sfr_halpha}
+
+The SFR can be calculated using combination of \halpha and \Spitzer  24\um maps.
+\halpha emission of galaxies is dominated by light emitted from young and massive stars.
+Star formation time scaled traced by this emission is $\sim 6-10$ Myr \citep[e.g.,][]{Kennicutt09, Calzetti13}.
+Therefore, \halpha alone could be used to calibrate the SFR \citep[e.g.,][]{Osterbrock06, Kennicutt09}.
+However, \halpha emission is very sensitive to dust extinction, too.
+Therefore, the combination of the \halpha and 24\um of is considerable choice for calculating the SFR.
+wW used a calibration introduced by \cite{Kennicutt09} to measure the SFR:
+\begin{equation}
+\label{equ: halphaplus24_g}
+SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.020L(24\mu m)]
+\end{equation}
+where L(H${\alpha}$)$_{obs}$ is the observed \halpha luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$.
+L(24$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}$yr$^{-1}$.
+It was indicated that the formulation above can only be used at the global situation i.e., the total SFR.
+
+\cite{Calzetti07} introduced a new calibration using the same band passes in a case of local regions (Figure~\ref{fig:sfr_halpha}):
+\begin{equation}
+\label{equ: halphaplus24_l}
+SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.033L(24\mu m)]
+\end{equation}
+the units here are the same as equation~\ref{equ: halphaplus24_g}.
+Equation~\ref{equ: halphaplus24_l} is useful for regions less than $\sim 1$ kpc.
+According to  \cite{Calzetti07} calibration constant in equations ~\ref{equ: halphaplus24_g} and ~\ref{equ: halphaplus24_l} can be different by changing an IMF.
+Changes in the IMF mostly affect on calibration based on \halpha luminosity, mostly because a significant amount of the ionizing photons comes from the stars more massive than $\sim 20$M$\sun$.
+Changing the calibration constant would change the total SFR by a factor of 1.5.
+In this paper, we used \cite{Kroupa01} IMF with an upper mass limit of 100M$\sun$.
+Total SFR calculated from equation~\ref{equ: halphaplus24_g} is $0.35 \pm 0.01$~M$\sun$~yr$^{-1}$, which is in good agreement with previous studies.
+
+Creating the SFR map using \halpha plus 24 \um was described in Section~\ref{sec:sfr_halpha}.
+In order to investigate the SFR laws, we used the same method of the fitting as Section~\ref{sec:fitting}.
+The fitting results using SFR(\halpha $+$ 24 \um ) are totally different from the other two SFR tracers.
+The main reason for this difference could is mainly because of the extreme amount of the nan values in the map especially lost of the data in the centre of the galaxy.\halpha data does not have a smooth background.
+Also the centre of galaxy in this data is diffused, so we do not have any data from the centre of the M31.
+Since it was the only available \halpha data from the M31, We used this data anyway.
+
 \subsubsection{Total Infrared Star Formation Rate}
 \label{sec:sfr_fir}
-The total infrared emission of a system, can also be used as a tracer of the SFR.
-Dust absorbs radiation from hot and young stars and re-emit it in infrared wavelengths, however, there is no one-to-one mapping between IR and UV emission.
+The total infrared emission of a system can also be used as a tracer of the SFR.
+Dust absorbs radiation from hot and young stars and re-emits it at infrared wavelengths; however, there is no one-to-one mapping between IR and UV emission.
 Therefore, integrating over the full wavelength range of the IR part and calculating the TIR luminosity is a better tracer of the SFR instead of IR single-band emission \citep{Calzetti13}.
-\cite{Calzetti13} assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{star}(bol) = L(TIR)$ and calibrated the TIR luminosity of a system to calculate the SFR for a stellar population undergoing constant star formation over 100 Myr:
+\cite{Calzetti13} assumed that stellar bolometric emission is completely absorbed and re-emitted by dust, i.e., $L_{star}(bol) = L(TIR)$, and calibrated the TIR luminosity of a system to calculate the SFR for a stellar population undergoing constant star formation over 100 Myr:
 
@@
 \label{equ:sfr_fir}
-SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR)
+SFR(\rm TIR) = 2.8 \times10^{-44}L(\rm TIR),
 \end{equation}
-where SFR(TIR) and L(TIR), the star formation rate calculated from TIR emission and TIR luminosity, are in M$_{\odot}$~yr$^{-1}$ and erg~s$^{-1}$ respectively.
-Part of the dust emission in galaxies (specially in M31) comes from the dust heated by the cosmic background radiation \citep[e.g.][]{Dole06, Calzetti13, Mattsson14}, hence, using the equation ~\ref{equ:sfr_fir} overestimates the SFR in M31.
+where SFR(TIR) and L(TIR), the star formation rate calculated from TIR emission and TIR luminosity, are in M$_{\odot}$~yr$^{-1}$ and erg~s$^{-1}$, respectively.
+Part of the dust emission in galaxies (specially in M31) comes from the dust heated by the cosmic background radiation \citep[e.g.][]{Dole06, Calzetti13, Mattsson14}, hence, using equation~\ref{equ:sfr_fir} overestimates the SFR in M31.
 
-TIR luminosity can be measured from the integration of the IR part of a spectral energy distribution (SED) of a galaxy or combining photometry data in different IR wavelengths.
-For the second approach \cite{Draine07} modelled \Spitzer data and calibrated IR single-band photometry data to calculate the TIR luminosity.
+TIR luminosity can be measured from the integration of the IR part of a spectral energy distribution (SED) of a galaxy or combining photometry data at different IR wavelengths.
+As a second approach, \cite{Draine07} modelled \Spitzer data and calibrated IR single-band photometry data to calculate the TIR luminosity.
 \cite{Boquien10} tested and modified this calibration as:
@@
  \label{equ: TIR}
-L(\rm TIR) = 0.95L(8) + 1.15L(24) + L(70) + L(160)
+L(\rm TIR) = 0.95L(8) + 1.15L(24) + L(70) + L(160),
 \end{equation}
-where L(8), L(24), L(70), and L(160) are luminosities of the galaxy in 8 \um, 24 \um, 70 \um and 160 \um in units of erg~s$^{-1}$.
+where L(8), L(24), L(70), and L(160) are luminosities of the galaxy in 8 $\mu$m, 24 $\mu$m, 70 $\mu$m,and 160 \um in units of erg~s$^{-1}$.
 We used equation~\ref{equ:sfr_fir} to calculate the second map of the SFR of M31 (Figure~\ref{fig:sfr,fir}).
-Using this method we calculated the total SFR as $0.40 \pm 0.04$~M$_{\odot}$~yr$^{-1}$.
-Table~\ref{table:sfr} compares the total SFR from literature and current work.
+Using this method, we calculated the total SFR to be $0.40 \pm 0.04$~M$_{\odot}$~yr$^{-1}$.
+Table~\ref{table:sfr} compares the total SFR from literature and the present work.
 
@@
 \hline
-Current work&FUV and 24\um&0.31 $\pm$ 0.04\\
-Current work&\halpha and 24\um&0.35 \\
+Current work&FUV and 24 M&0.31 $\pm$ 0.04\\
+Current work&\halpha and 24 M&0.35 \\
 Current work&TIR luminosity&0.4 $\pm$ 0.04\\
-\cite{Ford13}&FUV and 24\um&0.25\\
+\cite{Ford13}&FUV and 24 M&0.25\\
 \cite{Ford13}&TIR luminosity&0.48-0.52\\
-\cite{Azimlu11}& \halpha and 24\um&0.34\\
+\cite{Azimlu11}& \halpha and 24 M&0.34\\
 \cite{Azimlu11}&Extinction corrected \halpha&0.44\\
@@
 
-Near IR band such as: 3.6\um, 4.5\um and K band emission, are almost insensitive to the emission from the young stellar population, dust absorption and emission, which make them a good tracer of the mass of the older stellar populations\citep[e.g.,][]{Elmgreen84, Eskew12, Zhu10}.
+Near IR band such as: 3.6$\mu$m, 4.5\um and K band emission, are almost insensitive to the emission from the young stellar population, dust absorption and emission, which make them a good tracer of the mass of the older stellar populations\citep[e.g.,][]{Elmgreen84, Eskew12, Zhu10}.
 We calculated the stellar mass within M31 using calibration of the 3.6\um flux by \cite{Eskew12}.
@@
 %----------------------------------------------------------------------------------------
+%Metallicity
+%----------------------------------------------------------------------------------------
+\subsection{Metallicity}
+%----------------------------------------------------------------------------------------
 %SFR LAWS
@@
 As a result we were be able to test each law 36 times.
-In total, we produced 72 different plots, which show either the K-S law or the extended Schmidt law, both in whole galaxy and in different distances from the centre of the M31.
+In total, we produced 72 different plots, which show either the K-S law or the extended Schmidt law, both in whole galaxy and in different distances from the centre of M31.
 Additionally, we can use these results to see if there is any correlation between the SFR laws and the metallicity, as it is going to be described in ~\ref{sec:fitting}.
@@
 \begin{figure*}
-\includegraphics[width=164mm]{c3d_all_ks_regs_f.png}
+\includegraphics[width=164mm]{Results_all_3_regs.pdf}
 \caption{Same as Figure~\ref{fig:ks,all}, but in this figure we separated pixels from different regions in the galaxy by their colours.
@@
 First row plots are the surface density of the SFR(TIR), which is calculated using  the TIR emission form section ~\ref{sec:sfr_fir}, versus the gas surface density traced by only the molecular gas (H$_2$),  only atomic gas (HI), and total gas from right to left, respectively.
-The only difference between the upper and lower plots is that in the lower row the SFR indicator is the FUV plus 24\um emission.
+The only difference between the upper and lower plots is that in the lower row the SFR indicator is the FUV plus 24 M emission.
 Figure~\ref{fig:ks,regs} shows the same data as Figure~\ref{fig:ks,all}.
@@
         \centering
-        \includegraphics[width=\textwidth]{es_tot_fir_h2_f.png}
+        \includegraphics[width=\textwidth]{es_tot_fir_vs_h2_22.png}
         \caption{SFR,TIR vs surface density of H$_2$}
@@
         \centering
-        \includegraphics[width=\textwidth]{es_tot_fir_hi_f.png}
+        \includegraphics[width=\textwidth]{es_tot_fir_vs_hi2.png}
         \caption{SFR,TIR vs surface density of HI}
@@
         \centering
-        \includegraphics[width=\textwidth]{es_tot_fir_tot_gas_f.png}
+        \includegraphics[width=\textwidth]{es_tot_fir_vs_tot2.png}
         \caption{SFR,TIR vs surface density of total gas}
@@
         \centering
-        \includegraphics[width=\textwidth]{es_tot_fuv_h2_f.png}
-        \caption{SFR,FUV+24\um vs surface density of H$_2$}
+        \includegraphics[width=\textwidth]{es_tot_fuv_vs_h22.png}
+        \caption{SFR,FUV+24 M vs surface density of H$_2$}
         \label{fig:es,all,fuv,h2}
@@
         \centering
-        \includegraphics[width=\textwidth]{es_tot_fuv_hi_f.png}
-        \caption{SFR,FUV+24\um vs surface density of HI}
+        \includegraphics[width=\textwidth]{es_tot_fuv_vs_hi2.png}
+        \caption{SFR,FUV+24 M vs surface density of HI}
         \label{fig:es,all,fuv,hi}
@@
         \centering
-        \includegraphics[width=\textwidth]{es_tot_fuv_tot_gas_f.png}
-        \caption{SFR,FUV+24\um vs. surface density of total gas}
+        \includegraphics[width=\textwidth]{es_tot_fuv_vs_tot2.png}
+        \caption{SFR,FUV+24 M vs. surface density of total gas}
         \label{fig:es,all,fuv,tot}
+    \end{subfigure}
+    \hfill
+     \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{es_tot_halpha_vs_h22.png}
+        \caption{SFR,H$\alpha$+24 M vs surface density of H$_2$}
+        \label{fig:es,all,halpha,h2}
+    \end{subfigure}
+     \hfill
+   \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{es_tot_halpha_vs_hi2.png}
+        \caption{SFR,H$\alpha$+24 M vs surface density of HI}
+        \label{fig:es,all,halpha,hi}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{es_tot_halpha_vs_tot2.png}
+        \caption{SFR,H$\alpha$+24 M vs. surface density of total gas}
+        \label{fig:es,all,halpha,tot}
     \end{subfigure}
@@
 \centering
-\includegraphics[width=162mm]{c3d_fir_tot_f.png}
+\includegraphics[width=162mm]{tir_vs_tot_3_reg_extendS.png}
 \caption{Fitting result from the SFR(TIR) vs total gas.
@@
 \centering
-\includegraphics[width=162mm]{c3d_fuv_tot_f.png}
+\includegraphics[width=162mm]{fuv_vs_tot_3_reg_extendS.png}
 \caption{Fitting result from the SFR(FUV + 24 $\mu$m) vs total gas.
@@
 
+\begin{figure*}
+\centering
+\includegraphics[width=162mm]{halpha_vs_tot_3_reg_extendS_97perse.png}
+\caption{Fitting result from the SFR(H$\alpha$ + 24 $\mu$m) vs total gas.
+Same as Figure~\ref{fig:es,all,halpha,tot}, but in this figure we denote pixels from different regions in the galaxy by their colours.
+The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$ are shown in red, green and blue, respectively.}
+\label{fig:es,regs,fir,tot}
+\end{figure*}
+
 \begin{table*}
@@
 \label{table:res}
-\begin{tabular}{cccccrccccrr}
+\begin{tabular}{ccccrccrr}
 \hline\hline
-\multicolumn{1}{c}{\multirow{1}{*}{Region}} & SFR Tracer& Gas Tracer & $N$ & $\sigma_N$ & $A$ & \nprime & $\sigma_{\eqnprime}$ & $\beta$ & $\sigma_\beta$ & A$^\prime$& \\
+\multicolumn{1}{c}{\multirow{1}{*}{Region}} & SFR Tracer        & Gas Tracer & N    & A      & \nprime & $\beta$ & A$^\prime$ \\
 \hline
-\multicolumn{1}{c}{\multirow{6}{*}{Global case}} & TIR & H$_2$ only & 1.03 & 9.47e-3  & $-8.92$  & 0.95 & 9.77e-3 & 0.34 & 4.25e-3 & $-9.57$  \\
- & TIR         & HI only    & 1.15 & 1.47e-2 & $-9.63$  & 0.77 & 8.84e-3 & 0.75 & 4.58e-3 & $-10.71$ \\
- & TIR         & Total gas  & 0.81 & 6.27e-3 & $-9.84$  & 0.50 & 4.49e-3 & 0.55 & 4.57e-3 & $-10.53$\\
- & FUV + 24\um & H$_2$ only & 1.15 & 1.16e-2 & $-9.28$  & 1.09 & 1.21e-2 & 0.25 & 4.88e-3 & $-9.76$  \\
- & FUV + 24\um & HI only    & 1.21 & 9.13e-3 & $-9.87$  & 0.81 & 7.34e-3 & 0.60 & 4.10e-3 & $-10.70$ \\
- & FUV + 24\um & Total gas  & 0.78 & 4.67e-3 & $-10.06$ & 0.48 & 4.61e-3 & 0.45 & 4.69e-3 & $-10.57$ \\
+\multicolumn{1}{c}{\multirow{9}{*}{Whole Galaxy}} & TIR               & H$_2$ only & 1.05 & -8.98  & 0.97    & 0.35    & -9.53      \\
+ & TIR               & HI only    & 1.19 & -9.69  & 0.79    & 0.75    & -10.56     \\
+ & TIR               & Total gas  & 0.82 & -9.84  & 0.51    & 0.56    & -10.40     \\
+ & FUV + 24 M       & H$_2$ only & 1.16 & -9.36  &         &         &            \\
+ & FUV + 24 M       & HI only    & 1.19 & -9.96  & 0.81    & 0.61    & -10.62     \\
+ & FUV + 24 M       & Total gas  & 0.78 & -10.09 & 0.49    & 0.45    & -10.50     \\
+ & H$\alpha$ + 24 M & H$_2$ only & 1.16 & -9.26  & 1.07    & 0.38    & -9.86      \\
+ & H$\alpha$ + 24 M & HI only    & 0.54 & -9.61  & 0.53    & 0.76    & -10.69     \\
+ & H$\alpha$ + 24 M & Total gas  & 0.54 & -9.82  & 0.37    & 0.59    & -10.55     \\
 \hline
-\multicolumn{1}{c}{\multirow{6}{*}{R$< 8\kpc$}}& TIR & H$_2$ only & 0.96 & 1.48e-2 & $-8.95$  & 0.88 & 1.49e-2 & 0.30 & 6.11e-3 & $-9.54$  \\
- & TIR         & HI only    & 1.52 & 7.73e-2  & $-9.91$ & 1.00 & 7.27e-2  & 0.60 & 4.22e-2  & $-10.60$ \\
- & TIR         & Total gas  & 1.00 & 3.51e-2  & $-10.04$ & 0.63 & 3.47e-2  & 0.53 & 7.57e-2  & $-10.63$ \\
- & FUV + 24\um & H$_2$ only & 1.04 & 1.84e-2 & $-9.29$  & 1.00 & 1.85e-2 & 0.18 & 7.17e-3 & $-9.64$  \\
- & FUV + 24\um & HI only    & 1.28 & 4.73e-2  & $-10.00$ & 0.93 & 5.68e-2  & 0.42 & 3.81e-2  & $-10.50$ \\
- & FUV + 24\um & Total gas  & 0.88 & 2.59e-2  & $-10.12$ & 0.75 & 3.53e-2  & 0.16 & 3.93e-2  & $-10.28$ \\
+\multicolumn{1}{c}{\multirow{9}{*}{R$< 8\kpc$}} & TIR               & H$_2$ only & 1.01 & -8.95  & 0.92    & 0.36    & -6.66      \\
+ & TIR               & HI only    & 1.63 & -9.93  & 1.14    & 0.65    & -10.38     \\
+ & TIR               & Total gas  & 1.07 & -9.99  & 0.87    & 0.41    & -10.21     \\
+ & FUV + 24 M       & H$_2$ only & 1.07 & -9.30  & 1.03    & 0.18    & -9.62      \\
+ & FUV + 24 M       & HI only    & 1.29 & -10.06 & 1.02    & 0.45    & -10.34     \\
+ & FUV + 24 M       & Total gas  & 0.89 & -10.12 & 0.81    & 0.21    & -10.18      \\
+ & H$\alpha$ + 24 M & H$_2$ only & 1.14 & -9.23  & 1.03    & 0.41    & -6.47      \\
+ & H$\alpha$ + 24 M & HI only    & 1.29 & -9.56  & 0.96    & 1.54    & -11.10     \\
+ & H$\alpha$ + 24 M & Total gas  & 0.90 & -9.99  & 0.65    & 1.27    & -10.88    \\
 \hline
-\multicolumn{1}{c}{\multirow{6}{*}{$8\kpc < $R $< 18\kpc$}} & TIR & H$_2$ only & 1.08 & 1.26e-2 & $-8.90$  & 1.00 & 1.29e-2 & 0.40 & 5.74e-3 & $-9.66$  \\
- & TIR         & HI only    & 1.09 & 4.50e-2 & $-9.54$  & 0.77 & 2.52e-2  & 0.75 & 1.26e-2  & $-10.71$ \\
- & TIR         & Total gas  & 0.75 & 1.76e-2  & $-9.81$  & 0.47 & 1.18e-2  & 0.55 & 1.24e-2  & $-10.53$ \\
- & FUV + 24\um & H$_2$ only & 1.21 & 1.53e-2 & $-9.27$  & 1.15 & 1.57e-2 & 0.33 & 6.57e-3 & $-9.89$  \\
- & FUV + 24\um & HI only    & 1.18 & 2.89e-2 & $-9.81$  & 0.81 & 2.08e-2 & 0.61 & 1.12e-2 & $-10.73$ \\
- & FUV + 24\um & Total gas  & 0.71 & 1.34e-2 & $-9.81$  & 0.44 & 1.18e-2  & 0.45 & 1.28e-2  & $-10.58$ \\
+\multicolumn{1}{c}{\multirow{9}{*}{$8\kpc < $R $< 18\kpc$}} & TIR               & H$_2$ only & 1.08 & -8.90  & 1.00    & 0.40    & -9.59      \\
+ & TIR               & HI only    & 1.16 & -9.58  & 0.84    & 0.77    & -10.53     \\
+ & TIR               & Total gas  & 0.79 & -9.77  & 0.50    & 0.58    & -10.38     \\
+ & FUV + 24 M       & H$_2$ only & 1.21 & -9.28  & 1.15    & 0.31    & -9.82      \\
+ & FUV + 24 M       & HI only    & 1.19 & -9.88  & 0.85    & 0.63    & -10.61     \\
+ & FUV + 24 M       & Total gas  & 0.75 & -10.04 & 0.47    & 0.47    & -10.47     \\
+ & H$\alpha$ + 24 M & H$_2$ only & 1.18 & -9.18  & 1.09    & 0.41    & -9.88      \\
+ & H$\alpha$ + 24 M & HI only    & 0.56 & -9.49  & 0.72    & 0.81    & -10.67     \\
+ & H$\alpha$ + 24 M & Total gas  & 0.52 & -9.71  & 0.40    & 0.61    & -10.47  \\
 \hline
-\multicolumn{1}{c}{\multirow{6}{*}{$18\kpc <$ R $\la 25\kpc$}}  & TIR & H$_2$ only & 1.57 & 2.63e-1  & $-8.80$  & 0.97 & 2.00e-1  & 1.19 & 1.01e-1  & $-10.94$ \\
- & TIR         & HI only    & 1.17 & 4.67e-2 & $-9.65$  & 0.76 & 2.82e-2 & 0.75 & 1.48e-2 & $-10.72$ \\
- & TIR         & Total gas  & 0.84 & 2.06e-2  & $-9.85$  & 0.52 & 1.45e-2  & 0.56 & 1.42e-2  & $-10.56$ \\
- & FUV + 24\um & H$_2$ only & 1.87 & 3.03e-1  & $-9.15$  & 1.33 & 2.95e-1  & 1.38 & 1.12e-1  & $-11.65$ \\
- & FUV + 24\um & HI only    & 1.22 & 2.96e-2 & $-9.88$  & 0.79 & 2.31e-2 & 0.62 & 1.28e-2 & $-10.73$ \\
- & FUV + 24\um & Total gas  & 0.81 & 1.59e-2 & $-10.06$ & 0.42 & 1.14e-2  & 0.52 & 2.06e-1  & $-10.69$\\
+\multicolumn{1}{c}{\multirow{9}{*}{$18\kpc <$ R $\la 25\kpc$}} & TIR               & H$_2$ only & 2.08 & -8.76  & 1.81    & 1.32    & -5.82      \\
+ & TIR               & HI only    & 1.30 & -9.68  & 0.83    & 0.78    & -10.54     \\
+ & TIR               & Total gas  & 0.86 & -9.83  & 0.55    & 0.57    & -10.38     \\
+ & FUV + 24 M       & H$_2$ only & 2.87 & -9.18  & 2.89    & 1.49    & -11.33     \\
+ & FUV + 24 M       & HI only    & 1.27 & -9.95  & 0.85    & 0.64    & -10.63     \\
+ & FUV + 24 M       & Total gas  & 0.80 & -10.08 & 0.52    & 0.48    & -10.49     \\
+ & H$\alpha$ + 24 M & H$_2$ only & 2.86 & -9.05  & 3.12    & 1.30    & -10.86     \\
+ & H$\alpha$ + 24 M & HI only    & 0.63 & -9.62  & 0.44    & 0.81    & -10.62     \\
+ & H$\alpha$ + 24 M & Total gas  & 0.60 & -9.84  & 0.39    & 0.66    & -10.52     \\
  \hline
@@
 \centering
-\includegraphics[width=164mm]{ks_all_f.png}
+\includegraphics[width=164mm]{Results_for_all_regions.pdf}
 \caption{The result from fitting the Kennicutt-Schmidt law on data from whole galaxy using the pixel by pixel method. The points in the plots represent 
@@
 They found that across the galaxy, with increasing distance from the centre of galaxy dust/H ratio declines monotonically.
-Considering that dust/H ratio has a direct relation to metallicity, they conclude that the metallicity of the M31 changes in the same manner.
+Considering that dust/H ratio has a direct relation to metallicity, they conclude that the metallicity of M31 changes in the same manner.
 As a result they introduced these three different regions as $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$.
@@
 Metallicity affect on each component of the star formation laws in different way.
-There are many studies on correlation of the metallicity with stellar mass, SFR, and the effect of the metallicity on the ISM \citep[e.g.,][]{Boissier03, Leroy08, Krumholz09, Mannucci10, Dib11, Lilly13}.
+There are many studies on correlation of the metallicity with stellar mass, SFR, and the effect of the metallicity on the ISM \citep[e.g.,][]{Boissier03, Leroy08, Krumholz09, Mannucci10, Dib11a, Lilly13}.
 The scope of these studies is that metallicity has a critical role on the formation of the H$_2$ gas.
@@
 
+\subsection{750 kpc}
+
+\begin{table*}
+\caption{Fitting parameters of the SF laws from applying the Bayesian method in regions around 750 Kpc}
+\label{table:res750}
+\begin{tabular}{ccccrccrr}
+\hline\hline
+\multicolumn{1}{c}{\multirow{1}{*}{Region}} & SFR Tracer        & Gas Tracer & N    & A      & \nprime & $\beta$ & A$^\prime$ \\
+\hline
+\multicolumn{1}{c}{\multirow{3}{*}{Whole Galaxy}}
+ & FUV + 24 M       & H$_2$ only & 0.65(2.93) & -8.27(3.34)  & 1.61(0.68)  & 0.61(0.38) & 5.29(-10.01)   \\
+ & FUV + 24 M       & HI only    & 1.19 & -9.96  & 0.85    & 0.65    & -11.60     \\
+ & FUV + 24 M       & Total gas  & 0.78 & -10.09 & 0.52    & 0.49    & -10.48     \\
+\hline
+\multicolumn{1}{c}{\multirow{3}{*}{R$< 8\kpc$}}
+ & FUV + 24 M       & H$_2$ only & 0.65(2.93) & -8.27(3.34) & 0.86(2.25)    & 0.36(0.60)    & -10.57(-0.71)      \\
+ & FUV + 24 M       & HI only    & 1.73 & -10.87 & 1.03    & 1.42    & -10.52     \\
+ & FUV + 24 M       & Total gas  & 0.88 & -9.94 & 1.45    & 0.83    & -9.11      \\
+\hline
+\multicolumn{1}{c}{\multirow{3}{*}{$8\kpc < $R $< 18\kpc$}}
+ & FUV + 24 M       & H$_2$ only & 2.02 & -8.43  &    1.83     &  0.78       &   -9.16         \\
+ & FUV + 24 M       & HI only    & 1.38 & -11.06  & 1.26    & 0.65    & -11.33     \\
+ & FUV + 24 M       & Total gas  & 0.80 & -10.00 & 0.72    & 0.53    & -10.17     \\
+\hline
+\multicolumn{1}{c}{\multirow{3}{*}{$18\kpc <$ R $\la 25\kpc$}} 
+ & FUV + 24 M       & H$_2$ only & 1.50 (4.30) & -11.00(-1.02)  &  5.35    & 4.10    & -10.22   \\
+ & FUV + 24 M       & HI only    & 1.45 & -10.75  & 1.05    & 0.84    & -11.44     \\
+ & FUV + 24 M       & Total gas  & 0.85 & -9.86 & 0.58    & 0.66    & -10.26     \\
+ \hline
+\end{tabular}
+\end{table*}
+
+\subsection{Face On}
+
+\begin{table*}
+\caption{Fitting parameters of the SF laws from applying the Bayesian method Face on}
+\label{table:res}
+\begin{tabular}{ccccrccrr}
+\hline\hline
+\multicolumn{1}{c}{\multirow{1}{*}{Region}} & SFR Tracer        & Gas Tracer & N    & A      & \nprime & $\beta$ & A$^\prime$ \\
+\hline
+\multicolumn{1}{c}{\multirow{2}{*}{Whole Galaxy}}
+ & TIR               & Total gas & 0.79 & -9.97  &  0.51   & 0.56   & -10.39   \\
+ & FUV + 24 M       & Total gas  & 0.44 & -9.99 & 0.35    & 0.41    & -10.32     \\
+\hline
+\multicolumn{1}{c}{\multirow{2}{*}{R$< 8\kpc$}}
+ & TIR               & Total gas    & .73 & -9.98 & 0.53    & 0.62    & -10.50     \\
+ & FUV + 24 M       & Total gas  & 0.36 & -9.97 & 0.33    & 0.42    & -10.33      \\
+\hline
+\multicolumn{1}{c}{\multirow{2}{*}{$8\kpc < $R $< 18\kpc$}}
+ & TIR               & Total gas    & 0.79 & -9.96  & 0.52    & 0.58    & -10.41     \\
+ & FUV + 24 M       & Total gas  & 0.43 & -9.98 & 0.36    & 0.41    & -10.33     \\
+\hline
+\multicolumn{1}{c}{\multirow{2}{*}{$18\kpc <$ R $\la 25\kpc$}} 
+ & TIR              & Total gas   & 0.83 & -9.96  & 0.52    & 0.54    & -10.34     \\
+ & FUV + 24 M       & Total gas  & 0.49 & -9.99 & 0.38    & 0.40    & -10.29     \\
+ \hline
+\end{tabular}
+\end{table*}
 %----------------------------------------------------------------------------------------
@@
 
-As mentioned before, the K-S law in the M31 was tested by many groups.
+As mentioned before, the K-S law in M31 was tested by many groups.
 In one of the most recent works on M31, \cite{Ford13} investigated the K-S law in six annuli and the global case using the ordinary least squares (OLS) fitting method.
@@
 
-In order to test the effect of stars on the SFR in both global and local scales in the M31, we have determined surface density of star formation rate, gas mass and the stellar mass of this galaxy.
+In order to test the effect of stars on the SFR in both global and local scales in M31, we have determined surface density of star formation rate, gas mass and the stellar mass of this galaxy.
 We produced three SFR maps in M31.
@@
 \includegraphics[width=164mm]{halpha.eps}
-\caption{Mosaic created using the Montage programme from six fields of H$\alpha$ emission maps of the M31 from \cite{Massey07}.
+\caption{Mosaic created using the Montage programme from six fields of H$\alpha$ emission maps of M31 from \cite{Massey07}.
 The result image from Montage was continuum subtracted and masked out for all point sources.
@@
 
-\subsubsection{\halpha plus 24\um Star Formation Rate}
+\subsubsection{\halpha plus 24 M Star Formation Rate}
 \label{sec:sfr_halpha}
 
-The SFR can be calculated using combination of \halpha and \Spitzer  24\um maps.
+The SFR can be calculated using combination of \halpha and \Spitzer  24 M maps.
 \halpha emission of galaxies is dominated by light emitted from young and massive stars.
@@
 However, \halpha emission is very sensitive to dust extinction, too.
-Therefore, the combination of the \halpha and 24\um of is considerable choice for calculating the SFR.
+Therefore, the combination of the \halpha and 24 M of is considerable choice for calculating the SFR.
 wW used a calibration introduced by \cite{Kennicutt09} to measure the SFR:
@@
 The main reason for this difference could is mainly because of the extreme amount of the nan values in the map especially lost of the data in the centre of the galaxy.\halpha data does not have a smooth background.
-Also the centre of galaxy in this data is diffused, so we do not have any data from the centre of the M31.
-Since it was the only available \halpha data from the M31, We used this data anyway.
+Also the centre of galaxy in this data is diffused, so we do not have any data from the centre of M31.
+Since it was the only available \halpha data from M31, We used this data anyway.
 

### 2015-07-20 draft3.tex
draft - 8

@@
 % TITLE
-\title[STAR FORMATION LAWs IN M31]{Star formation laws in the Andromeda galaxy: effect of the gas mass, stellar mass, and metallicity }
+\title[STAR FORMATION LAWS IN M31]{Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation}
+%PB150629: suggestion (not sure it's better): Star formation laws in the Andromeda galaxy: gas, stars, metals and the surface density of star formation
+%older: Star formation laws in the Andromeda galaxy: gas mass, stellar mass, and metallicity
 \author[S. Rahmani, et. al.]{S.~Rahmani, S.~Lianou, P.~Barmby\\
@@
 %----------------------------------------------------------------------------------------
-\begin{abstract} % it is just my GESF2014 abstract, just for looks I will change it at the end. %PBNew: OK, no comments on this yet.
- We investigate the relation between star formation rate (SFR), gas surface density (\sigmagas) and stellar surface density (\sigmastar) in the Andromeda galaxy (M31) using the Kennicutt-Schmidt (K-S) law and the extended Schmidt law.
-\cite{Shi11} argued that the surface density of SFR is related not only to gas mass, as in the empirical K-S law,  but also to stellar mass surface density, in the ``extended Schmidt law''.
-Using all a combination of \halpha and 24 \um emission, a combination of FUV and 24 $\mu$m, and the total infrared emission, we estimate the total SFR in M31 to be between 0.35 M$_{\odot}$yr$^{-1}$ - 0.4 M$_{\odot}$yr$^{-1}$.
-We use maps of $^{12}$CO and 21cm emission to produce the \sigmagas map.% For regions that are not covered in the $^{12}$CO map, we used the dust map (obtained from $SPIRE$ data) as a tracer of total gas.
- The stellar mass surface density  map is calculated using mid-infrared IRAC imaging.
-Our preliminary results from testing the K-S law in M31 find a power-law index of  $N = 0.62 \pm 0.01$, at the low end of values compared with previous work.
-We determine additional K-S law fits using each SFR map independently with molecular hydrogen, atomic hydrogen and total gas maps.
-We then repeat the analysis considering the stellar mass density in order to test whether the regular or extended Schmidt laws are more appropriate for M31.
+\begin{abstract} 
+ We investigate star formation laws in the the Andromeda galaxy (M31).
+We studied the effects of the gas surface density (\sigmagas), stellar surface density (\sigmastar) and metallicity on the Star formation rate (SFR) both in local ($\sim$ 30 pc, $\sim$ 155 pc, and $\sim$ 750 pc) and global scales.
+Using a combination of \halpha and 24 \um emission, a combination of FUV and 24 $\mu$m, and the total infrared emission, we estimate the total SFR in M31 to be between 0.35 M$_{\odot}$yr$^{-1}\pm 0.04$~and~0.4 M$_{\odot}$yr$^{-1} \pm 0.04$.
+We use maps of $^{12}$CO and 21 cm emission to produce the \sigmagas map.
+We produce the stellar mass surface density using IRAC 3.6 $\mu$m and measured it to be $6.9 \times 10^{10}$ M $_{\odot}$.
+The hierarchical Bayesian regression analysis was applied to fit the star formation power laws.
+For the Kennicutt Schmidt (K-S) law in M31, we find the power-law index to be between $N = 0.52$ and $N = 2.87$.
+We show that the power index varies by gas tracer more than by changing the SFR tracer.
+We also show that the power index changes by distance from the centre of the galaxy.
+We that show the fitting method is important in the study of the star formation laws and that using different fitting methods leads to different power indices.
+We then repeat the analysis considering the stellar mass density in order to compare the K-S law and the extended Schmidt law and determine which is more appropriate for M31.
+We find a correlation between the surface density of SFR and the stellar mass surface density, which confirms that the K-S law needs to be extended to consider the other physical properties of galaxies.
+We could not find any correlation between metallicity, the SFR and the stellar mass surface density.
 
@@
 
-Understanding the undergoing processes of formation of stars is a necessary step for explaining the formation and evolution of galaxies from the early universe to current epoch, as well as the origin of planetary systems.
-Stars form by converting the gas inside galaxies; However, no complete answer on how this transformation happens and what physical properties affect it, is available.
-Various phenomena trigger the collapse of molecular clouds and star formation including the environment of the star-forming region, gas accretion and cooling, H$_2$ formation, the initial mass distribution of gas, chemical compositions of the gas,  dust existence, and other quantities in a galaxy.
-The physical processes leading to star formation are naturally complex.
+Understanding the undergoing processes of formation of stars is a necessary step for explaining the formation and evolution of galaxies from the early universe to the current epoch, as well as the origin of planetary systems.
+Stars form when molecular cloud cores collapse; However, a complete picture explaining the physical processes involved in the formation of stars is yet to emerge.
+Various phenomena trigger the collapse of molecular clouds and star formation including the environment of the star-forming region, gas accretion and cooling, H$_2$ formation, the initial mass distribution and chemical compositions of the gas,  existence of dust, and other quantities in a galaxy.
+The physical processes leading to the formation of stars are naturally complex.
 Therefore, the basis for a theory of star formation requires a strong foundation of empirical data and/or observations.
@@
 
-Finding a relation between the total star formation rate (SFR) and the mass of interstellar gas was proposed as the first attempt at scaling the star formation rate.
-\cite{Schmidt59} scaled SFR with a power {\it N} of the gas mass, $M_{\rm gas}$.
+The first attempt at scaling the star formation rate was to find a relation between the total star formation rate (SFR) and the mass of interstellar gas.
+\cite{Schmidt59} proposed a power law relation between SFR and the gas mass ($M_{\rm gas}$) with {\it N} as the power law exponent.
 Since then, for more than 50 years empirical star formation laws (relations) have been investigated using both observational data and numerical simulations.
 Later, \cite{Kennicutt98a} examined H$\alpha$, HI, and CO observations of 61 normal spiral galaxies and 36 starburst galaxies.
-He showed that the disk-average SFRs and gas densities for these samples are well represented by the Schmidt law with the power-low exponent of $1.4 \pm 0.15$.
+He showed that the disk-average SFRs and gas densities for these samples are well represented by the Schmidt law with the power-law exponent of $1.4 \pm 0.15$.
 Using this power index, the Schmidt law can be rewritten as: %me, Schmidt, Kennicutt and every papers on K-S law
+%Should I write laws (relations) or laws/relations?
 
@@
 \end{equation}
-which is often referred to as the Kennicutt-Schmidt (K-S) law, where \sigmasfr is the surface density of star formation, and \sigmagas is the surface density of gas in a galaxy.
-Moreover, \cite{Kennicutt07} investigated the K-S law in spatially resolved regions (0.5 - 2 kpc) in the spiral galaxy M51.
-To calculate the SFR they used $24 \mu$m plus H${\alpha}$ emission, and for the gas surface density, a constant conversion factor for CO to H$_2$ was applied.
-They found a correlation, from the radial variation of both the SFR and the gas surface density, with an index of $1.56 \pm 0.04$.
+\noindent which is often referred to as the Kennicutt-Schmidt (K-S) law, where \sigmasfr is the surface density of star formation, and \sigmagas is the surface density of gas in a galaxy.
+Moreover, \cite{Kennicutt07} investigated the K-S law in spatially resolved regions (0.5 - 2 kpc across) in the spiral galaxy M51.
+To calculate the SFR, they used a combination of 24 $\mu$m and H${\alpha}$ emission, and for the gas surface density, a constant conversion factor for CO to H$_2$ was applied.
+They showed that the K-S law also holds locally in galaxies, and found {\it N} to be $1.56 \pm 0.04$.
 %kennicutt07
 
-The K-S law was applied to different types of both local and high redshift galaxies \citep[e.g.,][]{Boissier07,Kennicutt07, Bigiel08, Freundlich13}, but the results were never precise.
-Low gas density regions, $( < 1-10\sim$ M$_{\odot}$ pc$^{-2})$, such as regions outside the disk of the galaxy, are one of the regions, for which the K-S law fails.
-The calculated SFR for these regions is much lower than the value predicted by the K-S law \citep[e.g.,][]{Martin01, Bigiel08}.
+The K-S law was applied to different types of both local and high-redshift galaxies \citep[e.g.][]{Boissier07,Kennicutt07, Bigiel08, Freundlich13}, but the results were never precise.
+Low gas density regions $( < 1-10\sim$ M$_{\odot}$ pc$^{-2})$, such as regions outside disks of galaxies, are an example of the regions for which the K-S law fails.
+The calculated SFR for these regions is much lower than the value predicted by the K-S law \citep[e.g.][]{Martin01, Bigiel08}.
 Using different instability models, \cite{Hunter98} showed that in low surface brightness galaxies, the current star formation activity correlates with stellar mass density.
 Furthermore, a correlation between the star formation rate and the stellar mass density was measured in many studies using both observational data and numerical simulations \citep[e.g.][]{Hunter04,Leroy08,Krumholz09,Shi11,Kim11,Kim13}.
-\cite{Shi11} found a tight relationship between stellar mass surface density, SFR and gas surface density by studying a large sample of galaxies.
-They showed this relation as a power law relation and referred to it as the extended Schmidt law: %me + all the ppl I cite
+\cite{Shi11} found a close relationship between stellar mass surface density, SFR and gas surface density by studying a large sample of galaxies.
+They showed this relation as a power law and referred to it as the extended Schmidt law \footnote{\cite{Shi11} introduced the extended Schmidt law as a power law relation between the star formation efficiency (surface density of SFR per surface density of gas, SFE) and \sigmastar, but we are using the equation~\ref{equ:es_org}, which is the equation 5 in their paper, to be consistent with equation~\ref{equ:ks_org}.}: %me + all the ppl I cite
 
@@
 \label{equ:es_org}
-\eqsigmasfr \propto \eqsigmagas^{\eqnprime} \eqsigmastar^{\beta}
-\end{equation}
-where \sigmasfr is the SFR surface density while \sigmagas and \sigmastar are the gas mass and stellar mass surface densities, \nprime and $\beta$ are the indices found by \cite{Shi11} to be $1.13 \pm 0.05$ and $0.36\pm0.04$ respectibely in a global case.
-By testing this relation on sub-kiloparsec resolution regions in 12 spiral galaxies, they showed that the extended Schmidt law predicts SFR as well as the K-S law for spatially resolved regions ($\sim$1 kpc).
-They demonstrated that the power indices for the local regions are $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$, and concluded that this law is acceptable for low surface brightness galaxies and regions where the K-S law fails.%me
+\eqsigmasfr \propto \eqsigmagas^{\eqnprime} \eqsigmastar^{\beta},
+\end{equation}
+\noindent where \sigmasfr is the SFR surface density while \sigmagas and \sigmastar are the gas mass and stellar mass surface densities, \nprime and $\beta$ are the indices found by \cite{Shi11} to be $1.13 \pm 0.05$ and $0.36\pm0.04$, respectively, in a global case.
+By testing this relation in sub-kiloparsec resolution regions in 12 spiral galaxies, they showed that the extended Schmidt law works just as well in spatially resolved regions ($\sim$1 kpc) as the K-S law.
+Furthermore, they found the power indices for the local regions to be $\eqnprime = 0.80 \pm 0.01$ and $\beta = 0.63\pm0.01$, and concluded that this law is acceptable for low surface brightness galaxies and regions where the K-S law fails.%me
+
+%P5: How to measure it
+A galaxy's metallicity is another physical quantity that likely plays a role in the rate of star formation.
+However, it affects each component of star formation laws in a different way, making it complicated to fully understand its implications.
+There are many studies on correlation of metallicity with stellar mass, SFR, as well as the effect of metallicity on the ISM \citep[e.g.][]{Boissier03, Leroy08, Krumholz09, Mannucci10, Dib11a, Lilly13}.
+These studies suggest that metallicity has a critical role on the formation of H$_2$ gas.
+Thus there should be a correlation between metallicity and the SFR.
+\cite{Krumholz09} introduced a theoretical SFR law which suggests that the SFR and metallicity of galaxies have a power-law correlation, but the power index changes with the amount of total gas.
+%should I say more?
+ Using results obtained from both observations and analytical models, \cite{Mannucci10} and \cite{Lilly13} showed that metallicity depends on both stellar mass and the SFR, which they referred to as a 'fundamental metallicity relation'.
+They found that at any fixed stellar mass, metallicity and the SFR have an inverse correlation.
+It should be noted that the above two correlations are only valid in the global case.
+However, \cite{Leroy08} showed that the SFR(FUV+24$\mu$m) does not change with changing metallicity.
+\cite{Roychowdhury15} argued that in nearby spiral galaxies effect of metallicity on the SFR calculation is smaller than the calibration errors and can be ignored.
+On the other side, \cite{Boissier03} showed that metallicity has inverse correlation with CO-H$_2$ conversion factor.
+Therefore, using a constant conversion factor at high metallicity regions causes the overestimation of the molecular gas, and in low metallicity it leads to the underestimation of the H$_2$.
 
@@
 In order to investigate star formation laws, the first step is to calculate the SFR.
-Many studies are devoted to determining how flux measurments of the star forming regions can accuratelly be traslated to the rate of the formation of new stars \citep[e.g.,][]{Kennicutt12, Calzetti13, Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
-\cite{Kennicutt98b} calibrated luminosity of galaxies as a way of measuring the SFR in specific wavelengths using relations between the SFR per unit mass or per unit luminosity and the integrated colour of the system provided by synthesis models \citep[e.g.,][]{Bruzual93}.
+Many studies are devoted to determining how flux measurements of star-forming regions can be accurately translated into the rate of formation of new stars \citep[e.g.][]{Kennicutt12, Calzetti13, Zhu08, Kennicutt09, Boquien10, Boquien11, Hao11}.
+\cite{Kennicutt98b} calibrated luminosity of galaxies as a way of measuring the SFR in specific wavelengths using relations between the SFR per unit mass or per unit luminosity and the integrated colour of the system provided by synthesis models \citep[e.g.][]{Bruzual93}.
 Subsequent studies tried to find a similar calibration for measuring the SFR of galaxies in other bands.
-\cite{Kennicutt09} and \cite{Hao11} introduced new SFR calibrations using a combination of \halpha or FUV and far-infrared (FIR) emission, respectively.
-In addition to using suitable calibrations for each region, considering the differences between the global case and local ($\sim 0.5-1$~\kpc) case is important.
-In $\S$\ref{sec:sfr}, we will discuss the SFR in the Andromeda galaxy and how it was determined.
+\cite{Kennicutt09} and \cite{Hao11} introduced new SFR calibrations using a combination of \halpha or FUV and far-infrared (FIR) emission.
+In addition to using suitable calibrations for each region, considering the differences between the global and the local ($\sim 0.5-1$~\kpc) cases is important.
+In $\S$~\ref{sec:sfr}, we will discuss the SFR in the Andromeda galaxy and how it was determined.
 %me and Keniccutt98b and then me again, with Maryam's corrections
@@
 %P3: Gas cloud, variety, observing etc
-Calculating the surface density of gas in galaxies is the other most important ingredient of testing star formation laws.
-Considering the effect of the interstellar medium (ISM) on studying the star formation law is important due to the fact that stars are born from the gas and also release their material into the ISM when they reach the end of their evolution.
+Calculating the surface density of gas in galaxies is another important parameter in testing star formation laws.
+Considering the effect of the interstellar medium (ISM) is essential in understanding star formation laws since stars are born from gas and also release their material into the ISM when they reach the end of their evolution.
 A map of the total gas in the ISM is produced by direct observations of the gas or by using interstellar dust as a tracer.
 Neutral and molecular hydrogen are the most common elements in the ISM.
-Therefore, for producing the map of the total gas in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements which are mostly He.
-Calculations of the gas surface density for the Andromeda galaxy are shown in $\S$\ref{sec:ISM}.
+Therefore, for producing the map of the total gas in galaxies, maps of these two components can be added together and multiplied by a constant factor to account for heavier elements, mostly He.
+Calculations of the gas surface density for the Andromeda galaxy are shown in $\S$~\ref{sec:ISM}.
 %me
@@
 Additionally, for testing the Extended Schmidt law, measuring the stellar mass density is necessary.
-Measuring the mass of the stellar population is indirect and subject to significant uncertainties.
+Measuring the mass of stellar populations is indirect and subject to significant uncertainties.
 One method to calculate the stellar mass within a galaxy is based on stellar population models \citep[e.g.][]{ Bruzual93, Kotulla09}.
-These models are used to connect stellar mass to an observable quantity such as, luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations.
-Having different methods to measure stellar mass helps to compare the results and determine whether there are any systematic differences.
-Comparing the results from measuring the stellar mass via different methods in stellar clusters shows there is no significant difference \citep{Tamm12}.
+These models are used to connect stellar mass to an observable quantity such as luminosity in different wavelengths, colours, spectral energy distribution from spectroscopy or multi-band observations.
+Having various methods to measure stellar mass helps to compare the results and determine whether there are any systematic differences.
 In fact, the differences are found to be on the order of a few x10 percent; so one should be more careful to model subtleties \citep{McLaughlin05}.
-Calculating stellar mass in the Andromeda galaxy is described in $\S$\ref{sec:starmass}.
+However, Comparing the results from measuring the stellar mass via different methods in stellar clusters showed no significant difference \citep{Tamm12}.
+Section $\S$~\ref{sec:starmass} describes our calculations of stellar mass in the Andromeda galaxy.
 %me and Tamm and the rest I cited
 
-%P5(2*): What we did and why Andromeda and
+%P6(2*): What we did and why Andromeda
 In this paper, we present our results from testing and comparing both the K-S law and the Extended Schmidt law on the Andromeda galaxy (M31).
 Additionally, We applied these two laws on three different regions in M31 to determine if there is any dependence on distance from the centre of the galaxy.
-Since M31 is the nearest spiral galaxy to the Milky Way, we can have higher resolution images of this spiral galaxy.
-High resolution images of this spiral galaxy are avaiable that provide data from various regions within the galaxy with different physical properties (e.g.
+Since M31 is the nearest spiral galaxy to our own, high resolution images of this galaxy are available, providing data from various regions with different physical properties (e.g.
 metallicity, surface brightness, gas density).
-This inside look helps us to test star formation laws in diverse physical conditions.
-Thus, M31 is a suitable test bed for studying scaling laws.
+This inside look helps us test star formation laws in diverse physical conditions.
+Thus M31 is a suitable testbed for studying scaling laws.
 %me
 
-Furthermore, the range of the power index of the K-S law calculated for the Andromeda galaxy is between 0.5 - 2 \citep[e.g.,][]{Tabatabaei10,Ford13}.
-Various groups used different methods and data, and measured different values for the power index.
-In the most recent study of the K-S law in M31, \cite{Ford13} tested this law on six regions from the centre of the galaxy using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus HI maps, and total gas calculated from dust emission).
+Furthermore, the range of power indices calculated for the Andromeda galaxy using the K-S law is between 0.5 and 2 \citep[e.g.][]{Tabatabaei10,Ford13}.
+The use of different methods and data results in measuring different values for the power index.
+In a recent study of the K-S law in M31, \cite{Ford13} tested this law on six regions extending radially outward from the centre of the galaxy using three different ISM maps (H$_2$ only, total gas calculated from H$_2$ plus HI maps, and total gas calculated from dust emission).
 The measured power indices for each map and each region vary between 0.6 to 2.03.
-The origin of these variations in the results is still an open
-question.
-It is unclear whether it depends on distance from the centre of the galaxy, metallicity, gas tracers, SFR tracers, fitting methods, or because of the K-S law not working on M31.
-We also applied a new statistical method instead of the ordinary least square fitting (OLS), which is the most common fitting method for testing K-S law, to test the importance of the fitting method on the results.
+The origin of these variations in the results is still an open question.
+It is unclear whether it depends on distance from the centre of the galaxy, metallicity, gas tracers, SFR tracers, fitting methods, or it is because of the K-S law not working in M31.
+In order to examine the dependence of the results on the fitting method, we also applied a new statistical method instead of Ordinary Least Square (OLS) fitting, which is more commonly used in the literature to test the K-S law ($\S$~\ref{sec:fitting}).
 %me
@@
 \label{sec:data}
-Being the closest neighbouring galaxy to our own Milky Way, M31 has extensively been studied using both ground- and space- based telescopes.
-%Since M31 is the closest spiral galaxy to the Milky Way, it was aimed by many probes and telescopes, both space based and ground based ones. 
-Therefore, large data sets exist on M31 spanning from gamma-ray to radio wavelengths, allowing us to %a variety of data from gamma-ray to radio wavelengths are available.
-Wide ranges of data provide us the ability to
-measure all the required parameters to test the star formation laws in this galaxy.
+Being the closest neighbouring galaxy to the Milky Way (MW), M31 has extensively been studied using both ground- and space- based telescopes.
+Therefore, large datasets exist on M31 spanning from gamma-ray to radio wavelengths, allowing us to measure all the required parameters to test star formation laws in this galaxy.
 Table~\ref{table:data} lists the data we used in this paper.
-Each data comes with a different Full Width Half Maximum (FWHM), spacial resolution and grids.
-In order to make sure that all our data contains the same amount of information, we smoothed maps with smaller FWHM using Aniano's Kernels' library and convolution code \citep{Aniano12} to have the same resolution as either the $^{12}$CO(J:$1\rightarrow0$) data or atomic gas data.
-Moreover, considering the Nyquist relation \citep{Nyquist}, we re-sampled and re-gridded all our maps to have a pixel size matching with their new resolution.
-%I do not like this centence but I am not sure how to fixt it.
-%PBnew: what exactly does 'highest resolution available' mean? Same for 'proper pixel size' ? /done!
+Each data comes with a different angular resolution and pixel size.
+In order to match the images at different wavelengths, we smoothed the maps to the same FWHM using the kernel library and convolution code of \citet{Aniano11}.
+Our final results have two different angular resolutions depending on which gas tracer we use in studying the SFR laws.
+For studying the correlations between the SFR and molecular gas, our maps have the same resolution and pixel size as the $^{12}$CO(J:$1\rightarrow0$) data; while for investigating the relationships between the SFR and atomic gas (or total gas), we smoothed and re-gridded our maps to the resolution and pixel size of the one from the atomic gas.
 
@@
 6570~\AA  & 1\arcsec & 2\arcmin.2 $\times$ 0\degr.6 &KPNO& \cite{Massey07}\\
-3.6~\um & 1\arcsec.7 & 3\degr.7 $\times$ 1\degr.6 &\Spitzer & \cite{Barmby06} \\ %PB: write {\it Spitzer}, {\it Herschel}
-4.5~\um & 1\arcsec.7 & 3\degr.7 $\times$ 1\degr.6 &\Spitzer & \cite{Barmby06} \\ %PB because those are both missions and names
+3.6~\um & 1\arcsec.7 & 3\degr.7 $\times$ 1\degr.6 &\Spitzer & \cite{Barmby06} \\ %PB: write {\it Spitzer}, {\it Herschel} %PB because those are both missions and names
 8~\um & 1\arcsec.9 & 1\degr $\times$ 3\degr &\Spitzer & \cite{Barmby06} \\ % PB: of people - italics means the mission, not
@@
 160~\um & 12\arcsec & 5\degr.5 $\times$ 2\degr.5 &\Herschel & \cite{Fritz12} \\
-350~\um & 24\arcsec.5 & 5\degr.5 $\times$ 2\degr.5 &\Herschel & \cite{Fritz12} \\
+350~\um & 24\arcsec.9 & 5\degr.5 $\times$ 2\degr.5 &\Herschel & \cite{Fritz12} \\
 2.6~mm & 23\arcsec & 2\degr $\times$ 0\degr.5 &IRAM 30-m & \cite{Nieten06}\\
@@
 
-One of the calibrations used to calculate SFR uses FUV emission as a tracer of the star forming regions.
-FUV emission of M31 was observed by the Galaxy Evolution Explorer (GALEX; \cite{Martin05}).
-GALEX telescope data contains information for two bands, FUV:1350--1750 and NUV:1750--2750~\AA, with FWHM of 4~\farcs5, and 6~\arcsec.
-
-%\subsection{Visible light}
-\label{sec:vislight}
-Our other method to calculate the SFR involved using a combination of \halpha and 24 M emission.
-\cite{Massey06, Massey07} mapped UBVRI and \halpha emission line of M31 as part of the Nearby Galaxies Survey using the KPNO telescope.
-\halpha maps, which were obtained from the NOAO science archive, are available in 10 overlapping fields and were observed between August 2000 and September 2002.
-We created a Mosaic image of the maps using the Montage \citep{Berriman08}.
-Assuming that all stars have the same fraction of \halpha light in their spectra, we subtracted the R band emission from the \halpha image using the averaged scaling factor between R band images and \halpha provided by \cite{Azimlu11}.
-We also took a masked map from \cite{Azimlu11} and masked all foreground or partially saturated stars (Figure~\ref{fig:halpha}).
-Details about making the \halpha map can be found in Appendix ~\ref{app:halpha}.
+Several different observational datasets are used to compute properties of M31 for testing star formation laws.
+One method for calculating the SFR uses FUV emission as a tracer of the star-forming regions: for this we
+use the FUV image of M31 as observed by the Galaxy Evolution Explorer (GALEX; \cite{Martin05}).
+
+Our other method to calculate the SFR involved using a combination of \halpha and 24 $\mu$m emission.
+\citet{Massey06, Massey07} mapped M31 in broad and narrow bands, including \halpha, as part of the Nearby Galaxies Survey using the KPNO 4-m telescope.
+A detailed description of how our \halpha map is made can be found in Appendix~\ref{app:halpha}.
 
 %\subsection{IR and sub mm Data}
-Both {\em Spitzer} \citep{Werner04} and {\em Herschel} \citep{Pilbratt10}  space telescopes observed M31 at IR and sub mm bands.
-Observations with Infrared Array Camera (IRAC; \citep{Fazio04}) are made in four channels (3.6, 4.5, 5.8, and 8 \um).
-IRAC observations of M31 were obtained by \cite{Barmby06}, covering a region $3\degr.7 \times 1\degr.6$.
-IRAC 3.6 \um bands were used to calculate the stellar mass.
-Multiband Imaging Photometer for \Spitzer (MIPS) observed M31 at 24, 60, and 160 \um and covered region $\sim 1\degr \times 3\degr$ \citep{Gordon06}.
-
-Calculation of the SFR using TIR emission requires maps of M31 in 8, 24, 70, and 160 \um.
-IRAC 8, MIPS 24, MIPS 70 bands were used to calculate TIR emission; however due to better quality and resolution of $Herschel$s$'$data, PACS \citep[Photodetector Array Camera and Spectrometer;][]{Poglitsch10} were used.
-PACS 160 \um observation of the Andromeda galaxy alongside of PACS 100 \um band and three (250 $\mu$m, 350 $\mu$m, and 500 \um) SPIRE \citep[Spectral and Photometric Imaging Receiver;][]{Griffin10} bands coveres $\sim 5\degr.5 \times 2\degr.5$ regions in M31 \citep{Fritz12}.
+Calculations of the SFR using the total infrared emission requires observations at 8, 24, 70, and 160~\um, made
+with the {\em Spitzer} \citep{Werner04} and {\em Herschel} \citep{Pilbratt10}  space telescopes. 
+Observations with the Infrared Array Camera (IRAC; \citep{Fazio04}) are made in four channels (3.6, 4.5, 5.8, and 8~\um); IRAC observations of M31 were obtained by \cite{Barmby06}, covering a region $3\degr.7 \times 1\degr.6$.
+The Multiband Imaging Photometer for \Spitzer (MIPS) observed M31 at 24, 60, and 160 \um and covered a region $\sim 1\degr \times 3\degr$ \citep{Gordon06}.
+{\em Herschel} observations of M31 were made with with PACS \citep[Photodetector Array Camera and Spectrometer;][]{Poglitsch10}  at 100 and 160~\um and SPIRE  \citep[Spectral and Photometric Imaging Receiver;][]{Griffin10}
+at 250, 350, and 500~\um, covering a region  $\sim 5\degr.5 \times 2\degr.5$ \citep{Fritz12}.
+The IRAC 8, MIPS 24, MIPS 70, and PACS 160 images were used to calculate M31's total infrared emission. 
+The IRAC 3.6~\um band image was used to calculate the stellar mass.
 
 %\subsection{Radio Emission}
-Emission from $^{12}$CO (J:$1\rightarrow0$) line that, was observed on-the-fly with the IRAM 30-m telescope \citep{Nieten06} was used to calculate the H$_2$ column density of the interstellar medium.
-This mapa a region $2\degr \times 0\degr.5$ that has the best resolution CO image of M31 (FWHM = $23\arcsec$), but the smallest coverage of the halo of the galaxy among the maps we used in this paper.
-In this study we also used 21 cm emission map from the atomic gas (HI) in M31 from \cite{Chemin09}.
-They used Synthesis telescope and the 26 m antenna at the Dominion Radio Astrophysical Observatory to map HI emission in the 21 cm band of M31.
-
-\section{Measuring the component of Star Formation Laws}
+Gas densities in galaxies are derived from observations at millimetre and centimetre radio wavelengths.
+Emission from the $^{12}$CO (J:$1\rightarrow0$) line observed on-the-fly with the IRAM 30-m telescope \citep{Nieten06} was used to calculate the H$_2$ column density of M31's interstellar medium.
+This map covers a $2\degr \times 0\degr.5$ region with an angular resolution of $23\arcsec$ and has the smallest coverage of the galaxy among the maps we used in this paper.
+In this study, we also used a 21-cm emission map of the atomic gas (HI) in M31 from \cite{Chemin09}.
+This map was made using the synthesis telescope at the Dominion Radio Astrophysical Observatory and covers a $5\degr.1 \times 1\degr.5$ region with an angular resolution of $60\arcsec \times 90\arcsec$.
+
+\section{Measuring the components of Star Formation Laws}
+Before studying the star formation laws, we need to calculate the components of these laws.
+We used different data and calibrations to produce the SFR maps, the stellar mass surface density and the gas mass surface density.
+To use this calibrations, we used M31 distance to be 0.78~Mpc~\cite{McConnachie05}, and all the total values recorded in this paper are up to~23~kpc from centre of the galaxy.
+In this section we are showing how we measured every ingredients using available data, and calibrations.
+
+\subsection{Stellar Initial Mass Function}%I know it is too basic. But I couldn't decide which part should I delete.
+\label{sec: imf}
+
+% edited version, 20150715
+In order to determine star formation rate and stellar mass from calibrated photometric data, it is necessary to know the IMF. 
+Stellar population synthesis models make different assumptions about the IMF, often either  \cite{Salpeter55},
+$ dN / d \log M \propto M^{-3.5 }$ over the full range of masses, or \cite{Kroupa01} $ dN / d \log M \propto M^{-\Gamma }$ 
+with $\Gamma=-2.3$ at low masses and  $\Gamma=-3.3$.
+
+%%% Sahar_ans: dN/d log M = mdN/dM so your number should be correct.
+For the same total mass, the Salpeter and Kroupa IMFs produce almost the same amount of high-mass stars, but the Salpeter IMF produces more low-mass stars.
+\cite{Calzetti12} showed the impact of different IMF assumptions on SFR calibrations.
+Adopting a modified \cite{Kroupa01} IMF, with its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes the SFR calibration constant by factors 1.4 to 5.6 for different SFR indicators.
+Changes in the IMF mostly affect the calibration based on \halpha luminosity, because a significant amount of the ionizing photons comes from stars more massive than $\sim 20$~M$\sun$.
+
+In this project we used values based on the \cite{Kroupa01} IMF as is standard in the field, although discussion continues on whether the IMF is universal \citep{Bastin10}.
+Where necessary we converted from SFR calibration values based on the Salpeter IMF by multiplying by 1.61  \citep{Madau14}.
+
+%One of the most basic and difficult questions that a complete theory of the star formation must answer is the initial mass function (IMF).
+In order to determine SFR and stellar mass, from calibrated photometry data, it is necessary to know the IMF.
+Most problem in modern astrophysical studies regarding origin and evolution of stars and galaxies can be solved by varying an IMF \citep{Bastin10}.
+\cite{Salpeter55} empirically derived the IMF from the observed stellar luminosity function from the solar neighbourhood \citep{Shu87}.
+He introduced a power law IMF of the form:
+
+%\begin{equation}
+%\label{equ: salp}
+%\Phi (\log M) = dN / d \log M \propto M^{-\Gamma }
+%\end{equation} 
+%where M is the mass of a star and N is the number of stars in some logarithmic mass range $\log M + d\log M$.
+
+%It was recognised that the using the single power low IMF over all stellar masses is not a correct assumption.
+Since then many groups have studied the IMF and find the different power laws for it \citep{Bastin10}.
+Most SFR calibrations have the same assumption that the IMF is constant across all environments and adopted from the standard IMF of \cite{Kroupa01}:
+
+%\begin{align}
+%\chi (M) = dN/dM = A M^{-1.3}    \quad    (0.1 \le M(M{\odot}) \le 0.5)\\                  
+ %          = 0.5 A M^{-2.3}    \quad    (0.5 \le M(M{\odot}) \le 100)
+%\end{align}
+%where $\chi(M)$ is the number of stars between mass $M$ and $M+dM$.
+Although the Salpeter IMF produces more low-mass stars then the Krupa IMF, but they produce almost the same amount of the high mass stars.
+therefore, the SFR calibrations, which mostly trace massive stars in galaxies, based on the Kroupa IMF and Salpeter IMF can be converted together by multiplying the calibration$^\prime$s constant by $ \sim 1.6$ \citep{Calzetti12}.
+For co \cite{Bastin10} reviewed  the IMF  by using many observational results showed that the IMF is constant and universal, although there are uncertainly in different mass bins especially at the high mass end.
+
+ %Carefully measuring the IMF is a key to understanding the SFR.
+In distant galaxies, only massive stars can be detected, therefore, IMF must be measured to include all stellar mass ranges to SFR calibrations.
+To show the impact of the different IMF assumption on the SFR calibrations, \cite{Calzetti12} used two different IMFs and derived the SFR calibrations with these new assumptions.
+Adopting a modified \cite{Kroupa01} IMF, which its maximum stellar mass set to 30 M$_{\odot}$ instead of 100 M$_{\odot}$, changes the SFR calibration constant by factors 1.4 to 5.6 for different SFR indicators.
+Changes in the IMF mostly affect the calibration based on \halpha luminosity, because a significant amount of the ionizing photons comes from the stars more massive than $\sim 20$~M$\sun$.
+In this project we used \cite{Kroupa01} IMF.
 
@@
 \label{sec:sfr}
-\subsubsection{FUV plus 24 M Star Formation Rate}
+\subsubsection{FUV plus 24 $\mu$m Star Formation Rate}
 
 In this project the first star formation map was produced using a calibration of a combination of FUV emission and 24 \um emission introduced by \cite{Hao11}.
-Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.,][]{Kennicutt89}.
-The UV emission traces recently formed stars with the age of $\sim 100$ Myr \citep[e.g.,][]{Kennicutt98a, Calzetti05}.
-However, the downside of only using the FUV light as a tracer of the star forming region is that this emission is very sensitive to dust extinction.
+Since the peak of the emission of massive and young stars (O-B and A type) is in the UV part of the spectrum, this wavelength is one of the most commonly used star formation rate indicators \citep[e.g.][]{Kennicutt89}.
+The UV emission traces recently formed stars ($\sim 100$ Myr) \citep[e.g.][]{Kennicutt98a, Calzetti05}.
+However, the downside of only using the FUV light as a tracer of the star-forming region is that this emission is very sensitive to dust extinction.
 On the other hand, 24 \um emission is dominated by emission from dust heated by UV photons from young and hot stars.
 This emission is sensitive to the star formation timescale of $\la10$ Myr \citep{Calzetti07}.
-The FUV band of \Galex and the 24 \um band of \Spitzer data were used to measure the SFR calibrated by \cite{Hao11} as:
+The FUV band of \Galex and the 24 \um band of \Spitzer data were used to measure the SFR calibrated by \cite{Hao11} using nearby galaxies and the \cite{Kroupa01} IMF as:
 \begin{equation}
@@
 \end{equation}
-where SFR is in M$_{\odot}$yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{obs}$ are in erg~s$^{-1}$.
+\noindent where SFR is in M$_{\odot}$yr$^{-1}$, and L(24$\mu$m) and L(FUV)$_{obs}$ are in erg~s$^{-1}$.
 L(FUV)$_{obs}$ is the luminosity of the galaxy in the FUV emission.
-The subscript "obs" is shown to indicate that the FUV emission is not corrected for the effect of extinction.
-Nevertheless, this emission was corrected for the foreground star's emission using a method introduced by \cite{Leroy08}.
-We assumed for any pixel in FUV$_{obs}$ map, if I$_{NUV}$/I$_{FUV}$ $>$ 15 that pixel value is dominated by foreground emission and masked them out.
-We also masked the same region in the galaxy for the 24 \um map.
-Using this method, we calculated the total SFR to be $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$.
+The subscript "obs" indicates that the FUV emission is not corrected for extinction.
+Nevertheless, this emission was corrected for the foreground stars' emission using a method introduced by \cite{Leroy08}.
+We masked out pixel values in the FUV$_{obs}$ map for which I$_{NUV}$/I$_{FUV}$ $>$ 15, assuming that those pixels are dominated by foreground emission.
+Then we smoothed our map to have the same angular resolution and pixel size as the MIPS 24 $\mu$m, and masked the same regions in the galaxy for the 24 \um map.
+Figure \ref{fig:sfr,fuv} shows the SFR(FUV+24 $\mu$m) map.
+We added all the pixels in the map and calculated the total SFR to be $0.31\pm 0.04$~M$_{\odot}$~yr$^{-1}$.
 
@@
         \includegraphics[width=164mm]{sfr_fuv.eps}
-        \caption{SFR,FUV+24 M}
+        \caption{SFR(FUV+24 $\mu$m)}
         \label{fig:sfr,fuv}
@@
         \includegraphics[width=164mm]{sfr_halpha.eps}
-        \caption{SFR,H$_{\alpha}$}
+        \caption{SFR(H$_{\alpha}$)}
         \label{fig:sfr_halpha}
@@
         \includegraphics[width=164mm]{sfr_fir.eps}
-        \caption{SFR,TIR}
+        \caption{SFR(TIR)}
         \label{fig:sfr,fir}
     \end{subfigure}
-    \caption{SFR map from a combination of FUV + 24 M emission (top), \halpha and 24 M emission (middle), and total infrared emission (bottom)}
+    \caption{SFR map from a combination of FUV + 24 $\mu$m emission (top), \halpha and 24 $\mu$m emission (middle), and total infrared emission (bottom).
+All the SFR maps here, have the angular resolution of the 18\arcsec and pixel size of 9.85\arcsec, same as MIPS 70 $\mu$m map; highest angular resolution among the components of the SFR}
     \label{fig:sfrs}
@@
 
-The SFR can be calculated using combination of \halpha and \Spitzer  24\um maps.
+The SFR can also be calculated using a combination of \halpha and \Spitzer  24 \um maps.
 \halpha emission of galaxies is dominated by light emitted from young and massive stars.
-Star formation time scaled traced by this emission is $\sim 6-10$ Myr \citep[e.g.,][]{Kennicutt09, Calzetti13}.
-Therefore, \halpha alone could be used to calibrate the SFR \citep[e.g.,][]{Osterbrock06, Kennicutt09}.
-However, \halpha emission is very sensitive to dust extinction, too.
+Star formation timescales traced by this emission is $\sim 6-10$ Myr \citep[e.g.][]{Kennicutt09, Calzetti13}.
+Therefore, \halpha alone could be used to calibrate the SFR \citep[e.g.][]{Osterbrock06, Kennicutt09}.
+However, \halpha emission is very sensitive to dust extinction.
 Therefore, the combination of the \halpha and 24\um of is considerable choice for calculating the SFR.
-wW used a calibration introduced by \cite{Kennicutt09} to measure the SFR:
+We used a calibration introduced by \cite{Kennicutt09} to measure the SFR:
 \begin{equation}
 \label{equ: halphaplus24_g}
-SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.020L(24\mu m)]
-\end{equation}
-where L(H${\alpha}$)$_{obs}$ is the observed \halpha luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$.
+SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.020L(24\mu m)],
+\end{equation}
+\noindent where L(H${\alpha}$)$_{obs}$ is the observed \halpha luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$.
 L(24$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}$yr$^{-1}$.
@@
 \cite{Calzetti07} introduced a new calibration using the same band passes in a case of local regions (Figure~\ref{fig:sfr_halpha}):
+
 \begin{equation}
 \label{equ: halphaplus24_l}
-SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.033L(24\mu m)]
-\end{equation}
-the units here are the same as equation~\ref{equ: halphaplus24_g}.
+SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.033L(24\mu m)],
+\end{equation}
+
+\noindent the units here are the same as equation~\ref{equ: halphaplus24_g}.
 Equation~\ref{equ: halphaplus24_l} is useful for regions less than $\sim 1$ kpc.
-According to  \cite{Calzetti07} calibration constant in equations ~\ref{equ: halphaplus24_g} and ~\ref{equ: halphaplus24_l} can be different by changing an IMF.
-Changes in the IMF mostly affect on calibration based on \halpha luminosity, mostly because a significant amount of the ionizing photons comes from the stars more massive than $\sim 20$M$\sun$.
-Changing the calibration constant would change the total SFR by a factor of 1.5.
-In this paper, we used \cite{Kroupa01} IMF with an upper mass limit of 100M$\sun$.
+For testing the SFR laws in local regions we used equation~\ref{equ: halphaplus24_l}.
 Total SFR calculated from equation~\ref{equ: halphaplus24_g} is $0.35 \pm 0.01$~M$\sun$~yr$^{-1}$, which is in good agreement with previous studies.
-
-Creating the SFR map using \halpha plus 24 \um was described in Section~\ref{sec:sfr_halpha}.
-In order to investigate the SFR laws, we used the same method of the fitting as Section~\ref{sec:fitting}.
-The fitting results using SFR(\halpha $+$ 24 \um ) are totally different from the other two SFR tracers.
-The main reason for this difference could is mainly because of the extreme amount of the nan values in the map especially lost of the data in the centre of the galaxy.\halpha data does not have a smooth background.
-Also the centre of galaxy in this data is diffused, so we do not have any data from the centre of the M31.
-Since it was the only available \halpha data from the M31, We used this data anyway.
 
@@
 \end{equation}
-where SFR(TIR) and L(TIR), the star formation rate calculated from TIR emission and TIR luminosity, are in M$_{\odot}$~yr$^{-1}$ and erg~s$^{-1}$, respectively.
+\noindent where SFR(TIR) and L(TIR), the star formation rate calculated from TIR emission and TIR luminosity, are in M$_{\odot}$~yr$^{-1}$ and erg~s$^{-1}$, respectively.
 Part of the dust emission in galaxies (specially in M31) comes from the dust heated by the cosmic background radiation \citep[e.g.][]{Dole06, Calzetti13, Mattsson14}, hence, using equation~\ref{equ:sfr_fir} overestimates the SFR in M31.
@@
 \end{equation}
-where L(8), L(24), L(70), and L(160) are luminosities of the galaxy in 8 $\mu$m, 24 $\mu$m, 70 $\mu$m,and 160 \um in units of erg~s$^{-1}$.
-We used equation~\ref{equ:sfr_fir} to calculate the second map of the SFR of M31 (Figure~\ref{fig:sfr,fir}).
-Using this method, we calculated the total SFR to be $0.40 \pm 0.04$~M$_{\odot}$~yr$^{-1}$.
+\noindent where L(8), L(24), L(70), and L(160) are luminosities of the galaxy in 8 $\mu$m, 24 $\mu$m, 70 $\mu$m,and 160 \um in units of erg~s$^{-1}$.
+We used results from equation~\ref{equ: TIR} in the equation~\ref{equ:sfr_fir} to calculate our last map of the SFR of M31 (Figure~\ref{fig:sfr,fir}).
+Using this method, we calculated the total SFR by adding all the pixels to be $0.40 \pm 0.04$~M$_{\odot}$~yr$^{-1}$.
 Table~\ref{table:sfr} compares the total SFR from literature and the present work.
@@
 \hline
-Current work&FUV and 24 M&0.31 $\pm$ 0.04\\
-Current work&\halpha and 24 M&0.35 \\
-Current work&TIR luminosity&0.4 $\pm$ 0.04\\
-\cite{Ford13}&FUV and 24 M&0.25\\
+%Current work&FUV and 24 $\mu$m&0.31 $\pm$ 0.04\\
+%Current work&\halpha and 24 $\mu$m&0.35 $\pm$ 0.01\\
+%Current work&TIR luminosity&0.4 $\pm$ 0.04\\
+Current work&FUV and 24 $\mu$m&0.31 \\
+Current work&\halpha and 24 $\mu$m&0.35 \\
+Current work&TIR luminosity&0.4\\
+\cite{Ford13}&FUV and 24 $\mu$m&0.25\\
 \cite{Ford13}&TIR luminosity&0.48-0.52\\
-\cite{Azimlu11}& \halpha and 24 M&0.34\\
+\cite{Azimlu11}& \halpha and 24 $\mu$m&0.34\\
 \cite{Azimlu11}&Extinction corrected \halpha&0.44\\
@@
 %----------------------------------------------------------------------------------------
+
 \subsection{Gas Surface Density}
@@
 
- The molecular form of hydrogen is really hard to detect.
-H$_2$ molecules are located in cool and dense molecular clouds, but fortunately they are not the only component of the molecular gas.
-CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen \citep[see, for example,][] {Sanders84}.
-Higher rotational transition of CO can be used as a tracer as well, but they are not as common as $J(1\rightarrow 0)$.
-The relation between CO emission and H$_2$ cloud mass is shown as:
+ The molecular form of hydrogen is very hard to detect.
+Therefore, CO (usually the $J(1\rightarrow 0)$ rotational transition, observed at 2.6 mm) is used as a tracer of the mass of the molecular cloud dominated by molecular hydrogen \citep[see, for example,][] {Sanders84}.
+Higher rotational transitions of CO can be used as tracers as well; however, they are not as common as $J(1\rightarrow 0)$.
+Equation \ref{equ:conversion} shows the relation between CO emission and H$_2$ column density:
 
@@
 \label{equ:conversion}
-\rm N_{H_2}/\rm cm^{-2} = X_{CO} \times I_{CO}/\rm K km s^{-1}
-\end{equation}
-where X$_{CO}$ is the conversion factor (also known as the X-factor).
-The X-factor could be different in regions within a galaxy due to the difference in metallicity \citep{Wilson95, Bosselli02, Bolato13}.
-In case of M31, different values of X-factor ($1-5.6 \times 10^{20}$) were adopted in the previous studies \citep[e.g.][]{Ford13, Bolato13, Leroy11, Bolato08, Nieten06}; however, since any constant differences in X-factor leads to horizontal changes in a plot of log(SFR) versus Log($\Sigma_{\rm {gas}}$), and does not affect our K-S law power index for molecular gas,  we chose $X_{\rm {CO}}= 2 \times 10^{20}$  the same as many other works \citep[e.g.][]{Ford13, Smith12}.
-Since HI mass dominates H$_2$ mass in M31, the constant X-factor has negligible affect on the total gas mass.
+\rm N_{H_2}/\rm cm^{-2} = X_{CO} \times I_{CO}/\rm K km s^{-1} ~,
+\end{equation}
+
+\noindent where X$_{CO}$ is the conversion factor (also known as the X-factor), I$_{CO}$ is CO intensity in  K km s$^{-1}$ and N$_{H_2}$ is molecular hydrogen column density.
+The X-factor could be different in regions within a galaxy due to the different metallicities \citep{Wilson95, Bosselli02, Bolato13}.
+In the case of M31, different values of X-factor in the range of ($1-5.6 \times 10^{20}$) were adopted in previous studies \citep[e.g.][]{Ford13, Bolato13, Leroy11, Bolato08, Nieten06}; however, since any constant difference in X-factor leads to horizontal changes in a plot of log(SFR) versus log($\Sigma_{\rm {gas}}$) and does not affect our power indices for molecular gas, we chose $X_{\rm {CO}}= 2 \times 10^{20}$ which is the same value that is adopted in many other works \citep[e.g.][]{Ford13, Smith12}.
+Since HI mass dominates the H$_2$ mass in M31, the constant X-factor has a negligible effect on the total gas mass.
+We assumed each hydrogen molecule has a mass of 2.34 mass of H, and calculate the H$_2$ mass density.
+
 The total gas mass was calculated from:
@@
 \label{equ:total_gas}
-\rm M_{\rm \bld {total \, gas}} = 1.36[M_{HI}+M_{H_2}]
-\end{equation}
-where  factor of 1.36 is a constant to consider He and the other heavier elements affect on the total gas mass, M$_{HI}$ is mass of neutral hydrogen that were obtained from 21cm observations, and M$_{H_2}$ calculated from equation~\ref{equ:conversion} in units of M$_{\sun}$.
+\rm M_{\rm \bld {total \, gas}} = 1.36[M_{\rm HI}+M_{H_2}],
+\end{equation}
+\noindent where the factor of 1.36 is a constant that takes into account the contribution of He and other heavier elements to the total gas mass, M$_{\rm HI}$ is the mass of neutral hydrogen that was obtained from 21 cm observations (the map, which we got from \cite{Chemin09} has a unit of number density which we used it to calculate mass density of HI), and M$_{H_2}$ was calculated from equation~\ref{equ:conversion} in units of M$_{\sun}$/pc$^2$.
 
@@
 \includegraphics[width=164mm]{star.eps}
-\caption{Stellar Mass surface density with pixel size of 4.3\arcsec and FWHM of 1\arcsec.7.
-The stellar surface density map is produced using IRAC 3.6~$\mu$m data and its calibration presented in equation~\ref{equ:eskew}.}
+\caption{The stellar surface density map is produced using IRAC 3.6~$\mu$m data and its calibration is presented in equation~\ref{equ:eskew}.}
 \label{fig:stellarmass}
@@
 
-Near IR band such as: 3.6$\mu$m, 4.5\um and K band emission, are almost insensitive to the emission from the young stellar population, dust absorption and emission, which make them a good tracer of the mass of the older stellar populations\citep[e.g.,][]{Elmgreen84, Eskew12, Zhu10}.
-We calculated the stellar mass within M31 using calibration of the 3.6\um flux by \cite{Eskew12}.
-They used data from the Large Magellanic Cloud, and introduced an empirical relation between stellar mass and flux of stars:
+Near IR bands, such as: 3.6$\mu$m, 4.5\um and K band emission, are almost insensitive to the emission from the young stellar population, dust absorption and emission, which make them good tracers of the mass of the older stellar populations \citep[e.g.][]{Elmgreen84, Eskew12, Zhu10}.
+We calculated the stellar mass within M31 using calibration of the 3.6 \um flux by \cite{Eskew12}.
+They used data from the Large Magellanic Cloud and introduced an empirical relation between stellar mass and flux:
 
@@
 \end{equation}
-where M$_{\star}$ is the stellar mass in solar masses, $F_{3.6}$ is 3.6\um flux in Jy, and $D$ is the distance of the galaxy in Mpc.
-Figure~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6\um.
-In this figure pixels with dark blue colour show zero M$_{\odot}$, while dark red ones show pixels with mass of more than 6.4e3 M$_{\odot}$.
-Using this method we calculated the total stellar mass of the galaxy to be $6.9 \times 10^{10}$M$_{\odot}$ with 6$\%$ uncertainty.
-This result is in fair agreement with the result from \cite{Tamm12}.
+
+\noindent where M$_{\star}$ is the stellar mass in solar masses, $F_{3.6}$ is 3.6 \um flux in Jy, and $D$ is the distance to the galaxy in Mpc.
+This calibration is based on the Salpeter \cite{Salpeter55} IMF.
+Since the Kroupa IMF is adopted for the SFR maps, we corrected the calibration for the Kroupa IMF (see section~\ref{sec: imf}).
+We should note that \cite{Eskew12} have two calibrations for calculating the stellar mass in their paper, one is equation~\ref{equ:eskew} which only uses 3.6 \um emission and the other is using both 3.6 \um and 4.5 \um emission.
+We noticed that the other calibration can only be used in the case of total stellar mass due to the fact that the correlation shows a non-linear dependency of stellar mass to the $F_{3.6 \mu m}$ and $F_{4.5 \mu m}$, though this was not mentioned in aforementioned paper.
+Figure~\ref{fig:stellarmass} shows the stellar mass map for M31 using IRAC 3.6 \um in original angular resolution and pixel size of the IRAC 3.6 \um.
+We had a coverage map of the IRAC 3.6 \um band; and we used only regions with coverage of more than 2, and replaced the rest with zero M$_{\odot}$ which are shown as dark blue pixels in this figure.
+Using this method we calculated the total stellar mass of the galaxy by adding all pixel values and found it to be $6.9 \times 10^{10}$M$_{\odot}$ $\pm$ 6$\%$.
+This result is in fairly good agreement with the results of \cite{Tamm12}.
 They calculated that stellar mass in M31 is $(10-15) \times 10^{10}$M$_{\odot}$, 56$\%$ of which is in the disk with the rest in the bulge of the galaxy.
@@
 \subsection{Metallicity}
+\label{sec:metal}
+
+Metallicity of galaxies can be estimated by measuring abundances of heavier elements of the ISM in galaxies.
+Assuming gas phase oxygen abundance, $[$O$/$H$]$, is proportional to abundances of heavier elements and [O/H] would be a gauge to determine metallicity \citep[e.g.][]{McGaugh91, Zaritsky94}.
+Results from modelling dust in the MW and nearby galaxies showed that the dust to gas mass ratio depends on $[$O$/$H$]$ and, consequently, on metallicity \cite{Draine07}.
+\cite{Draine14} assumed that depletion of gas elements from the gas to diffuse ISM in M31 is similar to the MW, and proposed that:
+
+ \begin{equation*}
+ \label{equ: metal}
+\frac{M_d}{M_H}=0.0091 \frac{Z}{Z_{\odot}},
+ \end{equation*} 
+ \noindent where M$_d$ and M$_H$ are the masses of dust and hydrogen atom, Z is metallicity of M31 and Z$_{\odot}$ is solar metallicity.
+\cite{Draine14} produced two dust maps of M31 using MIPS 160 resolution (angular resolution = 39\arcsec; 18\arcsec $\times$ 18\arcsec pixels) and SPIRE 350 resolution (angular resolution = 24\arcsec.9; 10\arcsec $\times$ 10\arcsec pixels), which are publicly available.
+We used dust map with SPIRE 350 resolution, convolved and re-gridded it to have the same resolution and pixel size for the HI map, then we divided this dust mass by the mass of hydrogen in M31.
+However, in a private correspondence with the author, Draine pointed out that based on the Plank observation of the MW dust \cite{Tauber10}, the dust mass surface density map estimated for M31 by \cite{Draine14} may be systematically high by a factor of 2.
+Therefore, we divided the dust map by 2 to account for this correction.
+We then generated the metallicity map of M31 by using the dust map in combination with equation~\ref{equ: metal}.
+\cite{Draine14} showed that with increasing distance from the centre of M31, dust to H mass ratio declines monotonically and concluded that metallicity also behaves in the same way.
+Their fitting results showed that M31 can be divided into three regions ($R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$) where dust to H mass ratio (or metallicity) has different correlations with distance from the centre of the galaxy.
+
 %----------------------------------------------------------------------------------------
@@
 \section{Scaling SFR}
+
+\subsection{Fitting method}
+\label{sec:fitting}
+
+\begin{figure*}
+\centering
+\includegraphics[width=164mm]{Results_for_all_regions.pdf}
+\caption{Results from fitting the Kennicutt-Schmidt law to data from the entire galaxy using the pixel by pixel method.
+The points in the plots represent different pixel sizes due to differences in the resolution of the H$_2$ and HI maps.
+Each point on the plots where the surface density of H$_2$ is used as a tracer of gas mass represents a region of size $\sim$30~pc while each point for which the surface density of HI or total gas mass is a tracer represents a region of size $\sim$155~pc.
+Solid lines shows the best fit, using the max value of the ranges in table~\ref{table:res}
+} 
+\label{fig:ks,all}
+\end{figure*}
+
+Producing the SFR, gas mass, stellar mass, and metallicity maps provides enough data to examine and compare the K-S law and the extended Schmidt law.
+To create the surface density map, we divided the value of each pixel by its area in pc$^2$.
+We investigated the K-S law and the extended Schmidt law by using pixel by pixel method in the entire galaxy as well as comparing the laws in three elliptical regions, assuming the position angle 38$\degr$, inclination of 77$\degr$ for M31 with distance from the centre of the galaxy the same as the ones described in section~\ref{sec: metal}.
+As mentioned in section~\ref{sec:data}, since the H$_2$ gas mass map has higher angular resolution and smaller pixel size than the HI gas mass map, our final results have two sets of different pixel sizes.
+Consequently, any plots with surface density of H$_2$ as a tracer of the gas mass will have more data points.
+
+Equations~\ref{equ:ks_org}~and~\ref{equ:es_org} can be re-written in logarithmic scale to obtain two linear equations:
+
+\begin{subequations}
+\begin{equation}
+\label{eq:sfr_law_ks_log}
+\log_{10} \eqsigmasfr = N~\log_{10} \eqsigmagas + A,
+\end{equation}
+\begin{equation}
+\label{eq:sfr_law_es_log}
+\log_{10} \eqsigmasfr = \eqnprime~\log_{10} \eqsigmagas + \beta~\log_{10}\eqsigmastar  + A^\prime,
+\end{equation}
+\end{subequations}
+\noindent where, {\it N}, $\eqnprime$, $\beta$, A, and A$^\prime$ are free fitting parameters.
+The units in the above equations are the same as those in equations ~\ref{equ:ks_org} and ~\ref{equ:es_org}.
+
+We found the free parameters by applying the hierarchical Bayesian linear regression method as described in \cite{Shetty13}.
+Shetty and his colleagues used a Bayesian linear regression approach to develop a new method to find the K-S law parameters, considering the measurement uncertainties as well as hierarchical data structure.
+We used the same technique as \cite{Shetty13} to estimate the KS law parameters.
+For the extended Schmidt law, we extended the code such that instead of using  simple hierarchical Bayesian linear regression, which is used for the K-S law, it uses multiple hierarchical Bayesian linear regression.
+In this case, we were able to examine the effect of the stellar mass in the SFR as shown in equation ~\ref{eq:sfr_law_es_log}.
+% It doesn't sound good!
+
+Uncertainties in each observable quantities were measured by following the method described in \cite{Kennicutt07}.
+We used the quadratic sum of the variance of the local background for each luminosity map from the original pixel size images, Poisson noise of images, and calibration uncertainties.
+
+We also tested each law on three different regions which were chosen in the same manner as explained in~\ref{sec:metal}.
+Applying the SFR laws in these regions provides a tool to consider the effect of the distance from the centre of the galaxy on SFR laws such as metallicity, gas mass, stellar mass gradients and changing the ratio of H$_2$ to HI.
+
 \subsection{Star formation laws}
+\label{sec: sfl}
 
 We made three SFR maps, three gas mass density maps and a stellar mass density map of whole galaxy.
-We applied both laws on whole galaxy on each two combination of SFR and gas mass density maps, along with applying the laws on three different regions.
-As a result we were be able to test each law 36 times.
-In total, we produced 72 different plots, which show either the K-S law or the extended Schmidt law, both in whole galaxy and in different distances from the centre of M31.
-Additionally, we can use these results to see if there is any correlation between the SFR laws and the metallicity, as it is going to be described in ~\ref{sec:fitting}.
+We applied both laws on the whole galaxy using each two combination of SFR and gas mass density maps, along with applying the laws on three different regions.\cite{Kennicutt12} reviewed star formation in the MW and the nearby galaxies and described that there might be a breakdown on SFR laws for small size regions.
+Therefore, we re-gridded all the maps to have a pixel size equivalent to 750~pc, and repeated all of our processes on these new maps (table~\ref{table:res750}).
+Additionally, we used these results to see if there is any correlation between the SFR laws and metallicity, as it is going to be described in ~\ref{sec:fitting}.
 
@@
 First row plots are the surface density of the SFR(TIR), which is calculated using  the TIR emission form section ~\ref{sec:sfr_fir}, versus the gas surface density traced by only the molecular gas (H$_2$),  only atomic gas (HI), and total gas from right to left, respectively.
-The only difference between the upper and lower plots is that in the lower row the SFR indicator is the FUV plus 24 M emission.
-Figure~\ref{fig:ks,regs} shows the same data as Figure~\ref{fig:ks,all}.
+The only difference between the upper and the other rows is that in the lower rows the SFR indicator is the FUV plus 24 $\mu$m (second row), and \halpha plus 24 $\mu$m emission (third row).
+Figure~\ref{fig:ks,regs} shows the same data as figure~\ref{fig:ks,all}.
 However, in this figure we separated pixels from different regions in the galaxy by their colours.
 The regions with R less than 8$\kpc$, $8\kpc < $R $< 18\kpc$, and $18\kpc <$ R $\la 25\kpc$ are shown in red, green and blue, respectively.
+There is a deviation in middle panel plots of figure~\ref{fig:ks,all} which shows region with high star formation rate and low HI gas.
+It is clear that these deviation belongs to regions further than 8~kpc from centre (figure~\ref{fig:ks,regs}).
+HI surface density profile of M31 \citep[See figure 16 in.][]{Chemin09} shows several local minimum from centre of M31 to 30~kpc distance which could be results of the HI wrap.
+Some of these minimums are around the rings area of M31, which has higher SFR regarding to the other regions in the galaxy and causes these deviations.
+Since the total gas mass is calculated by adding HI and H$_2$ gas mass, we can see these deviation on right panel of figure~\ref{fig:ks,all}, too.
+However, since we have higher H$_2$ emission in those regions compare to other regions of M31 these deviations are less than the ones in the middle panel.
 
 We took the similar approach for the extended Schmidt law.
-Figures~\ref{fig:es,all}--\ref{fig:es,regs,fuv,tot} show the results of the pixel by pixel fitting of this law.
+Figures~\ref{fig:es,all}-~\ref{fig:es,regs,halpha,tot} show the results of the pixel by pixel fitting of the extended Schmidt law.
 For the extended Schmidt law fitting, we plotted our results in 3D to illustrate the relationship between the surface density of the SFR, the gas mass surface density, and stellar mass density more clearly.
-In these series of plots, X-axis is the gas mass  surface density, either molecular gas (H$_2$), the atomic gas (HI) or the total gas, Y-axis is the SFR(TIR) or SFR(FUV + 24 $\mu$m), and Z-axis is the stellar mass surface density.
+In these series of plots, X-axis is the gas mass surface density, either molecular gas (H$_2$), the atomic gas (HI), or the total gas, Y-axis is the SFR(TIR) or SFR(FUV + 24 $\mu$m), and Z-axis is the stellar mass surface density.
 Shadows of our data on each surface are also plotted, to have a more clear picture of correlations between components.
-For a comparison, one can easily conclude that shadows on the X-Y surface is a reproduction of the K-S law.
+Shadows on the X-Y surface is the same as figure~\ref{fig:ks,all}.
 
@@
         \includegraphics[width=\textwidth]{es_tot_fuv_vs_h22.png}
-        \caption{SFR,FUV+24 M vs surface density of H$_2$}
+        \caption{SFR,FUV+24 $\mu$m vs surface density of H$_2$}
         \label{fig:es,all,fuv,h2}
@@
         \includegraphics[width=\textwidth]{es_tot_fuv_vs_hi2.png}
-        \caption{SFR,FUV+24 M vs surface density of HI}
+        \caption{SFR,FUV+24 $\mu$m vs surface density of HI}
         \label{fig:es,all,fuv,hi}
@@
         \includegraphics[width=\textwidth]{es_tot_fuv_vs_tot2.png}
-        \caption{SFR,FUV+24 M vs. surface density of total gas}
+        \caption{SFR,FUV+24 $\mu$m vs. surface density of total gas}
         \label{fig:es,all,fuv,tot}
@@
         \includegraphics[width=\textwidth]{es_tot_halpha_vs_h22.png}
-        \caption{SFR,H$\alpha$+24 M vs surface density of H$_2$}
+        \caption{SFR,H$\alpha$+24 $\mu$m vs surface density of H$_2$}
         \label{fig:es,all,halpha,h2}
@@
         \includegraphics[width=\textwidth]{es_tot_halpha_vs_hi2.png}
-        \caption{SFR,H$\alpha$+24 M vs surface density of HI}
+        \caption{SFR,H$\alpha$+24 $\mu$m vs surface density of HI}
         \label{fig:es,all,halpha,hi}
@@
         \includegraphics[width=\textwidth]{es_tot_halpha_vs_tot2.png}
-        \caption{SFR,H$\alpha$+24 M vs. surface density of total gas}
+        \caption{SFR,H$\alpha$+24 $\mu$m vs. surface density of total gas}
         \label{fig:es,all,halpha,tot}
@@
 As in Figure~\ref{fig:ks,all}, the analyses use different pixel sizes.
-Each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents a region of size $\sim$30~pc and each point in plots with surface density of HI or total gas mass represent a region of size $\sim$155~pc.}
+Each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents a region of size $\sim$30~pc and each point in plots with surface density of HI or total gas mass represent a region of size $\sim$155~pc.
+Solid lines shows the best fit, using the max value of the ranges in table~\ref{table:res}}
     \label{fig:es,all}
@@
 
-\begin{figure*}
-\centering
-\includegraphics[width=162mm]{halpha_vs_tot_3_reg_extendS_97perse.png}
-\caption{Fitting result from the SFR(H$\alpha$ + 24 $\mu$m) vs total gas.
+%\begin{figure*}
+%\centering
+%\includegraphics[width=162mm]{halpha_vs_tot_3_reg_extendS_97perse.png}
+%\caption{Fitting result from the SFR(H$\alpha$ + 24 $\mu$m) vs total gas.
 Same as Figure~\ref{fig:es,all,halpha,tot}, but in this figure we denote pixels from different regions in the galaxy by their colours.
 The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$ are shown in red, green and blue, respectively.}
-\label{fig:es,regs,fir,tot}
-\end{figure*}
+%\label{fig:es,regs,halpha,tot}
+%\end{figure*}
 
 \begin{table*}
-\caption{Fitting parameters of the SF laws from applying the Bayesian method}
+\caption{Fitting parameters of the SF laws from applying the Bayesian method, {\it N} is the power index of the K-S law; A is the intercept of the K-S law; \nprime is the gas power index in the extended Schmidt law; $\beta$ is the power index of the stellar component in the extended Schmidt law; and A$^\prime$ is the intercept of the extended Schmidt law}
 \label{table:res}
@@
 \hline\hline
-\multicolumn{1}{c}{\multirow{1}{*}{Region}} & SFR Tracer        & Gas Tracer & N    & A      & \nprime & $\beta$ & A$^\prime$ \\
+\multicolumn{1}{c}{\multirow{1}{*}{Region}} & SFR Tracer        & Gas Tracer & {\it N}    & A      & \nprime & $\beta$ & A$^\prime$ \\
 \hline
@@
  & TIR               & Total gas  & 0.82 & -9.84  & 0.51    & 0.56    & -10.40     \\
- & FUV + 24 M       & H$_2$ only & 1.16 & -9.36  &         &         &            \\
- & FUV + 24 M       & HI only    & 1.19 & -9.96  & 0.81    & 0.61    & -10.62     \\
- & FUV + 24 M       & Total gas  & 0.78 & -10.09 & 0.49    & 0.45    & -10.50     \\
- & H$\alpha$ + 24 M & H$_2$ only & 1.16 & -9.26  & 1.07    & 0.38    & -9.86      \\
- & H$\alpha$ + 24 M & HI only    & 0.54 & -9.61  & 0.53    & 0.76    & -10.69     \\
- & H$\alpha$ + 24 M & Total gas  & 0.54 & -9.82  & 0.37    & 0.59    & -10.55     \\
+ & FUV + 24 $\mu$m       & H$_2$ only & 1.16 & -9.36  & 1.15    & 0.25    & -9.74      \\
+ & FUV + 24 $\mu$m       & HI only    & 1.19 & -9.96  & 0.81    & 0.61    & -10.62     \\
+ & FUV + 24 $\mu$m       & Total gas  & 0.78 & -10.09 & 0.49    & 0.45    & -10.50     \\
+ & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.16 & -9.26  & 1.07    & 0.38    & -9.86      \\
+ & H$\alpha$ + 24 $\mu$m & HI only    & 0.54 & -9.61  & 0.53    & 0.76    & -10.69     \\
+ & H$\alpha$ + 24 $\mu$m & Total gas  & 0.54 & -9.82  & 0.37    & 0.59    & -10.55     \\
 \hline
@@
  & TIR               & Total gas  & 1.07 & -9.99  & 0.87    & 0.41    & -10.21     \\
- & FUV + 24 M       & H$_2$ only & 1.07 & -9.30  & 1.03    & 0.18    & -9.62      \\
- & FUV + 24 M       & HI only    & 1.29 & -10.06 & 1.02    & 0.45    & -10.34     \\
- & FUV + 24 M       & Total gas  & 0.89 & -10.12 & 0.81    & 0.21    & -10.18      \\
- & H$\alpha$ + 24 M & H$_2$ only & 1.14 & -9.23  & 1.03    & 0.41    & -6.47      \\
- & H$\alpha$ + 24 M & HI only    & 1.29 & -9.56  & 0.96    & 1.54    & -11.10     \\
- & H$\alpha$ + 24 M & Total gas  & 0.90 & -9.99  & 0.65    & 1.27    & -10.88    \\
+ & FUV + 24 $\mu$m       & H$_2$ only & 1.07 & -9.30  & 1.03    & 0.18    & -9.62      \\
+ & FUV + 24 $\mu$m       & HI only    & 1.29 & -10.06 & 1.02    & 0.45    & -10.34     \\
+ & FUV + 24 $\mu$m       & Total gas  & 0.89 & -10.12 & 0.81    & 0.21    & -10.18      \\
+ & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.14 & -9.23  & 1.03    & 0.41    & -6.47      \\
+ & H$\alpha$ + 24 $\mu$m & HI only    & 1.29 & -9.56  & 0.96    & 1.54    & -11.10     \\
+ & H$\alpha$ + 24 $\mu$m & Total gas  & 0.90 & -9.99  & 0.65    & 1.27    & -10.88    \\
 \hline
@@
  & TIR               & Total gas  & 0.79 & -9.77  & 0.50    & 0.58    & -10.38     \\
- & FUV + 24 M       & H$_2$ only & 1.21 & -9.28  & 1.15    & 0.31    & -9.82      \\
- & FUV + 24 M       & HI only    & 1.19 & -9.88  & 0.85    & 0.63    & -10.61     \\
- & FUV + 24 M       & Total gas  & 0.75 & -10.04 & 0.47    & 0.47    & -10.47     \\
- & H$\alpha$ + 24 M & H$_2$ only & 1.18 & -9.18  & 1.09    & 0.41    & -9.88      \\
- & H$\alpha$ + 24 M & HI only    & 0.56 & -9.49  & 0.72    & 0.81    & -10.67     \\
- & H$\alpha$ + 24 M & Total gas  & 0.52 & -9.71  & 0.40    & 0.61    & -10.47  \\
+ & FUV + 24 $\mu$m       & H$_2$ only & 1.21 & -9.28  & 1.15    & 0.31    & -9.82      \\
+ & FUV + 24 $\mu$m       & HI only    & 1.19 & -9.88  & 0.85    & 0.63    & -10.61     \\
+ & FUV + 24 $\mu$m       & Total gas  & 0.75 & -10.04 & 0.47    & 0.47    & -10.47     \\
+ & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.18 & -9.18  & 1.09    & 0.41    & -9.88      \\
+ & H$\alpha$ + 24 $\mu$m & HI only    & 0.56 & -9.49  & 0.72    & 0.81    & -10.67     \\
+ & H$\alpha$ + 24 $\mu$m & Total gas  & 0.52 & -9.71  & 0.40    & 0.61    & -10.47  \\
 \hline
@@
  & TIR               & Total gas  & 0.86 & -9.83  & 0.55    & 0.57    & -10.38     \\
- & FUV + 24 M       & H$_2$ only & 2.87 & -9.18  & 2.89    & 1.49    & -11.33     \\
- & FUV + 24 M       & HI only    & 1.27 & -9.95  & 0.85    & 0.64    & -10.63     \\
- & FUV + 24 M       & Total gas  & 0.80 & -10.08 & 0.52    & 0.48    & -10.49     \\
- & H$\alpha$ + 24 M & H$_2$ only & 2.86 & -9.05  & 3.12    & 1.30    & -10.86     \\
- & H$\alpha$ + 24 M & HI only    & 0.63 & -9.62  & 0.44    & 0.81    & -10.62     \\
- & H$\alpha$ + 24 M & Total gas  & 0.60 & -9.84  & 0.39    & 0.66    & -10.52     \\
+ & FUV + 24 $\mu$m       & H$_2$ only & 2.87 & -9.18  & 2.89    & 1.49    & -11.33     \\
+ & FUV + 24 $\mu$m       & HI only    & 1.27 & -9.95  & 0.85    & 0.64    & -10.63     \\
+ & FUV + 24 $\mu$m       & Total gas  & 0.80 & -10.08 & 0.52    & 0.48    & -10.49     \\
+ & H$\alpha$ + 24 $\mu$m & H$_2$ only & 2.86 & -9.05  & 3.12    & 1.30    & -10.86     \\
+ & H$\alpha$ + 24 $\mu$m & HI only    & 0.63 & -9.62  & 0.44    & 0.81    & -10.62     \\
+ & H$\alpha$ + 24 $\mu$m & Total gas  & 0.60 & -9.84  & 0.39    & 0.66    & -10.52     \\
  \hline
@@
 
-\subsection{Fitting method}
-\label{sec:fitting}
-
-\begin{figure*}
-\centering
-\includegraphics[width=164mm]{Results_for_all_regions.pdf}
-\caption{The result from fitting the Kennicutt-Schmidt law on data from whole galaxy using the pixel by pixel method. The points in the plots represent 
-different pixel sizes due to differences in the resolution of the H$_2$ and HI maps.
-Each point in the plots with the surface density of H$_2$ as a tracer of gas mass represents a region of size $\sim$30~pc and each point in the plots with surface density of HI or total gas mass represents a region of size $\sim$155~pc.
-} 
-\label{fig:ks,all}
-\end{figure*}
-
-Producing the SFR, gas mass and stellar mass maps, provides enough data to examine and compare the K-S law and the extended Schmidt law.
-We investigated the K-S law and the extended Schmidt law by using pixel by pixel method in whole galaxy as well as comparing the laws in three different regions of galaxy based on their distance from the centre of the galaxy.
-Our final results have two sets of different pixel sizes.
-That is because the H$_2$ gas mass map has better resolution and smaller pixel size of the HI gas mass map.
-Consequently, any plots with surface density of H$_2$ as a tracer of the gas mass will have more data points.
-
-We can re-write equations~\ref{equ:ks_org}~and~\ref{equ:es_org} in a logarithmic scale. Hence, we would have two linear equations, as:
-
-\begin{subequations}
-\begin{equation}
-\label{eq:sfr_law_ks_log}
-\log_{10} \eqsigmasfr = N~\log_{10} \eqsigmagas + A
-\end{equation}
-\begin{equation}
-\label{eq:sfr_law_es_log}
-\log_{10} \eqsigmasfr = \eqnprime~\log_{10} \eqsigmagas + \beta~\log_{10}\eqsigmastar  + A^\prime
-\end{equation}
-\end{subequations}
-where, N, $\eqnprime$, $\beta$, A, and A$^\prime$ are free parameters of fittings. Units in the equation above, are the same as the units in the equations ~\ref{equ:ks_org} and ~\ref{equ:es_org}.
-
-We found the free parameters by applying the hierarchical Bayesian linear regression method as described in \cite{Shetty13}.
-Shetty and his colleagues used a Bayesian linear regression approached to develop a new method to find the K-S law parameters, considering the measurement uncertainties as well as hierarchical data structure.
-For the K-S law's fitting parameters, we used a 'R' code provided by Shetty's group.
-For the extended Schmidt law, we expended the code in the way that instead of using simple linear regression, which is the case of the K-S law, it uses multiple linear regression.
-In this case, we were able to examine the effect of the stellar mass in the SFR as shown in equation ~\ref{eq:sfr_law_es_log}.
-
-Uncertainties on each observable quantities were measured by following the method described in \cite{Kennicutt07}.
-We used quadratic sum of variance of the local background of each luminosity map, from the original pixel size images, Poisson noise of images, and calibration uncertainties.
-Since we used pixel by pixel fitting, we do not consider the photometric uncertainties in our methods.
-%PBnew: not sure I see how pixel by pixel fitting means that you don't have to
-% worry about photometric uncertainty; maybe I am just not understanding this sentence
-%meeting: background uncertainties
-
-%PB20150428: I just realized that you first  discuss the 3 different regions a couple of paragraphs above this. Think this means that this paragraph should go after the first paragraph of section 4.1.
-We also test each laws on three different regions.
-The regions were chosen the same as regions introduced in \cite{Draine14}.
-They found that across the galaxy, with increasing distance from the centre of galaxy dust/H ratio declines monotonically.
-Considering that dust/H ratio has a direct relation to metallicity, they conclude that the metallicity of M31 changes in the same manner.
-As a result they introduced these three different regions as $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$.
-%PB20150428: not really clear from the text above why the 3 different regions are defined where they are.
-Need more detail about what Draine et al did.
-that made them think that 8 and 18 kpc were important, although I still think that (as in my comments below) the precise Md/Mh values are not what's important.
-Also, from the Draine paper I see that they are using elliptical annuli and not circular ones (which Ford et al did as well).
-You are doing the same, right?
-Need to describe this.
-%PBnew: don't think you really need the Md/MH values here, just giving the
-% region locations is enough. But this makes me think: what are the effects of
-% a changing Md/Mh on the derived SFR? Could they be driving (or hiding) differences in SFR laws between regions?
-
-% \begin{equation}
-% \label{eq:dust2gas_vs_R}
-% \frac{M_d}{M_H} \approx
-% \left\{ \begin{array}{l l}
-% 0.0280 \exp(-R/8.4\kpc)  & R< 8\kpc\\
-% 0.0165 \exp(-R/19\kpc)   & 8\kpc < R < 18\kpc\\
-% 0.0605 \exp(-R/8\kpc)    & 18\kpc < R \la 25\kpc ~~~,\\
-% \end{array}
-% \right.
-% \end{equation}
-
-%new metal materials
-%PB20150428: this is a good start but needs more detail and grammar work.
-(Some of this material might go better in the introduction.) List the other things besides metallicity that change with distance from the centre of the galaxy.
-Explain in more detail how the metallicity affects the components of the SFR law.
-If there is a correlation between metallicity and SFR (last sentence), what is the sense of the correlation, how big is it?
-Applying the SFR laws in these regions, provides a tool to consider the effect of the distance from the centre of the galaxy on SFR laws as well as the effect of the metallicity on them.
-
-The effect of the metallicity on the star formation laws are very complicated.
-Metallicity affect on each component of the star formation laws in different way.
-There are many studies on correlation of the metallicity with stellar mass, SFR, and the effect of the metallicity on the ISM \citep[e.g.,][]{Boissier03, Leroy08, Krumholz09, Mannucci10, Dib11a, Lilly13}.
-The scope of these studies is that metallicity has a critical role on the formation of the H$_2$ gas.
-Thus, there should be a correlation between metallicity and the SFR.
-
-\subsection{750 kpc}
-
 \begin{table*}
-\caption{Fitting parameters of the SF laws from applying the Bayesian method in regions around 750 Kpc}
+\caption{Similar to table~\ref{table:res} but here the fitting performed on the regions with size of 750~pc, and we only showed the results from SFR(FUV+24$\mu$m).}
 \label{table:res750}
-\begin{tabular}{ccccrccrr}
+\begin{tabular}{cccrccrr}
 \hline\hline
-\multicolumn{1}{c}{\multirow{1}{*}{Region}} & SFR Tracer        & Gas Tracer & N    & A      & \nprime & $\beta$ & A$^\prime$ \\
+\multicolumn{1}{c}{\multirow{1}{*}{Region}}  & Gas Tracer & {\it N} & A  & \nprime & $\beta$ & A$^\prime$ \\
 \hline
 \multicolumn{1}{c}{\multirow{3}{*}{Whole Galaxy}}
- & FUV + 24 M       & H$_2$ only & 0.65(2.93) & -8.27(3.34)  & 1.61(0.68)  & 0.61(0.38) & 5.29(-10.01)   \\
- & FUV + 24 M       & HI only    & 1.19 & -9.96  & 0.85    & 0.65    & -11.60     \\
- & FUV + 24 M       & Total gas  & 0.78 & -10.09 & 0.52    & 0.49    & -10.48     \\
+ & H$_2$ only & 0.32 & -9.91   & 0.27  & 0.41    &  -10.31  \\
+ & HI only    & 1.24 & -11.36  & 0.85  & 0.65    & -11.60     \\
+ & Total gas  & 0.89 & -9.94 & 0.52    & 0.49    & -10.48     \\
 \hline
 \multicolumn{1}{c}{\multirow{3}{*}{R$< 8\kpc$}}
- & FUV + 24 M       & H$_2$ only & 0.65(2.93) & -8.27(3.34) & 0.86(2.25)    & 0.36(0.60)    & -10.57(-0.71)      \\
- & FUV + 24 M       & HI only    & 1.73 & -10.87 & 1.03    & 1.42    & -10.52     \\
- & FUV + 24 M       & Total gas  & 0.88 & -9.94 & 1.45    & 0.83    & -9.11      \\
+ & H$_2$ only & 0.91 & -9.03  & 0.41   & 0.71   & -9.88      \\
+ & HI only    & 1.73 & -10.88 & 1.03    & 1.42    & -10.52     \\
+ & Total gas  & 0.88 & -9.94  & 1.45    & 0.83    & -9.11      \\
 \hline
 \multicolumn{1}{c}{\multirow{3}{*}{$8\kpc < $R $< 18\kpc$}}
- & FUV + 24 M       & H$_2$ only & 2.02 & -8.43  &    1.83     &  0.78       &   -9.16         \\
- & FUV + 24 M       & HI only    & 1.38 & -11.06  & 1.26    & 0.65    & -11.33     \\
- & FUV + 24 M       & Total gas  & 0.80 & -10.00 & 0.72    & 0.53    & -10.17     \\
+ & H$_2$ only & 0.36 & -9.66  & 0.28    &  0.53   & -10.15       \\
+ & HI only    & 1.38 & -11.06 & 1.26    & 0.65    & -11.33     \\
+ & Total gas  & 0.80 & -10.00 & 0.72    & 0.53    & -10.17     \\
 \hline
 \multicolumn{1}{c}{\multirow{3}{*}{$18\kpc <$ R $\la 25\kpc$}} 
- & FUV + 24 M       & H$_2$ only & 1.50 (4.30) & -11.00(-1.02)  &  5.35    & 4.10    & -10.22   \\
- & FUV + 24 M       & HI only    & 1.45 & -10.75  & 1.05    & 0.84    & -11.44     \\
- & FUV + 24 M       & Total gas  & 0.85 & -9.86 & 0.58    & 0.66    & -10.26     \\
+ & H$_2$ only & 0.34 & -9.47  &  0.34    & 0.75    & -9.72   \\
+ & HI only    & 1.46 & -10.73  & 1.05    & 0.84    & -11.44     \\
+ & Total gas  & 0.85 & -9.86 & 0.58    & 0.66    & -10.26     \\
  \hline
@@
 
-\subsection{Face On}
-
-\begin{table*}
-\caption{Fitting parameters of the SF laws from applying the Bayesian method Face on}
-\label{table:res}
-\begin{tabular}{ccccrccrr}
-\hline\hline
-\multicolumn{1}{c}{\multirow{1}{*}{Region}} & SFR Tracer        & Gas Tracer & N    & A      & \nprime & $\beta$ & A$^\prime$ \\
-\hline
-\multicolumn{1}{c}{\multirow{2}{*}{Whole Galaxy}}
- & TIR               & Total gas & 0.79 & -9.97  &  0.51   & 0.56   & -10.39   \\
- & FUV + 24 M       & Total gas  & 0.44 & -9.99 & 0.35    & 0.41    & -10.32     \\
-\hline
-\multicolumn{1}{c}{\multirow{2}{*}{R$< 8\kpc$}}
- & TIR               & Total gas    & .73 & -9.98 & 0.53    & 0.62    & -10.50     \\
- & FUV + 24 M       & Total gas  & 0.36 & -9.97 & 0.33    & 0.42    & -10.33      \\
-\hline
-\multicolumn{1}{c}{\multirow{2}{*}{$8\kpc < $R $< 18\kpc$}}
- & TIR               & Total gas    & 0.79 & -9.96  & 0.52    & 0.58    & -10.41     \\
- & FUV + 24 M       & Total gas  & 0.43 & -9.98 & 0.36    & 0.41    & -10.33     \\
-\hline
-\multicolumn{1}{c}{\multirow{2}{*}{$18\kpc <$ R $\la 25\kpc$}} 
- & TIR              & Total gas   & 0.83 & -9.96  & 0.52    & 0.54    & -10.34     \\
- & FUV + 24 M       & Total gas  & 0.49 & -9.99 & 0.38    & 0.40    & -10.29     \\
- \hline
-\end{tabular}
-\end{table*}
 %----------------------------------------------------------------------------------------
@@
 
-Table ~\ref{table:res} shows the results of the hierarchical Bayesian fit and their uncertainties for the whole galaxy and each different regions..
-Due to the similarity of our results for both SFR(TIR) and SFR(FUV+24$\mu$m), we only interpret the results from the SFR(FUV+24$\mu$m).
-Results from the SFR(H$\alpha$) fitting are going to be discussed in the Appendix ~\ref{app:halpha}.
-%PBnew: Use a few sentences to discuss similarity between SFR(TIR) and SFR(FUV+24$\mu$m), then go on to say you're only going to discuss one. /done
+Table~\ref{table:res} shows the results of the hierarchical Bayesian fitting for the whole galaxy and all three regions.
+Considering the data and uncertainties for each parameters, we are 95$\%$ confident that our fitting parameters are in given ranges in table~\ref{table:res}.
+Our results suggest changing SFR tracers doesn't have a significant impact to the determination of the power law index, while changing gas tracer is more important.
+Therefore, we only discuss the results from the SFR(FUV+24$\mu$m), and in~\ref{table:res750} we only showed results from this SFR map.
 
@@
 To make comparisons between our results easier, we averaged the power indices for their annuli which overlap with our three different regions so we could compare results in the same regions.
-\cite{Tabatabaei10} also applied the K-S law to M31 using the OLS fitting method, and have different results from \cite{Ford13}.
-
-Our results for the global case of the K-S law show that using total gas gives a sub-linear relation between the \sigmasfr and \sigmatotalgas.
+\cite{Tabatabaei10} also applied the K-S law to M31 using the OLS fitting method, and have some differences with results from \cite{Ford13}.
+\cite{Ford13} argued that the main reason for these differences is the cut-off they used to fit the data.
+
+our results for the whole-galaxy fit of the K-S law show that using total gas gives a sub-linear relation between \sigmasfr and \sigmatotalgas.
 While, for using the H$_{2}$ only gas or HI only gas we find the nearly super-linear relation.
@@
 The reason behind these differences is mostly because of the statical method we chose.
-The OLS fitting using \sigmatotalgas gives us the power index of $N=1.20\pm0.10$ which is in good agreement with \cite{Tabatabaei10} results.
+The OLS fitting using H$_{2}$ only gas gives us the power index of $N=0.57\pm1e-4$ which is close to \cite{Ford13} results but still different from the results from \cite{Tabatabaei10} which, could be the same reason \cite{Ford13} suggested for discrepancy between their results and results from \cite{Tabatabaei10}.
+However, results from the OLS fitting with \sigmatotalgas gives the same results as the fitting with the Bayesian method.% Another differences between our calculation with \cite{Ford13} and \cite{Tabatabaei10} is that both of them used the de-projected values for their calculation which, were calculated by multiplying all of their map by factor of $cos(i)$, inclination angle.
+We didn't include the calculation of effect of the inclination angle in our results.
+I checked and my reults doesn't changed
 
@@
 They also showed that the SFR and the molecular hydrogen have a linear relationship.
-Furthermore, \cite{Shetty13} used the same data as \cite{Bigiel08} and argued that using the hierarchical Bayesian fit leads to significant galaxy-by-galaxy variation between power indices and all of them are lower than \cite{Bigiel08}.
-%PBnew: Need to link material in this paragraph to our results.
-
-The sub-linear power index in the case of the total gas surface density suggests that the star formation efficiency (surface density of SFR per surface density of gas, SFE) is decreasing by increasing the total gas.
+\cite{Shetty13} used the same data as \cite{Bigiel08} and argued that using the hierarchical Bayesian fit leads to significant galaxy-by-galaxy variation between power indices and all of them are lower than \cite{Bigiel08}.
+Although some of our results in table`\ref{table: res} showed the nearly linear correlation between the SFR and the molecular hydrogen, we couldn't find any specific trend between power indices in the different regions.
+
+The sub-linear power index in the case of the total gas surface density suggests that the star formation efficiency is decreasing by increasing the total gas.
 Consequently, the depletion time increases by increasing the total gas.
@@
 
-% PBnew: in following paragraph, switch the order so that you compare with Ford
-% (observational) first, then Krumholz (theory). Is there theoretical work that 
-% predicts different dependencies? It's important to note the work that disagrees
-% with you as well as agrees.
-The results of the hierarchical Bayesian fitting on the regions with different distances from the centre of the galaxy give us similar values as the global case.
+The results of the hierarchical Bayesian fitting on the regions with different distances from the centre of the galaxy give us similar values as the fitting to the whole galaxy data.
 For all three regions, the K-S law using the total gas leads to sub-linear relation between the SFR and the surface density of the total gas.
-Likewise, for using the H$_{2}$ only gas or HI only gas, this relationship is either linear or nearly super-linear.
-These results agree with results from \cite{Krumholz09}.
+Likewise, for using the H$_{2}$ only gas or HI only gas, this relationship is either nearly linear or super-linear.
+These results agree with those from the models of \cite{Krumholz09}.
 They showed that for the regions with \sigmagas $\leq 100$ M$_{\odot}$pc$^{-2}$, \sigmasfr and $\Sigma_{H_2}$ have a nearly linear correlation.
 They also conclude that, at the intermediate total gas column density, (\sigmagas $\leq 100$ M$_{\odot}$pc$^{-2}$), \sigmasfr and \sigmagas have a linear or slightly sub-linear correlation which is similar to our results.
-The K-S law power index varies with the distance of the galaxy.
-Considering molecular gas, the power law index is increasing by going to further distances from the centre of the galaxy, which can be seen in the results from \cite{Ford13}, too.
-However, this growth does not happen for total gas or atomic gas cases.
-The increasing of the power index in this case may be an effect of the decreasing metallicity across the galaxy, which leads to have less SFE, or other physical properties of the galaxy such as stellar mass (see section ~\ref{sec:es_res}).
+However, they also showed the SFR has dependency on metallicity of the galaxy which we could not see any correlation between metallicity and the SFR in M31, (~\ref{fig:metal}).
+
+The K-S law power index varies with the distance of the centre of the galaxy.
+Similar to results from \cite{Ford13}, the power index increases by going to further distances from the centre of the galaxy considering molecular gas only.
+The power index using total gas or atomic gas does not show any particular correlation with distance.
+The increasing of the power index while using molecular cloud only may be an effect of the decreasing metallicity across the galaxy or other physical properties of the galaxy such as stellar mass (see section ~\ref{sec:es_res}).
 
@@
 The extended Schmidt law has been a recently proposed law \citep{Shi11}, which shows a tight correlation between the SFR and the total gas surface density and the surface density of the stellar mass.
-The results of the fitting the extended Schmidt law in a global case give us a sub-linear relation between the SFR and the density of stars.
-Results from the fitting the extended Schmidt law using the molecular gas only are %$\eqnprime = 1.09 \pm 0.01$ and $\beta = 0.25 \pm 0.004$ which
-follows the same trend of the extended Schmidt law in the global case,% $\eqnprime = 1.38 \pm 0.05$ and $\beta = 0.36\pm0.02$, 
-,which is the nearly super-linear correlation with \sigmagas and sub-linear correlation with \sigmastar.
-Although, the original results were average results of many type galaxies using the total gas surface density.
-Our results from the fitting the total gas surface density gives us a lower power index of the gas mass and a higher power index of the stellar mass.This relation suggests that, although increasing the total gas causes a decrease to the SFE but the existing stars will increase the SFE.
-
- The fitting results on the regions with different distances from the centre of the galaxy are more similar to the results from \cite{Shi11}, $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$.
-Taking the average $\beta$  from results of using molecular gas only gives us $\beta = 0.63$ which is in good agreement with \cite{Shi11} but, $\eqnprime$ is more than the original suggestion.
-In the local case, the same as global case power indices calculated using total gas surface density, are much smaller than the original suggestion of \cite{Shi11}.
-However, the final indices reported in the extended Schmidt law are an average over 12 different spiral galaxies, and our result is a lower limit for this law.
-%PBnew: why is our result a lower limit? 
- Another reason of differences between indices could be because of fitting method.
-Using the OLS fitting, one only will consider the SFR errors, nevertheless, the hierarchical Bayesian regression fitting considers uncertainties on all the parameters.
-Different treating with uncertainties would give us the different result.
-
- Thus, we can conclude that the stars affect on the SFR specially on the regions with lower amount of the gas.
-\cite{Kim13} using 3D numerical hydrodynamic simulations showed that in outer disk regions of the galaxy  where the total gas is dominated by HI gas,, the SFR have correlation with $\rho_{sd}^{0.5}$ where $\rho_{sd}$ is the mid-plane density of the stellar disk plus dark matter.
+Our results from fitting whole galaxy shows a sub-linear relation between \sigmasfr and \sigmastar.
+
+Using only atomic gas $\beta$ is in good agreement with the original suggestion of the extended Schmidt law $\eqnprime = 0.8 \pm 0.01$ and $\beta = 0.62\pm0.01$.
+However, $\beta$ is way smaller in other two gas tracers.
+Using total gas mass, we find $\eqnprime$ to be very close to $\beta$.
+This relation suggests that, although increasing the total gas causes a decrease to the SFE but the existing stars will increase the SFE.
+
+The fitting results on the three regions (see table ~\ref{table:res}) shows the same results as the fitting whole galaxy together.
+However, taking the average $\beta$ from results of using molecular gas only gives us $\beta = 0.66$ which is in good agreement with \cite{Shi11}, but $\eqnprime$ is almost twice of the original suggestion.
+However, the final indices reported in the extended Schmidt law are an average over 12 different spiral galaxies, and some of their results (e.g.
+NGC 4736, NGC 4726) have similar results to M31.
+
+Similar to the K-S law, the extended Schmidt law is sensitive to fitting method.
+Using the OLS fitting, one only will consider the SFR and stellar mass surface density errors, nevertheless, the hierarchical Bayesian regression fitting considers uncertainties on all the parameters.
+
+Thus we can conclude that the stars affect on the SFR in most cases this effect is more on the regions with lower amount of the gas.
+\cite{Kim13} using 3D numerical hydrodynamic simulations showed that in outer disk regions of the galaxy  where the total gas is dominated by HI gas, the SFR have correlation with $\rho_{sd}^{0.5}$ where $\rho_{sd}$ is the mid-plane density of the stellar disk plus dark matter.
 This is because of the fact that in outer regions of the disk the gravity from stars dominates.
-This results are in agree with our finding regarding that in outer regions of M31 the stellar surfaces density has more effect on the SFR.
-
-%PBnew: need to discuss metallicity here as well.
-%new metal material
-%%PB20150428: this paragraph neeeds a topic sentence
-\cite{Leroy08} showed that the SFR(FUV+24$\mu$m) does not change with changing metallicity.
-However, \cite{Boissier03} showed that the metallicity has inverse correlation with CO-H$_2$ conversion factor, which means that, using a constant conversion factor at high metallicity regions causes the overestimation of the molecular gas, and in low metallicity it leads to the underestimation of the H$_2$.
-Since \cite{Draine14} showed that metallicity in the centre of M31 is more than the outer disk regions, power index from the fitting the K-S law in the case of the molecular gas only or total gas should be steeper than what we measured.
-%PB20150428: rather than saying "the true PL index should be steeper" I think it's better to say "our estimate is an underestimate" or "our estimate is a lower limit".
-What does it mean for the PL index in the centre to be an underestimate?
-(ie if we corrected for this would it agree better with other regions/other studies, or worse, or what?)
-
-%%PB20150428: this paragraph neeeds a topic sentence
-\cite{Mannucci10} and \cite{Lilly13} using both observations and simulation results showed that metallicity depends on both the stellar mass and the SFR.
-They found that at any fixed stellar mass, metallicity and the SFR have an inverse correlation.
-Afterward, assuming the K-S law holds for their sample they found the correlation between, metallicity and the stellar mass, the gas mass and the SFR.
+This results are in agree with our finding regarding that in outer regions of M31 the stellar surfaces density has more effect on the SFR.% we cannot say that about Halpha map, but these regions are the ones, halpha map has more uncertaiintly on it!
+
+\section{Metallicity}
+
+It is well established that metallicity in the centre of M31 is more than the outer disk regions \citep[e.g.][]{Draine14}.
+Inverse correlation between metallicity and x-factor, which was described in section~\ref{sec:intro} gives the underestimation of the power indices from fitting the K-S law in the case of the molecular gas only and total gas.
+Thus power index of the K-S law is more closer to the original suggestion for the KS law ($\lt N \sim 1.56$).
+Moreover, results of \cite{Krumholz09} showed that a correlation between SFR and metallicity is strongly depends on amount of total gas in galaxies.
+We could not see any correlation between the SFR and metallicity in sub-kiloparces regions~\ref{fig:metal}.
+We estimated the SFR using \cite{Krumholz09} star formation rate for regions with size of $\sim$750~pc.
+We found that the SFR calculated using Krumholz law in average 45$\%$ different from the measured SFR.
+We used an average value of metallicity 1.65, clumping factor of 1.2 to get this results.
+A through calculation is needed to solve the issue of this controversy which is beyond scope of this paper.
+
+ \cite{Mannucci10} and \cite{Lilly13} assumed the K-S law holds for their sample of study and obtained a correlation between, metallicity and the stellar mass, the gas mass and the SFR.
 They found that increasing both the SFR and the stellar mass increases metallicity, but increasing the gas mass decreases metallicity (equation 9 in \citep{Mannucci10}).
- %%PB20150428: what does this mean for our work? Does it agree or disagree?
+However, by considering results from \cite{wong13} regarding the dependency of rate of HI-H$_2$ conversion to metallicity, \cite{Roychowdhury15} showed that the KS law is independent of metallicity in galaxies with HI as a dominant gas.
+As demonstrated in ~\ref{fig:metal}, we plot metallicity versus the SFR and the stellar mass, and could not find any correlation.
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{053\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{metal_vs_sfr.png}
+        \caption{SFR(FUV + 24 $\mu$m) vs matalicity surface density}
+        \label{fig:mtal_sfr}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{metal_vs_star.png}
+        \caption{Stellar mass vs metalicity surface density}
+        \label{fig:metal_star}}
+    \end{subfigure}
+    \caption{Right: the SFR(FUV + 24 $\mu$m) surface density versus metalicity surface density and left: Stellar mass vs metalicity surface density  shows the stellar mass.
+Each point shows a region with size of $\sim$750~pc.
+The regions with $R< 8\kpc$, $8\kpc < R < 18\kpc$, and $18\kpc < R \la 25\kpc$ are shown in red, green and blue, respectively.}
+    \label{fig:metal}
+\end{figure*}
 
@@
 \section{Summary}
-
-In order to test the effect of stars on the SFR in both global and local scales in M31, we have determined surface density of star formation rate, gas mass and the stellar mass of this galaxy.
+ We investigated the K-S law, the extended Schmidt law and the Krumholz law in both global and local scales in M31.
+We have determined surface density of star formation rate, gas mass and the stellar mass of this galaxy.
 We produced three SFR maps in M31.
@@
 We calculated the total SFR from FUV and 24 \um emission is 0.31$\pm$ 0.04 M$_{\odot}$yr$^{-1}$.
-
-We also produced the ISM map, using molecular gas only, atomic gas only and the total gas. %PBnew: following 2 sentences are too much detail for a summary. 
-For the molecular gas map, we assumed the CO-H$_2$ conversion factor is $2 \times 10^{20}$ (K km s$^{-1}$)$^{-1}$cm$^{-2}$. 
-In order to calculate the total gas, we combined the molecular gas and atomic gas and multiplied this combination by a factor of 1.36 for effect of the heavier elements.
-We have determined the stellar mass using 3.6 \um emission to create the stellar mass surface density.
-Then, we used the hierarchical Bayesian fitting to apply both the K-S law and the extended Schmidt law on M31.
-
-We confirmed \cite{Shi11} suggestions that the surface density of stars has impact on the SFR, and in regions with law gas surface brightness this impact is even more important.
-We also showed that, one of the reasons of adversity of results of power index of K-S law in M31 comes from differences in fitting method and error analysis.
-%PBnew: do you mean 'diversity' instead of 'adversity' ?
-%PBnew: description of your results should be more extensive: 2 sentences is not enough.
+We also produced the ISM map, using molecular gas only, atomic gas only and the total gas.
+
+1) We found the power index of the K-S law is mostly depended on which gas we use as a tracer of the gas mass in galaxy. And it is mostly independent of the SFR tracer.
+
+2) We showed that, using different fitting methods gives us different results
+
+3) Our results showed although there is a correlation between \sigmasfr and \sigmagas, it is not the same in all regions in M31.
+
+4) We confirmed \cite{Shi11} suggestions that the surface density of stars has impact on the SFR, and in regions with law gas surface brightness this impact is even more important.
+
+5) We could not find any relation between SFR and metallicity.
 
@@
 %\section*{Acknowledgement}
-The authors thank Dr. R. Shetty for giving us his hierarchical Bayesian fitting code, and Dr. D. Kruijssen for his idea about 3D plots.
+The authors thank R.
+Shetty for giving us his hierarchical Bayesian fitting code, D.
+Kruijssen for his idea about 3D plots, L.
+Chemin for giving us HI map, K.
+Gordon for his latest version of the Mips 24 \um and 70 \um maps, and M.
+Smith for \Herschel data.
+We also want to thank B.T Draine, P.
+Massey, K.
+Sandstorm, M.
+Azimlu, and G.
+Ford for their useful suggestions.
 The authors acknowledge research support from the Natural Sciences and Engineering Research Council of Canada and from the Academic Development Fund of the University of Western Ontario. 
@@
 %----------------------------------------------------------------------------------------
-%PBnew: something is wrong with the references here: should have 'et al.' instead of 'e.a.'
+
 \bibliography{ref.bib}
@@
 
-As mentioned in Section~\ref{sec:vislight}, we used the H$\alpha$ data from the Nearby Galaxies Survey \citep{Massey07} to create the SFR map.
-These data are publicly available in H$\alpha$ and R band in 10 overlapping fields across the disk of M31.
+As mentioned in Section~\ref{sec:data}, we used the H$\alpha$ data from the Nearby Galaxies Survey \citep{Massey07} to create one of our SFR maps.
+These data cover 10 overlapping fields across the disk of M31 in broad and narrow bands in 10 overlapping fields and were observed between August 2000 and September 2002; we obtained them  from the NOAO science archive.
 Making a spatially resolved SFR map of M31 using H$\alpha$ emission requires removal of background and stellar emission in each field, masking out foreground stars and saturated regions, creating a mosaic of H$\alpha$ continuum-subtracted map, and finally correcting for the flux contribution to the \halpha filter from the [N II] 6583~\AA line.
@@
 On the other hand, there is no image of the further area in the sky to measure the sky contribution from there, which makes the removal of background emission even harder.
-The only choice were left here is to subtract the local background for each region% which gave us an image with non-smooth background.
-. However, subtracting a local background of images will result in a non-smooth background in final mosaic image.
+The only choice were left here is to subtract the local background for each region.
+However, subtracting a local background of images will result in a non-smooth background in final mosaic image.
 
@@
 At the end, we masked out all the foreground and saturated regions which include a $10\arcmin \times 10\arcmin$ region in the centre of the galaxy.
-In total, nearly 50$\%$ of the pixels in the \halpha map were masked out.
-To account for the flux contribution of the [N II] emission we used the flux ratio of the [NII]$/$\halpha $= 0.54$ from \cite{Kennicutt08}.
-
-\subsubsection{\halpha plus 24 M Star Formation Rate}
-\label{sec:sfr_halpha}
-
-The SFR can be calculated using combination of \halpha and \Spitzer  24 M maps.
-\halpha emission of galaxies is dominated by light emitted from young and massive stars.
-Star formation time scaled traced by this emission is $\sim 6-10$ Myr \citep[e.g.,][]{Kennicutt09, Calzetti13}.
-Therefore, \halpha alone could be used to calibrate the SFR \citep[e.g.,][]{Osterbrock06, Kennicutt09}.
-However, \halpha emission is very sensitive to dust extinction, too.
-Therefore, the combination of the \halpha and 24 M of is considerable choice for calculating the SFR.
-wW used a calibration introduced by \cite{Kennicutt09} to measure the SFR:
-\begin{equation}
-\label{equ: halphaplus24_g}
-SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.020L(24\mu m)]
-\end{equation}
-where L(H${\alpha}$)$_{obs}$ is the observed \halpha luminosity without correction for internal dust attenuation, given in the unit of erg~s$^{-1}$.
-L(24$\mu$m) is the $24\mu$m IR luminosity in erg~s$^{-1}$, and SFR is in M$_{\odot}$yr$^{-1}$.
-It was indicated that the formulation above can only be used at the global situation i.e., the total SFR.
-
-\cite{Calzetti07} introduced a new calibration using the same band passes in a case of local regions (Figure~\ref{fig:sfr_halpha}):
-\begin{equation}
-\label{equ: halphaplus24_l}
-SFR = 5.5 \times 10^{-42}[L(H{\alpha})_{obs} + 0.033L(24\mu m)]
-\end{equation}
-the units here are the same as equation~\ref{equ: halphaplus24_g}.
-Equation~\ref{equ: halphaplus24_l} is useful for regions less than $\sim 1$ kpc.
-According to  \cite{Calzetti07} calibration constant in equations ~\ref{equ: halphaplus24_g} and ~\ref{equ: halphaplus24_l} can be different by changing an IMF.
-Changes in the IMF mostly affect on calibration based on \halpha luminosity, mostly because a significant amount of the ionizing photons comes from the stars more massive than $\sim 20$M$\sun$.
-Changing the calibration constant would change the total SFR by a factor of 1.5.
-In this paper, we used \cite{Kroupa01} IMF with an upper mass limit of 100M$\sun$.
-Total SFR calculated from equation~\ref{equ: halphaplus24_g} is $0.35 \pm 0.01$~M$\sun$~yr$^{-1}$, which is in good agreement with previous studies.
+To account for the flux contribution of the [N II] emission we used the flux ratio of the [NII]$/$\halpha $= 0.54$ from \cite{Kennicutt08}, and subtracted it from \halpha map.
+We created the final mosaic image~\ref{fig:halpha} using the Montage program \citep{Berriman08}.
 
@@
 In order to investigate the SFR laws, we used the same method of the fitting as Section~\ref{sec:fitting}.
-The fitting results using SFR(\halpha $+$ 24 \um ) are totally different from the other two SFR tracers.
-The main reason for this difference could is mainly because of the extreme amount of the nan values in the map especially lost of the data in the centre of the galaxy.\halpha data does not have a smooth background.
-Also the centre of galaxy in this data is diffused, so we do not have any data from the centre of M31.
-Since it was the only available \halpha data from M31, We used this data anyway.
+The fitting results using SFR(\halpha $+$ 24 \um ) are more or less the same as the other two SFR tracers.
+The main reason for this difference could is mainly because of lost data in the centre of the galaxy.\halpha data does not have a smooth background.
+Thus we did not include the SFR(\halpha $+$ 24 \um ) in our final analysis.
 

### 2015-07-20 draft3.tex
final1

@@
 To create the surface density map, we divided the value of each pixel by its area in pc$^2$.
-We investigated the K-S law and the extended Schmidt law by using pixel by pixel method in the entire galaxy as well as comparing the laws in three elliptical regions, assuming the position angle 38$\degr$, inclination of 77$\degr$ for M31 with distance from the centre of the galaxy the same as the ones described in section~\ref{sec: metal}.
+We investigated the K-S law and the extended Schmidt law by using pixel by pixel method in the entire galaxy as well as comparing the laws in three elliptical regions, assuming the position angle 38$\degr$, inclination of 77$\degr$ for M31 with distance from the centre of the galaxy the same as the ones described in section~\ref{sec:metal}.
 As mentioned in section~\ref{sec:data}, since the H$_2$ gas mass map has higher angular resolution and smaller pixel size than the HI gas mass map, our final results have two sets of different pixel sizes.
@@
 We took the similar approach for the extended Schmidt law.
-Figures~\ref{fig:es,all}-~\ref{fig:es,regs,halpha,tot} show the results of the pixel by pixel fitting of the extended Schmidt law.
+Figures~\ref{fig:es,all}-~\ref{fig:es,regs,fuv,tot} show the results of the pixel by pixel fitting of the extended Schmidt law.
 For the extended Schmidt law fitting, we plotted our results in 3D to illustrate the relationship between the surface density of the SFR, the gas mass surface density, and stellar mass density more clearly.
@@
 \hline
-\multicolumn{1}{c}{\multirow{9}{*}{Whole Galaxy}} & TIR               & H$_2$ only & 1.05 & -8.98  & 0.97    & 0.35    & -9.53      \\
- & TIR               & HI only    & 1.19 & -9.69  & 0.79    & 0.75    & -10.56     \\
- & TIR               & Total gas  & 0.82 & -9.84  & 0.51    & 0.56    & -10.40     \\
- & FUV + 24 $\mu$m       & H$_2$ only & 1.16 & -9.36  & 1.15    & 0.25    & -9.74      \\
- & FUV + 24 $\mu$m       & HI only    & 1.19 & -9.96  & 0.81    & 0.61    & -10.62     \\
- & FUV + 24 $\mu$m       & Total gas  & 0.78 & -10.09 & 0.49    & 0.45    & -10.50     \\
- & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.16 & -9.26  & 1.07    & 0.38    & -9.86      \\
- & H$\alpha$ + 24 $\mu$m & HI only    & 0.54 & -9.61  & 0.53    & 0.76    & -10.69     \\
- & H$\alpha$ + 24 $\mu$m & Total gas  & 0.54 & -9.82  & 0.37    & 0.59    & -10.55     \\
-\hline
-\multicolumn{1}{c}{\multirow{9}{*}{R$< 8\kpc$}} & TIR               & H$_2$ only & 1.01 & -8.95  & 0.92    & 0.36    & -6.66      \\
- & TIR               & HI only    & 1.63 & -9.93  & 1.14    & 0.65    & -10.38     \\
- & TIR               & Total gas  & 1.07 & -9.99  & 0.87    & 0.41    & -10.21     \\
- & FUV + 24 $\mu$m       & H$_2$ only & 1.07 & -9.30  & 1.03    & 0.18    & -9.62      \\
- & FUV + 24 $\mu$m       & HI only    & 1.29 & -10.06 & 1.02    & 0.45    & -10.34     \\
- & FUV + 24 $\mu$m       & Total gas  & 0.89 & -10.12 & 0.81    & 0.21    & -10.18      \\
- & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.14 & -9.23  & 1.03    & 0.41    & -6.47      \\
- & H$\alpha$ + 24 $\mu$m & HI only    & 1.29 & -9.56  & 0.96    & 1.54    & -11.10     \\
- & H$\alpha$ + 24 $\mu$m & Total gas  & 0.90 & -9.99  & 0.65    & 1.27    & -10.88    \\
-\hline
-\multicolumn{1}{c}{\multirow{9}{*}{$8\kpc < $R $< 18\kpc$}} & TIR               & H$_2$ only & 1.08 & -8.90  & 1.00    & 0.40    & -9.59      \\
- & TIR               & HI only    & 1.16 & -9.58  & 0.84    & 0.77    & -10.53     \\
- & TIR               & Total gas  & 0.79 & -9.77  & 0.50    & 0.58    & -10.38     \\
- & FUV + 24 $\mu$m       & H$_2$ only & 1.21 & -9.28  & 1.15    & 0.31    & -9.82      \\
- & FUV + 24 $\mu$m       & HI only    & 1.19 & -9.88  & 0.85    & 0.63    & -10.61     \\
- & FUV + 24 $\mu$m       & Total gas  & 0.75 & -10.04 & 0.47    & 0.47    & -10.47     \\
- & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.18 & -9.18  & 1.09    & 0.41    & -9.88      \\
- & H$\alpha$ + 24 $\mu$m & HI only    & 0.56 & -9.49  & 0.72    & 0.81    & -10.67     \\
- & H$\alpha$ + 24 $\mu$m & Total gas  & 0.52 & -9.71  & 0.40    & 0.61    & -10.47  \\
-\hline
-\multicolumn{1}{c}{\multirow{9}{*}{$18\kpc <$ R $\la 25\kpc$}} & TIR               & H$_2$ only & 2.08 & -8.76  & 1.81    & 1.32    & -5.82      \\
- & TIR               & HI only    & 1.30 & -9.68  & 0.83    & 0.78    & -10.54     \\
- & TIR               & Total gas  & 0.86 & -9.83  & 0.55    & 0.57    & -10.38     \\
- & FUV + 24 $\mu$m       & H$_2$ only & 2.87 & -9.18  & 2.89    & 1.49    & -11.33     \\
- & FUV + 24 $\mu$m       & HI only    & 1.27 & -9.95  & 0.85    & 0.64    & -10.63     \\
- & FUV + 24 $\mu$m       & Total gas  & 0.80 & -10.08 & 0.52    & 0.48    & -10.49     \\
- & H$\alpha$ + 24 $\mu$m & H$_2$ only & 2.86 & -9.05  & 3.12    & 1.30    & -10.86     \\
- & H$\alpha$ + 24 $\mu$m & HI only    & 0.63 & -9.62  & 0.44    & 0.81    & -10.62     \\
- & H$\alpha$ + 24 $\mu$m & Total gas  & 0.60 & -9.84  & 0.39    & 0.66    & -10.52     \\
+\multicolumn{1}{c}{\multirow{9}{*}{Whole Galaxy}} & TIR  & H$_2$ only & 1.02 - 1.05 & -8.99 - -8.98  & 0.93 - 0.97    & 0.33 - 0.35    & -9.56 - -9.53  \\
+ & TIR               & HI only    & 1.13 - 1.19 & -9.71 - -9.69  & 0.76 - 0.79    & 0.74 - 0.75    & -10.58 - -10.56     \\
+ & TIR               & Total gas  & 0.80 - 0.82 & -9.86 - -9.84  & 0.50 - 0.51    & 0.54 - 0.56    & -10.42 - -10.40     \\
+ & FUV + 24 $\mu$m       & H$_2$ only & 1.11 - 1.16 & -9.37-9.36  & 1.06 - 1.15   & 0.23 - 0.25    & -9.78 - -9.74      \\
+ & FUV + 24 $\mu$m       & HI only    & 1.16 - 1.19 & -9.97 - -9.96  & 0.78 - 0.81    & 0.59 - 0.61   & -10.64 - -10.62     \\
+ & FUV + 24 $\mu$m       & Total gas  & 0.76 - 0.78 & -10.10 - -10.09 & 0.47 - 0.49    & 0.44 - 0.45    & -10.52 - -10.50     \\
+ & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.11 - 1.16 & -9.27- -9.26  & 1.02 - 1.07    & 0.36 - 0.38    & -9.89 - -9.86      \\
+ & H$\alpha$ + 24 $\mu$m & HI only    & 0.46 - 0.54 & -9.64 - -9.61  & 048 - 0.53    & 0.72 - 0.76    & -10.75 -10.69     \\
+ & H$\alpha$ + 24 $\mu$m & Total gas  & 0.50 - 0.54 & -9.85 - -9.82  & 0.34 - 0.37    & 0.55 - 0.59    & -10.61 - -10.55     \\
+\hline
+\multicolumn{1}{c}{\multirow{9}{*}{R$< 8\kpc$}} & TIR & H$_2$ only & 0.94-1.01 & -8.97 - -8.95  & 0.87 - 0.92    & 0.30 - 0.36    & -9.49 - -6.66 \\
+ & TIR               & HI only    & 1.31 - 1.63 & -10.00 - -9.93  & 0.84 - 1.14    & 0.48 - 0.65    & -10.55 - -10.38     \\
+ & TIR               & Total gas  & 0.92 - 1.07 & -10.10 - -9.99  & 0.80 - 0.87    & 0.24 - 0.41    & -10.37 - -10.21     \\
+ & FUV + 24 $\mu$m       & H$_2$ only & 1.00 - 1.07 & -9.32 - -9.30  & 0.95 - 1.03  & 0.15 - 0.18  & -9.68 - -9.62      \\
+ & FUV + 24 $\mu$m       & HI only    & 1.11 - 1.29 & -10.10 - -10.06 & 0.78 - 1.02    & 0.29 - 0.45   & -10.49 - -10.34     \\
+ & FUV + 24 $\mu$m       & Total gas  & 0.78 - 0.89 &-10.20 - -10.12 & 0.66 - 0.81    & 0.05 - 0.21    & -10.32 - -10.18      \\
+ & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.06 - 1.14 & -9.25 - -9.23  & 0.97 - 1.03    & 0.36 - 0.41    & -9.86 - -6.47      \\
+ & H$\alpha$ + 24 $\mu$m & HI only    & 0.31 - 1.29 & -9.10 - -9.56  & 0.21 - 0.96    & 0.90 - 1.54    & -12.01 - -11.10     \\
+ & H$\alpha$ + 24 $\mu$m & Total gas  & 0.49 - 0.90 & -10.30 - -9.99  & 0.28 - 0.65    & 0.62 - 1.27    & -11.71 - -10.88    \\
+\hline
+\multicolumn{1}{c}{\multirow{9}{*}{$8\kpc < $R $< 18\kpc$}} & TIR & H$_2$ only & 1.04 - 1.08 & -8.91- -8.90 & 0.95 - 1.00 & 0.38 - 0.40 & -9.92 - -9.59 \\
+ & TIR               & HI only    & 0.97 - 1.16 & -9.64 - -9.58  & 0.72 - 0.84    & 0.72 - 0.77    & -10.61 - -10.53     \\
+ & TIR               & Total gas  & 0.71 - 0.79 & -9.83 - -9.77  & 0.45 - 0.50    & 0.53 - 0.58    & -10.45 - -10.38     \\
+ & FUV + 24 $\mu$m       & H$_2$ only & 1.16 - 1.21 & -9.30 - -9.28  & 1.10 - 1.15    & 0.28 - 0.31    & -9.86 - -9.82      \\
+ & FUV + 24 $\mu$m       & HI only    & 1.07 - 1.19 & -9.92 - -9.88  & 0.76 - 0.85    & 0.56 - 0.63    & -10.68 - -10.61     \\
+ & FUV + 24 $\mu$m       & Total gas  & 0.69 - 0.75 & -10.10 - -10.04 & 0.42 - 0.47    & 0.42 - 0.47    & -10.55 - -10.47     \\
+ & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.12 - 1.18 & -9.19 - -9.18  & 1.04 - 1.09    & 0.39 - 0.41    & -9.93 - -9.88      \\
+ & H$\alpha$ + 24 $\mu$m & HI only    & 0.33 - 0.56 & -9.95 - -9.49  & 0.57 - 0.72    & 0.70 - 0.81    & -10.85 -10.67     \\
+ & H$\alpha$ + 24 $\mu$m & Total gas  & 0.42 - 0.52 & -9.79 - -9.71  & 0.32 - 0.40    & 0.51 - 0.61    & -10.63 - -10.47  \\
+\hline
+\multicolumn{1}{c}{\multirow{9}{*}{$18\kpc <$ R $\la 25\kpc$}} & TIR & H$_2$ only & 1.42 - 2.08 &-8.87- -8.76 & 1.25 - 1.81& 1.20 - 1.32& -10.72 - -5.82 \\
+ & TIR               & HI only    & 1.11 - 1.30 & -9.74 - -9.68  & 0.71 - 0.83    & 0.72 - 0.78    & -10.63 - -10.54     \\
+ & TIR               & Total gas  & 0.79 - 0.86 &  -9.88 - -9.83  & 0.50 - 0.55    & 0.51 - 0.57    & -10.45 - -10.38     \\
+ & FUV + 24 $\mu$m       & H$_2$ only & 1.93 - 2.87 & -9.32 - -9.18  & 1.60 - 2.89    & 1.26 - 1.49& -11.72 - -11.33     \\
+ & FUV + 24 $\mu$m       & HI only    & 1.15 - 1.27 & -9.99 - -9.95  & 0.75 - 0.85    & 0.59 - 0.64    & -10.70 - -10.63     \\
+ & FUV + 24 $\mu$m       & Total gas  & 0.74 - 0.80 & -10.10 - -10.08 & 0.46 - 0.52    & 0.42 - 0.48    & -10.56 - -10.49     \\
+ & H$\alpha$ + 24 $\mu$m & H$_2$ only & 1.76 - 2.86 & -9.20- -9.05  & 1.55 - 3.12    & 1.06 - 1.30    & -11.33 - -10.86     \\
+ & H$\alpha$ + 24 $\mu$m & HI only    & 0.36 - 0.63 &  -9.71 - -9.62  & 0.23 - 0.44    & 0.69 - 0.81    & -10.80 - -10.62     \\
+ & H$\alpha$ + 24 $\mu$m & Total gas  & 0.49 - 0.60 & -9.39 - -9.84  & 0.28 - 0.39    & 0.53 - 0.66    & -10.70 - -10.52     \\
  \hline
@@
 \multicolumn{1}{c}{\multirow{3}{*}{Whole Galaxy}}
- & H$_2$ only & 0.32 & -9.91   & 0.27  & 0.41    &  -10.31  \\
- & HI only    & 1.24 & -11.36  & 0.85  & 0.65    & -11.60     \\
- & Total gas  & 0.89 & -9.94 & 0.52    & 0.49    & -10.48     \\
+ & H$_2$ only & 0.26 - 0.32 & -10.00 - -9.91   & 0.22 - 0.27  & 0.27 - 0.41    & -10.52 - -10.31  \\
+ & HI only    & 1.08 - 1.24 & -11.60 - -11.36  & 0.73 - 0.85  & 0.58 - 0.65    & -11.78 - -11.60     \\
+ & Total gas  & 0.73 - 0.89 & -10.10 - -9.94 & 0.44 - 0.52    & 0.41 - 0.49    & -10.57 - -10.48     \\
 \hline
 \multicolumn{1}{c}{\multirow{3}{*}{R$< 8\kpc$}}
- & H$_2$ only & 0.91 & -9.03  & 0.41   & 0.71   & -9.88      \\
- & HI only    & 1.73 & -10.88 & 1.03    & 1.42    & -10.52     \\
- & Total gas  & 0.88 & -9.94  & 1.45    & 0.83    & -9.11      \\
+ & H$_2$ only & 0.10 - 0.91 & -11.19 - -9.03  & 0.20 - 0.41   & 0.24 - 0.71   & -9.73 - -9.88      \\
+ & HI only    & 0.74 - 1.73 & -12.04 - -10.88 & 0.11 - 1.04    & 0.64 - 1.40    & -11.32 - -10.54     \\
+ & Total gas  & 0.51 - 0.88 & -10.20 - -9.94  & 0.91 - 1.47    & 0.24 - 0.91    & -9.71 - -9.10      \\%????
 \hline
 \multicolumn{1}{c}{\multirow{3}{*}{$8\kpc < $R $< 18\kpc$}}
- & H$_2$ only & 0.36 & -9.66  & 0.28    &  0.53   & -10.15       \\
- & HI only    & 1.38 & -11.06 & 1.26    & 0.65    & -11.33     \\
- & Total gas  & 0.80 & -10.00 & 0.72    & 0.53    & -10.17     \\
+ & H$_2$ only & 0.17 - 0.36 & -10.00 - -9.66  & 0.13 - 0.28    &  0.21 - 0.53   & -10.70 - -10.15       \\
+ & HI only    & 0.88 - 1.38 & -11.80 - -11.06 & 0.66 - 1.26    & 0.16 - 0.65    & -12.14 - -11.33     \\
+ & Total gas  & 0.55 - 0.80 & -10.20 - -10.00 & 0.41 - 0.72    & 0.08 - 0.53    & -10.72 - -10.17     \\
 \hline
 \multicolumn{1}{c}{\multirow{3}{*}{$18\kpc <$ R $\la 25\kpc$}} 
- & H$_2$ only & 0.34 & -9.47  &  0.34    & 0.75    & -9.72   \\
- & HI only    & 1.46 & -10.73  & 1.05    & 0.84    & -11.44     \\
- & Total gas  & 0.85 & -9.86 & 0.58    & 0.66    & -10.26     \\
+ & H$_2$ only & 0.11 - 0.34 & -9.95 - -9.47  & 0.19 - 0.34    & 0.24 - 0.75    & -10.64 - -9.72   \\
+ & HI only    & 0.76 - 1.46 & -11.80 - -10.73  & 0.60 - 1.05    & 0.55 - 0.84    & -12.02 -11.44     \\
+ & Total gas  & 0.52 - 0.85 & -10.10 - -9.86 & 0.28 - 0.58    & 0.30 - 0.65    & -10.75 - -10.26     \\
  \hline
@@
 We didn't include the calculation of effect of the inclination angle in our results.
-I checked and my reults doesn't changed
+%%%% Sahar:I checked and my reults doesn't changed
 
@@
 \cite{Shetty13} used the same data as \cite{Bigiel08} and argued that using the hierarchical Bayesian fit leads to significant galaxy-by-galaxy variation between power indices and all of them are lower than \cite{Bigiel08}.
-Although some of our results in table`\ref{table: res} showed the nearly linear correlation between the SFR and the molecular hydrogen, we couldn't find any specific trend between power indices in the different regions.
+Although some of our results in table`\ref{table:res} showed the nearly linear correlation between the SFR and the molecular hydrogen, we couldn't find any specific trend between power indices in the different regions.
 
@@
 Inverse correlation between metallicity and x-factor, which was described in section~\ref{sec:intro} gives the underestimation of the power indices from fitting the K-S law in the case of the molecular gas only and total gas.
-Thus power index of the K-S law is more closer to the original suggestion for the KS law ($\lt N \sim 1.56$).
-Moreover, results of \cite{Krumholz09} showed that a correlation between SFR and metallicity is strongly depends on amount of total gas in galaxies.
-We could not see any correlation between the SFR and metallicity in sub-kiloparces regions~\ref{fig:metal}.
-We estimated the SFR using \cite{Krumholz09} star formation rate for regions with size of $\sim$750~pc.
-We found that the SFR calculated using Krumholz law in average 45$\%$ different from the measured SFR.
-We used an average value of metallicity 1.65, clumping factor of 1.2 to get this results.
-A through calculation is needed to solve the issue of this controversy which is beyond scope of this paper.
-
- \cite{Mannucci10} and \cite{Lilly13} assumed the K-S law holds for their sample of study and obtained a correlation between, metallicity and the stellar mass, the gas mass and the SFR.
+Thus the calculated power index of the K-S law is more than we showed in table~\ref{table:res}.
+Another correlation between components of the SFR laws and metalicity was introduced by \cite{Krumholz09}.
+They found a new SFR law based on a correlation between SFR and metalicity, and suggested that this correlation is strongly depends on amount of total gas in galaxies.
+We estimated the SFR using \cite{Krumholz09} SFR laws for regions with size of $\sim$750~pc.
+Using the mid value of metallicity, 1.65, and clumping factor of 1.2, We found that the SFR calculated using Krumholz law in average 45$\%$ different from the measured SFR(FUV + 24 $\mu$m) in this work.
+%Another way to talk about this law is to show the equation and introduced all the factors and adding that we used it and found this result!
+.
+
+In more recent studies, \cite{Mannucci10} and \cite{Lilly13} assumed the K-S law holds for their sample of local and high-redshift galaxies and obtained a correlation between, metallicity and the stellar mass, the gas mass and the SFR.
 They found that increasing both the SFR and the stellar mass increases metallicity, but increasing the gas mass decreases metallicity (equation 9 in \citep{Mannucci10}).
 However, by considering results from \cite{wong13} regarding the dependency of rate of HI-H$_2$ conversion to metallicity, \cite{Roychowdhury15} showed that the KS law is independent of metallicity in galaxies with HI as a dominant gas.
-As demonstrated in ~\ref{fig:metal}, we plot metallicity versus the SFR and the stellar mass, and could not find any correlation.
+As demonstrated in ~\ref{fig:metal}, we plot metallicity versus the SFR(FUV + 24 $\mu$m) and the stellar mass, and could not find any correlation.
+We also calculated the Pearson correlation coefficient between metallicity and the SFR, and metallicity and the stellar mass to be 0.07 and 0.04, which confirmed that there is no correlation between metallicity and neither the SFR  nor the stellar mass.
+Although, we could not find any direct correlation between the SFR and metallicity, we should note that effect of the metallicity on SF laws is ambiguous and more high resolution data is needed to complete this puzzle.
 
@@
 \centering
-    \begin{subfigure}[b]{053\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{metal_vs_sfr.png}
-        \caption{SFR(FUV + 24 $\mu$m) vs matalicity surface density}
-        \label{fig:mtal_sfr}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{metal_vs_star.png}
-        \caption{Stellar mass vs metalicity surface density}
-        \label{fig:metal_star}}
-    \end{subfigure}
+\includegraphics[width=162mm]{metal12.png}
     \caption{Right: the SFR(FUV + 24 $\mu$m) surface density versus metalicity surface density and left: Stellar mass vs metalicity surface density  shows the stellar mass.
@@
 We also produced the ISM map, using molecular gas only, atomic gas only and the total gas.
-
+\newline
 1) We found the power index of the K-S law is mostly depended on which gas we use as a tracer of the gas mass in galaxy. And it is mostly independent of the SFR tracer.
-
+\newline
 2) We showed that, using different fitting methods gives us different results
-
+\newline
 3) Our results showed although there is a correlation between \sigmasfr and \sigmagas, it is not the same in all regions in M31. 
-
+\newline
 4) We confirmed \cite{Shi11} suggestions that the surface density of stars has impact on the SFR, and in regions with law gas surface brightness this impact is even more important. 
-
-5) We could not find any relation between SFR and metallicity.
+\newline
+5) We performed statistical tests to find any correlation between the SFR, or the stellar mass surface density and metallicity, and we could not find any.
+\newline
+Obtaining images with higher resolution and maps with better coverage of this galaxy will enable us to continue these studies in finer details and will enhance our chances of discovering new star forming regions and novel phenomena.
 
